### 2015-06-11 doc/abc.tex
first

\documentclass[preprint]{aastex}
\usepackage{amsmath,amssymb}
\usepackage{mathrsfs}

\bibliographystyle{plain}

\begin{document}

\title{Type Ia Supernova Model}
\author{Alex Kim}

\section{Science Interest}
The discovery of the accelerating expansion of the Universe came as a great surprise,
although such behavior was already known to be a theoretical possibility.
General Relativity (GR) long provided a basis for such an acceleration through
the Cosmological Constant $\Lambda$, which as a constant vacuum energy density has the
negative pressure that leads to gravitational repulsion.  An expectation
for vacuum energy density also comes from particle physics but naive predictions anticipate
a higher energy density than that observed: the existence of a
non-zero but small Cosmological Constant is a major challenge confronting physics theory.

There are no viable first-principles physical models, rather the acceleration caused by
``dark energy''  with an equation of state of fairly unconstrained functional form. The parameterized model used to analyze data are based on a Taylor expansion for which GR is the zeroth-order solution.

Most physicists think that the accelerating universe is due to
GR's $\Lambda$. The ``easiest'' great physics discovery that can be made with the next 
generation of surveys is to establish the inconsistency of the data relative to the
expectations of GR; only if the data can exclude GR do we have 
a hope to track down the nature of the next generation of physics.  Therefore, it seems that 
the first layer of statistical analysis should be hypothesis testing with
GR as the null hypothesis.

The technique we are familiar with is the goodness-of-fit test using $p$-values.
The likelihood does not reduce to a simple least-squares
so a $\chi^2$-distribution does not apply.  The model of the data involves latent parameters
drawn from unknown distributions, and objects not discovered due to survey inefficiency.

GR makes a prediction for the distance modulus as a function of redshift,
\begin{equation}
\mu_\Lambda(z;H_0, \Omega_M, \Omega_\Lambda),
\end{equation}
where  three free parameters are accommodated, or two when flatness is assumed i.e.\
$\Omega_M+\Omega_\Lambda=1$.  For the purposes of hypothesis testing,
$H_0$, $\Omega_M$, $\Omega_\Lambda$ are nuisance parameters.

Each object (transient) in the Universe has intrinsic properties
\begin{equation}
\{M(\lambda,t), A(\lambda,t), z, \mu\},
\end{equation}
where $M$ is the absolute magnitude, $z$ represents the cosmological redshift (peculiar velocities are ignored), and $\mu$ is the distance modulus corresponding to that redshift.

We access information about these objects
\begin{equation}
\{\hat{T}, \hat{m}(t), \hat{H}, \hat{z}, \hat{\mu}
\},
\end{equation}
where $\hat{T}$ is a boolean whether the transient is discovered and $\hat{m}$ are the measurements.
$\hat{H}$ is the weight of the object in the analysis, clearly non-discovery implies $\hat{H}=0$
and traditional Type~Ia SN classification gives a binary $\hat{H} \in \{0,1\}$ for consideration in
the cosmology analysis.  The measured redshift $\hat{z}$ can have uncertainty due to host-misidentification and further spectroscopic or photometric redshift uncertainty.  $\hat{mu}$
is a number usually derived from the use of an SN~Ia model to interpret $\hat{m}$.

The underlying function $\mu(z)$ is what we want to infer from the data.  Of particular interest
is to show that $\mu(z)$ is inconsistent with the theoretical expectation from the theoretical expectation for a Cosmological Constant universe.

\end{document}

### 2015-06-11 src/gen_pgm.py

@@ -1,0 +1,203 @@
+#!/usr/bin/env python
+
+from matplotlib import rc
+from daft import PGM, Node, Plate
+rc("font", family="serif", size=10)
+rc("text", usetex=True)
+
+
+pgm = PGM([10.5, 7.5], origin=[0., 0.2], observed_style='inner')
+
+pgm.add_node(Node("Standard", r"Stands.", 5, 1, scale=1.5))
+pgm.add_node(Node("^ni", r"$\hat{ADU}_{i}$", 6, 1, observed=True,scale=1.5))
+pgm.add_node(Node("^thetai", r"$\hat{\theta}_{S \alpha i}$", 8, 1, observed=True))
+pgm.add_node(Node("^zi", r"$\hat{z}_{Si}$", 9, 1, observed=True))
+
+pgm.add_node(Node("gal_D", r"$\hat{D}$", 1, 2, observed=True))
+pgm.add_node(Node("^gal_ni", r"$\hat{ADU}_{\alpha}$", 4, 2, observed=True,scale=1.5))
+pgm.add_node(Node("Z", r"$\hat{Z}$", 5, 2, observed=True))
+
+pgm.add_node(Node("^gal_thetai", r"$\hat{\theta}_{S \alpha}$", 2, 3, observed=True))
+pgm.add_node(Node("gal_ni", r"$ADU_{\alpha}$", 3, 3,scale=1.5))
+pgm.add_node(Node("Optics", r"Trans.", 5, 3, scale=1.5))
+pgm.add_node(Node("ni", r"$ADU_{\alpha i}$", 6, 3,scale=1.5))
+pgm.add_node(Node("D", r"$\hat{D}$", 8, 3, observed=True))
+
+pgm.add_node(Node("^gal_zi", r"$\hat{z}_{S \alpha}$", 1, 4, observed=True))
+pgm.add_node(Node("gal_fi", r"$f_{\alpha}$", 3, 4))
+pgm.add_node(Node("D_L", r"$D_L$", 5, 4))
+pgm.add_node(Node("fi", r"$f_{\alpha i}$", 6, 4))
+
+pgm.add_node(Node("gal_zi", r"$z_{\alpha}$", 4, 5))
+pgm.add_node(Node("zi", r"$z_{\alpha i}$", 6, 5))
+pgm.add_node(Node("pi", r"$p^{SN}_{\alpha i}$", 7, 5))
+
[…]

### 2015-06-18 doc/model.tex
Another look at the model

\documentclass[preprint]{aastex}
\usepackage{amsmath,amssymb}
\usepackage{mathrsfs}
\usepackage{graphicx}
\newcommand{\mli}[1]{\mathit{#1}}
%\usepackage{epstopdf}

\bibliographystyle{plain}

\begin{document}

\title{Type Ia Supernova Model}
\author{Alex Kim}

\section{Model}
Supernova cosmology analysis is based on the Hubble diagram: measurements of
redshift $z$ and distance modulus $\mu$.  The inferred Hubble diagram
can be expressed as the pdf of the true underlying
quantities given these measurements 
\begin{equation}
P(\vec{\mu},\vec{z}| \vec{\hat{\mu}}, \vec{\hat{z}}, \vec{\hat{D}}=1, \vec{\hat{T}}=\text{SN~Ia}),
\end{equation}
where $\hat{D}=1$ and $\hat{T}=\text{SN~Ia}$ indicate that the objects are discovered and typed
as SNe~Ia.  
The caret labels measurements and quantities derived
from measurements.  This Hubble diagram can then be used to infer parameters
of cosmological and dark energy models.

A model of the experiment is necessary to interpret the data, as in the
calculation of the likelihood function $P(\vec{\hat{\mu}}, \vec{\hat{z}}, \vec{\hat{D}}=1, \vec{\hat{T}}=\text{SN~Ia}|\vec{\mu},\vec{z})$.
A sketch of a such a model is shown in the Probabilistic Graphical Model
shown in Figure~\ref{pgm:fig}.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=7in]{/Users/akim/project/abc/results/hdpgm.eps} 
   \caption{Probabilistic Graphical Model for the SN~Ia analysis.
   The bottom right corner containing the connection between observed light curves
   $\hat{f}$, transient spectral information $\hat{z}_S$, $\hat{\theta}_S$, and
   host information $\hat{z}_H$, $\hat{\theta}_H$ with the determined type, redshift, and distance
   modulus $\hat{\mathit{Type}}$, $\hat{z}$, and $\hat{\mu}$ is the purview of
   the traditional light-curve and Hubble diagram fitters.
   \label{pgm:fig}}
\end{figure}

\subsection{Forward Model}
I first walk through the PGM as a forward process.  This is useful for understanding
how the model would be simulated.

There is a set of redshifts
at which a transients explode $\vec{z}$ and for each (cosmological) redshift there is a corresponding distance
modulus $\vec{\mu}$; these $z$-$\mu$ pairs are the fundamental parameters that
specify the Hubble diagram.

Given that there is a transient at redshift $z$, it has a probability of being a particular
Type associated with a Host. 
The Host is anything that projects onto the line of sight of the transient and so contributes
to measurement noise.   For our purposes, the Type and Host include information on the
sources and line-of-sight effects that can be encapsulated as an effective SED. 
This SED and distance modulus determine the photon flux incident above the Earth's
atmosphere, $n$ and $n_g$.

The experiment has an optical chain summarized by the transmission functions $T(\lambda)$, which determine the expected counts of the transient and galaxy, $\mathit{ADU}$ and
$\mathit{ADU}_g$.  
The realized observed counts determine whether the transient
is discovered $\hat{D}$, and the 
calibration $\hat{Z}$ of the transmission functions set the
measured flux-calibrated light curves $\hat{f}$.

Spectra $\hat{\mathit{Spec.}}$ may be obtained for active candidates, from which typing, redshift and spectral parameters $\hat{z}_S$, $\hat{\theta}_S$ are derived.
From the detected galaxies Gals.\ a host is associate with the transient, the measured
host redshift and parameters are $\hat{z}_{H}$, $\hat{\theta}_H$.

Given the transient light curves, spectra, and host-galaxy measurements, the transient
type $\hat{\mathit{Type}}$, redshift $\hat{z}$, and distance modulus $\hat{\mu}$ are
determined.  Depending on what information is available, this is done by some combination
of a light-curve fitter, classifier, and empirical SN~Ia modeler; in this note this black box
is referred to as a Fitter.

\subsection{Backward Model}

I now systematically
examine the model going backwards, from the observables to the fundamental parameters.
This is useful for understanding dependencies in constructing the likelihood.

\begin{description}
\item[$\hat{D}$] Transient detection.  It depends on
the observed signal $\hat{f}$ and its noise, mostly through the signal-to-noise
$\mathit{SNR}$.
\item[$\hat{z}$] Cosmological redshift.  There is an ordering of how the redshift
is determined. If there is an unambiguous host its spectroscopic redshift $\hat{z}_H$ is
selected.  Next, the transient's spectroscopic redshift $\hat{z}_S$ is preferred.
Generally these spectroscopic redshifts have negligible uncertainties for our purposes.
When the host is ambiguous, has only a photometric redshift, and/or there is
no transient redshift,
the calibrated supernova light curve $\hat{f}$ and all other information is combined to
infer redshift.
\item[$\hat{\mathit{Type}}$] Transient classification.  Traditionally only objects
typed as SN~Ia are used in the analysis: alternatively a probability of being
SN~Ia could be used.  The soundest classification comes from a transient
spectrum $\hat{\mathit{Spec}}$.  Otherwise typing is informed by host information
$\hat{z}_H$ and $\hat{\theta}_H$, and
calibrated light curves $\hat{f}$.
\item[ $\hat{\mu}$]  Distance modulus.  This is typically done with a light-curve
analysis using $\hat{f}$, $\hat{z}_S$ or
$\hat{z}_H$, and transient spectral features $\hat{\theta}_S$ and host
properties $\hat{\theta}_H$.
\end{description}

Generically the typing, redshift, and distance modulus are obtained
using a Fitter, with the details depending on the available information.
A calibration of the empirical SN~Ia absolute magnitude model is fit in this step.
Therefore $\hat{z}$, $\hat{\mathit{Type}}$
and $\hat{\mu}$ may be correlated, and correlations between transients are expected.

\begin{description}
\item[$\hat{z}_H$, $\hat{\theta}_H$] Host galaxy redshift and properties from spectroscopic
and photometric data, based on association
of the host from the pool of detected galaxies Gals.
\item[Gals] Detected galaxies from which a host is associated with a transient.
\item[$\hat{z}_S$, $\hat{\theta}_S$] Transient redshift and properties from
spectroscopic data $\hat{\mathit{Spec.}}$
\item[ $\hat{\mathit{Spec.}}$] Spectrum of the transient. I skip the details of the actual measurement  make a direct association
with the fluxes of the transient and underlying galaxy $n$, $n_g$.
\item[$\hat{f}$] Measured light curves.  Depends on the expected counts of
the transient and background $\mathit{ADU}$, $\mathit{ADU}_g$
(as a contributor to noise), and the photometric zeropoints $\hat{Z}$.
\item[$\hat{\mathit{ADU}}$, $\hat{\mathit{ADU}_g}$]  Expected counts
of the transient and background galaxy respectively.  Depends
on the incident fluxes $n$, $n_g$ and the instrumental
transmission $T(\lambda)$.
\item[$\hat{Z}$] Calibration zeropoints.  Depends on the calibration process
and the underlying transmission functions $T(\lambda)$.  This may be a zeropoint
but most probably will be calibratied transmission functions.
\item[$T(\lambda)$] DES transmission functions.
\item[$n$, $n_g$] The incident fluxes at Earth of the transient and background
galaxy.  Depends on  $z$ and $\mu$, and the SEDs of the Type and Hiost.
\item[Type/Host]  The type of transient and projected galaxies (referred to as host),
used to the specify the
underlying SED.  The realization depends on the redshift $z$.
\item[$\vec{\mu}$, $\vec{z}$]  The true distance moduli and cosmological redshifts under
consideration.  Each redshift has a unique distance modulus.
\end{description}

\section{Comments on Parts of the Model}

\subsection{Type}
The model allows for transients of all types to be detected
and potentially classified as SN~Ia. 
The full population of potential interlopers and their rates, $P(\text{Type} | z)$,
is poorly constrained.
I therefore propose that the model be constrained to SNe~Ia only,
and have the experiment measure
$P(non-Ia |  \hat{\mathit{Type}}=\text{SN~Ia})$,
$\left. \langle \hat{\mu}-\mu(z)\rangle \right|_{non-Ia}$ and its uncertainty.
This would be added as a correction to the Hubble diagram under the assumption
that all objects are SNe~Ia.

\subsection{The Fitter}
The model contains the term
\begin{align}
\begin{split}
P(\hat{\mu},\hat{z}, \hat{D}=1, \hat{\mathit{Type}}=\text{SN~Ia}|X) & =  P(\hat{D=1}|X) P(\hat{\mu},\hat{z},\hat{\mathit{Type}}=\text{SN~Ia}|X)\\
&=  P(\hat{D=1}|\hat{f}) P(\hat{\mu},\hat{z}, \hat{\mathit{Type}}=\text{SN~Ia}|X)\\
\end{split}
\label{fitter:eqn}
\end{align}
where $X=\{\hat{f}, \hat{\mathit{Spec.}}, \hat{z}_S, \hat{\theta}_S, \hat{z}_H, \hat{\theta}_H\}$
represents relevant measurements.  The first term on the right side of Eqn.~\ref{fitter:eqn}
is the detection efficiency.  The second term is what I have generically called the
Fitter.

Traditional supernova cosmology analysis is covered by the arrows that lead to
the measured type, redshift, and distance modulus.  Within this larger
context, probably the supernova absolute magnitudes should be calibrated relative
to a model that does not depend on the cosmological parameters.

Need to calibrate $P(x|y,\hat{T=\text{SN~Ia}})$.

\end{document}

### 2015-06-18 src/gen_pgm.py

@@ -9,37 +9,36 @@ rc("text", usetex=True)
 pgm = PGM([10.5, 7.5], origin=[0., 0.2], observed_style='inner')
 
 pgm.add_node(Node("Standard", r"Stands.", 5, 1, scale=1.5))
-pgm.add_node(Node("^ni", r"$\hat{ADU}_{i}$", 6, 1, observed=True,scale=1.5))
-pgm.add_node(Node("^thetai", r"$\hat{\theta}_{S \alpha i}$", 8, 1, observed=True))
+pgm.add_node(Node("^thetai", r"$\hat{\theta}_{S i}$", 8, 1, observed=True))
 pgm.add_node(Node("^zi", r"$\hat{z}_{Si}$", 9, 1, observed=True))
 
+pgm.add_node(Node("^ni", r"$\hat{ADU}_{i}$", 6, 2, observed=True,scale=1.5))
 pgm.add_node(Node("gal_D", r"$\hat{D}$", 1, 2, observed=True))
 pgm.add_node(Node("^gal_ni", r"$\hat{ADU}_{\alpha}$", 4, 2, observed=True,scale=1.5))
 pgm.add_node(Node("Z", r"$\hat{Z}$", 5, 2, observed=True))
 
+
 pgm.add_node(Node("^gal_thetai", r"$\hat{\theta}_{S \alpha}$", 2, 3, observed=True))
-pgm.add_node(Node("gal_ni", r"$ADU_{\alpha}$", 3, 3,scale=1.5))
 pgm.add_node(Node("Optics", r"Trans.", 5, 3, scale=1.5))
-pgm.add_node(Node("ni", r"$ADU_{\alpha i}$", 6, 3,scale=1.5))
-pgm.add_node(Node("D", r"$\hat{D}$", 8, 3, observed=True))
+pgm.add_node(Node("gal_ni", r"$ADU_{\alpha}$", 3, 3,scale=1.5))
+pgm.add_node(Node("ni", r"$ADU_{i}$", 6, 3,scale=1.5))
 
 pgm.add_node(Node("^gal_zi", r"$\hat{z}_{S \alpha}$", 1, 4, observed=True))
-pgm.add_node(Node("gal_fi", r"$f_{\alpha}$", 3, 4))
 pgm.add_node(Node("D_L", r"$D_L$", 5, 4))
-pgm.add_node(Node("fi", r"$f_{\alpha i}$", 6, 4))
+pgm.add_node(Node("D", r"$\hat{D}$", 8, 4, observed=True))
 
[…]

### 2015-06-18 src/hd_pgm.py

@@ -1,0 +1,126 @@
+#!/usr/bin/env python
+
+from matplotlib import rc
+from daft import PGM, Node, Plate
+rc("font", family="serif", size=10)
+rc("text", usetex=True)
+
+
+pgm = PGM([7.5, 6.5], origin=[0., 0.2], observed_style='inner')
+
+pgm.add_node(Node('HD',r"$\vec{\mu},\vec{z}$", 1,6))
+pgm.add_node(Node('TypeHost',r"Type, Host", 3, 6, scale=1.8))
+pgm.add_node(Node('Flux',r"$n(t,\lambda)$", 2, 5))
+pgm.add_node(Node('Flux_g',r"$n_g(\lambda)$", 3, 5))
+pgm.add_node(Node('Transmission',r"$T(\lambda)$", 6, 6))
+pgm.add_node(Node('Spectrum',r"$\hat{\mathit{Spec}}$.", 2, 2, observed=True))
+pgm.add_node(Node('Counts',r"$\mathit{ADU}$", 3, 4))
+pgm.add_node(Node('Counts_g',r"$\mathit{ADU}_g$", 4, 4))
+pgm.add_node(Node('Zeropoints',r"$\hat{Z}$", 6, 5, observed=True))
+pgm.add_node(Node('^Counts',r"$\hat{f}$", 3, 3, observed=True))
+pgm.add_node(Node('Spars',r"$\hat{z_S},\hat{\theta_S}$", 3, 2, observed=True))
+pgm.add_node(Node('^Host',r"$\hat{z_H},\hat{\theta_H}$", 3, 1, observed=True))
+pgm.add_node(Node('Galaxies',r"Gals.", 1, 1, observed=True))
+pgm.add_node(Node('^z',r"$\hat{z}$", 5, 2, observed=True))
+pgm.add_node(Node('^mu',r"$\hat{\mu}$", 5, 1, observed=True))
+pgm.add_node(Node('^Type',r"$\hat{\mathit{Type}}$", 5, 3, observed=True))
+pgm.add_node(Node('Detected',r"$\hat{D}$", 5, 4, observed=True))
+
+pgm.add_edge("HD","TypeHost")
+pgm.add_edge("HD","Flux")
+pgm.add_edge("HD","Flux_g")
+
+pgm.add_edge("TypeHost","Flux")
+pgm.add_edge("TypeHost","Flux_g")
+
+
+pgm.add_edge("Flux","Counts")
+pgm.add_edge("Flux_g","Counts_g")
+
[…]

### 2015-06-26 doc/model.tex
presented to DES

@@
 \usepackage{graphicx}
+\usepackage{natbib}
+\bibliographystyle{apj}
+
 \newcommand{\mli}[1]{\mathit{#1}}
 %\usepackage{epstopdf}
-
-\bibliographystyle{plain}
 
@@
 \section{Model}
-Supernova cosmology analysis is based on the Hubble diagram: measurements of
-redshift $z$ and distance modulus $\mu$.  The inferred Hubble diagram
-can be expressed as the pdf of the true underlying
-quantities given these measurements 
+We infer a Hubble diagram based on measurements of discovered transients
+classified as Type~Ia supernovae (SNe~Ia).  The inferred Hubble diagram can be
+expressed as
 \begin{equation}
-P(\vec{\mu},\vec{z}| \vec{\hat{\mu}}, \vec{\hat{z}}, \vec{\hat{D}}=1, \vec{\hat{T}}=\text{SN~Ia}),
+P(\vec{\mu},\vec{z}| \vec{\hat{D}}=1, \vec{\hat{ADU}}, \vec{\hat{T}}_S=\text{SN~Ia},\vec{\hat{z}}_S,
+\vec{\hat{\theta}}_S,\vec{\hat{z}}_H,\vec{\hat{\theta}}_H),
+\label{hd:eqn}
 \end{equation}
-where $\hat{D}=1$ and $\hat{T}=\text{SN~Ia}$ indicate that the objects are discovered and typed
-as SNe~Ia.  
-The caret labels measurements and quantities derived
-from measurements.  This Hubble diagram can then be used to infer parameters
-of cosmological and dark energy models.
+where the inferred quantities are the set of distance moduli ($\vec{\mu}$)
+and redshifts ($\vec{z}$), and 
+the measurements include: $\hat{D}$ the boolean that indicates that
+the transient was discovered; $\hat{ADU}$ the transient photometry;
+spectroscopically derived transient
+typing, redshift and parameters $\hat{T}_S$, $\hat{z}_S$, $\hat{\theta}_S$;
+and the redshift and parameters of the associated host galaxy $\hat{z}_{H}$, $\hat{\theta}_H$.
+The conditions $\vec{\hat{D}}=1$, $\vec{\hat{T}}_S,=\text{SN~Ia}$ hold as only transients
+discovered and classified as SNe~Ia are modelled.  We use the convention of using carets $\hat{}$
+to  label measurements.
 
-A model of the experiment is necessary to interpret the data, as in the
-calculation of the likelihood function $P(\vec{\hat{\mu}}, \vec{\hat{z}}, \vec{\hat{D}}=1, \vec{\hat{T}}=\text{SN~Ia}|\vec{\mu},\vec{z})$.
-A sketch of a such a model is shown in the Probabilistic Graphical Model
+A sketch of a model explaining the data is depicted through the Probabilistic Graphical Model
+(PGM)
 shown in Figure~\ref{pgm:fig}.
+Although only transients that are detected and classified as
+SN~Ia are modeled, the model accommodates the possibility that they could not have been found
+or not classified as SN~Ia.
 
@@
    host information $\hat{z}_H$, $\hat{\theta}_H$ with the determined type, redshift, and distance
-   modulus $\hat{\mathit{Type}}$, $\hat{z}$, and $\hat{\mu}$ is the purview of
+   modulus $\hat{T}$, $\hat{z}$, and $\hat{\mu}$ is the purview of
    the traditional light-curve and Hubble diagram fitters.
@@
 \end{figure}
+
+One feature to note is that $\mu$ is a model parameter; most analyses instead
+directly have cosmological parameters $\{\Omega_M, \Omega_\Lambda, w_0, w_a\}$.
+A motivation is to provide results that can be applied to test arbitrary cosmological models:
+indeed the model-dependence of the $\mu$'s reported for high-$z$ supernovae 
+\citep[e.g.][]{2012ApJ...746...85S} is a source of confusion to the community.
+An example of a non-parametric model for $\mu$ that is independent of cosmological
+parameters is given in the Appendix of
+\citet{2013ApJ...764..116W}.
 
@@
 
-There is a set of redshifts
-at which a transients explode $\vec{z}$ and for each (cosmological) redshift there is a corresponding distance
-modulus $\vec{\mu}$; these $z$-$\mu$ pairs are the fundamental parameters that
-specify the Hubble diagram.
+Discovered transients typed as SNe~Ia are modeled.  Each has
+a cosmological redshift and corresponding distance modulus; these $z$-$\mu$ pairs are the  parameters that
+constitute the Hubble diagram.  For the moment, the coordinates RA/Dec are considered
+precisely determined from the images.
 
-Given that there is a transient at redshift $z$, it has a probability of being a particular
-Type associated with a Host. 
-The Host is anything that projects onto the line of sight of the transient and so contributes
-to measurement noise.   For our purposes, the Type and Host include information on the
-sources and line-of-sight effects that can be encapsulated as an effective SED. 
-This SED and distance modulus determine the photon flux incident above the Earth's
+Each transient indexed by $i$ is of a certain type $T$ and comes from a  host galaxy of type $G$.  
+(``Host'' includes the host as well as  all galaxies that project onto the coordinate of
+the transient.)  The
+transients (galaxies) are modeled and described by global parameters $\theta_T$ ($\theta_G$),
+and  parameters specific to the transient $\theta_{Ti}$ ($\theta_{Gi}$).  For example, the SALT2 SN~Ia
+model has individual $c$ and $x_1$ parameters that would fill $\theta_{Ti}$,
+and global $\alpha$, $\beta$, and intrinsic dispersion  parameters  common to all supernovae
+ and  underlying  $c$ and $x_1$ distributions that would fill $\theta_T$.
+The Type model includes  information on the
+source and line-of-sight effects, which specify the effective SED. 
+This SED, redshift, and  distance modulus determine the photon flux incident above the Earth's
 atmosphere, $n$ and $n_g$.
 
-The experiment has an optical chain summarized by the transmission functions $T(\lambda)$, which determine the expected counts of the transient and galaxy, $\mathit{ADU}$ and
-$\mathit{ADU}_g$.  
-The realized observed counts determine whether the transient
-is discovered $\hat{D}$, and the 
-calibration $\hat{Z}$ of the transmission functions set the
-measured flux-calibrated light curves $\hat{f}$.
+The experiment has an optical chain summarized by the transmission functions $\phi(\lambda)$, which determine the expected counts of the transient and galaxy, $\mathit{ADU}$ and
+$\mathit{ADU}_g$.   These expected counts in turn determine realized  transient counts 
+$\mathit{ADU}_V$.
+The signal to noise of the realized counts specify the probability of discovery
+$\hat{D}$ .    The photometry of the subset of discovered transients
+are denoted as $\hat{\mathit{ADU}}$.
 
-Spectra $\hat{\mathit{Spec.}}$ may be obtained for active candidates, from which typing, redshift and spectral parameters $\hat{z}_S$, $\hat{\theta}_S$ are derived.
-From the detected galaxies Gals.\ a host is associate with the transient, the measured
-host redshift and parameters are $\hat{z}_{H}$, $\hat{\theta}_H$.
+For discovered transients, there may be spectra of the object itself
+from which typing, redshift and spectral parameters $\hat{T}_S$, $\hat{z}_S$, $\hat{\theta}_S$ are derived.
+From amongst the detected galaxies $\hat{\mathit{Gals.}}$  a host is associated with the transient
+based on its RA/Dec, its
+host redshift (spectroscopic or photometric) and parameters are $\hat{z}_{H}$, $\hat{\theta}_H$.
 
-Given the transient light curves, spectra, and host-galaxy measurements, the transient
-type $\hat{\mathit{Type}}$, redshift $\hat{z}$, and distance modulus $\hat{\mu}$ are
-determined.  Depending on what information is available, this is done by some combination
-of a light-curve fitter, classifier, and empirical SN~Ia modeler; in this note this black box
-is referred to as a Fitter.
+The observatory transmission $\phi$ are calibrated $\hat{Z}$.
 
@@
 
+The observables are:
 \begin{description}
+\item[$\hat{\mathit{Gals}}$] Detected galaxies from which a host is associated with a transient.
+Depends on the model for galaxies $\theta_G$.
 \item[$\hat{D}$] Transient detection.  It depends on
-the observed signal $\hat{f}$ and its noise, mostly through the signal-to-noise
+the realized signal $\hat{\mathit{ADU}_V}$ and its noise, mostly through the signal-to-noise
 $\mathit{SNR}$.
-\item[$\hat{z}$] Cosmological redshift.  There is an ordering of how the redshift
-is determined. If there is an unambiguous host its spectroscopic redshift $\hat{z}_H$ is
-selected.  Next, the transient's spectroscopic redshift $\hat{z}_S$ is preferred.
-Generally these spectroscopic redshifts have negligible uncertainties for our purposes.
-When the host is ambiguous, has only a photometric redshift, and/or there is
-no transient redshift,
-the calibrated supernova light curve $\hat{f}$ and all other information is combined to
-infer redshift.
-\item[$\hat{\mathit{Type}}$] Transient classification.  Traditionally only objects
-typed as SN~Ia are used in the analysis: alternatively a probability of being
-SN~Ia could be used.  The soundest classification comes from a transient
-spectrum $\hat{\mathit{Spec}}$.  Otherwise typing is informed by host information
-$\hat{z}_H$ and $\hat{\theta}_H$, and
-calibrated light curves $\hat{f}$.
-\item[ $\hat{\mu}$]  Distance modulus.  This is typically done with a light-curve
-analysis using $\hat{f}$, $\hat{z}_S$ or
-$\hat{z}_H$, and transient spectral features $\hat{\theta}_S$ and host
-properties $\hat{\theta}_H$.
+\item[$\hat{\mathit{ADU}}$]  Photometry of discovered transients.  Exactly the value
+of the  realized signal $\mathit{ADU}_V$ and discovery $\hat{D}$.
+\item[$\hat{z}_H$, $\hat{\theta}_H$] Host galaxy redshift and properties from spectroscopic
+and photometric data, based on association
+of the host from the pool of detected galaxies $\hat{\mathit{Gals}}$ and the transient RA/Dec.
+\item[$\hat{T}_S$, $\hat{z}_S$, $\hat{\theta}_S$] Transient redshift and properties from
+spectroscopic data. I skip the details of the actual measurement  and make a direct association
+with the fluxes of the transient and underlying galaxy $n$, $n_g$.
+\item[$\hat{Z}$] Calibration zeropoints.  Depends on the calibration process
+and the underlying transmission functions $\phi(\lambda)$.  This may be a zeropoint
+but most probably will be calibrated transmission functions.
 \end{description}
 
-Generically the typing, redshift, and distance modulus are obtained
-using a Fitter, with the details depending on the available information.
-A calibration of the empirical SN~Ia absolute magnitude model is fit in this step.
-Therefore $\hat{z}$, $\hat{\mathit{Type}}$
-and $\hat{\mu}$ may be correlated, and correlations between transients are expected.
-
+The following are elements of the model.
 \begin{description}
-\item[$\hat{z}_H$, $\hat{\theta}_H$] Host galaxy redshift and properties from spectroscopic
-and photometric data, based on association
-of the host from the pool of detected galaxies Gals.
-\item[Gals] Detected galaxies from which a host is associated with a transient.
-\item[$\hat{z}_S$, $\hat{\theta}_S$] Transient redshift and properties from
-spectroscopic data $\hat{\mathit{Spec.}}$
-\item[ $\hat{\mathit{Spec.}}$] Spectrum of the transient. I skip the details of the actual measurement  make a direct association
-with the fluxes of the transient and underlying galaxy $n$, $n_g$.
-\item[$\hat{f}$] Measured light curves.  Depends on the expected counts of
-the transient and background $\mathit{ADU}$, $\mathit{ADU}_g$
-(as a contributor to noise), and the photometric zeropoints $\hat{Z}$.
-\item[$\hat{\mathit{ADU}}$, $\hat{\mathit{ADU}_g}$]  Expected counts
+\item[$\mathit{ADU}_V$]  Realized counts
+of the transient.  Depends
+on the expected counts of the transient and host $\mathit{ADU}$, $\mathit{ADU}_g$.
+This is distinct from $\hat{\mathit{ADU}}$, which only has photometry of detected transients.
+\item[$\mathit{ADU}$, $\mathit{ADU}_{g}$]  Expected counts
 of the transient and background galaxy respectively.  Depends
 on the incident fluxes $n$, $n_g$ and the instrumental
-transmission $T(\lambda)$.
-\item[$\hat{Z}$] Calibration zeropoints.  Depends on the calibration process
-and the underlying transmission functions $T(\lambda)$.  This may be a zeropoint
-but most probably will be calibratied transmission functions.
-\item[$T(\lambda)$] DES transmission functions.
+transmission $\phi(\lambda)$.
+\item[$\phi(\lambda)$] DES transmission functions.
 \item[$n$, $n_g$] The incident fluxes at Earth of the transient and background
-galaxy.  Depends on  $z$ and $\mu$, and the SEDs of the Type and Hiost.
-\item[Type/Host]  The type of transient and projected galaxies (referred to as host),
-used to the specify the
-underlying SED.  The realization depends on the redshift $z$.
+galaxy.  Depends on  $z$ and $\mu$, and the SEDs of the Type and Host as
+specified by $\theta_{Ti}$, $\theta_{Gi}$,$\theta_{T}$, $\theta_{G}$.
+\item[$\theta_{Ti}$, $\theta_{Gi}$] Parameters that describe the properties of the individual transient
+and host respectively.
+\item[$\theta_{T}$, $\theta_{G}$] Parameters that describe the global properties of the transient
+and host models.
+\item[$T$,$G$]  The type of transient and projected galaxies (referred to as host), which
+specifies which model to use. The realization depends on the redshift $z$.
 \item[$\vec{\mu}$, $\vec{z}$]  The true distance moduli and cosmological redshifts under
 consideration.  Each redshift has a unique distance modulus.
+\item[$\mathbf{RA/Dec}$] The coordinate of the transient.  It will be the actual coordinate of the found discovered object.
 \end{description}
 
-\section{Comments on Parts of the Model}
+\section{Subsections of the Model}
 
 \subsection{Type}
-The model allows for transients of all types to be detected
-and potentially classified as SN~Ia. 
-The full population of potential interlopers and their rates, $P(\text{Type} | z)$,
-is poorly constrained.
-I therefore propose that the model be constrained to SNe~Ia only,
-and have the experiment measure
-$P(non-Ia |  \hat{\mathit{Type}}=\text{SN~Ia})$,
-$\left. \langle \hat{\mu}-\mu(z)\rangle \right|_{non-Ia}$ and its uncertainty.
-This would be added as a correction to the Hubble diagram under the assumption
-that all objects are SNe~Ia.
+\label{type:sec}
+Given that our transient sample may not consist purely of SNe~Ia, the model
+has a term of the form $P(T, G | z,\mu)$, which should account for all types of
+objects that could potentially be mistaken for Type~Ia:
+the rates and association with host galaxies are described for
+the full population of potential interlopers.
+%Note the condition $\hat{T}=\text{SN~Ia}$ means that non-Ia transients unlikely to
+%be identified as SN~Ia can be described with poorer accuracy.
+This term is not currently well known, particularly at the highest redshifts probed by DES.
+It could be constructed through modeling, although then the uncertainties 
+of that modeling must in turn be quantified.
 
-\subsection{The Fitter}
-The model contains the term
-\begin{align}
-\begin{split}
-P(\hat{\mu},\hat{z}, \hat{D}=1, \hat{\mathit{Type}}=\text{SN~Ia}|X) & =  P(\hat{D=1}|X) P(\hat{\mu},\hat{z},\hat{\mathit{Type}}=\text{SN~Ia}|X)\\
-&=  P(\hat{D=1}|\hat{f}) P(\hat{\mu},\hat{z}, \hat{\mathit{Type}}=\text{SN~Ia}|X)\\
-\end{split}
-\label{fitter:eqn}
-\end{align}
-where $X=\{\hat{f}, \hat{\mathit{Spec.}}, \hat{z}_S, \hat{\theta}_S, \hat{z}_H, \hat{\theta}_H\}$
-represents relevant measurements.  The first term on the right side of Eqn.~\ref{fitter:eqn}
-is the detection efficiency.  The second term is what I have generically called the
-Fitter.
+I posit that a concise way of addressing this term is to only model $T=\text{SN~Ia}$,
+and experimentally determine $P(\text{non-Ia})$, 
+$\left. \langle \mu-\mu_{model} \rangle \right|_{non-Ia}$, and its uncertainty for the
+sample of non-Ia's that are discovered and misclassified as SN~Ia.
+This measurement is achieved through spectroscopic
+typing of a subset drawn from the populations used in the Hubble diagram.
+Other supernova surveys
+with spectroscopic follow-up (e.g.\ SNLS) that replicate the DES population
+can be used, for example on magnitude-limited samples with
+complete  spectroscopic follow-up. 
+The weighted bias would be added as a correction to the Hubble diagram under the assumption that all objects are SNe~Ia.
 
-Traditional supernova cosmology analysis is covered by the arrows that lead to
-the measured type, redshift, and distance modulus.  Within this larger
-context, probably the supernova absolute magnitudes should be calibrated relative
-to a model that does not depend on the cosmological parameters.
+To minimize the contribution of non-Ia contamination we strive for
+an excellent classifier so that $P(non-Ia) \rightarrow 0$.
 
-Need to calibrate $P(x|y,\hat{T=\text{SN~Ia}})$.
+\subsection{Host Matching}
+\sloppy
+The host-galaxy properties depends on the galaxy catalog and the transient
+coordinates $P(\hat{z}_H, \hat{\theta}_H | \hat{\mathit{Gals.}}, \text{RA/Dec})$.  With a
+spectrum of the transient and the underlying background, identification of the host galaxy
+is usually straightforward.
+Otherwise, projections or ambiguous cases can result in the misidentification of
+the host.
+
+A similar strategy can be taken as with non-Ia contamination in \S\ref{type:sec}:
+analyze the supernova assuming a correct host match, and
+experimentally determine $P(\text{mismatch} )$ and
+$\left. \langle \hat{\mu}-\mu(z)\rangle \right|_{\text{mismatch}}$, $\left. \langle \hat{z}-z \rangle \right|_{\text{mismatch}}$ to correct bias in the Hubble diagram. 
+We strive to have $P(\text{mismatch}) \rightarrow 0$.
+
+\subsection{Type~Ia Supernova Model}
+\label{snmodel:sec}
+The model contains a piece $P(\hat{\mathit{ADU}}_{i} \hat{z}_{Si}| \mu_i,z_i,\theta_T, \theta_{Ti}, ,\phi(\lambda))$, which
+is the piece that describes underlying SN~Ia properties and light-curve fits.
+
+Need something more general?
+$P(\hat{D}_i,\hat{\mathit{ADU}}_{i}, \hat{T}_{Si}, \hat{z}_{Si}, \hat{\theta}_{Si}, \hat{z}_{Hi}, \hat{\theta}_{Hi}
+ | \mu_i,z_i,T_i,\theta_T,\theta_{Ti},\phi(\lambda))$
+\subsection{Detection Efficiency}
+There term $P(\hat{D}|\mathit{ADU}_V)$.  For all high-redshift supernova searches
+I know of, this depends on the signal-to-noise of the data, and very weakly on the
+structure of the underlying galaxy.  Our detection is now based on machine learning,
+we should confirm that detection dependencies do not depend on our model parameters
+(except for RA/Dec).
+
+\section{Systematic Tests}
+The Hubble diagrams of subsets of data quantify systematic uncertainty.  
+Subsets that may be expected to show evidence for systematics include:
+spectroscopically typed SNe~Ia; transients in deep (3) versus shallow (1/2) DES fields;
+transients with NIR data; splits based on host properties.
+
+A potentially more probative test is to compare the distance moduii inferred for the same
+supernovae, but reducing the amount of data considered.  A subset of DES
+transients have higher signal-to-noise, spectroscopic confirmation, and NIR coverage than
+the average transient, we can take away that extra information in calculating distance modulus
+to get $P(\mu | \mathit{data} - \mu | \mathit{data}^-, z | \mathit{data} - z | \mathit{data}^-)$.
+It is possible that differences in $\mu$s and $z$s have smaller uncertainties that the
+$\mu$ and $z$ alone due to common measurement uncertainties.
+
+\bibliography{/Users/akim/Documents/alex}
 

### 2015-06-26 src/gen_pgm.py

@@ -6,120 +6,52 @@ rc("font", family="serif", size=10)
 rc("text", usetex=True)
 
 
-pgm = PGM([10.5, 7.5], origin=[0., 0.2], observed_style='inner')
-
-pgm.add_node(Node("Standard", r"Stands.", 5, 1, scale=1.5))
-pgm.add_node(Node("^thetai", r"$\hat{\theta}_{S i}$", 8, 1, observed=True))
-pgm.add_node(Node("^zi", r"$\hat{z}_{Si}$", 9, 1, observed=True))
-
-pgm.add_node(Node("^ni", r"$\hat{ADU}_{i}$", 6, 2, observed=True,scale=1.5))
-pgm.add_node(Node("gal_D", r"$\hat{D}$", 1, 2, observed=True))
-pgm.add_node(Node("^gal_ni", r"$\hat{ADU}_{\alpha}$", 4, 2, observed=True,scale=1.5))
-pgm.add_node(Node("Z", r"$\hat{Z}$", 5, 2, observed=True))
+pgm = PGM([4.5, 4.5], origin=[0., 0.2], observed_style='inner')
 
 
-pgm.add_node(Node("^gal_thetai", r"$\hat{\theta}_{S \alpha}$", 2, 3, observed=True))
-pgm.add_node(Node("Optics", r"Trans.", 5, 3, scale=1.5))
-pgm.add_node(Node("gal_ni", r"$ADU_{\alpha}$", 3, 3,scale=1.5))
-pgm.add_node(Node("ni", r"$ADU_{i}$", 6, 3,scale=1.5))
 
-pgm.add_node(Node("^gal_zi", r"$\hat{z}_{S \alpha}$", 1, 4, observed=True))
-pgm.add_node(Node("D_L", r"$D_L$", 5, 4))
-pgm.add_node(Node("D", r"$\hat{D}$", 8, 4, observed=True))
+pgm.add_node(Node('Pars',r"$\theta_G$", 1, 3))
+pgm.add_node(Node('mu',r"$\mu_G$", 1, 1))
+pgm.add_node(Node('SNpars',r"$\theta^{dist}$", 1, 4))
+pgm.add_node(Node('^z',r"$\hat{z_i}$", 3,1))
 
-pgm.add_node(Node("gal_zi", r"$z_{\alpha}$", 4, 5))
-pgm.add_node(Node("zi", r"$z_{i}$", 6, 5))
[…]

### 2015-06-26 src/hd_pgm.py

@@ -8,64 +8,72 @@ rc("text", usetex=True)
 
 pgm = PGM([7.5, 6.5], origin=[0., 0.2], observed_style='inner')
 
-pgm.add_node(Node('HD',r"$\vec{\mu},\vec{z}$", 1,6))
-pgm.add_node(Node('TypeHost',r"Type, Host", 3, 6, scale=1.8))
-pgm.add_node(Node('Flux',r"$n(t,\lambda)$", 2, 5))
-pgm.add_node(Node('Flux_g',r"$n_g(\lambda)$", 3, 5))
-pgm.add_node(Node('Transmission',r"$T(\lambda)$", 6, 6))
-pgm.add_node(Node('Spectrum',r"$\hat{\mathit{Spec}}$.", 2, 2, observed=True))
-pgm.add_node(Node('Counts',r"$\mathit{ADU}$", 3, 4))
-pgm.add_node(Node('Counts_g',r"$\mathit{ADU}_g$", 4, 4))
+pgm.add_node(Node('HD',r"$\vec{\mu},\vec{z}$, $\vec{\mathit{RA/Dec}}$", 1,4,scale=2))
+pgm.add_node(Node('theta_T',r"$\theta_T$", 1,6))
+pgm.add_node(Node('theta_G',r"$\theta_G$", 1,2))
+
+pgm.add_node(Node('theta_Ti',r"$\theta_{Ti}$", 2,5))
+pgm.add_node(Node('theta_Gi',r"$\theta_{Gi}$", 2,3))
+
+
+pgm.add_node(Node('TypeHost',r"$T_i$, $G_i$", 2, 4, scale=1.5))
+pgm.add_node(Node('Flux',r"$n_i(t,\lambda)$", 2, 6, scale=1.2))
+pgm.add_node(Node('Flux_g',r"$n_{gi}(\lambda)$", 2, 2))
+pgm.add_node(Node('Transmission',r"$\phi(\lambda)$", 6, 4))
+pgm.add_node(Node('Counts',r"$\mathit{ADU}_i$", 3, 5,scale=1.2))
+pgm.add_node(Node('Counts_g',r"$\mathit{ADU}_{gi}$", 3, 1,scale=1.2))
 pgm.add_node(Node('Zeropoints',r"$\hat{Z}$", 6, 5, observed=True))
-pgm.add_node(Node('^Counts',r"$\hat{f}$", 3, 3, observed=True))
[…]

### 2015-07-02 doc/model.tex
version given locally

@@
 \begin{equation}
-P(\vec{\mu},\vec{z}| \vec{\hat{D}}=1, \vec{\hat{ADU}}, \vec{\hat{T}}_S=\text{SN~Ia},\vec{\hat{z}}_S,
+P(\vec{\mu},\vec{z} |  \vec{\hat{D}}=1, \vec{\hat{T}}=\text{SN~Ia}, \vec{\hat{ADU}}, \vec{\hat{T}}_S,\vec{\hat{z}}_S,
 \vec{\hat{\theta}}_S,\vec{\hat{z}}_H,\vec{\hat{\theta}}_H),
@@
 and the redshift and parameters of the associated host galaxy $\hat{z}_{H}$, $\hat{\theta}_H$.
-The conditions $\vec{\hat{D}}=1$, $\vec{\hat{T}}_S,=\text{SN~Ia}$ hold as only transients
-discovered and classified as SNe~Ia are modelled.  We use the convention of using carets $\hat{}$
+A classifier takes these data and infers types $\vec{\hat{T}}$.
+The conditions $\vec{\hat{D}}=1$, $\vec{\hat{T}}=\text{SN~Ia}$ hold as only transients
+discovered and classified as SNe~Ia are modeled.  We use the convention of using carets $\hat{}$
 to  label measurements.
 
-A sketch of a model explaining the data is depicted through the Probabilistic Graphical Model
-(PGM)
-shown in Figure~\ref{pgm:fig}.
-Although only transients that are detected and classified as
-SN~Ia are modeled, the model accommodates the possibility that they could not have been found
-or not classified as SN~Ia.
+An alternative would have been to
+model measurements of all discovered transients, not just those typed as SN~Ia. 
+The non-Ia transient population has significant model uncertainty and the information they impart on the expansion history is weak:  I anticipate it is cleaner to limit ourselves to
+modeling discoveries we think are SN~Ia.  This restriction does not obviate the need
+to consider non-Ia contamination in the sample.
 
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=7in]{/Users/akim/project/abc/results/hdpgm.eps} 
-   \caption{Probabilistic Graphical Model for the SN~Ia analysis.
-   The bottom right corner containing the connection between observed light curves
-   $\hat{f}$, transient spectral information $\hat{z}_S$, $\hat{\theta}_S$, and
-   host information $\hat{z}_H$, $\hat{\theta}_H$ with the determined type, redshift, and distance
-   modulus $\hat{T}$, $\hat{z}$, and $\hat{\mu}$ is the purview of
-   the traditional light-curve and Hubble diagram fitters.
-   \label{pgm:fig}}
-\end{figure}
-
-One feature to note is that $\mu$ is a model parameter; most analyses instead
+Here $\mu$ is modeled; most analyses instead
 directly have cosmological parameters $\{\Omega_M, \Omega_\Lambda, w_0, w_a\}$.
@@
 
+DES plans a ``photometry''-only analysis, in that a significant subset of transients used
+in the Hubble diagram will not observed spectroscopically while active.  Therefore,
+our model must account for transient mistyping and host-galaxy mismatches.  To obtain
+our targeted
+accuracy we need to account for covariances that occur due to photometric
+calibration and Malmquist bias.  Our model will contain elements that may not
+have been included in previous analyses.
+
+A sketch of a model explaining the data is depicted through the Probabilistic Graphical Model
+(PGM)
+shown in Figure~\ref{pgm:fig}.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=7in]{/Users/akim/project/abc/results/hdpgm.eps} 
+   \caption{Probabilistic Graphical Model for the SN~Ia analysis.  The forward modeling
+   flow goes from left to right.  Starting from the position and distance
+   $\mu$, $z$, $\text{RA/Dec}$ the transient and host types $T$, $G$ are realized. 
+   The transient- and
+   galaxy-model parameters $\theta_T$, $\theta_{Ti}$, $\theta_G$, $\theta_{Gi}$ along
+   with redshift and distance modulus determine the incoming photon flux $n$, $n_g$.
+   The instrumental transmission function $\phi$ gives the expected and realized
+   counts $\mathit{ADU}$, $\mathit{ADU}_g$, $\mathit{ADU}_V$.  The calibration measurements
+   are $Z$.  The measured galaxy catalog is $\hat{\mathit{Gals.}}$  Only detected
+   supernovae $\hat{D}$ have subsequent light curve ($\hat{ADU}$), spectral
+   $\hat{X}_S$, and associated host galaxy $\hat{X}_H$ measurements.  A supernova
+   classifier takes measurements and infers a type $\hat{T}$, which is used for sample selection.
+   \label{pgm:fig}}
+\end{figure}
+
 \subsection{Forward Model}
@@
 constitute the Hubble diagram.  For the moment, the coordinates RA/Dec are considered
-precisely determined from the images.
+precisely determined from imaging data.
 
@@
 and  parameters specific to the transient $\theta_{Ti}$ ($\theta_{Gi}$).  For example, the SALT2 SN~Ia
-model has individual $c$ and $x_1$ parameters that would fill $\theta_{Ti}$,
+model has individual $c$ and $x_1$ parameters that would constitute $\theta_{Ti}$,
 and global $\alpha$, $\beta$, and intrinsic dispersion  parameters  common to all supernovae
- and  underlying  $c$ and $x_1$ distributions that would fill $\theta_T$.
+ and  underlying  $c$ and $x_1$ distributions that would constitute $\theta_T$.
 The Type model includes  information on the
@@
 From amongst the detected galaxies $\hat{\mathit{Gals.}}$  a host is associated with the transient
-based on its RA/Dec, its
-host redshift (spectroscopic or photometric) and parameters are $\hat{z}_{H}$, $\hat{\theta}_H$.
+based on its RA/Dec; the host information is summarized as the
+host redshift (spectroscopic or photometric) and parameters $\hat{z}_{H}$, $\hat{\theta}_H$.
 
@@
 \begin{description}
-\item[$\hat{\mathit{Gals}}$] Detected galaxies from which a host is associated with a transient.
+\item[$\hat{\mathit{Gals}}$] Detected galaxies from which a transient's host is identified.
 Depends on the model for galaxies $\theta_G$.
@@
 $\mathit{SNR}$.
-\item[$\hat{\mathit{ADU}}$]  Photometry of discovered transients.  Exactly the value
-of the  realized signal $\mathit{ADU}_V$ and discovery $\hat{D}$.
+\item[$\hat{\mathit{ADU}}$]  Photometry of discovered transients.  Its inclusion
+depends on discovery $\hat{D}$ and has the value of the realized signal $\mathit{ADU}_V$.
 \item[$\hat{z}_H$, $\hat{\theta}_H$] Host galaxy redshift and properties from spectroscopic
@@
 \item[$\hat{Z}$] Calibration zeropoints.  Depends on the calibration process
-and the underlying transmission functions $\phi(\lambda)$.  This may be a zeropoint
-but most probably will be calibrated transmission functions.
+and the underlying transmission functions $\phi(\lambda)$.  Specifies
+the transmission functions.
 \end{description}
 
-The following are elements of the model.
+The following are elements that are to be modeled, including ``nuisance'' parameters.
 \begin{description}
@@
 on the expected counts of the transient and host $\mathit{ADU}$, $\mathit{ADU}_g$.
-This is distinct from $\hat{\mathit{ADU}}$, which only has photometry of detected transients.
+Although all transients will have realized counts but not all will be measured, hence the distinction
+from $\hat{\mathit{ADU}}$.
 \item[$\mathit{ADU}$, $\mathit{ADU}_{g}$]  Expected counts
@@
 galaxy.  Depends on  $z$ and $\mu$, and the SEDs of the Type and Host as
-specified by $\theta_{Ti}$, $\theta_{Gi}$,$\theta_{T}$, $\theta_{G}$.
+specified by $\theta_{Ti}$, $\theta_{Gi}$, $\theta_{T}$, $\theta_{G}$.
 \item[$\theta_{Ti}$, $\theta_{Gi}$] Parameters that describe the properties of the individual transient
@@
 and host models.
-\item[$T$,$G$]  The type of transient and projected galaxies (referred to as host), which
+\item[$T$, $G$]  The type of transient and projected galaxies (referred to as host), which
 specifies which model to use. The realization depends on the redshift $z$.
@@
 consideration.  Each redshift has a unique distance modulus.
-\item[$\mathbf{RA/Dec}$] The coordinate of the transient.  It will be the actual coordinate of the found discovered object.
+\item[$\mathbf{RA/Dec}$] The coordinate of the transient.  For us, it is sufficient to directly
+assign the coordinate measured
+from the images.
 \end{description}
@@
 \label{type:sec}
-Given that our transient sample may not consist purely of SNe~Ia, the model
+Since our transient sample may not consist purely of SNe~Ia, the model
 has a term of the form $P(T, G | z,\mu)$, which should account for all types of
@@
 the full population of potential interlopers.
-%Note the condition $\hat{T}=\text{SN~Ia}$ means that non-Ia transients unlikely to
-%be identified as SN~Ia can be described with poorer accuracy.
 This term is not currently well known, particularly at the highest redshifts probed by DES.
-It could be constructed through modeling, although then the uncertainties 
-of that modeling must in turn be quantified.
 
-I posit that a concise way of addressing this term is to only model $T=\text{SN~Ia}$,
-and experimentally determine $P(\text{non-Ia})$, 
-$\left. \langle \mu-\mu_{model} \rangle \right|_{non-Ia}$, and its uncertainty for the
-sample of non-Ia's that are discovered and misclassified as SN~Ia.
-This measurement is achieved through spectroscopic
-typing of a subset drawn from the populations used in the Hubble diagram.
-Other supernova surveys
-with spectroscopic follow-up (e.g.\ SNLS) that replicate the DES population
-can be used, for example on magnitude-limited samples with
-complete  spectroscopic follow-up. 
-The weighted bias would be added as a correction to the Hubble diagram under the assumption that all objects are SNe~Ia.
+An idea is to consider two types: SN~Ia and non-SN~Ia, where the latter's
+intrinsic distributions have loose priors.  Transients that have been spectroscopically
+classified as non-Ia will provide the strongest leverage in constraining the
+contamination: this subset must be unbiased or properly weighted
+relative to the underlying population that constitutes the Hubble diagram.
+Running the model on a pure sample of SNe~Ia can have benefits.
+As discussed in \S\ref{systematics:sec}, comparing these results with
+those from the full sample provides
+a test of systematics.  Alternatively, the non-Ia model may be better constrained
+with the pure sample.
 
 To minimize the contribution of non-Ia contamination we strive for
-an excellent classifier so that $P(non-Ia) \rightarrow 0$.
+a pure sample selection so that $P(T=\text{non-Ia}| \mu) \rightarrow 0$.
 
@@
 \sloppy
-The host-galaxy properties depends on the galaxy catalog and the transient
+The host-galaxy properties depend on the galaxy catalog and the transient
 coordinates $P(\hat{z}_H, \hat{\theta}_H | \hat{\mathit{Gals.}}, \text{RA/Dec})$.  With a
@@
 the host.
+Other supernova surveys (e.g.\ SNLS) 
+with spectroscopically confirmed host associations (e.g.\ with
+matched transient and galaxy redshifts) that replicate the DES population
+can be used to put a prior on this probability.
 
-A similar strategy can be taken as with non-Ia contamination in \S\ref{type:sec}:
-analyze the supernova assuming a correct host match, and
-experimentally determine $P(\text{mismatch} )$ and
-$\left. \langle \hat{\mu}-\mu(z)\rangle \right|_{\text{mismatch}}$, $\left. \langle \hat{z}-z \rangle \right|_{\text{mismatch}}$ to correct bias in the Hubble diagram. 
-We strive to have $P(\text{mismatch}) \rightarrow 0$.
+%An effective way of addressing this term is to
+%analyze the supernovae assuming a correct host match, and
+%experimentally determine $P(\text{mismatch} )$ and
+%$\left. \langle \hat{\mu}-\mu(z)\rangle \right|_{\text{mismatch}}$, $\left. \langle \hat{z}-z \rangle \right|_{\text{mismatch}}$ and cross-terms to correct bias in the Hubble diagram.
+
+% only model $T=\text{SN~Ia}$,
+%and experimentally determine $P(\text{non-Ia})$, 
+%$\left. \langle \mu-\mu_{model} \rangle \right|_{non-Ia}$, and its uncertainty for the
+%sample of non-Ia's that are discovered and misclassified as SN~Ia.
+%This measurement is achieved through spectroscopic
+%typing of a subset drawn from the populations used in the Hubble diagram.
+%The weighted bias would be added as a correction to the Hubble diagram under the assumption that all objects are SNe~Ia.
 
@@
 \label{snmodel:sec}
+The DES light curve analysis in principle may be used for typing and determining
+redshift, in addition to getting supernova properties.   
+Generally the relevant term is
+\begin{equation}
+P(\hat{D}_i=1,\hat{\mathit{ADU}}_{i}, \hat{T}_{Si}, \hat{z}_{Si}, \hat{\theta}_{Si}, \hat{z}_{Hi}, \hat{\theta}_{Hi}
+ | \mu_i,z_i,T_i,\theta_T,\theta_{Ti},\phi(\lambda)).
+ \end{equation}
+Detection and typing depend on the realized light curves, and hence the truncated
+distribution of discovered transients typed as SN~Ia.
+
 The model contains a piece $P(\hat{\mathit{ADU}}_{i} \hat{z}_{Si}| \mu_i,z_i,\theta_T, \theta_{Ti}, ,\phi(\lambda))$, which
@@
 
-Need something more general?
-$P(\hat{D}_i,\hat{\mathit{ADU}}_{i}, \hat{T}_{Si}, \hat{z}_{Si}, \hat{\theta}_{Si}, \hat{z}_{Hi}, \hat{\theta}_{Hi}
- | \mu_i,z_i,T_i,\theta_T,\theta_{Ti},\phi(\lambda))$
 \subsection{Detection Efficiency}
@@
 \section{Systematic Tests}
+\label{systematics:sec}
 The Hubble diagrams of subsets of data quantify systematic uncertainty.  

### 2015-07-02 src/hd_pgm.py

@@ -6,31 +6,38 @@ rc("font", family="serif", size=10)
 rc("text", usetex=True)
 
 
-pgm = PGM([7.5, 6.5], origin=[0., 0.2], observed_style='inner')
+pgm = PGM([9.5, 8.5], origin=[0., 0.2], observed_style='inner')
 
-pgm.add_node(Node('HD',r"$\vec{\mu},\vec{z}$, $\vec{\mathit{RA/Dec}}$", 1,4,scale=2))
-pgm.add_node(Node('theta_T',r"$\theta_T$", 1,6))
-pgm.add_node(Node('theta_G',r"$\theta_G$", 1,2))
+pgm.add_node(Node('HD',r"$\vec{\mu},\vec{z}$, $\vec{\mathit{RA/Dec}}$", 1,3,scale=2,aspect=1.2))
+pgm.add_node(Node('theta_T',r"$\theta_T$", 2,8))
+pgm.add_node(Node('theta_G',r"$\theta_G$", 2,1))
 
-pgm.add_node(Node('theta_Ti',r"$\theta_{Ti}$", 2,5))
-pgm.add_node(Node('theta_Gi',r"$\theta_{Gi}$", 2,3))
+pgm.add_node(Node('theta_Ti',r"$\theta_{Ti}$", 3,6))
+pgm.add_node(Node('theta_Gi',r"$\theta_{Gi}$", 3,4))
 
 
 pgm.add_node(Node('TypeHost',r"$T_i$, $G_i$", 2, 4, scale=1.5))
-pgm.add_node(Node('Flux',r"$n_i(t,\lambda)$", 2, 6, scale=1.2))
-pgm.add_node(Node('Flux_g',r"$n_{gi}(\lambda)$", 2, 2))
-pgm.add_node(Node('Transmission',r"$\phi(\lambda)$", 6, 4))
-pgm.add_node(Node('Counts',r"$\mathit{ADU}_i$", 3, 5,scale=1.2))
-pgm.add_node(Node('Counts_g',r"$\mathit{ADU}_{gi}$", 3, 1,scale=1.2))
-pgm.add_node(Node('Zeropoints',r"$\hat{Z}$", 6, 5, observed=True))
-pgm.add_node(Node('Counts_V',r"$\mathit{ADU}_{Vi}$", 3, 4, scale=1.2))
[…]

### 2015-07-09 doc/model.tex
got first comments from Kyle

@@
 modeling discoveries we think are SN~Ia. This restriction does not obviate the need
-to consider non-Ia contamination in the sample.
+to consider non-Ia contamination in the sample, rather
+we only need to model non-Ia's
+that are mistaken for Ia and not all discovered transients.
 
@@
 \citep[e.g.][]{2012ApJ...746...85S} is a source of confusion to the community.
-An example of a non-parametric model for $\mu$ that is independent of cosmological
-parameters is given in the Appendix of
-\citet{2013ApJ...764..116W}.
+%An example of a non-parametric model for $\mu$ that is independent of cosmological
+%parameters is given in the Appendix of
+%\citet{2013ApJ...764..116W}.
 
@@
    flow goes from left to right.  Starting from the position and distance
-   $\mu$, $z$, $\text{RA/Dec}$ the transient and host types $T$, $G$ are realized. 
-   The transient- and
-   galaxy-model parameters $\theta_T$, $\theta_{Ti}$, $\theta_G$, $\theta_{Gi}$ along
+   $\mu$, $z$, $\text{RA/Dec}$ and galaxies $G$, the transient type $T$ and host-galaxy
+   $\theta_{gi}$ are realized. 
+   The transient
+    parameters $\theta_T$, $\theta_{Ti}$ along
    with redshift and distance modulus determine the incoming photon flux $n$, $n_g$.
@@
 \subsection{Forward Model}
-I first walk through the PGM as a forward process.  This is useful for understanding
-how the model would be simulated.
+Let us start with the model description of the universe and its contents, specifically transients
+that are discovered as typed as SN~Ia.
+\begin{itemize}
+\item $G$ is the set of all galaxies that can host a transient.  It is
+the union of the observed galaxy catalog plus potential galaxies that have not
+met the detection threshold, presumably due to low surface brightness.
+\item $\text{RA}=\hat{\text{RA}}$, $\text{Dec} =\hat{\text{Dec}}$.  The observed
+coordinates are taken to be the true coordinates of the transient.
+\item $P(g_i | G, \text{RA/Dec})$. 
+The association of a host galaxy labeled by $g_i$ with the transient.
+This pdf is
+the deliverable we want from Ravi.
+\item $P(z_i, \theta_{gi} | g_i)$. 
+The redshift and galactic parameters associated with SN results.
+For observed galaxies the parameter distributions 
+are based on measurements e.g.\ $\theta_{gi} \sim \mathcal{N}(\hat{\theta}_{gi},\sigma^2_{\hat{\theta}_{gi}})$, otherwise the distribution
+of $\theta_{gi}$ for ``hostless'' galaxies can be fit as part of the model.
+\item $\mu_i=\mu(z_i; \theta_\mu)$.  The distance modulus is a function of redshift,
+we don't impose a specific form for  $\mu$ at the moment,  it could
+be a $\Lambda$CDM prediction with cosmological parameters, a spline with knot values
+as parameters, or as extreme as independent values for each $z$.
+The redshift of the galaxy is assumed to be that of the transient.
+\item $P(T_i | \theta_{gi})$.  The transient type, SN~Ia or non-Ia, depends
+on the host properties.  We could make the relative rates be dependent
+on specific star formation rate and morphology.
+\item $P(\theta_T^{Ia}, \theta_{Ti}^{Ia})$.  The model parameters for SNe~Ia, including
+parameters that describe distributions.
+Different SN~Ia models could be considered: the treatment of SALT2 parameters
+has been presented in \citet{2011MNRAS.418.2308M}.
+The SALT2 SN~Ia
+model has individual $c$ and $x_1$ parameters that would constitute $\theta_{Ti}^{Ia}$,
+and global $\alpha$, $\beta$, and intrinsic dispersion  parameters  common to all supernovae
+ and  underlying  $c$ and $x_1$ distributions that would constitute $\theta_T^{Ia}$.
+\item $P(\theta_T^{non-Ia}, \theta_{Ti}^{non-Ia})$.  Non-Ia transients
+that can be mistyped as Ia are described by a parameterized model.
+\item $L_i(t,\lambda; T_i, \theta_T^{Ia}, \theta_{Ti}^{Ia}, \theta_T^{non-Ia}, \theta_{Ti}^{non-Ia},
+\theta_{gi})$.  The source model specifies
+the luminosity. The  model includes  information on the
+source and line-of-sight effects, which specify the effective SED.   Only the
+parameters of the model of the appropriate type $T$ are relevant.  The galaxy parameters
+$\theta_{gi}$ are included if correlations with host-galaxy properties are to be modeled.
+\item $n_i(t,\lambda; L_i, \mu_i, z_i)$.  The  flux incident at Earth
+is specified by the luminosity, distance modulus, and redshift.
+\end{itemize}
 
-Discovered transients typed as SNe~Ia are modeled.  Each has
-a cosmological redshift and corresponding distance modulus; these $z$-$\mu$ pairs are the  parameters that
-constitute the Hubble diagram.  For the moment, the coordinates RA/Dec are considered
-precisely determined from imaging data.
+The universe is observed with an experiment.
+\begin{itemize}
+\item The transmission functions $\phi(\lambda)$ describe the optical path from the
+atmosphere to counts, and is calibrated with measurements $\hat{Z}$.  We expect
+that calibration group to provide us with this function and its uncertainties. 
+\item $\mathit{ADU}$ and
+$\mathit{ADU}_g$ are the expected counts of the transient and galaxy respectively,
+coming from the combination of source flux $n$ and transmission $\phi$.
+\item $\mathit{ADU}_V$ is the realized flux.
+\item The transient is discovered $\hat{D}$ depending on the realized $\mathit{ADU}_V$.
+This should depend mostly on signal-to-noise.
+\item $\hat{\mathit{ADU}}$ and
+$\hat{\mathit{ADU}}_g$ are measured light curves.
+\item $\hat{T}_S$, $\hat{z}_S$, $\hat{\theta}_S$ Transient redshift and properties from
+spectroscopic data. I skip the details of the actual measurement  and make a direct association
+with the fluxes of the transient and underlying galaxy $n$, $n_g$.
 
-Each transient indexed by $i$ is of a certain type $T$ and comes from a  host galaxy of type $G$.  
-(``Host'' includes the host as well as  all galaxies that project onto the coordinate of
-the transient.)  The
-transients (galaxies) are modeled and described by global parameters $\theta_T$ ($\theta_G$),
-and  parameters specific to the transient $\theta_{Ti}$ ($\theta_{Gi}$).  For example, the SALT2 SN~Ia
-model has individual $c$ and $x_1$ parameters that would constitute $\theta_{Ti}$,
-and global $\alpha$, $\beta$, and intrinsic dispersion  parameters  common to all supernovae
- and  underlying  $c$ and $x_1$ distributions that would constitute $\theta_T$.
-The Type model includes  information on the
-source and line-of-sight effects, which specify the effective SED. 
-This SED, redshift, and  distance modulus determine the photon flux incident above the Earth's
-atmosphere, $n$ and $n_g$.
-
-The experiment has an optical chain summarized by the transmission functions $\phi(\lambda)$, which determine the expected counts of the transient and galaxy, $\mathit{ADU}$ and
-$\mathit{ADU}_g$.   These expected counts in turn determine realized  transient counts 
-$\mathit{ADU}_V$.
+\end{itemize}
+has, which determine the expected counts of the transient and galaxy,    These expected counts in turn determine realized  transient counts 
 The signal to noise of the realized counts specify the probability of discovery

### 2015-07-09 src/hd_pgm.py

@@ -6,57 +6,85 @@ rc("font", family="serif", size=10)
 rc("text", usetex=True)
 
 
-pgm = PGM([9.5, 8.5], origin=[0., 0.2], observed_style='inner')
+pgm = PGM([10.5, 7.5], origin=[0., 0.2], observed_style='inner')
 
-pgm.add_node(Node('HD',r"$\vec{\mu},\vec{z}$, $\vec{\mathit{RA/Dec}}$", 1,3,scale=2,aspect=1.2))
-pgm.add_node(Node('theta_T',r"$\theta_T$", 2,8))
-pgm.add_node(Node('theta_G',r"$\theta_G$", 2,1))
+pgm.add_node(Node('G',r"$G$", 3,1))
+pgm.add_node(Node('Coords',r"$\mathit{RA/Dec}_i$", 2,2,scale=1.5,aspect=1.2,fixed=True))
+pgm.add_node(Node('G_i',r"$g_i$", 3,2))
 
-pgm.add_node(Node('theta_Ti',r"$\theta_{Ti}$", 3,6))
-pgm.add_node(Node('theta_Gi',r"$\theta_{Gi}$", 3,4))
+pgm.add_node(Node('mu',r"$\theta_\mu$", 1,4))
+pgm.add_node(Node('HD',r"$\mu_i$", 4,4))
+pgm.add_node(Node('theta_T',r"$\theta_T^{Ia}$, $\theta_T^{non-Ia}$", 3,7,scale=1.5,aspect=1.5))
+pgm.add_node(Node('theta_Ti',r"$\theta_{Ti}^{Ia}$, $\theta_{Ti}^{non-Ia}$", 2,6,scale=1.5,aspect=1.5))
 
 
-pgm.add_node(Node('TypeHost',r"$T_i$, $G_i$", 2, 4, scale=1.5))
-pgm.add_node(Node('Flux',r"$n_i(t,\lambda)$", 3, 7, scale=1.2))
-pgm.add_node(Node('Flux_g',r"$n_{gi}(\lambda)$", 3, 3))
-pgm.add_node(Node('Transmission',r"$\phi(\lambda)$", 4, 8))
-pgm.add_node(Node('Counts',r"$\mathit{ADU}_i$", 5, 6,scale=1.2))
-pgm.add_node(Node('Counts_g',r"$\mathit{ADU}_{gi}$", 5, 3,scale=1.2))
-pgm.add_node(Node('Zeropoints',r"$\hat{Z}$", 6, 8, observed=True))
[…]

### 2015-07-14 doc/model.tex
changes based on more Kyle discussion.

--- 2015-06-26 doc/model.tex
@@
 We infer a Hubble diagram based on measurements of discovered transients
-classified as Type~Ia supernovae (SNe~Ia).  The inferred Hubble diagram can be
-expressed as
+classified as Type~Ia supernovae (SNe~Ia).  The probability distribution
+function (pdf) of the Hubble diagram is denoted as
 \begin{equation}
-P(\vec{\mu},\vec{z}| \vec{\hat{D}}=1, \vec{\hat{ADU}}, \vec{\hat{T}}_S=\text{SN~Ia},\vec{\hat{z}}_S,
-\vec{\hat{\theta}}_S,\vec{\hat{z}}_H,\vec{\hat{\theta}}_H),
+P(\vec{\mu},\vec{z} |  \vec{\hat{ADU}}, \vec{\hat{T}}_S,\vec{\hat{z}}_S,
+\vec{\hat{\theta}}_S,\hat{\text{Gals.}}, \vec{\hat{D}}=1, \vec{\hat{T}}=\text{SN~Ia},
+\vec{\hat{\text{RA}}}, \vec{\hat{\text{Dec}}}),
 \label{hd:eqn}
@@
 and redshifts ($\vec{z}$), and 
-the measurements include: $\hat{D}$ the boolean that indicates that
-the transient was discovered; $\hat{ADU}$ the transient photometry;
+the measurements include:  the transient photometry $\hat{ADU}$;
 spectroscopically derived transient
 typing, redshift and parameters $\hat{T}_S$, $\hat{z}_S$, $\hat{\theta}_S$;
-and the redshift and parameters of the associated host galaxy $\hat{z}_{H}$, $\hat{\theta}_H$.
-The conditions $\vec{\hat{D}}=1$, $\vec{\hat{T}}_S,=\text{SN~Ia}$ hold as only transients
-discovered and classified as SNe~Ia are modelled.  We use the convention of using carets $\hat{}$
+and the galaxy catalog $\hat{\text{Gals.}}$
+The conditions $\vec{\hat{D}}=1$, $\vec{\hat{T}}=\text{SN~Ia}$ indicate a sample selection
+of transients
+discovered and classified as SNe~Ia. The observed coordinates of the transients
+are $\vec{\hat{\text{RA}}}$, $\vec{\hat{\text{Dec}}}$.
+We use the convention of using carets $\hat{}$
 to  label measurements.
 
-A sketch of a model explaining the data is depicted through the Probabilistic Graphical Model
+The pdf in Equation~\ref{hd:eqn} is proportional to
+\begin{equation}
+P(\vec{\mu},\vec{z},  \vec{\hat{D}}=1, \vec{\hat{T}}=\text{SN~Ia},
+\vec{\hat{\text{RA}}}, \vec{\hat{\text{Dec}}} |  \vec{\hat{ADU}}, \vec{\hat{T}}_S,\vec{\hat{z}}_S,
+\vec{\hat{\theta}}_S,\hat{\text{Gals.}})
+\label{hd2:eqn}
+\end{equation}
+and we model this scenario.  A sketch of such a model is depicted in the Probabilistic Graphical Model
 (PGM)
 shown in Figure~\ref{pgm:fig}.
-Although only transients that are detected and classified as
-SN~Ia are modeled, the model accommodates the possibility that they could not have been found
-or not classified as SN~Ia.
 
@@
    \caption{Probabilistic Graphical Model for the SN~Ia analysis.  
-   The bottom right corner containing the connection between observed light curves
-   $\hat{f}$, transient spectral information $\hat{z}_S$, $\hat{\theta}_S$, and
-   host information $\hat{z}_H$, $\hat{\theta}_H$ with the determined type, redshift, and distance
-   modulus $\hat{T}$, $\hat{z}$, and $\hat{\mu}$ is the purview of
-   the traditional light-curve and Hubble diagram fitters.
+   The forward modeling
+   flow goes from left to right, starting with the description of the universe, observatory,
+   and data.
+   A galaxy catalog $\hat{\mathit{Gal.}}$ informs the model for potential hosts $G$.  A transient
+   at coordinates  $\text{RA/Dec}$  has a host $g_i$ drawn from $G$.
+   The galaxy redshift redshift $z$ and parameters $\theta_{gi}$ are fixed based on the host.
+   A distance modulus model with parameters $\theta_\mu$ fix the distance modulus $\mu_i$.
+   The transient type $T$ depends on the host-galaxy.   The transient
+   parameters $\theta_T^X$, $\theta_{Ti}^X$ (and perhaps the host galaxy) fix the luminosity $L$.       The 
+   incoming photon flux $n$, $n_g$  are then fixed
+   with redshift and distance modulus.
+   The instrumental transmission function $\phi$ gives the expected
+   counts $\mathit{ADU}$, $\mathit{ADU}_g$.  The calibration measurements
+   are $\hat{Z}$.  The measured galaxy catalog is $\hat{\mathit{Gals.}}$  Only detected
+   supernovae $\hat{D}$ have subsequent light curve ($\hat{ADU}$), spectral
+   $\hat{X}_S$, and associated host galaxy $\hat{X}_H$ measurements.  A supernova
+   classifier takes measurements and infers a type $\hat{T}$, which is used for sample selection.
+       Nodes labeled by
+   \textasciicircum are fixed, the others are probilistic.
    \label{pgm:fig}}
@@
 
-One feature to note is that $\mu$ is a model parameter; most analyses instead
-directly have cosmological parameters $\{\Omega_M, \Omega_\Lambda, w_0, w_a\}$.
-A motivation is to provide results that can be applied to test arbitrary cosmological models:
-indeed the model-dependence of the $\mu$'s reported for high-$z$ supernovae 
-\citep[e.g.][]{2012ApJ...746...85S} is a source of confusion to the community.
-An example of a non-parametric model for $\mu$ that is independent of cosmological
-parameters is given in the Appendix of
-\citet{2013ApJ...764..116W}.
+The supernova survey provides the transients that are to be analyzed providing
+the following information:
+\begin{itemize}
+\item $\hat{\text{RA}}$, $\hat{\text{Dec}}$.  The observed
+coordinates.  For our purposes the observed, rather than true, coordinates are sufficient.
+\item $\hat{D}=1$.  The transient is discovered.
+\item $\hat{T}=\text{SN~Ia}$. The transient is classified as SN~Ia.
+\item $\hat{\text{Gals}}$ is a galaxy catalog used to make host-galaxy associations.
+\end{itemize}
+In the PGM, these parameters are labeled as fixed ($\bullet$) data (\textasciicircum).
 
-\subsection{Forward Model}
-I first walk through the PGM as a forward process.  This is useful for understanding
-how the model would be simulated.
+The model describes the universe and its contents, specifically transients
+that are discovered as typed as SN~Ia and their host galaxies.
+\begin{itemize}
+\item $G$ is a shorthand for the model of all galaxies that can host a transient.  It is
+the union of the objects in the observed galaxy catalog $\hat{\text{Gals}}$
+plus unobserved galaxies that have not
+met the detection threshold, presumably due to their low surface brightness.
+\item $P(g_i | G, \hat{\text{RA}}/\hat{\text{Dec}})$. The host galaxy $g_i$
+is drawn from the galaxy catalog based on coordinates.
+This pdf is
+the deliverable we want from Ravi.
+\item $z_i$, $\theta_{gi}$ are the galaxy redshift and parameters.
+For observed galaxies the parameter values are based on measurements e.g.\ $\theta_{gi} \sim \mathcal{N}(\hat{\theta}_{gi},\sigma^2_{\hat{\theta}_{gi}})$, otherwise the distribution
+of $\theta_{gi}$ for ``hostless'' galaxies is described by the model.
+Redshifts may be photometric or spectroscopic.
+\item $\theta_\mu$ are the parameters that specify that distance modulus.
+\item $\mu_i=\mu(z_i; \theta_\mu)$.  The distance modulus is a function of redshift,
+we don't impose a specific form for  $\mu$ at the moment,  it could
+be a $\Lambda$CDM prediction with cosmological parameters, a spline with knot values
+as parameters, or as extreme as independent values for each $z$.
+The redshift of the galaxy is used in the Hubble diagram.
+\item $P(T_i | \theta_{gi})$.  The transient type $T_i$, SN~Ia or non-Ia, depends
+on the host properties.  We could make the relative rates be dependent
+on specific star formation rate and morphology.
+\item $P(\theta_T^{Ia}, \theta_{Ti}^{Ia})$.  The model parameters for SNe~Ia, including
+parameters that describe distributions.
+Different SN~Ia models could be considered: the treatment of SALT2 parameters
+has been presented in \citet{2011MNRAS.418.2308M}.
+The SALT2 SN~Ia
+model has individual $c$ and $x_1$ parameters that would constitute $\theta_{Ti}^{Ia}$,
+and global $\alpha$, $\beta$, and intrinsic dispersion  parameters  common to all supernovae
+ and  underlying  $c$ and $x_1$ distributions that would constitute $\theta_T^{Ia}$.
+\item $P(\theta_T^{non-Ia}, \theta_{Ti}^{non-Ia})$.  Non-Ia transients
+that can be mistyped as Ia are described by a parameterized model.
+\item $L_i(t,\lambda; T_i, \theta_T^{Ia}, \theta_{Ti}^{Ia}, \theta_T^{non-Ia}, \theta_{Ti}^{non-Ia},
+\theta_{gi})$.  The source model fixes
+the luminosity. The  model includes  information on the
+source and line-of-sight effects, which specify the effective SED.   Only the
+parameters of the model of the appropriate type $T$ are relevant.  The galaxy parameters
+$\theta_{gi}$ are included if correlations with host-galaxy properties are to be modeled.
+\item $n_i(t,\lambda; L_i, \mu_i, z_i)$.  The  flux incident at Earth
+is fixed by the luminosity, distance modulus, and redshift.
+\end{itemize}
 
-Discovered transients typed as SNe~Ia are modeled.  Each has
-a cosmological redshift and corresponding distance modulus; these $z$-$\mu$ pairs are the  parameters that
-constitute the Hubble diagram.  For the moment, the coordinates RA/Dec are considered
-precisely determined from the images.
+The model expectation of measured  signals is governed by:
+\begin{itemize}
+\item The transmission functions $\phi(\lambda)$ describe the optical path from the
+atmosphere to counts.  We expect
+the calibration group to provide us with the functions and covariance
+$\phi \sim \mathcal{N}(\bar{\phi},C_\phi)$. Self-calibration, taking advantage of the
+fact that SNe~Ia are excellent standard stars, 
+may be included in this model.
+\item $\mathit{ADU}$ and
+$\mathit{ADU}_g$ are the expected counts of the transient and galaxy respectively,
+coming from $\int n_i \phi d\lambda$.
+\end{itemize}
 
-Each transient indexed by $i$ is of a certain type $T$ and comes from a  host galaxy of type $G$.  
-(``Host'' includes the host as well as  all galaxies that project onto the coordinate of
-the transient.)  The
-transients (galaxies) are modeled and described by global parameters $\theta_T$ ($\theta_G$),
-and  parameters specific to the transient $\theta_{Ti}$ ($\theta_{Gi}$).  For example, the SALT2 SN~Ia
-model has individual $c$ and $x_1$ parameters that would fill $\theta_{Ti}$,
-and global $\alpha$, $\beta$, and intrinsic dispersion  parameters  common to all supernovae
- and  underlying  $c$ and $x_1$ distributions that would fill $\theta_T$.
-The Type model includes  information on the
-source and line-of-sight effects, which specify the effective SED. 
-This SED, redshift, and  distance modulus determine the photon flux incident above the Earth's
-atmosphere, $n$ and $n_g$.
-
-The experiment has an optical chain summarized by the transmission functions $\phi(\lambda)$, which determine the expected counts of the transient and galaxy, $\mathit{ADU}$ and
-$\mathit{ADU}_g$.   These expected counts in turn determine realized  transient counts 
-$\mathit{ADU}_V$.
-The signal to noise of the realized counts specify the probability of discovery
-$\hat{D}$ .    The photometry of the subset of discovered transients
-are denoted as $\hat{\mathit{ADU}}$.
-
-For discovered transients, there may be spectra of the object itself
-from which typing, redshift and spectral parameters $\hat{T}_S$, $\hat{z}_S$, $\hat{\theta}_S$ are derived.
-From amongst the detected galaxies $\hat{\mathit{Gals.}}$  a host is associated with the transient
-based on its RA/Dec, its
-host redshift (spectroscopic or photometric) and parameters are $\hat{z}_{H}$, $\hat{\theta}_H$.
-
-The observatory transmission $\phi$ are calibrated $\hat{Z}$.
-
-\subsection{Backward Model}
-
-I now systematically
-examine the model going backwards, from the observables to the fundamental parameters.
-This is useful for understanding dependencies in constructing the likelihood.
-
-The observables are:
-\begin{description}
-\item[$\hat{\mathit{Gals}}$] Detected galaxies from which a host is associated with a transient.
-Depends on the model for galaxies $\theta_G$.
-\item[$\hat{D}$] Transient detection.  It depends on
-the realized signal $\hat{\mathit{ADU}_V}$ and its noise, mostly through the signal-to-noise
-$\mathit{SNR}$.
-\item[$\hat{\mathit{ADU}}$]  Photometry of discovered transients.  Exactly the value
-of the  realized signal $\mathit{ADU}_V$ and discovery $\hat{D}$.
-\item[$\hat{z}_H$, $\hat{\theta}_H$] Host galaxy redshift and properties from spectroscopic
-and photometric data, based on association
-of the host from the pool of detected galaxies $\hat{\mathit{Gals}}$ and the transient RA/Dec.
-\item[$\hat{T}_S$, $\hat{z}_S$, $\hat{\theta}_S$] Transient redshift and properties from
+The observations, denoted with \textasciicircum, are now discussed.
+\begin{itemize}
+\item $\hat{\mathit{ADU}}$ is the realized flux.  $\hat{\mathit{ADU}} \sim \mathcal{N}(ADU,C_{ADU})$
+where $C_{ADU}$ is the photometric noise.
+\item $\hat{T}_S$, $\hat{z}_S$, $\hat{\theta}_S$ Transient redshift and properties from
 spectroscopic data. I skip the details of the actual measurement  and make a direct association
 with the fluxes of the transient and underlying galaxy $n$, $n_g$.
-\item[$\hat{Z}$] Calibration zeropoints.  Depends on the calibration process
-and the underlying transmission functions $\phi(\lambda)$.  This may be a zeropoint
-but most probably will be calibrated transmission functions.
-\end{description}
+\item $\hat{Z}$ represents the calibration measurements.  Although we expect to receive
+the transmission functions from the Calibration Task Force, we may be want to include
+calibration as part of our analysis.
+\end{itemize}
 
-The following are elements of the model.
-\begin{description}
-\item[$\mathit{ADU}_V$]  Realized counts
-of the transient.  Depends
-on the expected counts of the transient and host $\mathit{ADU}$, $\mathit{ADU}_g$.
-This is distinct from $\hat{\mathit{ADU}}$, which only has photometry of detected transients.
-\item[$\mathit{ADU}$, $\mathit{ADU}_{g}$]  Expected counts
-of the transient and background galaxy respectively.  Depends
-on the incident fluxes $n$, $n_g$ and the instrumental
-transmission $\phi(\lambda)$.
-\item[$\phi(\lambda)$] DES transmission functions.
-\item[$n$, $n_g$] The incident fluxes at Earth of the transient and background
-galaxy.  Depends on  $z$ and $\mu$, and the SEDs of the Type and Host as
-specified by $\theta_{Ti}$, $\theta_{Gi}$,$\theta_{T}$, $\theta_{G}$.
-\item[$\theta_{Ti}$, $\theta_{Gi}$] Parameters that describe the properties of the individual transient
-and host respectively.
-\item[$\theta_{T}$, $\theta_{G}$] Parameters that describe the global properties of the transient
-and host models.
-\item[$T$,$G$]  The type of transient and projected galaxies (referred to as host), which
-specifies which model to use. The realization depends on the redshift $z$.
-\item[$\vec{\mu}$, $\vec{z}$]  The true distance moduli and cosmological redshifts under
-consideration.  Each redshift has a unique distance modulus.
-\item[$\mathbf{RA/Dec}$] The coordinate of the transient.  It will be the actual coordinate of the found discovered object.
-\end{description}
-
-\section{Subsections of the Model}
-
-\subsection{Type}
-\label{type:sec}
-Given that our transient sample may not consist purely of SNe~Ia, the model
-has a term of the form $P(T, G | z,\mu)$, which should account for all types of
-objects that could potentially be mistaken for Type~Ia:
-the rates and association with host galaxies are described for
-the full population of potential interlopers.
-%Note the condition $\hat{T}=\text{SN~Ia}$ means that non-Ia transients unlikely to
-%be identified as SN~Ia can be described with poorer accuracy.
-This term is not currently well known, particularly at the highest redshifts probed by DES.
-It could be constructed through modeling, although then the uncertainties 
-of that modeling must in turn be quantified.
-
-I posit that a concise way of addressing this term is to only model $T=\text{SN~Ia}$,
-and experimentally determine $P(\text{non-Ia})$, 
-$\left. \langle \mu-\mu_{model} \rangle \right|_{non-Ia}$, and its uncertainty for the
-sample of non-Ia's that are discovered and misclassified as SN~Ia.
-This measurement is achieved through spectroscopic
-typing of a subset drawn from the populations used in the Hubble diagram.
-Other supernova surveys
-with spectroscopic follow-up (e.g.\ SNLS) that replicate the DES population
-can be used, for example on magnitude-limited samples with
-complete  spectroscopic follow-up. 
-The weighted bias would be added as a correction to the Hubble diagram under the assumption that all objects are SNe~Ia.
-
-To minimize the contribution of non-Ia contamination we strive for
-an excellent classifier so that $P(non-Ia) \rightarrow 0$.
-
-\subsection{Host Matching}
-\sloppy
-The host-galaxy properties depends on the galaxy catalog and the transient
-coordinates $P(\hat{z}_H, \hat{\theta}_H | \hat{\mathit{Gals.}}, \text{RA/Dec})$.  With a
-spectrum of the transient and the underlying background, identification of the host galaxy
-is usually straightforward.
-Otherwise, projections or ambiguous cases can result in the misidentification of
-the host.
-
-A similar strategy can be taken as with non-Ia contamination in \S\ref{type:sec}:
-analyze the supernova assuming a correct host match, and
-experimentally determine $P(\text{mismatch} )$ and
-$\left. \langle \hat{\mu}-\mu(z)\rangle \right|_{\text{mismatch}}$, $\left. \langle \hat{z}-z \rangle \right|_{\text{mismatch}}$ to correct bias in the Hubble diagram. 
-We strive to have $P(\text{mismatch}) \rightarrow 0$.
-
-\subsection{Type~Ia Supernova Model}
-\label{snmodel:sec}
-The model contains a piece $P(\hat{\mathit{ADU}}_{i} \hat{z}_{Si}| \mu_i,z_i,\theta_T, \theta_{Ti}, ,\phi(\lambda))$, which
-is the piece that describes underlying SN~Ia properties and light-curve fits.
-
-Need something more general?
-$P(\hat{D}_i,\hat{\mathit{ADU}}_{i}, \hat{T}_{Si}, \hat{z}_{Si}, \hat{\theta}_{Si}, \hat{z}_{Hi}, \hat{\theta}_{Hi}
- | \mu_i,z_i,T_i,\theta_T,\theta_{Ti},\phi(\lambda))$
-\subsection{Detection Efficiency}
-There term $P(\hat{D}|\mathit{ADU}_V)$.  For all high-redshift supernova searches
-I know of, this depends on the signal-to-noise of the data, and very weakly on the
-structure of the underlying galaxy.  Our detection is now based on machine learning,
-we should confirm that detection dependencies do not depend on our model parameters
-(except for RA/Dec).
-
-\section{Systematic Tests}
-The Hubble diagrams of subsets of data quantify systematic uncertainty.  
-Subsets that may be expected to show evidence for systematics include:
-spectroscopically typed SNe~Ia; transients in deep (3) versus shallow (1/2) DES fields;
-transients with NIR data; splits based on host properties.
-
-A potentially more probative test is to compare the distance moduii inferred for the same
-supernovae, but reducing the amount of data considered.  A subset of DES
-transients have higher signal-to-noise, spectroscopic confirmation, and NIR coverage than
-the average transient, we can take away that extra information in calculating distance modulus
-to get $P(\mu | \mathit{data} - \mu | \mathit{data}^-, z | \mathit{data} - z | \mathit{data}^-)$.
-It is possible that differences in $\mu$s and $z$s have smaller uncertainties that the
-$\mu$ and $z$ alone due to common measurement uncertainties.
-
+%
+%\section{Subsections of the Model}
+%
+%\subsection{Type}
+%\label{type:sec}
+%Since our transient sample may not consist purely of SNe~Ia, the model
+%has a term of the form $P(T, G | z,\mu)$, which should account for all types of
+%objects that could potentially be mistaken for Type~Ia:
+%the rates and association with host galaxies are described for
+%the full population of potential interlopers.
+%This term is not currently well known, particularly at the highest redshifts probed by DES.
+%
+%An idea is to consider two types: SN~Ia and non-SN~Ia, where the latter's
+%intrinsic distributions have loose priors.  Transients that have been spectroscopically
+%classified as non-Ia will provide the strongest leverage in constraining the
+%contamination: this subset must be unbiased or properly weighted
+%relative to the underlying population that constitutes the Hubble diagram.
+%Running the model on a pure sample of SNe~Ia can have benefits.
+%As discussed in \S\ref{systematics:sec}, comparing these results with
+%those from the full sample provides
+%a test of systematics.  Alternatively, the non-Ia model may be better constrained
+%with the pure sample.
+%
+%
+%To minimize the contribution of non-Ia contamination we strive for
+%a pure sample selection so that $P(T=\text{non-Ia}| \mu) \rightarrow 0$.
+%
+%
+%\subsection{Host Matching}
+%\sloppy
+%The host-galaxy properties depend on the galaxy catalog and the transient
+%coordinates $P(\hat{z}_H, \hat{\theta}_H | \hat{\mathit{Gals.}}, \text{RA/Dec})$.  With a
+%spectrum of the transient and the underlying background, identification of the host galaxy
+%is usually straightforward.
+%Otherwise, projections or ambiguous cases can result in the misidentification of
+%the host.
+%Other supernova surveys (e.g.\ SNLS) 
+%with spectroscopically confirmed host associations (e.g.\ with
+%matched transient and galaxy redshifts) that replicate the DES population
+%can be used to put a prior on this probability.
+%
+%%An effective way of addressing this term is to
+%%analyze the supernovae assuming a correct host match, and
+%%experimentally determine $P(\text{mismatch} )$ and
+%%$\left. \langle \hat{\mu}-\mu(z)\rangle \right|_{\text{mismatch}}$, $\left. \langle \hat{z}-z \rangle \right|_{\text{mismatch}}$ and cross-terms to correct bias in the Hubble diagram. 
+%
+%
+%% only model $T=\text{SN~Ia}$,
+%%and experimentally determine $P(\text{non-Ia})$, 
+%%$\left. \langle \mu-\mu_{model} \rangle \right|_{non-Ia}$, and its uncertainty for the
+%%sample of non-Ia's that are discovered and misclassified as SN~Ia.
+%%This measurement is achieved through spectroscopic
+%%typing of a subset drawn from the populations used in the Hubble diagram.
+%%The weighted bias would be added as a correction to the Hubble diagram under the assumption that all objects are SNe~Ia.
+%
+%
+%
+%\subsection{Type~Ia Supernova Model}
+%\label{snmodel:sec}
+%The DES light curve analysis in principle may be used for typing and determining
+%redshift, in addition to getting supernova properties.   
+%Generally the relevant term is
+%\begin{equation}
+%P(\hat{D}_i=1,\hat{\mathit{ADU}}_{i}, \hat{T}_{Si}, \hat{z}_{Si}, \hat{\theta}_{Si}, \hat{z}_{Hi}, \hat{\theta}_{Hi}
+% | \mu_i,z_i,T_i,\theta_T,\theta_{Ti},\phi(\lambda)).
+% \end{equation}
+%Detection and typing depend on the realized light curves, and hence the truncated
+%distribution of discovered transients typed as SN~Ia.
+%
+%The model contains a piece $P(\hat{\mathit{ADU}}_{i} \hat{z}_{Si}| \mu_i,z_i,\theta_T, \theta_{Ti}, ,\phi(\lambda))$, which
+%is the piece that describes underlying SN~Ia properties and light-curve fits.
+%
+%
+%\subsection{Detection Efficiency}
+%There term $P(\hat{D}|\mathit{ADU}_V)$.  For all high-redshift supernova searches
+%I know of, this depends on the signal-to-noise of the data, and very weakly on the
+%structure of the underlying galaxy.  Our detection is now based on machine learning,
+%we should confirm that detection dependencies do not depend on our model parameters
+%(except for RA/Dec).
+%
+%\section{Systematic Tests}
+%\label{systematics:sec}
+%The Hubble diagrams of subsets of data quantify systematic uncertainty.  
+%Subsets that may be expected to show evidence for systematics include:
+%spectroscopically typed SNe~Ia; transients in deep (3) versus shallow (1/2) DES fields;
+%transients with NIR data; splits based on host properties.
+%
+%A potentially more probative test is to compare the distance moduii inferred for the same
+%supernovae, but reducing the amount of data considered.  A subset of DES
+%transients have higher signal-to-noise, spectroscopic confirmation, and NIR coverage than
+%the average transient, we can take away that extra information in calculating distance modulus
+%to get $P(\mu | \mathit{data} - \mu | \mathit{data}^-, z | \mathit{data} - z | \mathit{data}^-)$.
+%It is possible that differences in $\mu$s and $z$s have smaller uncertainties that the
+%$\mu$ and $z$ alone due to common measurement uncertainties. 
+%
+%\section{Misc.}
+%DES plans a ``photometry''-only analysis, in that a significant subset of transients used
+%in the Hubble diagram will not observed spectroscopically while active.  Therefore,
+%our model must account for transient mistyping and host-galaxy mismatches.  To obtain
+%our targeted
+%accuracy we need to account for covariances that occur due to photometric
+%calibration and Malmquist bias.  Our model will contain elements that may not
+%have been included in previous analyses. 
+%
+%
+%Generically $\vec{\hat{T}}$ can describe sample selection.  I choose to focus
+%on objects typed as SN~Ia, rather than  all discovered transients, not just those typed as SN~Ia. 
+%The non-Ia transient population has significant model uncertainty and the information they impart on the expansion history is weak:  I anticipate it is cleaner to limit ourselves to
+%modeling discoveries we think are SN~Ia. This restriction does not obviate the need
+%to consider non-Ia contamination in the sample, rather
+%we only need to model non-Ia's
+%that are mistaken for Ia and not all discovered transients. 
+%
+%
+%
+%Here $\mu$ is modeled; most analyses instead
+%directly have cosmological parameters $\{\Omega_M, \Omega_\Lambda, w_0, w_a\}$.
+%A motivation is to provide results that can be applied to test arbitrary cosmological models:
+%indeed the model-dependence of the $\mu$'s reported for high-$z$ supernovae 
+%\citep[e.g.][]{2012ApJ...746...85S} is a source of confusion to the community.
+%%An example of a non-parametric model for $\mu$ that is independent of cosmological
+%%parameters is given in the Appendix of
+%%\citet{2013ApJ...764..116W}.
+%
 \bibliography{/Users/akim/Documents/alex}

### 2015-07-14 src/hd_pgm.py

@@ -6,14 +6,14 @@ rc("font", family="serif", size=10)
 rc("text", usetex=True)
 
 
-pgm = PGM([10.5, 7.5], origin=[0., 0.2], observed_style='inner')
+pgm = PGM([9.5, 7.5], origin=[0., 0.2], observed_style='inner')
 
 pgm.add_node(Node('G',r"$G$", 3,1))
-pgm.add_node(Node('Coords',r"$\mathit{RA/Dec}_i$", 2,2,scale=1.5,aspect=1.2,fixed=True))
+pgm.add_node(Node('Coords',r"$\hat{RA}_i$/$\hat{Dec}_i$", 2,2,scale=1.5,aspect=1.2,fixed=True))
 pgm.add_node(Node('G_i',r"$g_i$", 3,2))
 
 pgm.add_node(Node('mu',r"$\theta_\mu$", 1,4))
-pgm.add_node(Node('HD',r"$\mu_i$", 4,4))
+pgm.add_node(Node('HD',r"$\mu_i$", 4,4,fixed=True))
 pgm.add_node(Node('theta_T',r"$\theta_T^{Ia}$, $\theta_T^{non-Ia}$", 3,7,scale=1.5,aspect=1.5))
 pgm.add_node(Node('theta_Ti',r"$\theta_{Ti}^{Ia}$, $\theta_{Ti}^{non-Ia}$", 2,6,scale=1.5,aspect=1.5))
 
@@ -30,29 +30,25 @@ pgm.add_node(Node('z',r"$z_i$", 3, 3))
 
 
 pgm.add_node(Node('Type',r"$T_i$", 2, 5))
-pgm.add_node(Node('Luminosity',r"$L_i(t,\lambda)$", 4, 6, scale=1.2))
-pgm.add_node(Node('Flux',r"$n_i(t,\lambda)$", 4, 5, scale=1.2))
-pgm.add_node(Node('Flux_g',r"$n_{gi}(\lambda)$", 4, 2))
+pgm.add_node(Node('Luminosity',r"$L_i(t,\lambda)$", 4, 6, scale=1.2,fixed=True))
+pgm.add_node(Node('Flux',r"$n_i(t,\lambda)$", 4, 5, scale=1.2,fixed=True))
+pgm.add_node(Node('Flux_g',r"$n_{gi}(\lambda)$", 4, 2,fixed=True))
 pgm.add_node(Node('Transmission',r"$\phi(\lambda)$", 5, 7))
[…]

### 2015-07-20 doc/model.tex
Incorporate Danny's comments

@@
 \usepackage{natbib}
+\usepackage{bm}
 \bibliographystyle{apj}
@@
 
-\title{Type Ia Supernova Model}
+\title{Model for DES Type Ia Supernova Cosmology Analysis}
 \author{Alex Kim}
@@
 \begin{equation}
-P(\vec{\mu},\vec{z} |  \vec{\hat{ADU}}, \vec{\hat{T}}_S,\vec{\hat{z}}_S,
-\vec{\hat{\theta}}_S,\hat{\text{Gals.}}, \vec{\hat{D}}=1, \vec{\hat{T}}=\text{SN~Ia},
-\vec{\hat{\text{RA}}}, \vec{\hat{\text{Dec}}}),
+p({\mu},{z} |  {{ADU}}, {{T}}_S,{{z}}_S,
+{{\theta}}_S,\text{GC}, \text{Detected}, {\text{Selected}},
+{\text{RA}}, {\text{Dec}}).
 \label{hd:eqn}
 \end{equation}
-where the inferred quantities are the set of distance moduli ($\vec{\mu}$)
-and redshifts ($\vec{z}$), and 
-the measurements include:  the transient photometry $\hat{ADU}$;
-spectroscopically derived transient
-typing, redshift and parameters $\hat{T}_S$, $\hat{z}_S$, $\hat{\theta}_S$;
-and the galaxy catalog $\hat{\text{Gals.}}$
-The conditions $\vec{\hat{D}}=1$, $\vec{\hat{T}}=\text{SN~Ia}$ indicate a sample selection
-of transients
-discovered and classified as SNe~Ia. The observed coordinates of the transients
-are $\vec{\hat{\text{RA}}}$, $\vec{\hat{\text{Dec}}}$.
-We use the convention of using carets $\hat{}$
-to  label measurements.
+The set of distance moduli
+and redshifts $(\mu, z)$ is the Hubble diagram.  The available information
+from which the Hubble diagram is inferred include:
+the transient photometry ${ADU}$; spectral measurements of
+transient
+type, redshift and SN-parameters ${T}_S$, ${z}_S$, ${\theta}_S$;
+the galaxy catalog ${\text{GC}}$; transient coordinates  $\text{RA}$, $\text{Dec}$;
+and the fact that the transients were Detected and Selected for the analysis.
 
@@
 \begin{equation}
-P(\vec{\mu},\vec{z},  \vec{\hat{D}}=1, \vec{\hat{T}}=\text{SN~Ia},
-\vec{\hat{\text{RA}}}, \vec{\hat{\text{Dec}}} |  \vec{\hat{ADU}}, \vec{\hat{T}}_S,\vec{\hat{z}}_S,
-\vec{\hat{\theta}}_S,\hat{\text{Gals.}})
+p({\mu},{z},   \text{Detected}, {\text{Selected}},
+\text{RA}, \text{Dec} |  {{ADU}}, {{T}}_S,{{z}}_S,
+{{\theta}}_S, \text{GC})
 \label{hd2:eqn}
@@
    and data.
-   A galaxy catalog $\hat{\mathit{Gal.}}$ informs the model for potential hosts $G$.  A transient
+   A GC ${\mathit{Gal.}}$ informs the model for potential hosts $G$.  A transient
    at coordinates  $\text{RA/Dec}$  has a host $g_i$ drawn from $G$.
-   The galaxy redshift redshift $z$ and parameters $\theta_{gi}$ are fixed based on the host.
+   The galaxy redshift redshift $z$ and parameters $\theta_{gi}$ depend on the host.
    A distance modulus model with parameters $\theta_\mu$ fix the distance modulus $\mu_i$.
@@
    with redshift and distance modulus.
-   The instrumental transmission function $\phi$ gives the expected
-   counts $\mathit{ADU}$, $\mathit{ADU}_g$.  The calibration measurements
-   are $\hat{Z}$.  The measured galaxy catalog is $\hat{\mathit{Gals.}}$  Only detected
-   supernovae $\hat{D}$ have subsequent light curve ($\hat{ADU}$), spectral
-   $\hat{X}_S$, and associated host galaxy $\hat{X}_H$ measurements.  A supernova
-   classifier takes measurements and infers a type $\hat{T}$, which is used for sample selection.
-       Nodes labeled by
-   \textasciicircum are fixed, the others are probilistic.
+   The instrumental transmission function $\phi$ is calibrated with data ${Z}$ and
+   gives the expected
+   counts $\overline{\mathit{ADU}}$, $\overline{\mathit{ADU}}_g$.  The galaxy catalog is GC. 
+   The realized light curve (${ADU}$) depends on the expected counts and also
+   must have been Detected and Selected.  Some transients have spectral data
+   ${X}_S$.
    \label{pgm:fig}}
@@
 \begin{itemize}
-\item $\hat{\text{RA}}$, $\hat{\text{Dec}}$.  The observed
+\item ${\text{RA}}$, ${\text{Dec}}$.  The observed
 coordinates.  For our purposes the observed, rather than true, coordinates are sufficient.
-\item $\hat{D}=1$.  The transient is discovered.
-\item $\hat{T}=\text{SN~Ia}$. The transient is classified as SN~Ia.
-\item $\hat{\text{Gals}}$ is a galaxy catalog used to make host-galaxy associations.
+\item Detected.  The transient is discovered.
+\item Selected. The transient is selected for the cosmology analysis.  This presumably
+includes its classification as SN~Ia.
+\item GC.  The galaxy catalog used to make host-galaxy associations.
 \end{itemize}
-In the PGM, these parameters are labeled as fixed ($\bullet$) data (\textasciicircum).
 
@@
 \item $G$ is a shorthand for the model of all galaxies that can host a transient.  It is
-the union of the objects in the observed galaxy catalog $\hat{\text{Gals}}$
+the union of the objects in the galaxy catalog GC
 plus unobserved galaxies that have not
 met the detection threshold, presumably due to their low surface brightness.
-\item $P(g_i | G, \hat{\text{RA}}/\hat{\text{Dec}})$. The host galaxy $g_i$
-is drawn from the galaxy catalog based on coordinates.
+\item $P(g_i | G, {\text{RA}}/{\text{Dec}})$. The host galaxy $g_i$
+is drawn from the GC based on coordinates.
 This pdf is
 the deliverable we want from Ravi.
-\item $z_i$, $\theta_{gi}$ are the galaxy redshift and parameters.
-For observed galaxies the parameter values are based on measurements e.g.\ $\theta_{gi} \sim \mathcal{N}(\hat{\theta}_{gi},\sigma^2_{\hat{\theta}_{gi}})$, otherwise the distribution
+\item $z_i$, $\theta_{gi}$ are the galaxy redshift and parameters (e.g.\ mass, sSFR, metallicity).
+For observed galaxies the parameter values are based on measurements e.g.\ $\theta_{gi} \sim \mathcal{N}({\theta}_{gi},\sigma^2_{{\theta}_{gi}})$, otherwise the distribution
 of $\theta_{gi}$ for ``hostless'' galaxies is described by the model.
@@
 on specific star formation rate and morphology.
-\item $P(\theta_T^{Ia}, \theta_{Ti}^{Ia})$.  The model parameters for SNe~Ia, including
+\item $p(\theta_T^{Ia}, \theta_{Ti}^{Ia})$.  The model parameters for SNe~Ia, including
 parameters that describe distributions.
@@
  and  underlying  $c$ and $x_1$ distributions that would constitute $\theta_T^{Ia}$.
-\item $P(\theta_T^{non-Ia}, \theta_{Ti}^{non-Ia})$.  Non-Ia transients
+\item $p(\theta_T^{non-Ia}, \theta_{Ti}^{non-Ia})$.  Non-Ia transients
 that can be mistyped as Ia are described by a parameterized model.
@@
 $\theta_{gi}$ are included if correlations with host-galaxy properties are to be modeled.
-\item $n_i(t,\lambda; L_i, \mu_i, z_i)$.  The  flux incident at Earth
+\item $n_i(t,\lambda; L_i, \mu_i, z_i)$, $n_{gi}(t,\lambda; L_i, \mu_i, z_i)$.  The  flux incident at Earth
 is fixed by the luminosity, distance modulus, and redshift.
@@
 may be included in this model.
-\item $\mathit{ADU}$ and
-$\mathit{ADU}_g$ are the expected counts of the transient and galaxy respectively,
+\item $\overline{\mathit{ADU}}$ and
+$\overline{\mathit{ADU}}_g$ are the expected counts of the transient and galaxy respectively,
 coming from $\int n_i \phi d\lambda$.
@@
 \begin{itemize}
-\item $\hat{\mathit{ADU}}$ is the realized flux.  $\hat{\mathit{ADU}} \sim \mathcal{N}(ADU,C_{ADU})$
-where $C_{ADU}$ is the photometric noise.
-\item $\hat{T}_S$, $\hat{z}_S$, $\hat{\theta}_S$ Transient redshift and properties from
+\item ${\mathit{ADU}}$ is the realized flux can be expressed as
+\begin{equation}
+P({\mathit{ADU}} | \text{Dectected}, \text{Selected}, \overline{\mathit{ADU}}, 
+\overline{\mathit{ADU}}_g)=\frac{P({\mathit{ADU}},\text{Dectected}, \text{Selected} |  
+\overline{\mathit{ADU}},  \overline{\mathit{ADU}}_g)}{P(\text{Dectected}, \text{Selected} | 
+\overline{\mathit{ADU}},  \overline{{\mathit{ADU}}}_g)},
+\end{equation}
+which can be determined from detection and typing efficiency studies.
+\item ${T}_S$, ${z}_S$, ${\theta}_S$ Transient type, redshift and properties from
 spectroscopic data. I skip the details of the actual measurement  and make a direct association
 with the fluxes of the transient and underlying galaxy $n$, $n_g$.
-\item $\hat{Z}$ represents the calibration measurements.  Although we expect to receive
+A very simple association is ${T}_S = T$, ${z}_S=z$, ${\theta}_S \in \theta_g$,
+or a blurry version instead of a straight equality.
+\item ${Z}$ represents the calibration measurements.  Although we expect to receive
 the transmission functions from the Calibration Task Force, we may be want to include
@@
 %\sloppy
-%The host-galaxy properties depend on the galaxy catalog and the transient
-%coordinates $P(\hat{z}_H, \hat{\theta}_H | \hat{\mathit{Gals.}}, \text{RA/Dec})$.  With a
+%The host-galaxy properties depend on the GC and the transient
+%coordinates $P({z}_H, {\theta}_H | {\mathit{Gals.}}, \text{RA/Dec})$.  With a
 %spectrum of the transient and the underlying background, identification of the host galaxy
@@
 %%experimentally determine $P(\text{mismatch} )$ and
-%%$\left. \langle \hat{\mu}-\mu(z)\rangle \right|_{\text{mismatch}}$, $\left. \langle \hat{z}-z \rangle \right|_{\text{mismatch}}$ and cross-terms to correct bias in the Hubble diagram. 
+%%$\left. \langle {\mu}-\mu(z)\rangle \right|_{\text{mismatch}}$, $\left. \langle {z}-z \rangle \right|_{\text{mismatch}}$ and cross-terms to correct bias in the Hubble diagram. 
 %
@@
 %\begin{equation}
-%P(\hat{D}_i=1,\hat{\mathit{ADU}}_{i}, \hat{T}_{Si}, \hat{z}_{Si}, \hat{\theta}_{Si}, \hat{z}_{Hi}, \hat{\theta}_{Hi}
+%P({D}_i=1,{\mathit{ADU}}_{i}, {T}_{Si}, {z}_{Si}, {\theta}_{Si}, {z}_{Hi}, {\theta}_{Hi}
 % | \mu_i,z_i,T_i,\theta_T,\theta_{Ti},\phi(\lambda)).
@@
 %
-%The model contains a piece $P(\hat{\mathit{ADU}}_{i} \hat{z}_{Si}| \mu_i,z_i,\theta_T, \theta_{Ti}, ,\phi(\lambda))$, which
+%The model contains a piece $P({\mathit{ADU}}_{i} {z}_{Si}| \mu_i,z_i,\theta_T, \theta_{Ti}, ,\phi(\lambda))$, which
 %is the piece that describes underlying SN~Ia properties and light-curve fits.
@@
 %\subsection{Detection Efficiency}
-%There term $P(\hat{D}|\mathit{ADU}_V)$.  For all high-redshift supernova searches
+%There term $P({D}|\mathit{ADU}_V)$.  For all high-redshift supernova searches
 %I know of, this depends on the signal-to-noise of the data, and very weakly on the
@@
 %
-%Generically $\vec{\hat{T}}$ can describe sample selection.  I choose to focus
+%Generically ${{T}}$ can describe sample selection.  I choose to focus
 %on objects typed as SN~Ia, rather than  all discovered transients, not just those typed as SN~Ia. 

### 2015-07-20 src/hd_pgm.py

@@ -6,15 +6,15 @@ rc("font", family="serif", size=10)
 rc("text", usetex=True)
 
 
-pgm = PGM([9.5, 7.5], origin=[0., 0.2], observed_style='inner')
+pgm = PGM([10.5, 7.5], origin=[0., 0.2], observed_style='inner')
 
 pgm.add_node(Node('G',r"$G$", 3,1))
-pgm.add_node(Node('Coords',r"$\hat{RA}_i$/$\hat{Dec}_i$", 2,2,scale=1.5,aspect=1.2,fixed=True))
+pgm.add_node(Node('Coords',r"${RA}_i$/${Dec}_i$", 2,2,fixed=True))
 pgm.add_node(Node('G_i',r"$g_i$", 3,2))
 
 pgm.add_node(Node('mu',r"$\theta_\mu$", 1,4))
 pgm.add_node(Node('HD',r"$\mu_i$", 4,4,fixed=True))
-pgm.add_node(Node('theta_T',r"$\theta_T^{Ia}$, $\theta_T^{non-Ia}$", 3,7,scale=1.5,aspect=1.5))
+pgm.add_node(Node('theta_T',r"$\theta_T^{Ia}$, $\theta_T^{non-Ia}$", 2,7,scale=1.5,aspect=1.5))
 pgm.add_node(Node('theta_Ti',r"$\theta_{Ti}^{Ia}$, $\theta_{Ti}^{non-Ia}$", 2,6,scale=1.5,aspect=1.5))
 
 
@@ -31,20 +31,20 @@ pgm.add_node(Node('z',r"$z_i$", 3, 3))
 
 pgm.add_node(Node('Type',r"$T_i$", 2, 5))
 pgm.add_node(Node('Luminosity',r"$L_i(t,\lambda)$", 4, 6, scale=1.2,fixed=True))
-pgm.add_node(Node('Flux',r"$n_i(t,\lambda)$", 4, 5, scale=1.2,fixed=True))
-pgm.add_node(Node('Flux_g',r"$n_{gi}(\lambda)$", 4, 2,fixed=True))
-pgm.add_node(Node('Transmission',r"$\phi(\lambda)$", 5, 7))
-pgm.add_node(Node('Counts',r"$\mathit{ADU}_i$", 6, 5,scale=1.2,fixed=True))
-pgm.add_node(Node('Counts_g',r"$\mathit{ADU}_{gi}$", 6, 2,scale=1.2,fixed=True))
[…]

### 2015-07-23 doc/model.tex
polishing

@@
 We infer a Hubble diagram based on measurements of discovered transients
-classified as Type~Ia supernovae (SNe~Ia).  The probability distribution
+that have passed some selection criteria (e.g.\ classified as Type~Ia supernovae, SNe~Ia).  The probability distribution
 function (pdf) of the Hubble diagram is denoted as
@@
 p({\mu},{z} |  {{ADU}}, {{T}}_S,{{z}}_S,
-{{\theta}}_S,\text{GC}, \text{Detected}, {\text{Selected}},
-{\text{RA}}, {\text{Dec}}).
+{{\theta}}_S,\text{GC},
+{\text{RA}}, {\text{Dec}}, \text{Detected}, {\text{Selected}}).
 \label{hd:eqn}
@@
 type, redshift and SN-parameters ${T}_S$, ${z}_S$, ${\theta}_S$;
-the galaxy catalog ${\text{GC}}$; transient coordinates  $\text{RA}$, $\text{Dec}$;
+the galaxy catalog ${\text{GC}}$ and associated galaxy properties such as redshift,
+mass, sSFR, etc.; transient coordinates  $\text{RA}$, $\text{Dec}$;
 and the fact that the transients were Detected and Selected for the analysis.
@@
 \begin{equation}
-p({\mu},{z},   \text{Detected}, {\text{Selected}},
-\text{RA}, \text{Dec} |  {{ADU}}, {{T}}_S,{{z}}_S,
-{{\theta}}_S, \text{GC})
+p({\mu},{z}, \text{RA}, \text{Dec}, \text{GC},  \text{Detected}, {\text{Selected}}
+ |  {{ADU}}, {{T}}_S,{{z}}_S,
+{{\theta}}_S)
 \label{hd2:eqn}
 \end{equation}
-and we model this scenario.  A sketch of such a model is depicted in the Probabilistic Graphical Model
+and this is what we model.  A sketch of the model (with the optional inclusion
+of calibration) is depicted in the Probabilistic Graphical Model
 (PGM)
 shown in Figure~\ref{pgm:fig}.
+Note that although we have been discussing the model for the Hubble diagram, the same PGM can
+ be used to express the pdf for cosmological
+parameters, labelled as $\theta_\mu$.
 
@@
    and data.
-   A GC ${\mathit{Gal.}}$ informs the model for potential hosts $G$.  A transient
+   A galaxy catalog GC informs the model for potential hosts $G$.  A transient
    at coordinates  $\text{RA/Dec}$  has a host $g_i$ drawn from $G$.
@@
    gives the expected
-   counts $\overline{\mathit{ADU}}$, $\overline{\mathit{ADU}}_g$.  The galaxy catalog is GC. 
-   The realized light curve (${ADU}$) depends on the expected counts and also
-   must have been Detected and Selected.  Some transients have spectral data
+   counts $\overline{\mathit{ADU}}$, $\overline{\mathit{ADU}}_g$. 
+   The transient must be Detected and Selected and its realized light curve (${ADU}$) depends on the expected counts.  Some transients have spectral data
    ${X}_S$.
@@
 
-The supernova survey provides the transients that are to be analyzed providing
-the following information:
+The model describes the transients that constitute the cosmology analysis, given the following
+information.  
 \begin{itemize}
@@
 includes its classification as SN~Ia.
-\item GC.  The galaxy catalog used to make host-galaxy associations.
+\item GC.  The galaxy catalog used to make host-galaxy associations, including with
+redshifts and galaxy properties.
 \end{itemize}
 
-The model describes the universe and its contents, specifically transients
-that are discovered as typed as SN~Ia and their host galaxies.
+The universe is modeled as the background cosmology, transients that could
+enter the sample, and their host galaxies.
 \begin{itemize}
@@
 \item $\mu_i=\mu(z_i; \theta_\mu)$.  The distance modulus is a function of redshift,
-we don't impose a specific form for  $\mu$ at the moment,  it could
+whose specific form is unspecified at the moment,  it could
 be a $\Lambda$CDM prediction with cosmological parameters, a spline with knot values
-as parameters, or as extreme as independent values for each $z$.
+as parameters.
 The redshift of the galaxy is used in the Hubble diagram.
@@
 $\theta_{gi}$ are included if correlations with host-galaxy properties are to be modeled.
-\item $n_i(t,\lambda; L_i, \mu_i, z_i)$, $n_{gi}(t,\lambda; L_i, \mu_i, z_i)$.  The  flux incident at Earth
-is fixed by the luminosity, distance modulus, and redshift.
+\item $n_i(t,\lambda; L_i, \mu_i, z_i)$, $n_{gi}(t,\lambda; L_i, \mu_i, z_i)$.  The  fluxes of
+the transient and host that are incident at Earth
+are fixed by the luminosity, distance modulus, and redshift.
 \end{itemize}
@@
 atmosphere to counts.  We expect
-the calibration group to provide us with the functions and covariance
-$\phi \sim \mathcal{N}(\bar{\phi},C_\phi)$. Self-calibration, taking advantage of the
-fact that SNe~Ia are excellent standard stars, 
-may be included in this model.
+the calibration group to provide us with the functions and covariance,
+in which case
+$\phi \sim \mathcal{N}(\bar{\phi},C_\phi)$ would be a fixed condition.
+However, the PGM is written for the more general case where the calibration
+is modeled within our analysis.
 \item $\overline{\mathit{ADU}}$ and
@@
 
-The observations, denoted with \textasciicircum, are now discussed.
+The observations are as follows:
 \begin{itemize}

### 2015-07-23 src/hd_pgm.py

@@ -17,17 +17,8 @@ pgm.add_node(Node('HD',r"$\mu_i$", 4,4,fixed=True))
 pgm.add_node(Node('theta_T',r"$\theta_T^{Ia}$, $\theta_T^{non-Ia}$", 2,7,scale=1.5,aspect=1.5))
 pgm.add_node(Node('theta_Ti',r"$\theta_{Ti}^{Ia}$, $\theta_{Ti}^{non-Ia}$", 2,6,scale=1.5,aspect=1.5))
 
-
-#pgm.add_node(Node('theta_G',r"$\theta_G$", 2,1))
-
-
-
-#pgm.add_node(Node('theta_Gi',r"$\theta_{Gi}$", 3,4))
-
-
 pgm.add_node(Node('Host',r"$\theta_{gi}$", 2, 3))
 pgm.add_node(Node('z',r"$z_i$", 3, 3))
-
 
 pgm.add_node(Node('Type',r"$T_i$", 2, 5))
 pgm.add_node(Node('Luminosity',r"$L_i(t,\lambda)$", 4, 6, scale=1.2,fixed=True))
@@ -41,13 +32,12 @@ pgm.add_node(Node('^Counts',r"${\mathit{ADU}_i}$", 9, 4, observed=True,scale=1.2
 
 pgm.add_node(Node('Spars',r"${T}_{Si}$, ${z}_{Si},{\theta}_{Si}$", 6, 4, scale=1.8,aspect=1.2, observed=True))
 #pgm.add_node(Node('^Host',r"${z}_{Hi},{\theta}_{Hi}$", 7, 2, scale=1.5,observed=True))
-pgm.add_node(Node('Galaxies',r"${\mathit{GC}}$", 5, 1, fixed=True))
+pgm.add_node(Node('Galaxies',r"${\mathit{GC}}$", 1, 1, fixed=True))
 
 pgm.add_node(Node('Detected',r"Detected", 8, 3, fixed=True,offset=(-10,-20)))
 pgm.add_node(Node('^Type',r"Selected", 8, 2, fixed=True,offset=(-10,-20)))
 
 pgm.add_edge("mu","HD")
-#pgm.add_edge("^Host","^Type")
 pgm.add_edge("^Type","^Counts")
 
 pgm.add_edge("Host","Luminosity")
@@ -75,7 +65,6 @@ pgm.add_edge("G","G_i")
 
 
 pgm.add_edge("theta_T","Luminosity")
[…]

### 2015-07-24 doc/model.tex
more comments from Danny input

@@
 p({\mu},{z} |  {{ADU}}, {{T}}_S,{{z}}_S,
-{{\theta}}_S,\text{GC},
+{{\theta}}_S; \text{GC},
 {\text{RA}}, {\text{Dec}}, \text{Detected}, {\text{Selected}}).
@@
 \begin{equation}
-p({\mu},{z}, \text{RA}, \text{Dec}, \text{GC},  \text{Detected}, {\text{Selected}}
+p({\mu},{z}; \text{RA}, \text{Dec}, \text{GC},  \text{Detected}, {\text{Selected}}
  |  {{ADU}}, {{T}}_S,{{z}}_S,
@@
    flow goes from left to right, starting with the description of the universe, observatory,
-   and data.
-   A galaxy catalog GC informs the model for potential hosts $G$.  A transient
-   at coordinates  $\text{RA/Dec}$  has a host $g_i$ drawn from $G$.
+   and data.  The galaxies that host transients are described by a galaxy catalog GC. 
+   A transient has
+   coordinates  $\text{RA/Dec}$.  Its host galaxy $g_i$ is drawn from from the GC.
    The galaxy redshift redshift $z$ and parameters $\theta_{gi}$ depend on the host.
@@
 \item GC.  The galaxy catalog used to make host-galaxy associations, including with
-redshifts and galaxy properties.
+redshifts and galaxy properties.  It is
+the union of the objects in the galaxy catalog GC
+plus unobserved galaxies that have not
+met the detection threshold, presumably due to their low surface brightness.
 \end{itemize}
@@
 \begin{itemize}
-\item $G$ is a shorthand for the model of all galaxies that can host a transient.  It is
-the union of the objects in the galaxy catalog GC
-plus unobserved galaxies that have not
-met the detection threshold, presumably due to their low surface brightness.
-\item $P(g_i | G, {\text{RA}}/{\text{Dec}})$. The host galaxy $g_i$
+\item $P(g_i ; \text{GC}, {\text{RA}}/{\text{Dec}})$. The host galaxy $g_i$
 is drawn from the GC based on coordinates.
@@
 \begin{equation}
-P({\mathit{ADU}} | \text{Dectected}, \text{Selected}, \overline{\mathit{ADU}}, 
-\overline{\mathit{ADU}}_g)=\frac{P({\mathit{ADU}},\text{Dectected}, \text{Selected} |  
+P({\mathit{ADU}} | \overline{\mathit{ADU}}, 
+\overline{\mathit{ADU}}_g; \text{Dectected}, \text{Selected})=\frac{P({\mathit{ADU}};\text{Dectected}, \text{Selected} |  
 \overline{\mathit{ADU}}, \overline{\mathit{ADU}}_g)}{P(\text{Dectected}, \text{Selected} | 

### 2015-07-24 src/hd_pgm.py

@@ -8,7 +8,7 @@ rc("text", usetex=True)
 
 pgm = PGM([10.5, 7.5], origin=[0., 0.2], observed_style='inner')
 
-pgm.add_node(Node('G',r"$G$", 3,1))
+#pgm.add_node(Node('G',r"$G$", 3,1))
 pgm.add_node(Node('Coords',r"${RA}_i$/${Dec}_i$", 2,2,fixed=True))
 pgm.add_node(Node('G_i',r"$g_i$", 3,2))
 
@@ -32,7 +32,7 @@ pgm.add_node(Node('^Counts',r"${\mathit{ADU}_i}$", 9, 4, observed=True,scale=1.2
 
 pgm.add_node(Node('Spars',r"${T}_{Si}$, ${z}_{Si},{\theta}_{Si}$", 6, 4, scale=1.8,aspect=1.2, observed=True))
 #pgm.add_node(Node('^Host',r"${z}_{Hi},{\theta}_{Hi}$", 7, 2, scale=1.5,observed=True))
-pgm.add_node(Node('Galaxies',r"${\mathit{GC}}$", 1, 1, fixed=True))
+pgm.add_node(Node('Galaxies',r"GC", 2, 1, fixed=True,offset=(0,-20)))
 
 pgm.add_node(Node('Detected',r"Detected", 8, 3, fixed=True,offset=(-10,-20)))
 pgm.add_node(Node('^Type',r"Selected", 8, 2, fixed=True,offset=(-10,-20)))
@@ -61,11 +61,11 @@ pgm.add_edge("Host","Type")
 
 pgm.add_edge("Type","Luminosity")
 pgm.add_edge("Luminosity","Flux")
-pgm.add_edge("G","G_i")
+pgm.add_edge("Galaxies","G_i")
 
 
 pgm.add_edge("theta_T","Luminosity")
-pgm.add_edge("Galaxies","G")
+#pgm.add_edge("Galaxies","G")
 
 pgm.add_edge("theta_Ti","Luminosity")
 pgm.add_edge("Host","Flux_g")
@@ -94,8 +94,8 @@ pgm.add_edge("Detected","^Counts")
 
 # Big Plate: Galaxy
 pgm.add_plate(Plate([1.5, 1.5, 8, 5.],
-                    label=r"SNe $\i = 1, \cdots, N_{SN}$",
-                    shift=-0.1))
+                    label=r"SNe $i = 1, \cdots, N_{SN}$",
[…]

### 2015-07-24 doc/model.tex
finishing touches

@@
 p({\mu},{z} |  {{ADU}}, {{T}}_S,{{z}}_S,
-{{\theta}}_S; \text{GC},
+{{\theta}}_S;
 {\text{RA}}, {\text{Dec}}, \text{Detected}, {\text{Selected}}).
@@
 \end{equation}
+The semicolon separates random and fixed parameters.
 The set of distance moduli
@@
 type, redshift and SN-parameters ${T}_S$, ${z}_S$, ${\theta}_S$;
-the galaxy catalog ${\text{GC}}$ and associated galaxy properties such as redshift,
 mass, sSFR, etc.; transient coordinates  $\text{RA}$, $\text{Dec}$;
@@
 \begin{equation}
-p({\mu},{z}; \text{RA}, \text{Dec}, \text{GC},  \text{Detected}, {\text{Selected}}
+p({\mu},{z}; \text{RA}, \text{Dec},  \text{Detected}, {\text{Selected}}
  |  {{ADU}}, {{T}}_S,{{z}}_S,
@@
    flow goes from left to right, starting with the description of the universe, observatory,
-   and data.  The galaxies that host transients are described by a galaxy catalog GC. 
-   A transient has
-   coordinates  $\text{RA/Dec}$.  Its host galaxy $g_i$ is drawn from from the GC.
+   and data.    A transient has
+   coordinates  $\text{RA/Dec}$.  It is associated with a host host galaxy $g_i$.
    The galaxy redshift redshift $z$ and parameters $\theta_{gi}$ depend on the host.
@@
 includes its classification as SN~Ia.
-\item GC.  The galaxy catalog used to make host-galaxy associations, including with
-redshifts and galaxy properties.  It is
-the union of the objects in the galaxy catalog GC
-plus unobserved galaxies that have not
-met the detection threshold, presumably due to their low surface brightness.
 \end{itemize}
@@
 \begin{itemize}
-\item $P(g_i ; \text{GC}, {\text{RA}}/{\text{Dec}})$. The host galaxy $g_i$
-is drawn from the GC based on coordinates.
+\item $P(g_i; {\text{RA}}/{\text{Dec}})$. The host galaxy $g_i$
+is drawn based on coordinates.
+It is drawn from
+the union of the objects in the observed galaxy catalog
+plus unobserved galaxies that have not
+met the detection threshold, presumably due to their low surface brightness.
 This pdf is
@@
 $\phi \sim \mathcal{N}(\bar{\phi},C_\phi)$ would be a fixed condition.
-However, the PGM is written for the more general case where the calibration
-is modeled within our analysis.
 \item $\overline{\mathit{ADU}}$ and
@@
 or a blurry version instead of a straight equality.
-\item ${Z}$ represents the calibration measurements.  Although we expect to receive
-the transmission functions from the Calibration Task Force, we may be want to include
-calibration as part of our analysis.
+\item ${Z}$ represents the calibration measurements.   Although this may be given
+by the Calibration Task Force, the PGM is written for the more general case where the calibration
+is modeled within our analysis.
 \end{itemize}

### 2015-07-24 src/hd_pgm.py

@@ -6,36 +6,35 @@ rc("font", family="serif", size=10)
 rc("text", usetex=True)
 
 
-pgm = PGM([10.5, 7.5], origin=[0., 0.2], observed_style='inner')
+pgm = PGM([10.5, 6.5], origin=[0., 0.2], observed_style='inner')
 
 #pgm.add_node(Node('G',r"$G$", 3,1))
-pgm.add_node(Node('Coords',r"${RA}_i$/${Dec}_i$", 2,2,fixed=True))
-pgm.add_node(Node('G_i',r"$g_i$", 3,2))
+pgm.add_node(Node('Coords',r"${RA}_i$/${Dec}_i$", 2,1,fixed=True))
+pgm.add_node(Node('G_i',r"$g_i$", 3,1))
 
-pgm.add_node(Node('mu',r"$\theta_\mu$", 1,4))
-pgm.add_node(Node('HD',r"$\mu_i$", 4,4,fixed=True))
-pgm.add_node(Node('theta_T',r"$\theta_T^{Ia}$, $\theta_T^{non-Ia}$", 2,7,scale=1.5,aspect=1.5))
-pgm.add_node(Node('theta_Ti',r"$\theta_{Ti}^{Ia}$, $\theta_{Ti}^{non-Ia}$", 2,6,scale=1.5,aspect=1.5))
+pgm.add_node(Node('mu',r"$\theta_\mu$", 1,3))
+pgm.add_node(Node('HD',r"$\mu_i$", 4,3,fixed=True))
+pgm.add_node(Node('theta_T',r"$\theta_T^{Ia}$, $\theta_T^{non-Ia}$", 2,6,scale=1.5,aspect=1.5))
+pgm.add_node(Node('theta_Ti',r"$\theta_{Ti}^{Ia}$, $\theta_{Ti}^{non-Ia}$", 2,5,scale=1.5,aspect=1.5))
 
-pgm.add_node(Node('Host',r"$\theta_{gi}$", 2, 3))
-pgm.add_node(Node('z',r"$z_i$", 3, 3))
+pgm.add_node(Node('Host',r"$\theta_{gi}$", 2, 2))
+pgm.add_node(Node('z',r"$z_i$", 3, 2))
 
-pgm.add_node(Node('Type',r"$T_i$", 2, 5))
-pgm.add_node(Node('Luminosity',r"$L_i(t,\lambda)$", 4, 6, scale=1.2,fixed=True))
[…]

### 2015-08-04 src/des.py
make it so that each run has same supernovae and realizations

@@ -1,25 +1,25 @@
 #!/usr/bin/env python
 
 import matplotlib
-matplotlib.use('Agg')
+#matplotlib.use('Agg')
 import matplotlib.pyplot as plt
 
 import pystan
 import numpy.random
 from astropy.cosmology import FlatLambdaCDM
 
+import pickle
 
-def genData(N_sn, N_s_obs, Ninit):
+
+def genData(N_sn, N_s_obs, Ninit, seed):
+
+	numpy.random.seed(seed)
+
 	omega_M=0.28
 	cosmo=FlatLambdaCDM(70,omega_M)
 
 	zmin=0.1
 	zmax=1.
-	zs = numpy.sort(numpy.random.uniform(zmin,zmax,N_sn))
-	s_obs = numpy.sort(numpy.random.choice(N_sn, N_s_obs,replace=False))
-	s_mis = numpy.zeros(N_sn,dtype=bool)
-	s_mis[s_obs] = True
-	s_mis = numpy.where(numpy.logical_not(s_mis))[0]
 
 	sigma_snIa=0.1
 	sigma_nonIa=1
@@ -28,18 +28,32 @@ def genData(N_sn, N_s_obs, Ninit):
 	alpha_nonIa=1.
 	frac_Ia=.8
 
+	zs = numpy.sort(numpy.random.uniform(zmin,zmax,N_sn))
+
 	snIa = numpy.random.binomial(1, frac_Ia, size=N_sn)
 
 	wsnIa = numpy.where(snIa)[0]
 	wnonIa = numpy.where(numpy.logical_not(snIa))[0]
 
 	adu = 1/(cosmo.luminosity_distance(zs).value/cosmo.hubble_distance.value)**2
-	adu[wsnIa] = alpha_snIa*adu[wsnIa]*10**(numpy.random.normal(loc=0, scale=sigma_snIa/2.5,size=len(wsnIa)))
-	adu[wnonIa] = alpha_nonIa*adu[wnonIa]*10**(numpy.random.normal(loc=0, scale=sigma_nonIa/2.5,size=len(wnonIa)))
 
-	host_zs_mis = zs[s_mis]*numpy.random.binomial(1,0.98,size=len(s_mis))
-	wrong_host_zs = host_zs_mis == 0
-	host_zs_mis[wrong_host_zs] = numpy.random.uniform(zmin/1.5,zmax*1.5,size=wrong_host_zs.sum())
+	adu_random = numpy.random.normal(size=N_sn)
+
[…]

### 2015-08-06 src/des.py
change the way the host galaxies are treated so that the candidate other redshifts are discrete

@@ -28,32 +28,52 @@ def genData(N_sn, N_s_obs, Ninit, seed):
 	alpha_nonIa=1.
 	frac_Ia=.8
 
+	# zs : the true redshifts
 	zs = numpy.sort(numpy.random.uniform(zmin,zmax,N_sn))
 
+	# snIa : the true types
 	snIa = numpy.random.binomial(1, frac_Ia, size=N_sn)
 
 	wsnIa = numpy.where(snIa)[0]
 	wnonIa = numpy.where(numpy.logical_not(snIa))[0]
 
+	# adu : the observed counts
 	adu = 1/(cosmo.luminosity_distance(zs).value/cosmo.hubble_distance.value)**2
-
 	adu_random = numpy.random.normal(size=N_sn)
-
 	adu[wsnIa] = alpha_snIa*adu[wsnIa]*10**(adu_random[wsnIa]*sigma_snIa/2.5)
 	adu[wnonIa] = alpha_nonIa*adu[wnonIa]*10**(adu_random[wnonIa]*sigma_nonIa/2.5)
 
-	host_zs_random = zs*numpy.random.binomial(1,0.98,size=N_sn)
-	wrong_host_zs = host_zs_random == 0
-	host_zs_random[wrong_host_zs] = 	numpy.random.uniform(zmin/1.5,zmax*1.5,size=wrong_host_zs.sum())
+	# host_choice : 1 if correct host is chosen to have highest probability, 0 otherwise
+	host_choice = numpy.random.binomial(1,0.98,size=N_sn)
+	neighbor_zs=numpy.random.uniform((1+zmin/1.5)**3,(1+zmax*1.5)**3,size=N_sn)**(1./3)-1
+	host_zs_random_ = zs*host_choice + neighbor_zs*(1-host_choice)
+	neighbor_zs_random_ = zs*(1-host_choice) + neighbor_zs*host_choice
+	# wrong_host_zs : indeces if incorrect host galaxy association
+	#wrong_host_zs = host_zs_random_ == 0
+	#host_zs_random_[wrong_host_zs] = 
 
-	numpy.random.seed()
+	# host_zs_random : redshifts of potential host galaxies with the probability of each
+	host_zs_random=[]
+	for i in xrange(N_sn):
+		ans=[]
+		ans.append(numpy.array([host_zs_random_[i],0.98]))
+		ans.append(numpy.array([neighbor_zs_random_[i],0.02]))
[…]

### 2015-08-07 doc/model.tex
clean up code getting rid of commented stuff, fix documents to revised view of model

@@
 p({\mu},{z} |  {{ADU}}, {{T}}_S,{{z}}_S,
-{{\theta}}_S;
-{\text{RA}}, {\text{Dec}}, \text{Detected}, {\text{Selected}}).
+{{\theta}}_S, \theta_G,
+{\text{Select}}).
 \label{hd:eqn}
 \end{equation}
-The semicolon separates random and fixed parameters.
 The set of distance moduli
@@
 type, redshift and SN-parameters ${T}_S$, ${z}_S$, ${\theta}_S$;
-mass, sSFR, etc.; transient coordinates  $\text{RA}$, $\text{Dec}$;
-and the fact that the transients were Detected and Selected for the analysis.
+host-galaxy parameter measurements $\theta_H$ including redshift,
+mass, sSFR, etc.; and the sample-selection score Select.
 
-The pdf in Equation~\ref{hd:eqn} is proportional to
-\begin{equation}
-p({\mu},{z}; \text{RA}, \text{Dec},  \text{Detected}, {\text{Selected}}
- |  {{ADU}}, {{T}}_S,{{z}}_S,
-{{\theta}}_S)
-\label{hd2:eqn}
-\end{equation}
-and this is what we model.  A sketch of the model (with the optional inclusion
-of calibration) is depicted in the Probabilistic Graphical Model
+A sketch of a more extensive model that includes the
+model of Equation~\ref{hd:eqn} is depicted in the Probabilistic Graphical Model
 (PGM)
@@
 
-The model describes the transients that constitute the cosmology analysis, given the following
-information.  
-\begin{itemize}
-\item ${\text{RA}}$, ${\text{Dec}}$.  The observed
-coordinates.  For our purposes the observed, rather than true, coordinates are sufficient.
-\item Detected.  The transient is discovered.
-\item Selected. The transient is selected for the cosmology analysis.  This presumably
-includes its classification as SN~Ia.
-\end{itemize}
-
 The universe is modeled as the background cosmology, transients that could
@@
 \begin{itemize}
-\item $P(g_i; {\text{RA}}/{\text{Dec}})$. The host galaxy $g_i$
-is drawn based on coordinates.
-It is drawn from
-the union of the objects in the observed galaxy catalog
-plus unobserved galaxies that have not
-met the detection threshold, presumably due to their low surface brightness.
-This pdf is
-the deliverable we want from Ravi.
+\item  $g_i$ labels the distinct galaxy that is the transient host.
 \item $z_i$, $\theta_{gi}$ are the galaxy redshift and parameters (e.g.\ mass, sSFR, metallicity).
-For observed galaxies the parameter values are based on measurements e.g.\ $\theta_{gi} \sim \mathcal{N}({\theta}_{gi},\sigma^2_{{\theta}_{gi}})$, otherwise the distribution
-of $\theta_{gi}$ for ``hostless'' galaxies is described by the model.
-Redshifts may be photometric or spectroscopic.
+Given the galaxy $g_i$, these values are specified.
 \item $\theta_\mu$ are the parameters that specify that distance modulus.
@@
 \begin{itemize}
-\item ${\mathit{ADU}}$ is the realized flux can be expressed as
+\item ${\mathit{ADU}}$ is the realized flux. 
+\item Select is the score used to decide if the transient is used in the analysis.
+It and $\mathit{ADU}$ are not independent so what is relevant is their joint distribution
 \begin{equation}
-P({\mathit{ADU}} | \overline{\mathit{ADU}}, 
-\overline{\mathit{ADU}}_g; \text{Dectected}, \text{Selected})=\frac{P({\mathit{ADU}};\text{Dectected}, \text{Selected} |  
-\overline{\mathit{ADU}}, \overline{\mathit{ADU}}_g)}{P(\text{Dectected}, \text{Selected} | 
-\overline{\mathit{ADU}},  \overline{{\mathit{ADU}}}_g)},
+P({\mathit{ADU},\text{Select}} | \overline{\mathit{ADU}}, 
+\overline{\mathit{ADU}}_g),
 \end{equation}
 which can be determined from detection and typing efficiency studies.
+\item $\theta_G$ represents the galaxy parameters of the
+galaxy catalog used to identify prospective host galaxies.
+The contribution to the likelihood $P(\theta_G|g_i)$ can be
+estimated as $P(g_i|\theta_G)\frac{P(\theta_G)}{P(z)}$: Ravi is determining $P(g_i|\theta_G)$.
 \item ${T}_S$, ${z}_S$, ${\theta}_S$ Transient type, redshift and properties from

### 2015-08-07 src/des.py

@@ -111,16 +111,16 @@ def genData(N_sn, N_s_obs, Ninit, seed):
 #		wrong_host_zs_init = host_zs_mis_init == 0
 #		host_zs_mis_init[wrong_host_zs_init] = numpy.random.uniform(zmin/1.5,zmax*1.5,size=wrong_host_zs_init.sum())
 		init.append ( {
-			'Omega_M':omega_M,
+			'Omega_M':numpy.random.normal(omega_M,0.1),
 			'Omega_L':1-omega_M,
-			'w': -1,
+			'w': numpy.random.normal(-0.9,0.1),
 			'zs_true_obs': zs[s_obs],
-		  	'zs_true_mis': host_zs_mis_init,
-		  	'alpha_Ia': alpha_snIa,
-		 	'alpha_nonIa': alpha_nonIa,
-		  	'sigma_Ia': sigma_snIa,
-		  	'sigma_nonIa':sigma_nonIa,
-		  	'snIa_rate':frac_Ia
+		  	'zs_true_mis': numpy.random.uniform((1+zmin/1.5)**3,(1+zmax*1.5)**3,size=N_sn-N_s_obs)**(1./3)-1, #host_zs_mis_init,
+		  	'alpha_Ia': numpy.random.normal(alpha_snIa,0.1),
+		 	'alpha_nonIa': numpy.random.normal(alpha_nonIa,0.1),
+		  	'sigma_Ia': numpy.random.normal(sigma_snIa,0.05),
+		  	'sigma_nonIa':numpy.random.normal(sigma_nonIa,0.5),
+		  	'snIa_rate':numpy.random.lognormal(numpy.log(frac_Ia),0.1)
 			} )
 
 	info = {
@@ -135,18 +135,18 @@ def genData(N_sn, N_s_obs, Ninit, seed):
 	return data, init, info
 
 def main():
-	Nchains=8
+	Nchains=4
 	N_sn=200
 
 	sm = pystan.StanModel(file='des.stan')
 
-	nspec = numpy.arange(100,N_sn+1,25)
+	nspec = numpy.arange(100,N_sn+1,250)
 	mn=[]
 	std=[]
 	for ns in nspec:
 		data, init, info = genData(N_sn,ns,Nchains,1)
 
-		fit = sm.sampling(data=data, iter=1000, chains=Nchains, init=init)
+		fit = sm.sampling(data=data, iter=100000, thin=100, warmup = 500, chains=Nchains, init=init)
[…]

### 2015-08-07 src/hd_pgm.py

@@ -6,38 +6,48 @@ rc("font", family="serif", size=10)
 rc("text", usetex=True)
 
 
-pgm = PGM([10.5, 6.5], origin=[0., 0.2], observed_style='inner')
+pgm = PGM([10.5, 7.5], origin=[0., 0.2], observed_style='inner')
 
 #pgm.add_node(Node('G',r"$G$", 3,1))
-pgm.add_node(Node('Coords',r"${RA}_i$/${Dec}_i$", 2,1,fixed=True))
-pgm.add_node(Node('G_i',r"$g_i$", 3,1))
+#pgm.add_node(Node('Coords',r"${RA}_i$/${Dec}_i$", 2,1,fixed=True))
+pgm.add_node(Node('G_i',r"$g_i$", 2,2))
 
-pgm.add_node(Node('mu',r"$\theta_\mu$", 1,3))
-pgm.add_node(Node('HD',r"$\mu_i$", 4,3,fixed=True))
-pgm.add_node(Node('theta_T',r"$\theta_T^{Ia}$, $\theta_T^{non-Ia}$", 2,6,scale=1.5,aspect=1.5))
-pgm.add_node(Node('theta_Ti',r"$\theta_{Ti}^{Ia}$, $\theta_{Ti}^{non-Ia}$", 2,5,scale=1.5,aspect=1.5))
+pgm.add_node(Node('mu',r"$\theta_\mu$", 1,4))
+pgm.add_node(Node('rate',r"$\theta_r$", 1,5))
+pgm.add_node(Node('HD',r"$\mu_i$", 4,4,fixed=True))
+pgm.add_node(Node('theta_T',r"$\theta_T^{Ia}$, $\theta_T^{non-Ia}$", 2,7,scale=1.5,aspect=1.5))
+pgm.add_node(Node('theta_Ti',r"$\theta_{Ti}^{Ia}$, $\theta_{Ti}^{non-Ia}$", 2,6,scale=1.5,aspect=1.5))
 
-pgm.add_node(Node('Host',r"$\theta_{gi}$", 2, 2))
-pgm.add_node(Node('z',r"$z_i$", 3, 2))
+pgm.add_node(Node('Host',r"$\theta_{gi}$", 2, 3, fixed=True,offset=(-10,-5)))
+pgm.add_node(Node('z',r"$z_i$", 3, 3, fixed=True,offset=(-10,-5)))
 
-pgm.add_node(Node('Type',r"$T_i$", 2, 4))
[…]

### 2015-08-07 doc/model.tex
fix documentation

@@
 p({\mu},{z} |  {{ADU}}, {{T}}_S,{{z}}_S,
-{{\theta}}_S, \theta_G,
-{\text{Select}}).
+{{\theta}}_S, \theta_G, \tau).
 \label{hd:eqn}
@@
 The set of distance moduli
-and redshifts $(\mu, z)$ is the Hubble diagram.  The available information
+and redshifts $(\mu, z)$ contains the points that constitute the Hubble diagram.  The available information
 from which the Hubble diagram is inferred include:
@@
 type, redshift and SN-parameters ${T}_S$, ${z}_S$, ${\theta}_S$;
-host-galaxy parameter measurements $\theta_H$ including redshift,
-mass, sSFR, etc.; and the sample-selection score Select.
+host-galaxy parameter measurements $\theta_H$ (including redshift,
+mass, sSFR, etc.).  Only a subset of all detected transients enter the cosmology
+analysis: the sample-selection criterion is denoted as $\tau$.  For example
+$\tau$ could be the classification score of PSNID.
 
@@
 Note that although we have been discussing the model for the Hubble diagram, the same PGM can
- be used to express the pdf for cosmological
+also expresses the pdf for cosmological
 parameters, labelled as $\theta_\mu$.
@@
    flow goes from left to right, starting with the description of the universe, observatory,
-   and data.    A transient has
-   coordinates  $\text{RA/Dec}$.  It is associated with a host host galaxy $g_i$.
-   The galaxy redshift redshift $z$ and parameters $\theta_{gi}$ depend on the host.
+   and data.    A transient has host galaxy $g_i$, which determines its redshift $z_i$
+   and galaxy parameters $\theta_{gi}$.
    A distance modulus model with parameters $\theta_\mu$ fix the distance modulus $\mu_i$.
-   The transient type $T$ depends on the host-galaxy.   The transient
-   parameters $\theta_T^X$, $\theta_{Ti}^X$ (and perhaps the host galaxy) fix the luminosity $L$.       The 
+   The transient type $T$ depends on the host-galaxy parameters  $\theta_{gi}$
+   and rates $\theta_r$.   The transient
+   parameters $\theta_T^X$, $\theta_{Ti}^X$ (and perhaps the host galaxy) determine the luminosity $L$.       The 
    incoming photon flux $n$, $n_g$  are then fixed
@@
    counts $\overline{\mathit{ADU}}$, $\overline{\mathit{ADU}}_g$. 
-   The transient must be Detected and Selected and its realized light curve (${ADU}$) depends on the expected counts.  Some transients have spectral data
+   The transient has realized light curves (${ADU}$) and passes selection criteria
+   through $\tau_i$ to be included in the sample.  Some transients have spectral data
    ${X}_S$.
@@
 
-The universe is modeled as the background cosmology, transients that could
-enter the sample, and their host galaxies.
+The fundamental parameters that need to be determined are those with no incoming arrows in Figure~\ref{pgm:fig}.  Most all are used to model the universe: 
+the background cosmology, transients that could enter the sample, and their host galaxies.
 \begin{itemize}
-\item  $g_i$ labels the distinct galaxy that is the transient host.
-\item $z_i$, $\theta_{gi}$ are the galaxy redshift and parameters (e.g.\ mass, sSFR, metallicity).
-Given the galaxy $g_i$, these values are specified.
-\item $\theta_\mu$ are the parameters that specify that distance modulus.
-\item $\mu_i=\mu(z_i; \theta_\mu)$.  The distance modulus is a function of redshift,
-whose specific form is unspecified at the moment,  it could
-be a $\Lambda$CDM prediction with cosmological parameters, a spline with knot values
-as parameters.
-The redshift of the galaxy is used in the Hubble diagram.
-\item $P(T_i | \theta_{gi})$.  The transient type $T_i$, SN~Ia or non-Ia, depends
-on the host properties.  We could make the relative rates be dependent
-on specific star formation rate and morphology.
-\item $p(\theta_T^{Ia}, \theta_{Ti}^{Ia})$.  The model parameters for SNe~Ia, including
+\item  $g_i$ labels the distinct galaxy that hosts the transient.
+\item $\theta_\mu$ are the parameters that specify that distance modulus, e.g.\ the cosmological
+parameters.
+\item $\theta_\tau$ govern the relative rates of supernovae of different types in galaxies.
+\item $\theta_T^{Ia}$, $\theta_{Ti}^{Ia}$.  The model parameters for SNe~Ia, including
 parameters that describe distributions.
@@
  and  underlying  $c$ and $x_1$ distributions that would constitute $\theta_T^{Ia}$.
-\item $p(\theta_T^{non-Ia}, \theta_{Ti}^{non-Ia})$.  Non-Ia transients
+\item $\theta_T^{non-Ia}$, $\theta_{Ti}^{non-Ia}$.  Non-Ia transients
 that can be mistyped as Ia are described by a parameterized model.
-\item $L_i(t,\lambda; T_i, \theta_T^{Ia}, \theta_{Ti}^{Ia}, \theta_T^{non-Ia}, \theta_{Ti}^{non-Ia},
-\theta_{gi})$.  The source model fixes
-the luminosity. The  model includes  information on the
+\item The transmission functions $\phi(\lambda)$ describe the optical path from the
+atmosphere to counts.  We expect
+the calibration group to provide us with the functions and covariance $\phi \sim \mathcal{N}(\bar{\phi},C_\phi)$, in which case it would not have to be determined as part
+of our analysis.    There is a chance that we will want to determine calibration ourselves,
+so it is included in Figure~\ref{pgm:fig}.
+\end{itemize}
+
+From these fundamental parameters we can determine the expected
+signals
+through a series of intermediary parameters,
+some of which are deterministic (points in Figure~\ref{pgm:fig}) and others
+probabilistic (ovals).
+\begin{itemize}
+\item $z_i$, $\theta_{gi}$ are the galaxy redshift and parameters (e.g.\ mass, sSFR, metallicity).
+Each galaxy $g_i$ has its values for these quantities.
+\item $\mu_i=\mu(z_i; \theta_\mu)$.  The distance modulus is a function of redshift,
+whose specific form is unspecified at the moment,  it could
+be a $\Lambda$CDM prediction with cosmological parameters, a spline with knot values
+as parameters.
+The redshift of the galaxy is used in the Hubble diagram.
+\item $P(T_i | \theta_r, \theta_{gi})$.  The transient type $T_i$, SN~Ia or non-Ia, depends
+on the relative rates given the host properties.  Note that the type is probabilistic.
+\item $P(L_i(t,\lambda)| T_i, \theta_T^{Ia}, \theta_{Ti}^{Ia}, \theta_T^{non-Ia}, \theta_{Ti}^{non-Ia},
+\theta_{gi})$.  The source model determines
+the luminosity; often the model includes intrinsic dispersion making the luminosity
+probabilistic. The  model includes  information on the
 source and line-of-sight effects, which specify the effective SED.   Only the
@@
 $\theta_{gi}$ are included if correlations with host-galaxy properties are to be modeled.
-\item $n_i(t,\lambda; L_i, \mu_i, z_i)$, $n_{gi}(t,\lambda; L_i, \mu_i, z_i)$.  The  fluxes of
+\item $n_i(t,\lambda; L_i, \mu_i, z_i)$, $n_{gi}(t; g_i, \mu_i, z_i)$.  The  fluxes of
 the transient and host that are incident at Earth
 are fixed by the luminosity, distance modulus, and redshift.
-\end{itemize}
-
-The model expectation of measured  signals is governed by:
-\begin{itemize}
-\item The transmission functions $\phi(\lambda)$ describe the optical path from the
-atmosphere to counts.  We expect
-the calibration group to provide us with the functions and covariance,
-in which case
-$\phi \sim \mathcal{N}(\bar{\phi},C_\phi)$ would be a fixed condition.
 \item $\overline{\mathit{ADU}}$ and
@@
 \begin{itemize}
-\item ${\mathit{ADU}}$ is the realized flux. 
-\item Select is the score used to decide if the transient is used in the analysis.
-It and $\mathit{ADU}$ are not independent so what is relevant is their joint distribution
-\begin{equation}
-P({\mathit{ADU},\text{Select}} | \overline{\mathit{ADU}}, 
-\overline{\mathit{ADU}}_g),
-\end{equation}
-which can be determined from detection and typing efficiency studies.
+\item ${\mathit{ADU}}$ is the realized flux. $P({\mathit{ADU}} | \overline{\mathit{ADU}}, 
+\overline{\mathit{ADU}}_g)$.
 \item $\theta_G$ represents the galaxy parameters of the
@@
 or a blurry version instead of a straight equality.
+\item $\tau$ is the score used to decide if the transient is used in the analysis.  It is
+determined based on other measurements $\tau(\mathit{ADU},T_S)$.
 \item ${Z}$ represents the calibration measurements.   Although this may be given

### 2015-08-07 src/hd_pgm.py

@@ -22,7 +22,7 @@ pgm.add_node(Node('Host',r"$\theta_{gi}$", 2, 3, fixed=True,offset=(-10,-5)))
 pgm.add_node(Node('z',r"$z_i$", 3, 3, fixed=True,offset=(-10,-5)))
 
 pgm.add_node(Node('Type',r"$T_i$", 2, 5))
-pgm.add_node(Node('Luminosity',r"$L_i(t,\lambda)$", 4, 6, scale=1.2,fixed=True))
+pgm.add_node(Node('Luminosity',r"$L_i(t,\lambda)$", 4, 6, scale=1.2))
 pgm.add_node(Node('Flux',r"$n_i(t,\lambda)$", 5, 5, scale=1.2,fixed=True,offset=(15,0)))
 pgm.add_node(Node('Flux_g',r"$n_{gi}(\lambda)$", 5, 2,fixed=True,offset=(0,-20)))
 pgm.add_node(Node('Transmission',r"$\phi(\lambda)$", 7, 7))
@@ -35,7 +35,7 @@ pgm.add_node(Node('Spars',r"${T}_{Si}$, ${z}_{Si},{\theta}_{Si}$", 6, 4, scale=1
 #pgm.add_node(Node('^Host',r"${z}_{Hi},{\theta}_{Hi}$", 7, 2, scale=1.5,observed=True))
 
 #pgm.add_node(Node('Detected',r"Detected$_i$", 8, 3, fixed=True,offset=(-10,-20)))
-pgm.add_node(Node('^Type',r"Select$_i$", 9, 5, observed=True,scale=1,aspect=1.5))
+pgm.add_node(Node('^Type',r"$\tau_i$", 9, 2, observed=True))
 
 pgm.add_node(Node('Gals',r"$\theta_G$", 6, 1, observed=True))
 
@@ -46,9 +46,8 @@ pgm.add_edge("rate","Type")
 
 
 pgm.add_edge("mu","HD")
-pgm.add_edge("Counts","^Type")
-pgm.add_edge("Counts_g","^Type")
-
+pgm.add_edge("^Counts","^Type")
+pgm.add_edge("Spars","^Type")
 pgm.add_edge("Host","Luminosity")
 
 
@@ -61,6 +60,7 @@ pgm.add_edge("G_i","Host")
 pgm.add_edge("G_i","z")
 pgm.add_edge("HD","Flux")
 pgm.add_edge("z","Flux")
[…]

### 2015-08-08 src/analyze.py
look at log posterior

@@ -1,0 +1,50 @@
+#!/usr/bin/env python
+
+import matplotlib
+#matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+
+import pystan
+import numpy.random
+from astropy.cosmology import FlatLambdaCDM
+
+import pickle
+import des
+
+def individual(N_sn, N_s):
+	[extract, info, logposterior] = pickle.load(file('model'+str(N_s)+'.pkl','rb'))
+
+	plt.plot(logposterior[0][200:])
+	plt.plot(logposterior[1][200:])
+	plt.plot(logposterior[2][200:])
+	plt.plot(logposterior[3][200:])
+	plt.show()
+	# plt.plot(extract['w'])
+	# plt.show()
+	# plt.hist(extract['w'])
+	# plt.show()
+
+	missed_wrong = info['host_choice'][info['s_mis']] == 0
+	print missed_wrong.sum()
+	if missed_wrong.sum !=0:
+		plt.plot(extract['zs_true_mis'][:,missed_wrong] - info['zs'][info['s_mis']][missed_wrong])
+		plt.show()
+	# plt.plot(extract['zs_true_mis'][:,missed_wrong] - info['host_zs_random'][info['s_mis']][missed_wrong])
+	# plt.show()
+	print info['snIa'][info['s_mis']][missed_wrong]
+
+
+
+def group(N_sn, nspec):
+
+	for n in nspec:
+		[extract, info] = pickle.load(file('model'+int(n)+'.pkl','rb'))
+		plt.hist(extract['w'])
+		plt.show()
+
+
+def main(n_s):
+	individual(200,n_s)
+
+if __name__ == "__main__":
+    main(100)

### 2015-08-08 src/des.py

@@ -146,11 +146,14 @@ def main():
 	for ns in nspec:
 		data, init, info = genData(N_sn,ns,Nchains,1)
 
-		fit = sm.sampling(data=data, iter=100000, thin=100, warmup = 500, chains=Nchains, init=init)
+		fit = sm.sampling(data=data, iter=1000,  chains=Nchains, init=init)
 		samples = fit.extract(['Omega_M','zs_true_mis','w'])
 
+		logposterior = fit.get_logposterior()
+
 		with open('model'+str(ns)+'.pkl', 'wb') as f:
-			pickle.dump([fit.extract(),info], f)
+			pickle.dump([fit.extract(),info, logposterior], f)
+
 
 if __name__ == "__main__":
     main()

### 2015-08-08 src/des.py
runs with refactoring to ainv. But in input galaxy probability should be logit

@@ -56,8 +56,8 @@ def genData(N_sn, N_s_obs, Ninit, seed):
 	host_zs_random=[]
 	for i in xrange(N_sn):
 		ans=[]
-		ans.append(numpy.array([host_zs_random_[i],0.98]))
-		ans.append(numpy.array([neighbor_zs_random_[i],0.02]))
+		ans.append(numpy.array([host_zs_random_[i],numpy.log(0.98/(1-0.98)]))
+		ans.append(numpy.array([neighbor_zs_random_[i],numpy.log(0.02/(1-0.02)]))
 		host_zs_random.append(ans)
 
 	# s_obs_random : order in which supernovae get a spectrum
@@ -90,7 +90,9 @@ def genData(N_sn, N_s_obs, Ninit, seed):
 			'snIa_obs': snIa[s_obs],
 
 			'host_zs_obs': host_zs_obs, #zs[s_obs],
-			'host_zs_mis_': host_zs_mis.flatten()
+			'host_zs_mis_': host_zs_mis.flatten(),
+
+			'n_int': 50
 			}
 
 	init=[]
@@ -114,8 +116,8 @@ def genData(N_sn, N_s_obs, Ninit, seed):
 			'Omega_M':numpy.random.normal(omega_M,0.1),
 			'Omega_L':1-omega_M,
 			'w': numpy.random.normal(-0.9,0.1),
-			'zs_true_obs': zs[s_obs],
-		  	'zs_true_mis': numpy.random.uniform((1+zmin/1.5)**3,(1+zmax*1.5)**3,size=N_sn-N_s_obs)**(1./3)-1, #host_zs_mis_init,
+			'ainv_true_obs': 1+zs[s_obs],
+		  	'ainv_true_mis': numpy.random.uniform((1+zmin/1.5)**3,(1+zmax*1.5)**3,size=N_sn-N_s_obs)**(1./3), #host_zs_mis_init,
 		  	'alpha_Ia': numpy.random.normal(alpha_snIa,0.1),
 		 	'alpha_nonIa': numpy.random.normal(alpha_nonIa,0.1),
 		  	'sigma_Ia': numpy.random.normal(sigma_snIa,0.05),
@@ -147,7 +149,7 @@ def main():
 		data, init, info = genData(N_sn,ns,Nchains,1)
 
 		fit = sm.sampling(data=data, iter=1000,  chains=Nchains, init=init)
-		samples = fit.extract(['Omega_M','zs_true_mis','w'])
[…]

### 2015-08-08 src/analyze.py
fixes

@@ -14,20 +14,24 @@ import des
 def individual(N_sn, N_s):
 	[extract, info, logposterior] = pickle.load(file('model'+str(N_s)+'.pkl','rb'))
 
-	plt.plot(logposterior[0][200:])
-	plt.plot(logposterior[1][200:])
-	plt.plot(logposterior[2][200:])
-	plt.plot(logposterior[3][200:])
+	plt.plot(logposterior[0][200:],label=0)
+	plt.plot(logposterior[1][200:],label=1)
+	plt.plot(logposterior[2][200:],label=2)
+	plt.plot(logposterior[3][200:],label=3)
+	plt.legend()
 	plt.show()
 	# plt.plot(extract['w'])
 	# plt.show()
 	# plt.hist(extract['w'])
 	# plt.show()
 
+	plt.plot(extract['w'])
+	plt.show()
+
 	missed_wrong = info['host_choice'][info['s_mis']] == 0
 	print missed_wrong.sum()
-	if missed_wrong.sum !=0:
-		plt.plot(extract['zs_true_mis'][:,missed_wrong] - info['zs'][info['s_mis']][missed_wrong])
+	if missed_wrong.sum() !=0:
+		plt.plot(extract['ainv_true_mis'][:,missed_wrong] - info['zs'][info['s_mis']][missed_wrong])
 		plt.show()
 	# plt.plot(extract['zs_true_mis'][:,missed_wrong] - info['host_zs_random'][info['s_mis']][missed_wrong])
 	# plt.show()
@@ -47,4 +51,4 @@ def main(n_s):
 	individual(200,n_s)
 
 if __name__ == "__main__":
-    main(100)
+    main(200)

### 2015-08-08 src/des.py

@@ -56,8 +56,8 @@ def genData(N_sn, N_s_obs, Ninit, seed):
 	host_zs_random=[]
 	for i in xrange(N_sn):
 		ans=[]
-		ans.append(numpy.array([host_zs_random_[i],numpy.log(0.98/(1-0.98)]))
-		ans.append(numpy.array([neighbor_zs_random_[i],numpy.log(0.02/(1-0.02)]))
+		ans.append(numpy.array([host_zs_random_[i],numpy.log(0.98/(1-0.98))]))  #logit
+		ans.append(numpy.array([neighbor_zs_random_[i],numpy.log(0.02/(1-0.02))]))
 		host_zs_random.append(ans)
 
 	# s_obs_random : order in which supernovae get a spectrum
@@ -142,7 +142,7 @@ def main():
 
 	sm = pystan.StanModel(file='des.stan')
 
-	nspec = numpy.arange(100,N_sn+1,250)
+	nspec = numpy.arange(200,N_sn+1,250)
 	mn=[]
 	std=[]
 	for ns in nspec:

### 2015-08-09 src/analyze.py
redo galaxy stuff.  Put things into local variablees

@@ -51,4 +51,4 @@ def main(n_s):
 	individual(200,n_s)
 
 if __name__ == "__main__":
-    main(200)
+    main(100)

### 2015-08-09 src/des.py

@@ -1,7 +1,7 @@
 #!/usr/bin/env python
 
 import matplotlib
-#matplotlib.use('Agg')
+matplotlib.use('Agg')
 import matplotlib.pyplot as plt
 
 import pystan
@@ -46,19 +46,12 @@ def genData(N_sn, N_s_obs, Ninit, seed):
 	# host_choice : 1 if correct host is chosen to have highest probability, 0 otherwise
 	host_choice = numpy.random.binomial(1,0.98,size=N_sn)
 	neighbor_zs=numpy.random.uniform((1+zmin/1.5)**3,(1+zmax*1.5)**3,size=N_sn)**(1./3)-1
-	host_zs_random_ = zs*host_choice + neighbor_zs*(1-host_choice)
-	neighbor_zs_random_ = zs*(1-host_choice) + neighbor_zs*host_choice
+	host_zs_random = zs*host_choice + neighbor_zs*(1-host_choice)
+	neighbor_zs_random = zs*(1-host_choice) + neighbor_zs*host_choice
 	# wrong_host_zs : indeces if incorrect host galaxy association
 	#wrong_host_zs = host_zs_random_ == 0
 	#host_zs_random_[wrong_host_zs] = 
 
-	# host_zs_random : redshifts of potential host galaxies with the probability of each
-	host_zs_random=[]
-	for i in xrange(N_sn):
-		ans=[]
-		ans.append(numpy.array([host_zs_random_[i],numpy.log(0.98/(1-0.98))]))  #logit
-		ans.append(numpy.array([neighbor_zs_random_[i],numpy.log(0.02/(1-0.02))]))
-		host_zs_random.append(ans)
 
 	# s_obs_random : order in which supernovae get a spectrum
 	s_obs_random = numpy.arange(N_sn,dtype='int')
@@ -66,14 +59,6 @@ def genData(N_sn, N_s_obs, Ninit, seed):
 	s_obs = numpy.sort(s_obs_random[:N_s_obs]).tolist()
 	s_mis = numpy.sort(s_obs_random[N_s_obs:]).tolist()
 
-	host_zs_obs=[]
-	for i in xrange(len(s_obs)):
-		host_zs_obs.append(host_zs_random[s_obs[i]])
-	host_zs_mis=[]
-	for i in xrange(len(s_mis)):
[…]

### 2015-08-09 src/des.py
vectorize the ADU of SNe typed by spectra

@@ -71,13 +71,14 @@ def genData(N_sn, N_s_obs, Ninit, seed):
 			'adu_obs': adu[s_obs,None],
 			'adu_mis': adu[s_mis,None],
 
-			'trans_zs_obs': zs[s_obs],
+			'trans_ainv_obs': 1+zs[s_obs],
 			'snIa_obs': snIa[s_obs],
 
 			'host_zs_obs': host_zs_random[s_obs], #zs[s_obs],
 			'host_zs_mis': host_zs_random[s_mis],
 
-			'n_int': 50
+			'n_int': 25,
+			'N_SNIa': snIa[s_obs].sum()
 			}
 
 	init=[]
@@ -97,6 +98,7 @@ def genData(N_sn, N_s_obs, Ninit, seed):
 #		host_zs_mis_init = host_zs_random[s_mis]*numpy.random.binomial(1,0.98,size=len(s_mis))
 #		wrong_host_zs_init = host_zs_mis_init == 0
 #		host_zs_mis_init[wrong_host_zs_init] = numpy.random.uniform(zmin/1.5,zmax*1.5,size=wrong_host_zs_init.sum())
+		rate = numpy.random.lognormal(numpy.log(frac_Ia),0.1)
 		init.append ( {
 			'Omega_M':numpy.random.normal(omega_M,0.1),
 			'Omega_L':1-omega_M,
@@ -107,7 +109,7 @@ def genData(N_sn, N_s_obs, Ninit, seed):
 		 	'alpha_nonIa': numpy.random.normal(alpha_nonIa,0.1),
 		  	'sigma_Ia': numpy.random.normal(sigma_snIa,0.05),
 		  	'sigma_nonIa':numpy.random.normal(sigma_nonIa,0.5),
-		  	'snIa_rate':numpy.random.lognormal(numpy.log(frac_Ia),0.1)
+		  	'snIa_rate': [rate,1-rate]
 			} )
 
 	info = {

### 2015-08-11 src/analyze.py
a stable (?) version

@@ -20,6 +20,7 @@ def individual(N_sn, N_s):
 	plt.plot(logposterior[3][200:],label=3)
 	plt.legend()
 	plt.show()
+
 	# plt.plot(extract['w'])
 	# plt.show()
 	# plt.hist(extract['w'])
@@ -29,9 +30,8 @@ def individual(N_sn, N_s):
 	plt.show()
 
 	missed_wrong = info['host_choice'][info['s_mis']] == 0
-	print missed_wrong.sum()
 	if missed_wrong.sum() !=0:
-		plt.plot(extract['ainv_true_mis'][:,missed_wrong] - info['zs'][info['s_mis']][missed_wrong])
+		plt.plot(extract['ainv_true_mis'][:,missed_wrong] - info['zs'][info['s_mis']][missed_wrong]-1)
 		plt.show()
 	# plt.plot(extract['zs_true_mis'][:,missed_wrong] - info['host_zs_random'][info['s_mis']][missed_wrong])
 	# plt.show()
@@ -48,7 +48,7 @@ def group(N_sn, nspec):
 
 
 def main(n_s):
-	individual(200,n_s)
+	individual(150,n_s)
 
 if __name__ == "__main__":
     main(100)

### 2015-08-11 src/des.py

@@ -25,7 +25,7 @@ def genData(N_sn, N_s_obs, Ninit, seed):
 	sigma_nonIa=1
 
 	alpha_snIa=2.
-	alpha_nonIa=1.
+	alpha_nonIa=alpha_snIa*10**(-2./2.5)
 	frac_Ia=.8
 
 	# zs : the true redshifts
@@ -104,7 +104,7 @@ def genData(N_sn, N_s_obs, Ninit, seed):
 			'Omega_L':1-omega_M,
 			'w': numpy.random.normal(-0.9,0.1),
 			'ainv_true_obs': 1+zs[s_obs],
-		  	'ainv_true_mis': 1+host_zs_random[s_mis], #host_zs_mis_init,
+		  	'ainv_true_mis': (i % 2)*(1+host_zs_random[s_mis]) + (1-(i%2))*(1+zs[s_mis]), #host_zs_mis_init,
 		  	'alpha_Ia': numpy.random.normal(alpha_snIa,0.1),
 		 	'alpha_nonIa': numpy.random.normal(alpha_nonIa,0.1),
 		  	'sigma_Ia': numpy.random.normal(sigma_snIa,0.05),
@@ -135,7 +135,7 @@ def main():
 	for ns in nspec:
 		data, init, info = genData(N_sn,ns,Nchains,1)
 
-		fit = sm.sampling(data=data, iter=1000, thin=1, chains=Nchains, init=init)
+		fit = sm.sampling(data=data, iter=10000, thin=10, chains=Nchains, init=init)
 		print fit
 		samples = fit.extract(['Omega_M','ainv_true_mis','w'])
 

### 2015-08-12 doc/model.tex
brushing up document

@@
 We infer a Hubble diagram based on measurements of discovered transients
-that have passed some selection criteria (e.g.\ classified as Type~Ia supernovae, SNe~Ia).  The probability distribution
-function (pdf) of the Hubble diagram is denoted as
+that have passed some selection criteria (e.g.\ classified as Type~Ia supernovae).  The posterior
+of the Hubble diagram is denoted as
 \begin{equation}
@@
 The set of distance moduli
-and redshifts $(\mu, z)$ contains the points that constitute the Hubble diagram.  The available information
+and redshifts $(\mu, z)$ contains the points that constitute the Hubble diagram.  The
+data
 from which the Hubble diagram is inferred include:
@@
 host-galaxy parameter measurements $\theta_H$ (including redshift,
-mass, sSFR, etc.).  Only a subset of all detected transients enter the cosmology
-analysis: the sample-selection criterion is denoted as $\tau$.  For example
-$\tau$ could be the classification score of PSNID.
+mass, sSFR, etc.).  
+The subset transients that enter the cosmology
+analysis is based on the sample-selection criteria $\tau$: for example
+the classification score from PSNID (a classifier based on multi-band
+light curves).
+
+The posterior of $\mu$ and $z$ is an efficient way
+to distribute supernova results in is a way that is independent of cosmological model,
+facilitating joint-probe analysis or consideration of non-standard models.  Choosing
+a specific cosmological model, the posterior of the model parameters $\theta_\mu$
+is of interest.  The model presented here accommodates both options.
 
@@
 shown in Figure~\ref{pgm:fig}.
-Note that although we have been discussing the model for the Hubble diagram, the same PGM can
-also expresses the pdf for cosmological
-parameters, labelled as $\theta_\mu$.
+The fundamental parameters are those with no incoming arrows;  most are
+used to model the universe: 
+the background cosmology, transients that could enter the sample, and their host galaxies.
+\begin{itemize}
+\item  $g$ labels the  galaxy that hosts the transient.
+\item $\theta_\mu$ are the parameters that specify that distance modulus.  They could
+be the parameters of a specific cosmological
+parameters, or an empirical model independent of physics.
+\item $\theta_\tau$ govern the relative rates of supernovae of different types in galaxies.
+\item $\theta_T^{Ia}$, $\theta_{Ti}^{Ia}$.  The model parameters for SNe~Ia, including
+parameters that describe distributions.
+Different SN~Ia models could be considered.  The treatment of SALT2
+has been presented in \citet{2011MNRAS.418.2308M}:
+in this model each supernova
+has individual $c$ and $x_1$ parameters that constitute $\theta_{Ti}^{Ia}$;
+global SN~Ia properties
+$\alpha$, $\beta$, $\sigma_{int}$ 
+ and  underlying  $c$ and $x_1$ distributions   constitute $\theta_T^{Ia}$.
+\item $\theta_T^{\mathit{non-Ia}}$, $\theta_{Ti}^{\mathit{non-Ia}}$.  False-positive non-Ia transients
+that enter the analysis are described by a parameterized model.
+\item The transmission functions $\phi(\lambda)$ describe the optical path from the
+atmosphere to counts.  Calibration solutions are generally provided
+but are included in Figure~\ref{pgm:fig} to encompass the case of self-calibration.
+\end{itemize}
 
@@
    and galaxy parameters $\theta_{gi}$.
-   A distance modulus model with parameters $\theta_\mu$ fix the distance modulus $\mu_i$.
+   A model with parameters $\theta_\mu$ fix the distance modulus $\mu_i$.
    The transient type $T$ depends on the host-galaxy parameters  $\theta_{gi}$
@@
    through $\tau_i$ to be included in the sample.  Some transients have spectral data
-   ${X}_S$.
+   ${X}_S$.  The properties of the galaxy identified as the host galaxy is $\theta_G$. 
    \label{pgm:fig}}
 \end{figure}
-
-The fundamental parameters that need to be determined are those with no incoming arrows in Figure~\ref{pgm:fig}.  Most all are used to model the universe: 
-the background cosmology, transients that could enter the sample, and their host galaxies.
-\begin{itemize}
-\item  $g_i$ labels the distinct galaxy that hosts the transient.
-\item $\theta_\mu$ are the parameters that specify that distance modulus, e.g.\ the cosmological
-parameters.
-\item $\theta_\tau$ govern the relative rates of supernovae of different types in galaxies.
-\item $\theta_T^{Ia}$, $\theta_{Ti}^{Ia}$.  The model parameters for SNe~Ia, including
-parameters that describe distributions.
-Different SN~Ia models could be considered: the treatment of SALT2 parameters
-has been presented in \citet{2011MNRAS.418.2308M}.
-The SALT2 SN~Ia
-model has individual $c$ and $x_1$ parameters that would constitute $\theta_{Ti}^{Ia}$,
-and global $\alpha$, $\beta$, and intrinsic dispersion  parameters  common to all supernovae
- and  underlying  $c$ and $x_1$ distributions that would constitute $\theta_T^{Ia}$.
-\item $\theta_T^{non-Ia}$, $\theta_{Ti}^{non-Ia}$.  Non-Ia transients
-that can be mistyped as Ia are described by a parameterized model.
-\item The transmission functions $\phi(\lambda)$ describe the optical path from the
-atmosphere to counts.  We expect
-the calibration group to provide us with the functions and covariance $\phi \sim \mathcal{N}(\bar{\phi},C_\phi)$, in which case it would not have to be determined as part
-of our analysis.    There is a chance that we will want to determine calibration ourselves,
-so it is included in Figure~\ref{pgm:fig}.
-\end{itemize}
 
@@
 \item $\mu_i=\mu(z_i; \theta_\mu)$.  The distance modulus is a function of redshift,
-whose specific form is unspecified at the moment,  it could
+Unspecified at the moment,  it could
 be a $\Lambda$CDM prediction with cosmological parameters, a spline with knot values
 as parameters.
-The redshift of the galaxy is used in the Hubble diagram.
+The redshift of the galaxy is used in the Hubble diagram, peculiar velocities are not considered.
 \item $P(T_i | \theta_r, \theta_{gi})$.  The transient type $T_i$, SN~Ia or non-Ia, depends
-on the relative rates given the host properties.  Note that the type is probabilistic.
-\item $P(L_i(t,\lambda)| T_i, \theta_T^{Ia}, \theta_{Ti}^{Ia}, \theta_T^{non-Ia}, \theta_{Ti}^{non-Ia},
+on the relative rates given the host properties.
+\item $P(L_i(t,\lambda)| T_i, \theta_T^{Ia}, \theta_{Ti}^{Ia}, \theta_T^{\mathit{non-Ia}}, \theta_{Ti}^{\mathit{non-Ia}},
 \theta_{gi})$.  The source model determines
-the luminosity; often the model includes intrinsic dispersion making the luminosity
+the luminosity; the model may include intrinsic dispersion to make the luminosity
 probabilistic. The  model includes  information on the
@@
 are fixed by the luminosity, distance modulus, and redshift.
+The supernova redshift is required for this calculation,
+for simplicity the supernova and host-galaxy redshift are assumed to be equal.
 \item $\overline{\mathit{ADU}}$ and
@@
 \begin{itemize}
-\item ${\mathit{ADU}}$ is the realized flux. $P({\mathit{ADU}} | \overline{\mathit{ADU}}, 
-\overline{\mathit{ADU}}_g)$.
+\item ${\mathit{ADU}}$ is the realized flux.  It depends on the underlying flux and
+the photometric noise.
 \item $\theta_G$ represents the galaxy parameters of the
 galaxy catalog used to identify prospective host galaxies.
-The contribution to the likelihood $P(\theta_G|g_i)$ can be
-estimated as $P(g_i|\theta_G)\frac{P(\theta_G)}{P(z)}$: Ravi is determining $P(g_i|\theta_G)$.
-\item ${T}_S$, ${z}_S$, ${\theta}_S$ Transient type, redshift and properties from
-spectroscopic data. I skip the details of the actual measurement  and make a direct association
-with the fluxes of the transient and underlying galaxy $n$, $n_g$.
-A very simple association is ${T}_S = T$, ${z}_S=z$, ${\theta}_S \in \theta_g$,
-or a blurry version instead of a straight equality.
+\item ${T}_S$, ${z}_S$, ${\theta}_S$ are the transient type, redshift and properties from
+spectroscopic data. Details of the actual measurement are ignored and a direct association
+is made with the fluxes of the transient and underlying galaxy $n$, $n_g$.
 \item $\tau$ is the score used to decide if the transient is used in the analysis.  It is
@@
 \end{itemize}
+
+%The likelihood for the model is
+%\begin{multline}
+%p(\mathit{ADU}, {{T}}_S,{{z}}_S,
+%{{\theta}}_S, \theta_G, \tau, Z | g, \theta_\mu, \theta_r, \theta_T^{Ia}, \theta_{Ti}^{Ia}, \theta_T^{non-Ia}, \theta_{Ti}^{non-Ia}, \phi) = \\
+%p(\theta_G|g)p(Z|\phi)p(\mathit{ADU}, {{T}}_S,{{z}}_S,
+%{{\theta}}_S, \tau | g, \theta_\mu, \theta_r, \theta_T^{Ia}, \theta_{Ti}^{Ia}, \theta_T^{non-Ia}, \theta_{Ti}^{non-Ia}, \phi).
+%\label{likelihood:eqn}
+%\end{multline}
+
+\section{Simple Example}
+\subsection{Model}
+A simplified version of the above model,
+\begin{equation}
+p(\mathit{ADU}, {{T}}_S,{{z}}_S, \theta_G| z, \Omega_M, w, \theta_r,\alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}}),
+\end{equation}
+is examined in this section.
+The measurements: 
+\begin{itemize}
+\item $\mathit{ADU}$ are measured counts at peak brightness.
+\item ${{T}}_S$, ${{z}}_S$ are spectroscopic type and redshift.
+\item $\theta_G$ is the redshift of the galaxy identified as the transient host.
+\end{itemize}
+The model parameters:
+\begin{itemize}
+\item $z$ is the cosmological redshift.
+\item $\Omega_M$, $w$ are the parameters of a flat dark-energy cosmology.
+\item $\theta_r$ is the fraction of transients that are SN~Ia, independent
+of host-galaxy properties and redshift.
+\item $\alpha_{Ia}$, $\sigma_{Ia}$, $\alpha_{\mathit{non-Ia}}$, $\sigma_{\mathit{non-Ia}}$ are
+the luminosity (times $4\pi$) and intrinsic dispersion for SNe~Ia and non-Ia at peak.
+Light-curve shape and color are not considered in this simple model.
+\end{itemize}
+
+The transients are divided into samples defined by available data: {\it obs} are transients observed spectroscopically while active, from which $T_S=1$ are those typed
+as SN~Ia and $T_S=0$ as non-Ia.  {\it mis} transients are not observed
+spectroscopically when active.
+
+\begin{itemize}
+\item All transients have measured counts at peak brightness $\mathit{ADU}$.
+For transients in set {\it mis} without active spectroscopy:
+\begin{multline}
+p(\mathit{ADU}| z, \Omega_M, w, \theta_r, \alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}})=\\
+\theta_r\mathcal{N}\left(\frac{\alpha_{Ia}}{d_L^2(z;\Omega_M, w)}, \frac{\ln{10}}{2.5}\sigma_{Ia}\right)+\left(1-\theta_r\right)
+\mathcal{N}\left(\frac{\alpha_{\mathit{non-Ia}}}{d_L^2(z;\Omega_M, w)}, \frac{\ln{10}}{2.5}\sigma_{\mathit{non-Ia}}\right).
+\end{multline}
+The luminosity distance $d_L$ is for a flat universe.  
+\item The transients of subset {\it obs} have spectroscopic observations of type $T_S$ and redshift
+$z_S$.
+\begin{itemize}
+\item A direct association of $z_S=z$ is made.
+\begin{equation}
+p(z_S|z) = \delta(z_S-z)
+\label{specz:eqn}
+\end{equation}
+\item For transients in set $T_S=1$:
+\begin{equation}
+p(\mathit{ADU}, T_S=1 | z, \Omega_M, w, \theta_r, \alpha_{Ia},\sigma_{Ia})=
+\theta_r\mathcal{N}\left(\frac{\alpha_{Ia}}{d_L^2(z;\Omega_M, w)}, \frac{\ln{10}}{2.5}\sigma_{Ia}\right).
+\end{equation}
+\item For transients in set $T_S=0$:
+\begin{multline}
+p(\mathit{ADU}, T_S=0 | z, \Omega_M, w, \theta_r, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}})= \\
+\left(1-\theta_r\right)
+\mathcal{N}\left(\frac{\alpha_{\mathit{non-Ia}}}{d_L^2(z;\Omega_M, w)}, \frac{\ln{10}}{2.5}\sigma_{\mathit{non-Ia}}\right).
+\end{multline}
+\end{itemize}
+\item All transients are associated with a host galaxy with spectroscopic redshift $\theta_G$,
+\begin{equation}
+p(\theta_G|z) =
+	P_{host} \ln{\mathcal{N}}(\theta_G;\ln(1+z),0.001) + (1-P_{host})\left(\frac{3 \theta_G^2}{z_{max}^3 - z_{min}^3}\right).
+\end{equation}
+The host is determined correctly with probability $P_{host}=0.98$ in which case the
+host redshift is determined from a log-normal distribution centered around the true redshift
+with 0.001 fractional uncertainty.   Otherwise the redshift is drawn from the ``uniform in volume'' term on the right.
+[Note: to speed the cacluation, I only consider host-galaxy measurements
+of the {\it mis} set.]
+\item This simple example does not consider data $\theta_S$, $\tau$ or $Z$, i.e.
+spectroscopic parameters, sample-selection effects, and calibration.
+\end{itemize}
+
+A prior is applied to the SN~Ia absolute magnitude
+\begin{equation}
+\alpha_{SNIa} \sim \ln\mathcal{N}\left(\ln\left(\alpha^0_{SNIa}\right),\frac{\ln{10}}{2.5}0.02\right),
+\end{equation}
+where $\alpha^0_{SNIa}$ is the true input luminosity.
+
+Note some of the choices for the distributions are driven by computational
+speed. 
+Also, Stan cannot handle discrete parameters and
+cannot except pdf's that support zero probability.
+
+\subsection{Analysis of Simulated Data}
+Simulated data is drawn from the above model with the following parameter
+choices:
+\begin{itemize}
+\item Cosmological parameters $\Omega_M=0.28$, $w=-1$.
+\item Type~Ia supernovae with intrinsic dispersion $\sigma_{Ia}=0.1$.
+\item Non-Ia supernovae 2 magnitudes fainter than SNe~Ia $\alpha_{\mathit{non-Ia}} = 10^{-2/2.5} \alpha_{Ia}$ with 
+ $\sigma_{\mathit{non-Ia}}=1$.
+\item $\theta_r=0.8$.
+\item 200 supernovae uniformly distributed in the range $0.1<z<1$.
+\item $z_{min}=0.05$ and $z_{max}=1.5$ used for the range of possible true redshifts.
+\end{itemize}
+From a realization of these data, spectroscopic follow-up is
+accumulated: analysis is performed at 50\%, 75\%, and 100\% 
+completeness.
 

### 2015-08-12 src/hd_pgm.py

@@ -35,7 +35,7 @@ pgm.add_node(Node('Spars',r"${T}_{Si}$, ${z}_{Si},{\theta}_{Si}$", 6, 4, scale=1
 #pgm.add_node(Node('^Host',r"${z}_{Hi},{\theta}_{Hi}$", 7, 2, scale=1.5,observed=True))
 
 #pgm.add_node(Node('Detected',r"Detected$_i$", 8, 3, fixed=True,offset=(-10,-20)))
-pgm.add_node(Node('^Type',r"$\tau_i$", 9, 2, observed=True))
+pgm.add_node(Node('^Type',r"$\tau_i$", 9, 2, fixed=True,offset=(10,-10)))
 
 pgm.add_node(Node('Gals',r"$\theta_G$", 6, 1, observed=True))
 

### 2015-08-15 doc/model.tex
making results of 50% run

@@
    \centering
-   \includegraphics[width=7in]{/Users/akim/project/abc/results/hdpgm.eps} 
+   \includegraphics[width=7in]{/Users/akim/project/abc/results/hdpgm.pdf} 
    \caption{Probabilistic Graphical Model for the SN~Ia analysis.  
@@
 as SN~Ia and $T_S=0$ as non-Ia.  {\it mis} transients are not observed
-spectroscopically when active.
+spectroscopically when active.  The same SN~Ia and non-Ia parameters are taken to
+apply to both {\it obs} and {\it mis} samples.
 
@@
 \end{equation}
-The host is determined correctly with probability $P_{host}=0.98$ in which case the
+The host is determined correctly with probability $P_{host}$ in which case the
 host redshift is determined from a log-normal distribution centered around the true redshift
@@
 \item $z_{min}=0.05$ and $z_{max}=1.5$ used for the range of possible true redshifts.
+\item $P_{host}=0.98$.
 \end{itemize}
@@
 completeness.
+
+The simulated data is analyzed using \citet{pystan-software:2015},
+the Python interface to
+\citet{stan-software:2015}, a probabilistic programming language for
+inference of Bayesian models with Hamiltonian Monte Carlo.  There are
+four chains run, each with 50,000 samples then thinned by 50.
+
+\subsubsection{50\% Spectroscopic Confirmation}
+Results for the $\Omega_M$--$w$ posterior for the
+case where 50\% of the transients have a direct spectrum
+are shown in Figure~\ref{contour.100:fig}.
+As will be discussed shortly, the Stan run does not result in a Markov Chain Monte Carlo
+that has
+converged to a stationary solution.  Nevertheless, the results are presented here
+in the hope that they will spark progress in producing robust posteriors or at the
+least provide an alert to the computational challenge of the analysis.
+Despite their dubious quality, we can be consoled that the distributions
+look similar to those of JLA \citep{2014A&A...568A..22B} 
+and so satisfy qualitative expectations.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[scale=0.6]{/Users/akim/project/abc/results/{contour.100}.pdf} 
+   \caption{Probability distribution function for $\Omega_M$--$w$  when 50\% of transients
+   get spectra while active.
+   Solid lines represent the input cosmology.  Dashed lines in the
+   histograms are the 0.16 and 0.86 quantiles. 
+   \label{contour.100:fig}}
+\end{figure}
+
+A transient
+without a spectrum has uncertain type and uncertain redshift: the redshift
+of the associated host galaxy, and redshifts associated with SNe~Ia and non-Ia's
+at the observed magnitude, are viable but disjoint possibilities.  The initial condition
+for redshifts of transients without an active spectrum is near the true redshift
+for chains 0 and 2, and near the host redshift in chains 1 and 3.
+
+Figure~\ref{missed_wrong.100:fig} shows draws
+for the redshift parameter for two transients: one is Type~Ia and the other is
+non-Ia, neither have a spectrum and both have an incorrect host galaxy association.
+The SN~Ia is placed at $z=0.95$ but is misassociated with a galaxy at
+$z=1.24$.  The posterior shows a preference for the input redshift, but as the analyzer
+must entertain the possibility it is non-Ia the posterior sometimes
+goes to lower redshifts. Although two of the chains start near the incorrect-host redshift,
+there are no such redshifts drawn.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[scale=0.6]{/Users/akim/project/abc/results/{missed_wrong.100}.pdf} 
+   \caption{Redshift posterior for a Type~Ia and a non-Ia that were not observed
+   spectroscopically and for whom the host-galaxy is misassociated.
+   The results of the four chains are
+   placed in sequence.   \label{missed_wrong.100:fig}}
+\end{figure}
+
+The non-Ia is placed at $z=0.39$ and is misassociated with a galaxy at $z=0.48$.
+Three of the four chains stay in the neighborhood of the incorrect-host redshift.
+Chain 2, whose initial condition was at the true redshift, also accepts redshift solutions as
+if were a Type~Ia.  Clearly this chain does not mix with the others.
+
+Figure~\ref{posterior.100:fig} shows the log-posteriors and histograms of
+the $w$-draws from Chain 2 compared to the others.
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[scale=0.5]{/Users/akim/project/abc/results/{posterior.100}.pdf} 
+   \includegraphics[scale=0.5]{/Users/akim/project/abc/results/{wsub.100}.pdf} 
+   \caption{Log-posterior and $w$-draws from  Chain 2 compared to the others.  \label{posterior.100:fig}}
+\end{figure}
 
@@
 %
-%
-%\subsection{Type~Ia Supernova Model}
-%\label{snmodel:sec}
-%The DES light curve analysis in principle may be used for typing and determining
-%redshift, in addition to getting supernova properties.   
-%Generally the relevant term is
-%\begin{equation}
-%P({D}_i=1,{\mathit{ADU}}_{i}, {T}_{Si}, {z}_{Si}, {\theta}_{Si}, {z}_{Hi}, {\theta}_{Hi}
-% | \mu_i,z_i,T_i,\theta_T,\theta_{Ti},\phi(\lambda)).
-% \end{equation}
-%Detection and typing depend on the realized light curves, and hence the truncated
-%distribution of discovered transients typed as SN~Ia.
-%
-%The model contains a piece $P({\mathit{ADU}}_{i} {z}_{Si}| \mu_i,z_i,\theta_T, \theta_{Ti}, ,\phi(\lambda))$, which
-%is the piece that describes underlying SN~Ia properties and light-curve fits.
-%
-%
-%\subsection{Detection Efficiency}
-%There term $P({D}|\mathit{ADU}_V)$.  For all high-redshift supernova searches
-%I know of, this depends on the signal-to-noise of the data, and very weakly on the
-%structure of the underlying galaxy.  Our detection is now based on machine learning,
-%we should confirm that detection dependencies do not depend on our model parameters
-%(except for RA/Dec).
-%
 %\section{Systematic Tests}
@@
 %
-%\section{Misc.}
-%DES plans a ``photometry''-only analysis, in that a significant subset of transients used
-%in the Hubble diagram will not observed spectroscopically while active.  Therefore,
-%our model must account for transient mistyping and host-galaxy mismatches.  To obtain
-%our targeted
-%accuracy we need to account for covariances that occur due to photometric
-%calibration and Malmquist bias.  Our model will contain elements that may not
-%have been included in previous analyses. 
 %
@@
 %that are mistaken for Ia and not all discovered transients.
-%
-%
-%
-%Here $\mu$ is modeled; most analyses instead
-%directly have cosmological parameters $\{\Omega_M, \Omega_\Lambda, w_0, w_a\}$.
-%A motivation is to provide results that can be applied to test arbitrary cosmological models:
-%indeed the model-dependence of the $\mu$'s reported for high-$z$ supernovae 
-%\citep[e.g.][]{2012ApJ...746...85S} is a source of confusion to the community.
-%%An example of a non-parametric model for $\mu$ that is independent of cosmological
-%%parameters is given in the Appendix of
-%%\citet{2013ApJ...764..116W}.
-%
+
 \bibliography{/Users/akim/Documents/alex}

### 2015-08-15 src/analyze.py

@@ -1,7 +1,7 @@
 #!/usr/bin/env python
 
 import matplotlib
-#matplotlib.use('Agg')
+matplotlib.use('Agg')
 import matplotlib.pyplot as plt
 
 import pystan
@@ -11,35 +11,69 @@ from astropy.cosmology import FlatLambdaCDM
 import pickle
 import des
 
-def individual(N_sn, N_s):
-	[extract, info, logposterior] = pickle.load(file('model'+str(N_s)+'.pkl','rb'))
+import triangle
 
-	plt.plot(logposterior[0][200:],label=0)
-	plt.plot(logposterior[1][200:],label=1)
-	plt.plot(logposterior[2][200:],label=2)
-	plt.plot(logposterior[3][200:],label=3)
-	plt.legend()
-	plt.show()
+def individual(N_s):
+	[extract, info, logposterior] = pickle.load(file('../results/model'+str(N_s)+'.pkl','rb'))
+
+	n_samples = len(extract[extract.keys()[0]])
+	samples=numpy.zeros((n_samples,2))
+	samples[:,0] = extract['Omega_M']
+	samples[:,1] = extract['w']
+	figure = triangle.corner(samples, labels=[r"$\Omega_M$", r"$w$"],truths=[0.28,-1],
+		quantiles=[0.16, 0.5, 0.84], plot_datapoints=False,plot_density=True)
+	plt.savefig('../results/contour.'+str(N_s)+'.pdf')
+	plt.clf()
+
+	matplotlib.rcParams.update(matplotlib.rcParamsDefault)
+
+	plt.plot(logposterior[0][500:],label=0)
+	plt.plot(logposterior[1][500:],label=1)
+	plt.plot(logposterior[2][500:],label=2)
+	plt.plot(logposterior[3][500:],label=3)
+	plt.ylabel('log-posterior')
+	plt.xlabel('link')
+	plt.legend(loc=3,prop={'size':9})
+	plt.savefig('../results/posterior.'+str(N_s)+'.pdf')
+	plt.clf()
 
 	# plt.plot(extract['w'])
 	# plt.show()
-	# plt.hist(extract['w'])
-	# plt.show()
 
-	plt.plot(extract['w'])
-	plt.show()
+	plt.hist(extract['w'],normed=True)
+	plt.xlabel(r'$w$')
+	plt.legend(loc=2)
+	plt.tight_layout()
[…]

### 2015-08-15 src/des.py

@@ -129,19 +129,19 @@ def main():
 
 	sm = pystan.StanModel(file='des.stan')
 
-	nspec = numpy.arange(100,N_sn+1,250)
+	nspec = numpy.arange(100,N_sn+1,50)
 	mn=[]
 	std=[]
 	for ns in nspec:
 		data, init, info = genData(N_sn,ns,Nchains,1)
 
-		fit = sm.sampling(data=data, iter=10000, thin=10, chains=Nchains, init=init)
+		fit = sm.sampling(data=data, iter=50000, thin=50, chains=Nchains, init=init)
 		print fit
-		samples = fit.extract(['Omega_M','ainv_true_mis','w'])
+		#samples = fit.extract(['Omega_M','ainv_true_mis','w'])
 
 		logposterior = fit.get_logposterior()
 
-		with open('model'+str(ns)+'.pkl', 'wb') as f:
+		with open('../results/model'+str(ns)+'.pkl', 'wb') as f:
 			pickle.dump([fit.extract(),info, logposterior], f)
 
 

### 2015-08-15 src/hd_pgm.py

@@ -2,7 +2,7 @@
 
 from matplotlib import rc
 from daft import PGM, Node, Plate
-rc("font", family="serif", size=10)
+rc("font", family="serif", size=12)
 rc("text", usetex=True)
 
 
@@ -111,4 +111,4 @@ pgm.render()
 # pgm.figure.text(0.45,0.98,r'\underline{OBSERVATORY}',size='large')
 # pgm.figure.text(0.72,0.98,r'\underline{DATA}',size='large')
 
-pgm.figure.savefig("../results/hdpgm.eps")
+pgm.figure.savefig("../results/hdpgm.pdf")

### 2015-08-19 doc/model.tex
stable before making change to model.

@@
 \subsection{Model}
+\label{example:sec}
 A simplified version of the above model,
@@
 \item $\mathit{ADU}$ are measured counts at peak brightness.
-\item ${{T}}_S$, ${{z}}_S$ are spectroscopic type and redshift.
+\item ${{T}}_S$, ${{z}}_S$ are spectroscopic type and redshift for a subset of transients.
 \item $\theta_G$ is the redshift of the galaxy identified as the transient host.
@@
 \item The transients of subset {\it obs} have spectroscopic observations of type $T_S$ and redshift
-$z_S$.
+$z_S$, which are taken to be unambiguous.
 \begin{itemize}
@@
 \subsection{Analysis of Simulated Data}
-Simulated data is drawn from the above model with the following parameter
+The simulation of data from the model presented in \S\ref{example:sec}
+and their analysis is implemented in Python and are available
+on GitHub\footnote{\url{git@github.com:AlexGKim/abc.git}}.
+
+The results that follow are based on the parameter
 choices:
@@
 \item Cosmological parameters $\Omega_M=0.28$, $w=-1$.
-\item Type~Ia supernovae with intrinsic dispersion $\sigma_{Ia}=0.1$.
-\item Non-Ia supernovae 2 magnitudes fainter than SNe~Ia $\alpha_{\mathit{non-Ia}} = 10^{-2/2.5} \alpha_{Ia}$ with 
- $\sigma_{\mathit{non-Ia}}=1$.
-\item $\theta_r=0.8$.
+\item Type~Ia supernovae with intrinsic dispersion $\sigma_{SNIa}=0.1$.
+\item Non-Ia supernovae 2 magnitudes fainter than SNe~Ia with intrinsic
+dispersion $\sigma_{non-Ia}=1$.
+\item $\theta_r=0.8$ for a constant relative fraction of SNe~Ia.
 \item 200 supernovae uniformly distributed in the range $0.1<z<1$.
-\item $z_{min}=0.05$ and $z_{max}=1.5$ used for the range of possible true redshifts.
-\item $P_{host}=0.98$.
+\item $z_{min}=0.05$ and $z_{max}=1.5$ is the range of possible true redshifts.
+\item $P_{host}=0.98$ for the probability of correct host-galaxy assignment.
+\item Accumulated spectra at 50\%, 75\%, and 100\% spectroscopic
+completeness.
 \end{itemize}
-From a realization of these data, spectroscopic follow-up is
-accumulated: analysis is performed at 50\%, 75\%, and 100\% 
-completeness.
 
-The simulated data is analyzed using \citet{pystan-software:2015},
-the Python interface to
-\citet{stan-software:2015}, a probabilistic programming language for
+The simulated data are analyzed using 
+\citet{stan-software:2015}, a
+a probabilistic programming language for
 inference of Bayesian models with Hamiltonian Monte Carlo.  There are
-four chains run, each with 50,000 samples then thinned by 50.
+four chains run, each with 50,000 samples then thinned by 50.  Half the links
+are used for burnin, so ultimately 2000 links are used as draws from the posterior.
+It took 2 days tor produce these results on my MacBook Air.  One chain, \#2
+in the 50\% run,  took the bulk of the time; presumably a different integration step size
+was determined during warmup.  As shown shortly, this chain samples
+a broader range of parameter space.
 
-\subsubsection{50\% Spectroscopic Confirmation}
-Results for the $\Omega_M$--$w$ posterior for the
-case where 50\% of the transients have a direct spectrum
-are shown in Figure~\ref{contour.100:fig}.
-As will be discussed shortly, the Stan run does not result in a Markov Chain Monte Carlo
-that has
-converged to a stationary solution.  Nevertheless, the results are presented here
-in the hope that they will spark progress in producing robust posteriors or at the
-least provide an alert to the computational challenge of the analysis.
-Despite their dubious quality, we can be consoled that the distributions
-look similar to those of JLA \citep{2014A&A...568A..22B} 
+\subsubsection{SN~Ia Only}
+A classical analysis would only include confirmed SNe~Ia with a definitive
+redshift. The realization of simulated data has 156 Type~Ia supernovae.
+Results of the analysis of a pure SN~Ia sample with no
+host misclassification are presented:  Figure~\ref{contour.100:fig}
+shows the posteriors for  $\Omega_M$--$w$ and Table~\ref{ia_only:tab} the
+credible equal-tailed intervals for $w$.  (Note that $w$ is the parameter
+of most interest for the experiment.)
+The distributions
+look similar to the latest results from real data \citep{2014A&A...568A..22B} 
 and so satisfy qualitative expectations.
@@
    \centering
-   \includegraphics[scale=0.6]{/Users/akim/project/abc/results/{contour.100}.pdf} 
-   \caption{Probability distribution function for $\Omega_M$--$w$  when 50\% of transients
-   get spectra while active.
+   \includegraphics[scale=0.55]{/Users/akim/project/abc/results/{contour..ia_only.200}.pdf} \newline
+   \includegraphics[scale=0.55]{/Users/akim/project/abc/results/{contour.100}.pdf} 
+   \includegraphics[scale=0.55]{/Users/akim/project/abc/results/{contour.200}.pdf}    \caption{Probability distribution function for $\Omega_M$--$w$ for: 156 SNe~Ia
+   with spectra (top);  SNe~Ia and non-Ia with 50\% (left),
+   and 100\% (right)  spectroscopic completeness.
    Solid lines represent the input cosmology.  Dashed lines in the
@@
 
+\begin{table}
+\centering
+\begin{tabular}{|c|cc|}
+\hline
+\%-ile & $w$ range & $\Delta$\\ \hline
+$0.68$ & $[-1.038, -0.648]$ & $0.389$ \\
+$0.90$ & $[-1.204, -0.577]$ & $0.627$ \\
+$0.95$ & $[-1.269, -0.556]$ & $0.713$ \\
+\hline
+\end{tabular}
+\caption{Credible intervals of $w$ using the 156 SNe~Ia only with spectroscopic
+observations.\label{ia_only:tab}}
+\end{table}
+
+\subsubsection{Full Sample: 50\% Spectroscopic Confirmation}
+We now turn to the full sample of SNe~Ia and non-Ia's.  Recall that our simple
+model treats the non-Ia's in the sample
+as standard candles with a large (1 mag) intrinsic dispersion.
+
+Results for the $\Omega_M$--$w$ posterior for the
+case of 50\% spectroscopic completeness
+are shown in Figure~\ref{contour.100:fig}.
+As will be discussed shortly, the Stan run does not result in a Markov Chain Monte Carlo
+that has
+converged to a stationary solution.
+
 A transient
-without a spectrum has uncertain type and uncertain redshift: the redshift
-of the associated host galaxy, and redshifts associated with SNe~Ia and non-Ia's
-at the observed magnitude, are viable but disjoint possibilities.  The initial condition
-for redshifts of transients without an active spectrum is near the true redshift
-for chains 0 and 2, and near the host redshift in chains 1 and 3.
+without a spectrum has uncertain type and redshift: the redshift
+of the associated host galaxy, and redshifts expected based on the
+flux of the SN~Ia and non-Ia standard candles,
+are viable but disjoint possibilities for the posterior of
+the true underlying redshift.  To test the mixing of the chains,
+the initial conditions 
+for redshifts of transients without an active spectrum are
+selected to be near local optima: the true redshift
+for chains 0 and 2 and near the host redshift in chains 1 and 3.
 
+Two objects, one Type~Ia and the other
+non-Ia, are assigned incorrect redshifts (recall 50\% do not have
+an active spectrum and the 98\% host misclassification rate).
 Figure~\ref{missed_wrong.100:fig} shows draws
-for the redshift parameter for two transients: one is Type~Ia and the other is
-non-Ia, neither have a spectrum and both have an incorrect host galaxy association.
+for the redshift parameter for these two transients.
 The SN~Ia is placed at $z=0.95$ but is misassociated with a galaxy at
-$z=1.24$.  The posterior shows a preference for the input redshift, but as the analyzer
-must entertain the possibility it is non-Ia the posterior sometimes
-goes to lower redshifts. Although two of the chains start near the incorrect-host redshift,
-there are no such redshifts drawn.
+$z=1.24$.  The posterior shows a preference for the correct redshift, but sometimes
+drops to lower redshifts as if it were a non-Ia. Although two of the chains start near the incorrect-host redshift, they do not return to that area of parameter space after burnin.
 
@@
    \centering
-   \includegraphics[scale=0.6]{/Users/akim/project/abc/results/{missed_wrong.100}.pdf} 
-   \caption{Redshift posterior for a Type~Ia and a non-Ia that were not observed
-   spectroscopically and for whom the host-galaxy is misassociated.
-   The results of the four chains are
-   placed in sequence.   \label{missed_wrong.100:fig}}
+   \includegraphics[scale=0.55]{/Users/akim/project/abc/results/{missed_wrong.100}.pdf} 
+   \caption{Redshift draws for a Type~Ia and a non-Ia that were not observed
+   spectroscopically and for whom the host-galaxies are misidentified.
+   The draws of the four chains are appended in series.   \label{missed_wrong.100:fig}}
 \end{figure}
@@
 Chain 2, whose initial condition was at the true redshift, also accepts redshift solutions as
-if were a Type~Ia.  Clearly this chain does not mix with the others.
+if were a Type~Ia. This
+object is a source of bias as the region around the true redshift is never sampled.
 
-Figure~\ref{posterior.100:fig} shows the log-posteriors and histograms of
-the $w$-draws from Chain 2 compared to the others.
+Clearly Chain 2 does not mix with the others, so I compare some of its behavior with
+Chains 0, 1, and 3 combined.
+Figure~\ref{posterior.100:fig} shows the log-posteriors
+of the two sets; the values are consistent so neither can be discounted as being trapped
+in a local but not global optimum.
+The $w$ draws from
+Chains 0, 1, and 3, and those from Chain 2 are shown in Figure~\ref{posterior.100:fig},
+and credible intervals in Table~\ref{split:tab}.
+
 \begin{figure}[htbp] %  figure placement: here, top, bottom, or page
    \centering
-   \includegraphics[scale=0.5]{/Users/akim/project/abc/results/{posterior.100}.pdf} 
-   \includegraphics[scale=0.5]{/Users/akim/project/abc/results/{wsub.100}.pdf} 
-   \caption{Log-posterior and $w$-draws from  Chain 2 compared to the others.  \label{posterior.100:fig}}
+   \includegraphics[scale=0.55]{/Users/akim/project/abc/results/{posterior.100}.pdf} 
+   \includegraphics[scale=0.55]{/Users/akim/project/abc/results/{wsub.100}.pdf} 
+   \caption{Log-posteriors and $w$ draws from the grouping of Chains 0, 1, and 3, 
+and Chain 2. \label{posterior.100:fig}}
 \end{figure}
+
+\begin{table}[htbp] 
+\centering
+\begin{tabular}{|cc|cc|}
+\hline
+Chains & \%-ile & $w$ range & $\Delta$\\ \hline
+013& $0.68$ & $[-1.029, -0.649]$ & $0.379$ \\
+013& $0.90$ & $[-1.201, -0.579]$ & $0.623$ \\
+013& $0.95$ & $[-1.290, -0.557]$ & $0.733$ \\ \hline
+2& $0.68$ & $[-1.048, -0.673]$ & $0.375$ \\
+2& $0.90$ & $[-1.197, -0.600]$ & $0.597$ \\
+2& $0.95$ & $[-1.282, -0.575]$ & $0.707$ \\
+\hline
+\end{tabular}
+\caption{Credible intervals of $w$ for the draws from the grouping of Chains 0, 1, and 3, 
+and Chain 2.\label{split:tab}}
+\end{table}
+
+\subsubsection{Full Sample: Varying Spectroscopic Completeness}
+The $\Omega_M$--$w$ posterior for the
+case where all transients have a direct spectrum
+is shown in Figure~\ref{contour.100:fig}.  The credible intervals
+of $w$ for 50\%, 75\%, and 100\% spectroscopic completeness
+are given in Table~\ref{compare:tab}.
+
+\begin{table}[htbp] 
+\centering
+\begin{tabular}{|cc|cc|}
+\hline
+\% Spectra & \%-ile & $w$ range & $\Delta$\\ \hline
+ 50& $0.68$ & $[-1.036, -0.657]$ & $0.380$ \\
+ 50& $0.90$ & $[-1.201, -0.583]$ & $0.618$ \\
+ 50& $0.95$ & $[-1.287, -0.562]$ & $0.725$ \\ \hline
+ 75& $0.68$ & $[-1.000, -0.642]$ & $0.358$ \\
+ 75& $0.90$ & $[-1.146, -0.586]$ & $0.560$ \\
+ 75& $0.95$ & $[-1.229, -0.566]$ & $0.663$ \\ \hline
+100& $0.68$ & $[-1.024, -0.654]$ & $0.370$ \\
+100& $0.90$ & $[-1.188, -0.586]$ & $0.601$ \\
+100& $0.95$ & $[-1.257, -0.569]$ & $0.688$ \\
+\hline
+\end{tabular}
+\caption{Credible intervals of $w$  for the draws from the grouping of Chains 0, 1, and 3, 
+and Chain 2.\label{compare:tab}}
+\end{table}
+
+\subsection{Proto-Conclusions}
+\begin{itemize}
+\item Host-galaxy misclassification and multiple populations can produce disjoint local maxima
+in the posterior.  Sampling the space is a challenge.
+\item For the simple model considered, statistical uncertainties dominate for the case
+of 200 transients.
+\end{itemize}
+
+For the moment, the priority is to generate robust results rather than improve
+the fidelity of the model.
+\begin{itemize}
+\item Run with $\sim 1000$ transients, which is more in line with what DES will get long-term
+and will be less sensitive to realization fluctuations.
+\item Save $\gg 2000$ links  of the chain to improve the accuracy of the posterior.
+\item Achieve mixing of the chains within a reasonable compute time.  Possibilities
+include reparametrization, optimization of the Stan code (I have already put non-trivial
+effort into this), use of a different MCMC algorithm.
+%\item Explore effect of galaxy-misclassification rate.  Its value is fairly uncertain at the moment.
+\end{itemize}
 

### 2015-08-19 src/analyze.py

@@ -1,7 +1,7 @@
 #!/usr/bin/env python
 
 import matplotlib
-matplotlib.use('Agg')
+#matplotlib.use('Agg')
 import matplotlib.pyplot as plt
 
 import pystan
@@ -13,8 +13,13 @@ import des
 
 import triangle
 
-def individual(N_s):
-	[extract, info, logposterior] = pickle.load(file('../results/model'+str(N_s)+'.pkl','rb'))
+levels = numpy.array([0.025, 0.05, 0.16, 1-0.16, 1-0.05, 1-.025])
+
+def individual(N_s, ia_only = False):
+	app = ''
+	if ia_only:
+		app+='.ia_only.'
+	[extract, info, logposterior] = pickle.load(file('../results/model'+app+str(N_s)+'.pkl','rb'))
 
 	n_samples = len(extract[extract.keys()[0]])
 	samples=numpy.zeros((n_samples,2))
@@ -22,7 +27,7 @@ def individual(N_s):
 	samples[:,1] = extract['w']
 	figure = triangle.corner(samples, labels=[r"$\Omega_M$", r"$w$"],truths=[0.28,-1],
 		quantiles=[0.16, 0.5, 0.84], plot_datapoints=False,plot_density=True)
-	plt.savefig('../results/contour.'+str(N_s)+'.pdf')
+	plt.savefig('../results/contour.'+app+str(N_s)+'.pdf')
 	plt.clf()
 
 	matplotlib.rcParams.update(matplotlib.rcParamsDefault)
@@ -34,7 +39,8 @@ def individual(N_s):
 	plt.ylabel('log-posterior')
 	plt.xlabel('link')
 	plt.legend(loc=3,prop={'size':9})
-	plt.savefig('../results/posterior.'+str(N_s)+'.pdf')
+	plt.tight_layout()
+	plt.savefig('../results/posterior.'+app+str(N_s)+'.pdf')
 	plt.clf()
 
 	# plt.plot(extract['w'])
@@ -44,45 +50,93 @@ def individual(N_s):
 	plt.xlabel(r'$w$')
 	plt.legend(loc=2)
 	plt.tight_layout()
-	plt.savefig('../results/w.'+str(N_s)+'.pdf')
+	plt.savefig('../results/w.'+app+str(N_s)+'.pdf')
 
 	plt.clf()
[…]

### 2015-08-19 src/des.py

@@ -1,7 +1,7 @@
 #!/usr/bin/env python
 
-import matplotlib
-matplotlib.use('Agg')
+#import matplotlib
+#matplotlib.use('Agg')
 import matplotlib.pyplot as plt
 
 import pystan
@@ -11,7 +11,7 @@ from astropy.cosmology import FlatLambdaCDM
 import pickle
 
 
-def genData(N_sn, N_s_obs, Ninit, seed):
+def genData(N_sn, N_s_obs, Ninit, seed, ia_only=False):
 
 	numpy.random.seed(seed)
 
@@ -56,9 +56,23 @@ def genData(N_sn, N_s_obs, Ninit, seed):
 	# s_obs_random : order in which supernovae get a spectrum
 	s_obs_random = numpy.arange(N_sn,dtype='int')
 	numpy.random.shuffle(s_obs_random)
-	s_obs = numpy.sort(s_obs_random[:N_s_obs]).tolist()
-	s_mis = numpy.sort(s_obs_random[N_s_obs:]).tolist()
 
+	s_obs=numpy.sort(s_obs_random[:N_s_obs])
+	s_mis= numpy.sort(s_obs_random[N_s_obs:])
+
+
+
+	if ia_only:
+		s_snIa = snIa[s_obs] ==1 
+		s_obs = s_obs[s_snIa]
+		s_snIa = snIa[s_mis] ==1 
+		s_mis = s_mis[s_snIa]
+		N_sn=snIa.sum()
+		N_s_obs = len(s_obs)
+
+
+	s_obs = s_obs.tolist()
+	s_mis = s_mis.tolist()
 
 	data = {'N_sn':N_sn,
 			'N_obs':N_s_obs,
@@ -126,22 +140,25 @@ def genData(N_sn, N_s_obs, Ninit, seed):
 def main():
 	Nchains=4
 	N_sn=200
-
+	ia_only=True
 	sm = pystan.StanModel(file='des.stan')
 
-	nspec = numpy.arange(100,N_sn+1,50)
+	nspec = numpy.arange(200,N_sn+1,50)
 	mn=[]
 	std=[]
 	for ns in nspec:
-		data, init, info = genData(N_sn,ns,Nchains,1)
+		data, init, info = genData(N_sn,ns,Nchains,1, ia_only=ia_only)
 
 		fit = sm.sampling(data=data, iter=50000, thin=50, chains=Nchains, init=init)
-		print fit
+		#print fit
[…]

### 2015-08-19 doc/model.tex
New version of the host galaxy model

@@
 \end{itemize}
-\item All transients are associated with a host galaxy with spectroscopic redshift $\theta_G$,
+\item All transients have a host with redshift $z$ and have a second
+galaxy at $z_N$ whose projection is close to the host, a potential source of ambiguity.
+The pdf for the redshift of the second galaxy is approximately uniform in volume:
 \begin{equation}
-p(\theta_G|z) =
-	P_{host} \ln{\mathcal{N}}(\theta_G;\ln(1+z),0.001) + (1-P_{host})\left(\frac{3 \theta_G^2}{z_{max}^3 - z_{min}^3}\right).
+\frac{3 z_N^2}{z_{max}^3 - z_{min}^3}.
 \end{equation}
-The host is determined correctly with probability $P_{host}$ in which case the
-host redshift is determined from a log-normal distribution centered around the true redshift
-with 0.001 fractional uncertainty.   Otherwise the redshift is drawn from the ``uniform in volume'' term on the right.
-[Note: to speed the cacluation, I only consider host-galaxy measurements
-of the {\it mis} set.]
+
+The host assignment $\theta_{G1}$ and that of the perceived neighbor
+$\theta_{G2}$ are drawn from
+\begin{equation}
+P(\theta_{G1},\theta_{G2}|z, z_N) =
+	P_{host}\delta(z-\theta_{G1})\delta(z_N-\theta_{G2}) +
+	(1-P_{host}) \delta(z-\theta_{G2})\delta(z_N-\theta_{G1}).
+\end{equation}
+
 \item This simple example does not consider data $\theta_S$, $\tau$ or $Z$, i.e.
@@
 \item $\theta_r=0.8$ for a constant relative fraction of SNe~Ia.
-\item 200 supernovae uniformly distributed in the range $0.1<z<1$.
+\item 500 transients uniformly distributed in the range $0.1<z<1$.
 \item $z_{min}=0.05$ and $z_{max}=1.5$ is the range of possible true redshifts.
 \item $P_{host}=0.98$ for the probability of correct host-galaxy assignment.
-\item Accumulated spectra at 50\%, 75\%, and 100\% spectroscopic
-completeness.
+\item Accumulated spectra for 300, 400, and 500 transients.
 \end{itemize}
@@
 \hline
-\% Spectra & \%-ile & $w$ range & $\Delta$\\ \hline
- 50& $0.68$ & $[-1.036, -0.657]$ & $0.380$ \\
- 50& $0.90$ & $[-1.201, -0.583]$ & $0.618$ \\
- 50& $0.95$ & $[-1.287, -0.562]$ & $0.725$ \\ \hline
- 75& $0.68$ & $[-1.000, -0.642]$ & $0.358$ \\
- 75& $0.90$ & $[-1.146, -0.586]$ & $0.560$ \\
- 75& $0.95$ & $[-1.229, -0.566]$ & $0.663$ \\ \hline
-100& $0.68$ & $[-1.024, -0.654]$ & $0.370$ \\
-100& $0.90$ & $[-1.188, -0.586]$ & $0.601$ \\
-100& $0.95$ & $[-1.257, -0.569]$ & $0.688$ \\
+\# Spectra & \%-ile & $w$ range & $\Delta$\\ \hline
+300& $0.68$ & $[-1.235, -0.943]$ & $0.292$ \\
+300& $0.90$ & $[-1.330, -0.852]$ & $0.478$ \\
+300& $0.95$ & $[-1.373, -0.806]$ & $0.568$ \\
+400& $0.68$ & $[-1.237, -0.946]$ & $0.291$ \\
+400& $0.90$ & $[-1.332, -0.858]$ & $0.474$ \\
+400& $0.95$ & $[-1.379, -0.819]$ & $0.560$ \\
+500& $0.68$ & $[-1.227, -0.945]$ & $0.282$ \\
+500& $0.90$ & $[-1.324, -0.838]$ & $0.486$ \\
+500& $0.95$ & $[-1.375, -0.785]$ & $0.590$ \\
 \hline

### 2015-08-19 src/analyze.py

@@ -22,15 +22,19 @@ def individual(N_s, ia_only = False):
 	[extract, info, logposterior] = pickle.load(file('../results/model'+app+str(N_s)+'.pkl','rb'))
 
 	n_samples = len(extract[extract.keys()[0]])
-	samples=numpy.zeros((n_samples,2))
+	samples=numpy.zeros((n_samples,7))
 	samples[:,0] = extract['Omega_M']
 	samples[:,1] = extract['w']
-	figure = triangle.corner(samples, labels=[r"$\Omega_M$", r"$w$"],truths=[0.28,-1],
+	samples[:,2] = extract['alpha_Ia']
+	samples[:,3] = extract['sigma_Ia']
+	samples[:,4] = extract['alpha_nonIa']
+	samples[:,5] = extract['sigma_nonIa']
+	samples[:,6] = extract['snIa_rate'][:,0]
+	figure = triangle.corner(samples, labels=[r"$\Omega_M$", r"$w$", r"$\alpha_{Ia}$", r"$\sigma_{Ia}$", r"$\alpha_{non-Ia}$", r"$\sigma_{Ia}$", r"SN Ia Rate"],truths=[0.28,-1, 2.,0.1,2*10**(-2./2.5),1,0.8],
 		quantiles=[0.16, 0.5, 0.84], plot_datapoints=False,plot_density=True)
 	plt.savefig('../results/contour.'+app+str(N_s)+'.pdf')
 	plt.clf()
 
-	matplotlib.rcParams.update(matplotlib.rcParamsDefault)
 
 	plt.plot(logposterior[0][500:],label=0)
 	plt.plot(logposterior[1][500:],label=1)
@@ -43,16 +47,20 @@ def individual(N_s, ia_only = False):
 	plt.savefig('../results/posterior.'+app+str(N_s)+'.pdf')
 	plt.clf()
 
-	# plt.plot(extract['w'])
-	# plt.show()
 
-	plt.hist(extract['w'],normed=True)
-	plt.xlabel(r'$w$')
-	plt.legend(loc=2)
+	plt.plot(extract['w'])
+	plt.ylabel(r'$w$')
+	plt.xlabel('link')
 	plt.tight_layout()
 	plt.savefig('../results/w.'+app+str(N_s)+'.pdf')
 
-	plt.clf()
+	# plt.hist(extract['w'],normed=True)
+	# plt.xlabel(r'$w$')
[…]

### 2015-08-19 src/des.py

@@ -90,6 +90,7 @@ def genData(N_sn, N_s_obs, Ninit, seed, ia_only=False):
 
 			'host_zs_obs': host_zs_random[s_obs], #zs[s_obs],
 			'host_zs_mis': host_zs_random[s_mis],
+			'host2_zs_mis': neighbor_zs_random[s_mis],
 
 			'n_int': 25,
 			'N_SNIa': snIa[s_obs].sum()
@@ -139,17 +140,17 @@ def genData(N_sn, N_s_obs, Ninit, seed, ia_only=False):
 
 def main():
 	Nchains=4
-	N_sn=200
-	ia_only=True
+	N_sn=500
+	ia_only=False
 	sm = pystan.StanModel(file='des.stan')
 
-	nspec = numpy.arange(200,N_sn+1,50)
+	nspec = numpy.arange(300,N_sn+1,100)
 	mn=[]
 	std=[]
 	for ns in nspec:
 		data, init, info = genData(N_sn,ns,Nchains,1, ia_only=ia_only)
 
-		fit = sm.sampling(data=data, iter=50000, thin=50, chains=Nchains, init=init)
+		fit = sm.sampling(data=data, iter=50000, thin=5, chains=Nchains, init=init)
 		#print fit
 		#samples = fit.extract(['Omega_M','ainv_true_mis','w'])
 

### 2015-08-22 doc/model.tex
Note for U Penn folks

@@
 \end{equation}
+The distribution of these galaxies is different from than the distribution of transient redshifts,
+which can lead to bias.
 
@@
 spectroscopic parameters, sample-selection effects, and calibration.
-\end{itemize}
-
-A prior is applied to the SN~Ia absolute magnitude
+\item A prior is applied to the SN~Ia absolute magnitude
 \begin{equation}
@@
 where $\alpha^0_{SNIa}$ is the true input luminosity.
+\end{itemize}
 
-Note some of the choices for the distributions are driven by computational
-speed. 
-Also, Stan cannot handle discrete parameters and
-cannot except pdf's that support zero probability.
+I highlight the treatment of redshift in this model; the cosmological redshift
+$z$ is set to the values of the
+observed redshifts through $\delta$-functions.  This choice was made specifically to aid
+in the convergence of the Monte Carlo: the discrete possibilities for redshift allow
+for their marginalized likelihood to be used in the calculation of the posterior.
+A more general model would replace the $\delta$-functions
+with coming from a continuous PDF's.
+Peculiar velocities, redshift measurement errors (particularly from
+photometric redshifts) justify this generalization.
+A transient
+without a spectrum has uncertain type and redshift: the redshift
+of the associated host galaxy, and redshifts expected based on the
+flux of the SN~Ia and non-Ia standard candles,
+are viable but disjoint possibilities for the posterior of
+the true underlying redshift. My runs of this scenario produce chains
+that do not mix so I resorted to the simplified treatment presented here.
 
@@
 \item 500 transients uniformly distributed in the range $0.1<z<1$.
-\item $z_{min}=0.05$ and $z_{max}=1.5$ is the range of possible true redshifts.
+\item $z_{min}=0.05$ and $z_{max}=1.5$ is the range of possible misassigned
+host redshift.
 \item $P_{host}=0.98$ for the probability of correct host-galaxy assignment.
-\item Accumulated spectra for 300, 400, and 500 transients.
+\item Accumulated spectra for 200, 350, and 500 transients.
 \end{itemize}
@@
 inference of Bayesian models with Hamiltonian Monte Carlo.  There are
-four chains run, each with 50,000 samples then thinned by 50.  Half the links
-are used for burnin, so ultimately 2000 links are used as draws from the posterior.
-It took 2 days tor produce these results on my MacBook Air.  One chain, \#2
-in the 50\% run,  took the bulk of the time; presumably a different integration step size
-was determined during warmup.  As shown shortly, this chain samples
-a broader range of parameter space.
+four chains run, each with 50,000 samples then thinned by 5.  Half the links
+are used for burnin, so ultimately 20,000 links are used as draws from the posterior.
 
@@
 A classical analysis would only include confirmed SNe~Ia with a definitive
-redshift. The realization of simulated data has 156 Type~Ia supernovae.
+redshift. The realization of simulated data has 415 Type~Ia supernovae.
 Results of the analysis of a pure SN~Ia sample with no
-host misclassification are presented:  Figure~\ref{contour.100:fig}
+host misclassification are presented:  Figure~\ref{contour.ia_only:fig}
 shows the posteriors for  $\Omega_M$--$w$ and Table~\ref{ia_only:tab} the
-credible equal-tailed intervals for $w$.  (Note that $w$ is the parameter
+credible equal-tailed intervals for $w$.  The true $w=-1$ is within
+the 0.58 credible interval. (Note that $w$ is the parameter
 of most interest for the experiment.)
-The distributions
-look similar to the latest results from real data \citep{2014A&A...568A..22B} 
-and so satisfy qualitative expectations.
 
@@
    \centering
-   \includegraphics[scale=0.55]{/Users/akim/project/abc/results/{contour..ia_only.200}.pdf} \newline
-   \includegraphics[scale=0.55]{/Users/akim/project/abc/results/{contour.100}.pdf} 
-   \includegraphics[scale=0.55]{/Users/akim/project/abc/results/{contour.200}.pdf}    \caption{Probability distribution function for $\Omega_M$--$w$ for: 156 SNe~Ia
-   with spectra (top);  SNe~Ia and non-Ia with 50\% (left),
-   and 100\% (right)  spectroscopic completeness.
+   \includegraphics[scale=0.55]{/Users/akim/project/abc/results/{contour..ia_only.500}.pdf} \newline
+\caption{Probability distribution function for $\Omega_M$--$w$ for only SNe~Ia
+   all with spectra.
    Solid lines represent the input cosmology.  Dashed lines in the
    histograms are the 0.16 and 0.86 quantiles. 
-   \label{contour.100:fig}}
+   \label{contour.ia_only:fig}}
 \end{figure}
@@
 \hline
-\%-ile & $w$ range & $\Delta$\\ \hline
-$0.68$ & $[-1.038, -0.648]$ & $0.389$ \\
-$0.90$ & $[-1.204, -0.577]$ & $0.627$ \\
-$0.95$ & $[-1.269, -0.556]$ & $0.713$ \\
+\%-ile & $w$ range & $\Delta w$\\ \hline
+$0.68$ & $[-1.254, -0.975]$ & $0.279$ \\
+$0.90$ & $[-1.347, -0.889]$ & $0.458$ \\
+$0.95$ & $[-1.396, -0.846]$ & $0.550$ \\
 \hline
 \end{tabular}
-\caption{Credible intervals of $w$ using the 156 SNe~Ia only with spectroscopic
+\caption{Credible intervals of $w$ using the SNe~Ia only with spectroscopic
 observations.\label{ia_only:tab}}
@@
 
-\subsubsection{Full Sample: 50\% Spectroscopic Confirmation}
+\subsubsection{Full Sample: Varying Spectroscopic Completeness}
 We now turn to the full sample of SNe~Ia and non-Ia's.  Recall that our simple
@@
 Results for the $\Omega_M$--$w$ posterior for the
-case of 50\% spectroscopic completeness
-are shown in Figure~\ref{contour.100:fig}.
-As will be discussed shortly, the Stan run does not result in a Markov Chain Monte Carlo
-that has
-converged to a stationary solution.
-
-A transient
-without a spectrum has uncertain type and redshift: the redshift
-of the associated host galaxy, and redshifts expected based on the
-flux of the SN~Ia and non-Ia standard candles,
-are viable but disjoint possibilities for the posterior of
-the true underlying redshift.  To test the mixing of the chains,
-the initial conditions 
-for redshifts of transients without an active spectrum are
-selected to be near local optima: the true redshift
-for chains 0 and 2 and near the host redshift in chains 1 and 3.
-
-Two objects, one Type~Ia and the other
-non-Ia, are assigned incorrect redshifts (recall 50\% do not have
-an active spectrum and the 98\% host misclassification rate).
-Figure~\ref{missed_wrong.100:fig} shows draws
-for the redshift parameter for these two transients.
-The SN~Ia is placed at $z=0.95$ but is misassociated with a galaxy at
-$z=1.24$.  The posterior shows a preference for the correct redshift, but sometimes
-drops to lower redshifts as if it were a non-Ia. Although two of the chains start near the incorrect-host redshift, they do not return to that area of parameter space after burnin.
+case of 40\%, 70\%, and 100\% spectroscopic completeness
+are shown in Figures~\ref{contour.200:fig}, \ref{contour.350:fig}, and
+\ref{contour.500:fig} respectively.
+The credible intervals
+of $w$ for are given in Table~\ref{compare:tab}, with
+the input $w=-1$ within the 0.65, 0.49, and 0.47  intervals
+respectively.
 
@@
    \centering
-   \includegraphics[scale=0.55]{/Users/akim/project/abc/results/{missed_wrong.100}.pdf} 
-   \caption{Redshift draws for a Type~Ia and a non-Ia that were not observed
-   spectroscopically and for whom the host-galaxies are misidentified.
-   The draws of the four chains are appended in series.   \label{missed_wrong.100:fig}}
+   \includegraphics[scale=0.40]{/Users/akim/project/abc/results/{contour.200}.pdf} 
+   \caption{Probability distribution function for $\Omega_M$--$w$ for:
+    SNe~Ia and non-Ia with 40\%  spectroscopic completeness.
+   \label{contour.200:fig}}
 \end{figure}
-
-The non-Ia is placed at $z=0.39$ and is misassociated with a galaxy at $z=0.48$.
-Three of the four chains stay in the neighborhood of the incorrect-host redshift.
-Chain 2, whose initial condition was at the true redshift, also accepts redshift solutions as
-if were a Type~Ia. This
-object is a source of bias as the region around the true redshift is never sampled.
-
-Clearly Chain 2 does not mix with the others, so I compare some of its behavior with
-Chains 0, 1, and 3 combined.
-Figure~\ref{posterior.100:fig} shows the log-posteriors
-of the two sets; the values are consistent so neither can be discounted as being trapped
-in a local but not global optimum.
-The $w$ draws from
-Chains 0, 1, and 3, and those from Chain 2 are shown in Figure~\ref{posterior.100:fig},
-and credible intervals in Table~\ref{split:tab}.
 
@@
    \centering
-   \includegraphics[scale=0.55]{/Users/akim/project/abc/results/{posterior.100}.pdf} 
-   \includegraphics[scale=0.55]{/Users/akim/project/abc/results/{wsub.100}.pdf} 
-   \caption{Log-posteriors and $w$ draws from the grouping of Chains 0, 1, and 3, 
-and Chain 2. \label{posterior.100:fig}}
+   \includegraphics[scale=0.40]{/Users/akim/project/abc/results/{contour.350}.pdf} 
+   \caption{Probability distribution function for $\Omega_M$--$w$ for
+    SNe~Ia and non-Ia with 70\%  spectroscopic completeness.
+   \label{contour.350:fig}}
+\end{figure}
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[scale=0.40]{/Users/akim/project/abc/results/{contour.500}.pdf} 
+   %\includegraphics[scale=0.55]{/Users/akim/project/abc/results/{contour.200}.pdf}    
+   \caption{Probability distribution function for $\Omega_M$--$w$ for
+    SNe~Ia and non-Ia with 100\%  spectroscopic completeness.
+   \label{contour.500:fig}}
 \end{figure}
@@
 \hline
-Chains & \%-ile & $w$ range & $\Delta$\\ \hline
-013& $0.68$ & $[-1.029, -0.649]$ & $0.379$ \\
-013& $0.90$ & $[-1.201, -0.579]$ & $0.623$ \\
-013& $0.95$ & $[-1.290, -0.557]$ & $0.733$ \\ \hline
-2& $0.68$ & $[-1.048, -0.673]$ & $0.375$ \\
-2& $0.90$ & $[-1.197, -0.600]$ & $0.597$ \\
-2& $0.95$ & $[-1.282, -0.575]$ & $0.707$ \\
+\# Spectra & \%-ile & $w$ range & $\Delta$\\ \hline
+200& $0.68$ & $[-1.284, -0.991]$ & $0.293$ \\
+200& $0.90$ & $[-1.385, -0.900]$ & $0.485$ \\
+200& $0.95$ & $[-1.435, -0.860]$ & $0.575$ \\
+350& $0.68$ & $[-1.243, -0.952]$ & $0.291$ \\
+350& $0.90$ & $[-1.339, -0.858]$ & $0.481$ \\
+350& $0.95$ & $[-1.390, -0.817]$ & $0.573$ \\
+500& $0.68$ & $[-1.236, -0.948]$ & $0.289$ \\
+500& $0.90$ & $[-1.336, -0.861]$ & $0.475$ \\
+500& $0.95$ & $[-1.385, -0.815]$ & $0.570$ \\
 \hline
 \end{tabular}
-\caption{Credible intervals of $w$ for the draws from the grouping of Chains 0, 1, and 3, 
-and Chain 2.\label{split:tab}}
+\caption{Credible intervals of $w$ given different levels of spectroscopy.  \label{compare:tab}}
 \end{table}
 
-\subsubsection{Full Sample: Varying Spectroscopic Completeness}
-The $\Omega_M$--$w$ posterior for the
-case where all transients have a direct spectrum
-is shown in Figure~\ref{contour.100:fig}.  The credible intervals
-of $w$ for 50\%, 75\%, and 100\% spectroscopic completeness
-are given in Table~\ref{compare:tab}.
-
-\begin{table}[htbp] 
-\centering
-\begin{tabular}{|cc|cc|}
-\hline
-\# Spectra & \%-ile & $w$ range & $\Delta$\\ \hline
-300& $0.68$ & $[-1.235, -0.943]$ & $0.292$ \\
-300& $0.90$ & $[-1.330, -0.852]$ & $0.478$ \\
-300& $0.95$ & $[-1.373, -0.806]$ & $0.568$ \\
-400& $0.68$ & $[-1.237, -0.946]$ & $0.291$ \\
-400& $0.90$ & $[-1.332, -0.858]$ & $0.474$ \\
-400& $0.95$ & $[-1.379, -0.819]$ & $0.560$ \\
-500& $0.68$ & $[-1.227, -0.945]$ & $0.282$ \\
-500& $0.90$ & $[-1.324, -0.838]$ & $0.486$ \\
-500& $0.95$ & $[-1.375, -0.785]$ & $0.590$ \\
-\hline
-\end{tabular}
-\caption{Credible intervals of $w$  for the draws from the grouping of Chains 0, 1, and 3, 
-and Chain 2.\label{compare:tab}}
-\end{table}
-
-\subsection{Proto-Conclusions}
-\begin{itemize}
-\item Host-galaxy misclassification and multiple populations can produce disjoint local maxima
-in the posterior.  Sampling the space is a challenge.
-\item For the simple model considered, statistical uncertainties dominate for the case
-of 200 transients.
-\end{itemize}
-
-For the moment, the priority is to generate robust results rather than improve
-the fidelity of the model.
-\begin{itemize}
-\item Run with $\sim 1000$ transients, which is more in line with what DES will get long-term
-and will be less sensitive to realization fluctuations.
-\item Save $\gg 2000$ links  of the chain to improve the accuracy of the posterior.
-\item Achieve mixing of the chains within a reasonable compute time.  Possibilities
-include reparametrization, optimization of the Stan code (I have already put non-trivial
-effort into this), use of a different MCMC algorithm.
-%\item Explore effect of galaxy-misclassification rate.  Its value is fairly uncertain at the moment.
-\end{itemize}
+As would be expected, the better the spectroscopic completeness, the less bias
+and smaller uncertainties that are obtained.
 

### 2015-08-22 src/analyze.py

@@ -20,20 +20,32 @@ def individual(N_s, ia_only = False):
 	if ia_only:
 		app+='.ia_only.'
 	[extract, info, logposterior] = pickle.load(file('../results/model'+app+str(N_s)+'.pkl','rb'))
-
+	print numpy.abs((extract['w'] < -1).sum()*1. / len(extract['w'])-0.5)*2
 	n_samples = len(extract[extract.keys()[0]])
-	samples=numpy.zeros((n_samples,7))
-	samples[:,0] = extract['Omega_M']
-	samples[:,1] = extract['w']
-	samples[:,2] = extract['alpha_Ia']
-	samples[:,3] = extract['sigma_Ia']
-	samples[:,4] = extract['alpha_nonIa']
-	samples[:,5] = extract['sigma_nonIa']
-	samples[:,6] = extract['snIa_rate'][:,0]
-	figure = triangle.corner(samples, labels=[r"$\Omega_M$", r"$w$", r"$\alpha_{Ia}$", r"$\sigma_{Ia}$", r"$\alpha_{non-Ia}$", r"$\sigma_{Ia}$", r"SN Ia Rate"],truths=[0.28,-1, 2.,0.1,2*10**(-2./2.5),1,0.8],
-		quantiles=[0.16, 0.5, 0.84], plot_datapoints=False,plot_density=True)
-	plt.savefig('../results/contour.'+app+str(N_s)+'.pdf')
-	plt.clf()
+
+	if ia_only:
+		samples=numpy.zeros((n_samples,4))
+		samples[:,0] = extract['Omega_M']
+		samples[:,1] = extract['w']
+		samples[:,2] = extract['alpha_Ia']
+		samples[:,3] = extract['sigma_Ia']
+		figure = triangle.corner(samples, labels=[r"$\Omega_M$", r"$w$", r"$\alpha_{Ia}$", r"$\sigma_{Ia}$"],truths=[0.28,-1, 2.,0.1],
+			quantiles=[0.16, 0.5, 0.84], plot_datapoints=False,plot_density=True)
+		plt.savefig('../results/contour.'+app+str(N_s)+'.pdf')
+		plt.clf()
+	else:
+		samples=numpy.zeros((n_samples,7))
+		samples[:,0] = extract['Omega_M']
+		samples[:,1] = extract['w']
+		samples[:,2] = extract['alpha_Ia']
+		samples[:,3] = extract['sigma_Ia']
[…]

### 2015-08-26 src/des.py
refactor data generation

@@ -3,170 +3,314 @@
 #import matplotlib
 #matplotlib.use('Agg')
 import matplotlib.pyplot as plt
-
+from matplotlib.backends.backend_pdf import PdfPages
 import pystan
 import numpy.random
 from astropy.cosmology import FlatLambdaCDM
+import scipy
 
 import pickle
 
+class Data(object):
+	"""docstring for Data"""
+	def __init__(self, N_sn, seed, ia_only=False):
+		super(Data, self).__init__()
+		self.N_sn = N_sn
+		self.seed = seed
+		self.ia_only = ia_only
 
-def genData(N_sn, N_s_obs, Ninit, seed, ia_only=False, ADU0=None):
+		self.omega_M=0.28
+		self.cosmo=FlatLambdaCDM(70,self.omega_M)
 
-	numpy.random.seed(seed)
+		self.zmin=0.1
+		self.zmax=1.
 
-	omega_M=0.28
-	cosmo=FlatLambdaCDM(70,omega_M)
+		self.sigma_snIa=0.1
+		self.sigma_nonIa=1
 
-	zmin=0.1
-	zmax=1.
+		self.alpha_snIa=2.
+		self.alpha_nonIa=self.alpha_snIa*10**(-2./2.5)
+		self.frac_Ia_0=.5
+		self.frac_Ia_1=.1
+		numpy.random.seed(seed)
+		self.initialize_()
 
-	sigma_snIa=0.1
-	sigma_nonIa=1
+	def initialize_(self):
+		self.redshifts_()
+		self.types_()
+		self.adus_()
+		self.hosts_()
 
-	alpha_snIa=2.
-	alpha_nonIa=alpha_snIa*10**(-2./2.5)
-	frac_Ia_0=.8
-	frac_Ia_1=.5
+	def redshifts_(self):
+		# zs : the true redshifts
+		volume_zero = self.cosmo.comoving_volume(self.zmin).value
+		volume_norm = self.cosmo.comoving_volume(self.zmax).value- volume_zero
 
-	# zs : the true redshifts
-	zs = numpy.sort(numpy.random.uniform(zmin,zmax,N_sn))
+		self.zs = numpy.sort(numpy.random.uniform(size=self.N_sn))
+		for i in xrange(len(self.zs)):
[…]

### 2015-08-27 src/analyze.py
vectorize stan code, expand redshift range, change directory for saving and reading

@@ -19,7 +19,7 @@ def individual(N_s, ia_only = False):
 	app = ''
 	if ia_only:
 		app+='.ia_only.'
-	[extract, info, logposterior] = pickle.load(file('../results/model'+app+str(N_s)+'.pkl','rb'))
+	[extract,logposterior] = pickle.load(file('../results/temp/model'+app+str(N_s)+'.pkl','rb'))
 	print numpy.abs((extract['w'] < -1).sum()*1. / len(extract['w'])-0.5)*2
 	n_samples = len(extract[extract.keys()[0]])
 
@@ -31,20 +31,21 @@ def individual(N_s, ia_only = False):
 		samples[:,3] = extract['sigma_Ia']
 		figure = triangle.corner(samples, labels=[r"$\Omega_M$", r"$w$", r"$\alpha_{Ia}$", r"$\sigma_{Ia}$"],truths=[0.28,-1, 2.,0.1],
 			quantiles=[0.16, 0.5, 0.84], plot_datapoints=False,plot_density=True)
-		plt.savefig('../results/contour.'+app+str(N_s)+'.pdf')
+		plt.savefig('../results/temp/contour.'+app+str(N_s)+'.pdf')
 		plt.clf()
 	else:
-		samples=numpy.zeros((n_samples,7))
+		samples=numpy.zeros((n_samples,8))
 		samples[:,0] = extract['Omega_M']
 		samples[:,1] = extract['w']
 		samples[:,2] = extract['alpha_Ia']
 		samples[:,3] = extract['sigma_Ia']
 		samples[:,4] = extract['alpha_nonIa']
 		samples[:,5] = extract['sigma_nonIa']
-		samples[:,6] = extract['snIa_rate'][:,0]
-		figure = triangle.corner(samples, labels=[r"$\Omega_M$", r"$w$", r"$\alpha_{Ia}$", r"$\sigma_{Ia}$", r"$\alpha_{non-Ia}$", r"$\sigma_{non-Ia}$", r"SN Ia Rate"],truths=[0.28,-1, 2.,0.1,2*10**(-2./2.5),1,0.8],
+		samples[:,6] = extract['snIa_rate_0'][:,0]
+		samples[:,7] = extract['snIa_rate_1'][:,0]
[…]

### 2015-08-27 src/des.py

@@ -23,7 +23,7 @@ class Data(object):
 		self.cosmo=FlatLambdaCDM(70,self.omega_M)
 
 		self.zmin=0.1
-		self.zmax=1.
+		self.zmax=1.4
 
 		self.sigma_snIa=0.1
 		self.sigma_nonIa=1
@@ -64,10 +64,10 @@ class Data(object):
 		self.adu = adu
 
 	def hosts_(self):
-		host_choice = numpy.random.binomial(1,0.98,size=self.N_sn)
+		self.host_choice = numpy.random.binomial(1,0.98,size=self.N_sn)
 		self.neighbor_zs=numpy.random.uniform((1+self.zmin/1.5)**3,(1+self.zmax*1.5)**3,size=self.N_sn)**(1./3)-1
-		self.host_zs_random = self.zs*host_choice + self.neighbor_zs*(1-host_choice)
-		self.neighbor_zs_random = self.zs*(1-host_choice) + self.neighbor_zs*host_choice
+		self.host_zs_random = self.zs*self.host_choice + self.neighbor_zs*(1-self.host_choice)
+		self.neighbor_zs_random = self.zs*(1-self.host_choice) + self.neighbor_zs*self.host_choice
 
 	def found(self, ADU0):
 		self.ADU0 =ADU0
@@ -89,14 +89,14 @@ class Data(object):
 	def dict(self):
 		return 	{'N_sn': self.found.sum(),
 			'N_obs': len(self.s_obs),
-
+			'N_SNIa': self.snIa[self.s_obs].sum(),
 			'N_adu_max':1,
 
 			'zmin':self.zmin,
 			'zmax':self.zmax,
 
-			'adu_obs': self.adu[self.s_obs,None],
-			'adu_mis': self.adu[self.s_mis,None],
+			'adu_obs': self.adu[self.s_obs],
+			'adu_mis': self.adu[self.s_mis],
 
 			'trans_ainv_obs': 1+self.zs[self.s_obs],
 			'snIa_obs': self.snIa[self.s_obs],
@@ -105,9 +105,9 @@ class Data(object):
 			'host_zs_mis': self.host_zs_random[self.s_mis],
 			'host2_zs_mis': self.neighbor_zs_random[self.s_mis],
 
-			'ADU0': self.ADU0,
+			'ADU0': self.ADU0
 #			'n_int': 25,
-			'N_SNIa': self.snIa[self.s_obs].sum()
+
 			}
 
[…]

### 2015-08-27 doc/model.tex
cleaning up comments

@@
 \mathcal{N}\left(\frac{\alpha_{\mathit{non-Ia}}}{d_L^2(z;\Omega_M, w)}, \frac{\ln{10}}{2.5}\sigma_{\mathit{non-Ia}}\right).
+\label{adumis:eqn}
 \end{multline}
@@
 \theta_r\mathcal{N}\left(\frac{\alpha_{Ia}}{d_L^2(z;\Omega_M, w)}, \frac{\ln{10}}{2.5}\sigma_{Ia}\right).
+\label{adusnIa:eqn}
 \end{equation}
@@
 \mathcal{N}\left(\frac{\alpha_{\mathit{non-Ia}}}{d_L^2(z;\Omega_M, w)}, \frac{\ln{10}}{2.5}\sigma_{\mathit{non-Ia}}\right).
+\label{adunonIa:eqn}
 \end{multline}
 \end{itemize}
+\item The ADU likelihoods in Equations~\ref{adumis:eqn}, \ref{adusnIa:eqn}, and
+\ref{adunonIa:eqn} are appropriate when there is no count-based sample selection.
+In practice the distribution will be truncated, as only transients that pass a brightness
+threshold $\mathit{ADU}_0$ make it into the sample.  The area of the truncated
+distribution in Equation~\ref{adumis:eqn} $\int_{\mathit{ADU}_0}^{\infty} p(\mathit{ADU})d\mathit{ADU}$
+normalizes the above ADU likelihoods.
 \item All transients have a host with redshift $z$ and have a second

### 2015-08-27 src/des.py

@@ -65,7 +65,7 @@ class Data(object):
 
 	def hosts_(self):
 		self.host_choice = numpy.random.binomial(1,0.98,size=self.N_sn)
-		self.neighbor_zs=numpy.random.uniform((1+self.zmin/1.5)**3,(1+self.zmax*1.5)**3,size=self.N_sn)**(1./3)-1
+		self.neighbor_zs=numpy.random.uniform((1+self.zmin/1.1)**3,(1+self.zmax*1.1)**3,size=self.N_sn)**(1./3)-1
 		self.host_zs_random = self.zs*self.host_choice + self.neighbor_zs*(1-self.host_choice)
 		self.neighbor_zs_random = self.zs*(1-self.host_choice) + self.neighbor_zs*self.host_choice
 
@@ -106,8 +106,6 @@ class Data(object):
 			'host2_zs_mis': self.neighbor_zs_random[self.s_mis],
 
 			'ADU0': self.ADU0
-#			'n_int': 25,
-
 			}
 
 	def init(self, n):
@@ -138,164 +136,32 @@ class Data(object):
 		     plt.legend()
 		     pdf.savefig(fig)
 		     fig = plt.figure()
-		     plt.scatter(self.zs[numpy.logical_and(self.found, self.snIa ==1)], -2.5*numpy.log10(self.adu[numpy.logical_and(self.found, self.snIa ==1)]),label='SN Ia',color='b')
-		     plt.scatter(self.zs[numpy.logical_and(self.found, self.snIa ==0)], -2.5*numpy.log10(self.adu[numpy.logical_and(self.found, self.snIa ==0)]),label='non-Ia',color='r')
+		     plt.scatter(self.zs[numpy.logical_and(self.found, self.snIa ==1)], -2.5*numpy.log10(self.adu[numpy.logical_and(self.found, self.snIa ==1)]),label='SN Ia',color='b',facecolors='none')
+		     plt.scatter(self.zs[numpy.logical_and(self.found, self.snIa ==0)], -2.5*numpy.log10(self.adu[numpy.logical_and(self.found, self.snIa ==0)]),label='non-Ia',color='r',facecolors='none')
[…]

### 2015-08-27 src/des.py
so Marisa can run

@@ -190,5 +190,5 @@ def main():
 			pickle.dump([fit.extract(), logposterior], f)
 
 if __name__ == "__main__":
-	dataPlot();
-#    main()
+#	dataPlot();
+    main()

### 2015-08-29 src/des.py
Works!!  Tested No malmquist and with all and fractional.

@@ -153,7 +153,6 @@ class Data(object):
 
 
 def dataPlot():
-	Nchains=4
 	N_sn=2000
 	ADU0=.5
 	ia_only=False
@@ -166,7 +165,7 @@ def dataPlot():
 def main():
 	Nchains=4
 	N_sn=2000
-	ADU0=1.
+	ADU0=0.2 #0.2
 	ia_only=False
 
 	data= Data(N_sn, 1, ia_only=ia_only)
@@ -175,11 +174,11 @@ def main():
 
 	sm = pystan.StanModel(file='des.stan')
 
-	fracspec = numpy.arange(.2,1.01,.4)
+	fracspec = numpy.arange(.2,1.01,4)
 	for ns in fracspec:
 		data.spectrum(ns)
 
-		fit = sm.sampling(data=data.dict(), iter=2000, thin=1, n_jobs=-1, chains=Nchains, init=data.init(Nchains))
+		fit = sm.sampling(data=data.dict(), iter=10000, thin=2, n_jobs=-1, chains=Nchains, init=data.init(Nchains))
 
 		logposterior = fit.get_logposterior()
 

### 2015-08-29 src/des.py
change config for reasonable run

@@ -174,7 +174,7 @@ def main():
 
 	sm = pystan.StanModel(file='des.stan')
 
-	fracspec = numpy.arange(.2,1.01,4)
+	fracspec = numpy.arange(.2,1.01,.4)
 	for ns in fracspec:
 		data.spectrum(ns)
 

### 2015-09-02 src/des.py
change rate init and put bound on non-Ia sigma

@@ -143,8 +143,8 @@ class Data(object):
 	def init(self, n):
 		ans=[]
 		for i in xrange(n):
-			rate = numpy.random.lognormal(numpy.log(self.frac_Ia_0),0.1)
-			rate1 = numpy.random.lognormal(numpy.log(self.frac_Ia_1),0.1)
+			rate = min(numpy.random.lognormal(numpy.log(self.frac_Ia_0),0.1),.99)
+			rate1 = min(numpy.random.lognormal(numpy.log(self.frac_Ia_1),0.1),.99)
 			ans.append( {
 				'Omega_M':numpy.random.normal(self.omega_M,0.1),
 				'Omega_L':1-self.omega_M,
@@ -211,7 +211,7 @@ def main():
 	Nchains=4
 	N_sn=2000
 	ADU0=0.2 #0.2
-	ia_only=True
+	ia_only=False
 
 	data= Data(N_sn, 1)
 	data.found(ADU0)
@@ -219,7 +219,7 @@ def main():
 
 	sm = pystan.StanModel(file='des.stan')
 
-	fracspec = numpy.arange(1,1.01,.4)
+	fracspec = numpy.arange(0.6,1.01,.4)
 	for ns in fracspec:
 		data.spectrum(ns)
 

### 2015-09-04 src/analyze.py
fix model for observe 1a SNE

@@ -15,10 +15,12 @@ import triangle
 
 levels = numpy.array([0.025, 0.05, 0.16, 1-0.16, 1-0.05, 1-.025])
 
-def individual(N_s, ia_only = False):
+def individual(N_s, ia_only = False, ADU0=None):
 	app = ''
 	if ia_only:
 		app+='.ia_only.'
+	if ADU0 == 0.:
+			app+='.noMalm.'
 	[extract,logposterior] = pickle.load(file('../results/temp/model'+app+str(N_s)+'.pkl','rb'))
 #	print numpy.abs((extract['w'] < -1).sum()*1. / len(extract['w'])-0.5)*2
 	n_samples = len(extract[extract.keys()[0]])
@@ -43,9 +45,11 @@ def individual(N_s, ia_only = False):
 		samples[:,5] = extract['sigma_nonIa']
 		samples[:,6] = extract['snIa_rate_0'][:,0]
 		samples[:,7] = extract['snIa_rate_1'][:,0]
+
+		kwargs = {'levels':1.0 - numpy.exp(-0.5 * numpy.arange(1, 3.1, 1) ** 2)}
 		figure = triangle.corner(samples, labels=[r"$\Omega_M$", r"$w$", r"$\alpha_{Ia}$", r"$\sigma_{Ia}$", r"$\alpha_{non-Ia}$", r"$\sigma_{non-Ia}$", r"SN Ia Rate 0", r"SN Ia Rate1"],
 			truths=[0.28,-1, 2.,0.1,2*10**(-2./2.5),1,0.95,0.2],
-			quantiles=[0.16, 0.5, 0.84], plot_datapoints=False,plot_density=True)
+			quantiles=[0.16, 0.5, 0.84], plot_datapoints=False,plot_density=True, **kwargs)
 		plt.savefig('../results/temp/contour.'+app+str(N_s)+'.pdf')
 		plt.clf()
 
@@ -160,7 +164,7 @@ def group(nspec):
 
 
 def main():
-	individual(0.2,ia_only=False)
+	individual(1.0,ia_only=False,ADU0=None)
 #	individual(500,ia_only=False)
 	wefew
 	group([200,350,500])

### 2015-09-04 src/des.py

@@ -25,7 +25,7 @@ class Data(object):
 		self.zmax=1.4
 
 		self.sigma_snIa=0.1
-		self.sigma_nonIa=1
+		self.sigma_nonIa=1.
 
 		self.alpha_snIa=2.
 		self.alpha_nonIa=self.alpha_snIa*10**(-2./2.5)
@@ -51,7 +51,7 @@ class Data(object):
 
 	def types_(self):
 		self.snIa = numpy.random.uniform(size=self.N_sn)
-		self.snIa = numpy.less_equal(self.snIa, self.frac_Ia_0 + (self.frac_Ia_1-self.frac_Ia_0)*self.zs/self.zmax/1.5).astype(int)
+		self.snIa = numpy.less_equal(self.snIa, self.frac_Ia_0 + (self.frac_Ia_1-self.frac_Ia_0)*self.zs/self.zmax/1.1).astype(int)
 
 	def adus_(self):
 		adu = 1/(self.cosmo.luminosity_distance(self.zs).value/self.cosmo.hubble_distance.value)**2
@@ -143,8 +143,8 @@ class Data(object):
 	def init(self, n):
 		ans=[]
 		for i in xrange(n):
-			rate = min(numpy.random.lognormal(numpy.log(self.frac_Ia_0),0.1),.99)
-			rate1 = min(numpy.random.lognormal(numpy.log(self.frac_Ia_1),0.1),.99)
+			rate = min(numpy.random.lognormal(numpy.log(self.frac_Ia_0),0.05),.99)
+			rate1 = min(numpy.random.lognormal(numpy.log(self.frac_Ia_1),0.05),.99)
 			ans.append( {
 				'Omega_M':numpy.random.normal(self.omega_M,0.1),
 				'Omega_L':1-self.omega_M,
@@ -157,6 +157,8 @@ class Data(object):
 			  	'sigma_nonIa':numpy.random.lognormal(numpy.log(self.sigma_nonIa),0.1),
 			  	'snIa_rate_0': [rate,1-rate],
 			  	'snIa_rate_1': [rate1,1-rate1]
+			  	# 'snIa_rate_0_logit': numpy.log(rate/(1-rate))
+			  	# 'snIa_rate_1_logit': numpy.log(rate1/(1-rate1))
 				})
 		return ans
 
@@ -210,16 +212,16 @@ def dataPlot():
 def main():
 	Nchains=4
[…]

### 2015-09-04 src/des.py
larger run

@@ -210,9 +210,9 @@ def dataPlot():
 	data.plot()
 
 def main():
-	Nchains=4
+	Nchains=16
 	N_sn=2000
-	ADU0=0. #0.2 #0.2
+	ADU0=0.2 #0.2 #0.2
 	ia_only=False
 
 	data= Data(N_sn, 2)
@@ -221,11 +221,11 @@ def main():
 
 	sm = pystan.StanModel(file='des.stan')
 
-	fracspec = numpy.arange(1.,1.01,4)
+	fracspec = numpy.arange(0.2,1.01,.4)
 	for ns in fracspec:
 		data.spectrum(ns)
 
-		fit = sm.sampling(data=data.dict(ia_only=ia_only), iter=1000, thin=1, n_jobs=-1, chains=Nchains, init=data.init(Nchains))
+		fit = sm.sampling(data=data.dict(ia_only=ia_only), iter=2000, thin=1, n_jobs=-1, chains=Nchains, init=data.init(Nchains))
 
 		logposterior = fit.get_logposterior()
 
@@ -236,6 +236,20 @@ def main():
 			app+='.noMalm.'
 		with open('../results/temp/model'+app+str(ns)+'.pkl', 'wb') as f:
 			pickle.dump([fit.extract(), logposterior], f)
+
+	ADU0=0.
+	ns=1.
+	data.spectrum(ns)
+	fit = sm.sampling(data=data.dict(ia_only=ia_only), iter=2000, thin=1, n_jobs=-1, chains=Nchains, init=data.init(Nchains))
+	logposterior = fit.get_logposterior()
+	app=''
+	if ia_only:
+		app+='.ia_only.'
+	if ADU0 == 0.:
+		app+='.noMalm.'
+	with open('../results/temp/model'+app+str(ns)+'.pkl', 'wb') as f:
+		pickle.dump([fit.extract(), logposterior], f)
+
 
 if __name__ == "__main__":
 #	dataPlot()

### 2015-09-04 doc/model.tex
new model description

--- 2015-08-22 doc/model.tex
@@
 \begin{equation}
-p(\mathit{ADU}, {{T}}_S,{{z}}_S, \theta_G| z, \Omega_M, w, \theta_r,\alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}}),
+p(\mathit{ADU}, {{T}}_S,{{z}}_S, \theta_G|  \Omega_M, w, \theta_r,\alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}}),
 \end{equation}
@@
 \begin{itemize}
-\item $z$ is the cosmological redshift.
 \item $\Omega_M$, $w$ are the parameters of a flat dark-energy cosmology.
-\item $\theta_r$ is the fraction of transients that are SN~Ia, independent
-of host-galaxy properties and redshift.
+\item $\theta_r$ describe the fraction of transients that are SN~Ia, independent
+of host-galaxy properties.
 \item $\alpha_{Ia}$, $\sigma_{Ia}$, $\alpha_{\mathit{non-Ia}}$, $\sigma_{\mathit{non-Ia}}$ are
@@
 
+In addition to the above, there are latent model parameters for each transient used internally
+by the model:
+\begin{itemize}
+\item $z$ are the cosmological redshifts.
+\item $T$ are the type, SN~Ia or non-Ia.
+\end{itemize}
+
 The transients are divided into samples defined by available data: {\it obs} are transients observed spectroscopically while active, from which $T_S=1$ are those typed
 as SN~Ia and $T_S=0$ as non-Ia.  {\it mis} transients are not observed
-spectroscopically when active.  The same SN~Ia and non-Ia parameters are taken to
-apply to both {\it obs} and {\it mis} samples.
+spectroscopically when active.  The  {\it obs} and {\it mis} samples
+are assumed to be drawn from the same underlying distribution, so that 
+same SN~Ia and non-Ia parameters apply for both sets.
 
+\subsubsection{Model for the {\it obs} set data}
+The modeling of data from the {\it obs} set, which has
+spectroscopic observations $T_S$ and redshift
+$z_S$, is described as follows.  We are interested in
+\begin{align}
+p(\mathit{ADU}, {{T}}_S,{{z}}_S|  \Omega_M, w, \theta_r,\alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}})  &=\sum_T \int_z dz\,
+p(\mathit{ADU}, {{T}}_S,{{z}}_S, T, z| \ldots)\\
+&= \sum_T \int_z dz\,
+p(\mathit{ADU}, {{T}}_S,{{z}}_S| T, z,\dots) P(T,z | \ldots)
+\end{align}
+
+A direct association of spectroscopic redshift and type are made so that
+\begin{align}
+p(z_S|z) &= \delta(z_S-z)\\
+p(T_S|T) &= \delta(T_S-T),
+\label{specz:eqn}
+\end{align}
+so that
+\begin{align}
+p(\mathit{ADU}, {{T}}_S,{{z}}_S|  \ldots) &= 
+p(\mathit{ADU}| T_S, z_s,\dots) P(T_S,z_S | \ldots)
+\end{align}
+
+The first term: Given the redshift
+and transient type, the brightness of the underlying population
+is modeled as being drawn from a standard candle
+with luminosity $4\pi\alpha_X$ and intrinsic magnitude dispersion  $\sigma_X$:
+\begin{equation}
+\mathit{ADU}| T_S, \Omega_M, w, \theta_r, \alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}} \sim \mathcal{N}_{\ln}\left(\ln{\left(\frac{\alpha_{T_S}}{d_L^2(z_S;\Omega_M, w)}\right)}, \frac{\ln{10}}{2.5}\sigma_{T_S}\right),
+\end{equation}
+where $\mathcal{N}_{\ln}$ is the log-normal distribution and $d_L$ is the luminosity distance.
+
+The subset of objects that enters our analysis comes from a truncated distribution:
 \begin{itemize}
-\item All transients have measured counts at peak brightness $\mathit{ADU}$.
-For transients in set {\it mis} without active spectroscopy:
-\begin{multline}
-p(\mathit{ADU}| z, \Omega_M, w, \theta_r, \alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}})=\\
-\theta_r\mathcal{N}\left(\frac{\alpha_{Ia}}{d_L^2(z;\Omega_M, w)}, \frac{\ln{10}}{2.5}\sigma_{Ia}\right)+\left(1-\theta_r\right)
-\mathcal{N}\left(\frac{\alpha_{\mathit{non-Ia}}}{d_L^2(z;\Omega_M, w)}, \frac{\ln{10}}{2.5}\sigma_{\mathit{non-Ia}}\right).
-\end{multline}
-The luminosity distance $d_L$ is for a flat universe.  
-\item The transients of subset {\it obs} have spectroscopic observations of type $T_S$ and redshift
-$z_S$, which are taken to be unambiguous.
-\begin{itemize}
-\item A direct association of $z_S=z$ is made.
-\begin{equation}
-p(z_S|z) = \delta(z_S-z)
-\label{specz:eqn}
-\end{equation}
 \item For transients in set $T_S=1$:
 \begin{equation}
-p(\mathit{ADU}, T_S=1 | z, \Omega_M, w, \theta_r, \alpha_{Ia},\sigma_{Ia})=
-\theta_r\mathcal{N}\left(\frac{\alpha_{Ia}}{d_L^2(z;\Omega_M, w)}, \frac{\ln{10}}{2.5}\sigma_{Ia}\right).
+\mathit{ADU} | \Omega_M, w, \alpha_{Ia},\sigma_{Ia} \sim
+\frac{\mathcal{N}_{\ln}\left(\ln{\left(\frac{\alpha_{Ia}}{d_L^2(z_S;\Omega_M, w)}\right)}, \frac{\ln{10}}{2.5}\sigma_{Ia}\right)}{P_{Ia}(\mathit{ADU} > \mathit{ADU}_0)}.
+\label{adusnIa:eqn}
 \end{equation}
 \item For transients in set $T_S=0$:
-\begin{multline}
-p(\mathit{ADU}, T_S=0 | z, \Omega_M, w, \theta_r, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}})= \\
-\left(1-\theta_r\right)
-\mathcal{N}\left(\frac{\alpha_{\mathit{non-Ia}}}{d_L^2(z;\Omega_M, w)}, \frac{\ln{10}}{2.5}\sigma_{\mathit{non-Ia}}\right).
-\end{multline}
+\begin{equation}
+\mathit{ADU} | \Omega_M, w, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}}\sim 
+\frac{\mathcal{N}_{\ln}\left(\ln{\left(\frac{\alpha_{\mathit{non-Ia}}}{d_L^2(z_S;\Omega_M, w)}\right)}, \frac{\ln{10}}{2.5}\sigma_{\mathit{non-Ia}}\right)}{P_{non-Ia}(\mathit{ADU} > \mathit{ADU}_0)},
+\label{adunonIa:eqn}
+\end{equation}
 \end{itemize}
-\item All transients have a host with redshift $z$ and have a second
-galaxy at $z_N$ whose projection is close to the host, a potential source of ambiguity.
-The pdf for the redshift of the second galaxy is approximately uniform in volume:
+where the normalization factor is the complementary cumulative distribution function
+for the corresponding log-normal distribution.
+It is understood that $p(\mathit{ADU}<\mathit{ADU}_0)=0$ is never evaluated.
+
+The second term is redshift and type probabilities.  In our model we adopt
+a flat prior on the redshift distribution.
+The underlying relative rates between SNe~Ia and non-Ia are modeled
+as being linear in redshift parameterized by the
+its value at $z=0$ and $1.1 \times z_{max}$, 
 \begin{equation}
-\frac{3 z_N^2}{z_{max}^3 - z_{min}^3}.
+\hat{\theta}_{r}=\theta_{r0}+z\left(\frac{\theta_{r1}-\theta_{r0}}{1.1 \times z_{max}}\right).
 \end{equation}
-The distribution of these galaxies is different from than the distribution of transient redshifts,
-which can lead to bias.
+The relative rate for SN~Ia discovery is then
+\begin{equation}
+\theta_{r}=\frac{\hat{\theta}_{r}}{\hat{\theta}_{r}P_{Ia}(\mathit{ADU} > \mathit{ADU}_0) + (1-\hat{\theta}_{r})P_{non-Ia}(\mathit{ADU} > \mathit{ADU}_0)}.
+\end{equation}
+The spectroscopic classifications are drawn from
+\begin{equation}
+T_S | \theta_{r0}, \theta_{r1} \sim \text{Bernoulli}(\theta_r).
+\end{equation}
 
-The host assignment $\theta_{G1}$ and that of the perceived neighbor
-$\theta_{G2}$ are drawn from
+\subsubsection{Model for the {\it mis} set data}
+
+We now consider the modeling of data from the  {\it mis}
+set that has no spectroscopic confirmation.
+The redshift measurement is treated as follows:
+For each transient there are two galaxies identified as
+the potential host, one ($\theta_{G1}$) with high probability $P_{host}$
+of being the host and the other
+($\theta_{G2}$) at lower $(1-P_{host})$ probability.
+In the model, the
+true host redshift is $z$ and that of the interloping galaxy is $z_N$.
 \begin{equation}
@@
 
-\item This simple example does not consider data $\theta_S$, $\tau$ or $Z$, i.e.
-spectroscopic parameters, sample-selection effects, and calibration.
-\item A prior is applied to the SN~Ia absolute magnitude
+The underlying distribution for counts at peak brightness $\mathit{ADU}$
+is
+\begin{multline}
+p(\mathit{ADU}, \theta_{G1}, \theta_{G2} | \Omega_M, w, \theta_r, \alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}}) \\
+ \sum_{z, T}  p(\mathit{ADU, \theta_{G1}, \theta_{G2}}| z , z_H, T \ldots)P(z, T|\ldots).
+\label{adumis:eqn}
+\end{multline}
+
+The marginalization of Eqn.~\ref{adumis:eqn} thus gives for a transient with $\theta_{G1}$,
+$\theta_{G2}$ an underlying distribution of counts of
+ \begin{multline}
+\mathit{ADU}| \Omega_M, w, \theta_r, \alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}} \\
+ \sim  P_{host} \left[\theta_r \mathcal{N}_{\ln}\left(\ln{\left(\frac{\alpha_{Ia}}{d_L^2(\theta_{G1})}\right)}, \frac{\ln{10}}{2.5}\sigma_{Ia}\right)
++\left(1-\theta_r\right)
+\mathcal{N}_{\ln}\left(\ln{\left(\frac{\alpha_{\mathit{non-Ia}}}{d_L^2(\theta_{G1})}\right)}, \frac{\ln{10}}{2.5}\sigma_{\mathit{non-Ia}}\right) \right] \\
+ + (1-P_{host})\left[ \theta_r \mathcal{N}_{\ln}\left(\ln{\left(\frac{\alpha_{Ia}}{d_L^2(\theta_{G2})}\right)}, \frac{\ln{10}}{2.5}\sigma_{Ia}\right) 
+ + \left(1-\theta_r\right)
+\mathcal{N}_{\ln}\left(\ln{\left(\frac{\alpha_{\mathit{non-Ia}}}{d_L^2(\theta_{G2})}\right)}, \frac{\ln{10}}{2.5}\sigma_{\mathit{non-Ia}}\right) \right],
+\label{adumis2:eqn}
+\end{multline}
+where again we adopt a flat prior in redshift.
+
+The distribution of $\mathit{ADU}$ for our sample is a truncated version of the
+underlying distribution.  
+For our analysis, we use the distribution in  Eqn.~\ref{adumis2:eqn} normalized by
+the complementary cumulative distribution function
 \begin{equation}
-\alpha_{SNIa} \sim \ln\mathcal{N}\left(\ln\left(\alpha^0_{SNIa}\right),\frac{\ln{10}}{2.5}0.02\right),
+P(\mathit{ADU}>\mathit{ADU}_0|\ldots) = \int_{\mathit{ADU}_0}^{\infty} p(\mathit{ADU}|\Omega_M, w, \theta_r, \alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}})d\mathit{ADU}
 \end{equation}
-where $\alpha^0_{SNIa}$ is the true input luminosity.
-\end{itemize}
+for a detection threshold of $\mathit{ADU}_0$.
 
-I highlight the treatment of redshift in this model; the cosmological redshift
-$z$ is set to the values of the
-observed redshifts through $\delta$-functions.  This choice was made specifically to aid
-in the convergence of the Monte Carlo: the discrete possibilities for redshift allow
-for their marginalized likelihood to be used in the calculation of the posterior.
-A more general model would replace the $\delta$-functions
-with coming from a continuous PDF's.
-Peculiar velocities, redshift measurement errors (particularly from
-photometric redshifts) justify this generalization.
-A transient
-without a spectrum has uncertain type and redshift: the redshift
-of the associated host galaxy, and redshifts expected based on the
-flux of the SN~Ia and non-Ia standard candles,
-are viable but disjoint possibilities for the posterior of
-the true underlying redshift. My runs of this scenario produce chains
-that do not mix so I resorted to the simplified treatment presented here.
+%I highlight the treatment of redshift in this model; the cosmological redshift
+%$z$ is set to the values of the
+%observed redshifts through $\delta$-functions.  This choice was made specifically to aid
+%in the convergence of the Monte Carlo: the discrete possibilities for redshift allow
+%for their marginalized likelihood to be used in the calculation of the posterior.
+%A more general model would replace the $\delta$-functions
+%with coming from a continuous PDF's.
+%Peculiar velocities, redshift measurement errors (particularly from
+%photometric redshifts) justify this generalization.
+%A transient
+%without a spectrum has uncertain type and redshift: the redshift
+%of the associated host galaxy, and redshifts expected based on the
+%flux of the SN~Ia and non-Ia standard candles,
+%are viable but disjoint possibilities for the posterior of
+%the true underlying redshift. My runs of this scenario produce chains
+%that do not mix so I resorted to the simplified treatment presented here.
 
@@
 dispersion $\sigma_{non-Ia}=1$.
-\item $\theta_r=0.8$ for a constant relative fraction of SNe~Ia.
-\item 500 transients uniformly distributed in the range $0.1<z<1$.
-\item $z_{min}=0.05$ and $z_{max}=1.5$ is the range of possible misassigned
+\item $\theta_r=r_0 + (r_1-r_0)z/2.1$ for a constant relative fraction of SNe~Ia where $r_1=0.2$,
+$r_0=0.95$.
+\item 2000 transients distributed by co-moving volume in the range $0.1<z<1.4$.
+\item Detection threshold at approximately the mean brightness SN~Ia at $z=1.2$.
+\item $z_{min}=0.1/1.1$ and $z_{max}=1.4\times 1.1$ is the range of possible misassigned
 host redshift.
 \item $P_{host}=0.98$ for the probability of correct host-galaxy assignment.
-\item Accumulated spectra for 200, 350, and 500 transients.
+\item Accumulated spectra for 20\%, 60\%, and 100\% of discovered transients.
 \end{itemize}
+
+In our simulated data sets, the
+pdf for the redshift of the second galaxy is approximately uniform in volume:
+\begin{equation}
+\frac{3 z_N^2}{z_{max}^3 - z_{min}^3}.
+\end{equation}
+
+A prior is applied to the SN~Ia absolute magnitude
+\begin{equation}
+\alpha_{SNIa} \sim \ln\mathcal{N}\left(\ln\left(\alpha^0_{SNIa}\right),\frac{\ln{10}}{2.5}0.02\right),
+\end{equation}
+where $\alpha^0_{SNIa}$ is the true input luminosity.
 

### 2015-09-06 src/des.py
This code works for nomalm 100% spectroscopy except for the renormalization of P(z)

@@ -42,12 +42,15 @@ class Data(object):
 
 	def redshifts_(self):
 		# zs : the true redshifts
-		volume_zero = self.cosmo.comoving_volume(self.zmin).value
-		volume_norm = self.cosmo.comoving_volume(self.zmax).value- volume_zero
+		# volume_zero = self.cosmo.comoving_volume(self.zmin).value
+		# volume_norm = self.cosmo.comoving_volume(self.zmax).value- volume_zero
 
-		self.zs = numpy.sort(numpy.random.uniform(size=self.N_sn))
-		for i in xrange(len(self.zs)):
-			self.zs[i]=scipy.optimize.newton(lambda z: (self.cosmo.comoving_volume(z).value - volume_zero)/volume_norm-self.zs[i], 0.5)		
+		# self.zs = numpy.sort(numpy.random.uniform(size=self.N_sn))
+
+		self.zs=numpy.sort(numpy.random.uniform((1+self.zmin)**3,(1+self.zmax)**3,size=self.N_sn)**(1./3)-1)
+
+		# for i in xrange(len(self.zs)):
+		# 	self.zs[i]=scipy.optimize.newton(lambda z: (self.cosmo.comoving_volume(z).value - volume_zero)/volume_norm-self.zs[i], 0.5)		
 
 	def types_(self):
 		self.snIa = numpy.random.uniform(size=self.N_sn)
@@ -77,19 +80,19 @@ class Data(object):
 
 	def found(self, ADU0):
 		self.ADU0 =ADU0
-		self.found = self.adu>=ADU0
-		self.s_obs_random = numpy.where(self.found)[0]
+		self.found_ = self.adu>=ADU0
+		self.s_obs_random = numpy.where(self.found_)[0]
 		numpy.random.shuffle(self.s_obs_random)
 
 	def spectrum(self, frac_obs):
-		self.N_s_obs = frac_obs*self.found.sum()
+		self.N_s_obs = frac_obs*self.found_.sum()
 		s_obs=numpy.sort(self.s_obs_random[:self.N_s_obs])
 		s_mis= numpy.sort(self.s_obs_random[self.N_s_obs:])
 		self.s_obs = s_obs
 		self.s_mis = s_mis
 
 	def observe(self, ADU0, frac_obs):
-		data.found(ADU0)
+		data.found_(ADU0)
 		data.spectrum(frac_obs)
 
 	def dict(self, ia_only = False):
[…]

### 2015-09-10 src/analyze.py
for real run

@@ -15,8 +15,10 @@ import triangle
 
 levels = numpy.array([0.025, 0.05, 0.16, 1-0.16, 1-0.05, 1-.025])
 
-def individual(N_s, ia_only = False, ADU0=None):
-	app = ''
+def individual(N_s, ia_only = False, ADU0=None,N_sn=None):
+	app=''
+	if N_sn is not None:
+		app='.'+str(N_sn)+'.'
 	if ia_only:
 		app+='.ia_only.'
 	if ADU0 == 0.:
@@ -43,8 +45,8 @@ def individual(N_s, ia_only = False, ADU0=None):
 		samples[:,3] = extract['sigma_Ia']
 		samples[:,4] = extract['alpha_nonIa']
 		samples[:,5] = extract['sigma_nonIa']
-		samples[:,6] = extract['snIa_rate_0'][:,0]
-		samples[:,7] = extract['snIa_rate_1'][:,0]
+		samples[:,6] = extract['snIa_rate_0'][:]
+		samples[:,7] = extract['snIa_rate_1'][:]
 
 		kwargs = {'levels':1.0 - numpy.exp(-0.5 * numpy.arange(1, 3.1, 1) ** 2)}
 		figure = triangle.corner(samples, labels=[r"$\Omega_M$", r"$w$", r"$\alpha_{Ia}$", r"$\sigma_{Ia}$", r"$\alpha_{non-Ia}$", r"$\sigma_{non-Ia}$", r"SN Ia Rate 0", r"SN Ia Rate1"],
@@ -66,12 +68,27 @@ def individual(N_s, ia_only = False, ADU0=None):
 	plt.clf()
 
 
+	plt.plot(extract['snIa_rate_0'])
+	plt.ylabel(r'snIa_rate_0')
+	plt.xlabel('link')
+	plt.tight_layout()
+	plt.savefig('../results/temp/snIa_rate_0.'+app+str(N_s)+'.pdf')
+	plt.clf()
+
+	plt.plot(extract['snIa_rate_1'])
+	plt.ylabel(r'snIa_rate_1')
+	plt.xlabel('link')
+	plt.tight_layout()
+	plt.savefig('../results/temp/snIa_rate_1.'+app+str(N_s)+'.pdf')
+	plt.clf()
+
 	plt.plot(extract['w'])
 	plt.ylabel(r'$w$')
 	plt.xlabel('link')
 	plt.tight_layout()
[…]

### 2015-09-10 src/des.py

@@ -217,6 +217,7 @@ def main():
 	Nchains=4
 	N_sn=2000
 
+	app='.'+str(N_sn)+'.'
 	ia_only=False
 
 	data= Data(N_sn, 2)
@@ -226,7 +227,7 @@ def main():
 	ADU0=0.2 #0.2 #0.2
 	data.found(ADU0)
 
-	fracspec = numpy.arange(1.,1.01,.4)
+	fracspec = numpy.arange(0.2,1.0,0.4)
 	for ns in fracspec:
 		data.spectrum(ns)
 
@@ -234,7 +235,7 @@ def main():
 
 		logposterior = fit.get_logposterior()
 
-		app=''
+
 		if ia_only:
 			app+='.ia_only.'
 		if ADU0 == 0.:
@@ -242,11 +243,26 @@ def main():
 		with open('../results/temp/model'+app+str(ns)+'.pkl', 'wb') as f:
 			pickle.dump([fit.extract(), logposterior], f)
 
+
 	ADU0=0.
 	ns=1.
 	data.found(ADU0)
 	data.spectrum(ns)
 
+
+	fit = sm.sampling(data=data.dict(ia_only=ia_only), iter=1000, thin=1, n_jobs=-1, chains=Nchains, init=data.init(Nchains))
+	logposterior = fit.get_logposterior()
+	app=''
+	if ia_only:
+		app+='.ia_only.'
+	if ADU0 == 0.:
+		app+='.noMalm.'
+	with open('../results/temp/model'+app+str(ns)+'.pkl', 'wb') as f:
+		pickle.dump([fit.extract(), logposterior], f)
+
+	ns=0.2
+	data.found(ADU0)
+	data.spectrum(ns)
 
 	fit = sm.sampling(data=data.dict(ia_only=ia_only), iter=1000, thin=1, n_jobs=-1, chains=Nchains, init=data.init(Nchains))
 	logposterior = fit.get_logposterior()

### 2015-09-10 src/des.py
fix string for output

@@ -252,7 +252,6 @@ def main():
 
 	fit = sm.sampling(data=data.dict(ia_only=ia_only), iter=1000, thin=1, n_jobs=-1, chains=Nchains, init=data.init(Nchains))
 	logposterior = fit.get_logposterior()
-	app=''
 	if ia_only:
 		app+='.ia_only.'
 	if ADU0 == 0.:
@@ -266,7 +265,6 @@ def main():
 
 	fit = sm.sampling(data=data.dict(ia_only=ia_only), iter=1000, thin=1, n_jobs=-1, chains=Nchains, init=data.init(Nchains))
 	logposterior = fit.get_logposterior()
-	app=''
 	if ia_only:
 		app+='.ia_only.'
 	if ADU0 == 0.:

### 2015-09-10 doc/model.tex
current status of code and output now in document

@@
 \item ${{T}}_S$, ${{z}}_S$ are spectroscopic type and redshift for a subset of transients.
-\item $\theta_G$ is the redshift of the galaxy identified as the transient host.
+\item $\theta_G$ are the redshift of the galaxy identified as the transient host.
 \end{itemize}
@@
 &= \sum_T \int_z dz\,
-p(\mathit{ADU}, {{T}}_S,{{z}}_S| T, z,\dots) P(T,z | \ldots)
+p(\mathit{ADU}, {{T}}_S,{{z}}_S| T, z,\dots) p(T,z | \ldots)
 \end{align}
@@
 p(\mathit{ADU}, {{T}}_S,{{z}}_S|  \ldots) &= 
-p(\mathit{ADU}| T_S, z_s,\dots) P(T_S,z_S | \ldots)
+p(\mathit{ADU}| T=T_S, z=z_s,\dots) P(T_S| z= z_S , \ldots) p(z_S|\ldots).
+\label{obs:eqn}
 \end{align}
+We remark that in a flux limited survey, the pdf's for the data are truncated versions of the universal
+pdf's of the observables.
 
-The first term: Given the redshift
+The first term describes the expected counts. Given the redshift
 and transient type, the brightness of the underlying population
@@
 \begin{equation}
-\mathit{ADU}| T_S, \Omega_M, w, \theta_r, \alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}} \sim \mathcal{N}_{\ln}\left(\ln{\left(\frac{\alpha_{T_S}}{d_L^2(z_S;\Omega_M, w)}\right)}, \frac{\ln{10}}{2.5}\sigma_{T_S}\right),
+\mathit{ADU}| T_S, z_S, \Omega_M, w, \theta_r, \alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}} \sim \mathcal{N}_{\ln}\left(\ln{\left(\frac{\alpha_{T_S}}{d_L^2(z_S;\Omega_M, w)}\right)}, \frac{\ln{10}}{2.5}\sigma_{T_S}\right),
 \end{equation}
@@
 \begin{equation}
-\mathit{ADU} | \Omega_M, w, \alpha_{Ia},\sigma_{Ia} \sim
+\mathit{ADU} | T_S=1, z_S, \Omega_M, w, \alpha_{Ia},\sigma_{Ia} \sim
 \frac{\mathcal{N}_{\ln}\left(\ln{\left(\frac{\alpha_{Ia}}{d_L^2(z_S;\Omega_M, w)}\right)}, \frac{\ln{10}}{2.5}\sigma_{Ia}\right)}{P_{Ia}(\mathit{ADU} > \mathit{ADU}_0)}.
@@
 \begin{equation}
-\mathit{ADU} | \Omega_M, w, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}}\sim 
+\mathit{ADU} | T_S=0, z_S, \Omega_M, w, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}}\sim 
 \frac{\mathcal{N}_{\ln}\left(\ln{\left(\frac{\alpha_{\mathit{non-Ia}}}{d_L^2(z_S;\Omega_M, w)}\right)}, \frac{\ln{10}}{2.5}\sigma_{\mathit{non-Ia}}\right)}{P_{non-Ia}(\mathit{ADU} > \mathit{ADU}_0)},
@@
 
-The second term is redshift and type probabilities.  In our model we adopt
-a flat prior on the redshift distribution.
-The underlying relative rates between SNe~Ia and non-Ia are modeled
-as being linear in redshift parameterized by the
+The second term gives the type probability. In our model,
+the underlying relative rates between SNe~Ia and non-Ia is linear in redshift,
+ parameterized by the
 its value at $z=0$ and $1.1 \times z_{max}$, 
@@
 \end{equation}
-The relative rate for SN~Ia discovery is then
+The relative rate for SN~Ia discovery for the truncated distribution is
 \begin{equation}
@@
 \begin{equation}
-T_S | \theta_{r0}, \theta_{r1} \sim \text{Bernoulli}(\theta_r).
+T_S | \Omega_M, w, \theta_{r0}, \theta_{r1} , \alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}} \sim \text{Bernoulli}(\theta_r).
 \end{equation}
+Although the underlying type distribution depends only on $ \theta_{r0}$ and $ \theta_{r1}$,  
+the observed truncated distribution does depend on the other parameters through 
+$P_{X}(\mathit{ADU} > \mathit{ADU}_0)$.
+
+The third term is the redshift distribution of transient discoveries.
+In our model we adopt
+a redshift distribution of transients in the universe
+\begin{equation}
+P(z) \propto z^2.
+\end{equation}
+The redshift distribution of discovered transients is then
+\begin{equation}
+P(z) = \left(\int_{z_{min}}^{z_{max}} dz'\, z'^2\left( 
+\hat{\theta}_{r}P_{Ia}(\mathit{ADU} > \mathit{ADU}_0) + (1-\hat{\theta}_{r})P_{non-Ia}(\mathit{ADU} > \mathit{ADU}_0)
+\right)\right)^{-1}z^2.
+\end{equation}
+
+In the presented model, the data from different transients are independent.
 
@@
 \end{equation}
+As for the {\it obs} set, the redshifts of the supernova
+ and neighbor are drawn from distributions $P(z) \propto z^2$, $P(z_N) \propto z^2_N$.
 
-The underlying distribution for counts at peak brightness $\mathit{ADU}$
-is
+The data likelihood is 
 \begin{multline}
 p(\mathit{ADU}, \theta_{G1}, \theta_{G2} | \Omega_M, w, \theta_r, \alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}})  \\
- \sum_{z, T}  p(\mathit{ADU, \theta_{G1}, \theta_{G2}}| z , z_H, T \ldots)P(z, T|\ldots).
+= \sum_{T}\int_{z,z_N} dz\,dz_N \, p(\mathit{ADU, \theta_{G1}, \theta_{G2}}| z , z_N, T, \ldots)P(T| z, z_N,\ldots) P(z, z_N|\ldots)\\
+ =\sum_{T} \int_{z,z_N} dz\,dz_N\, p(\mathit{ADU}| z ,T, \ldots)p(\theta_{G1}, \theta_{G2}| z , z_N) P(T| z, \ldots) P(z, z_N|\ldots)\\
+= \sum_{T} P_{host} p(\mathit{ADU}| z=\theta_{G1} ,T, \ldots) P(T| z=\theta_{G1}, \ldots) P(\theta_{G1},\theta_{G2}|\ldots) \\
+ +  (1-P_{host}) p(\mathit{ADU}| z=\theta_{G2} ,T, \ldots) P(T| z=\theta_{G2}, \ldots) P(\theta_{G2},
+ \theta_{G1}|\ldots)\\
+\propto \sum_{T} P_{host} p(\mathit{ADU}| z=\theta_{G1} ,T, \ldots) P(T| z=\theta_{G1}, \ldots) \\
+ +  (1-P_{host}) p(\mathit{ADU}| z=\theta_{G2} ,T, \ldots) P(T| z=\theta_{G2}, \ldots),
 \label{adumis:eqn}
 \end{multline}
-
-The marginalization of Eqn.~\ref{adumis:eqn} thus gives for a transient with $\theta_{G1}$,
-$\theta_{G2}$ an underlying distribution of counts of
- \begin{multline}
-\mathit{ADU}| \Omega_M, w, \theta_r, \alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}} \\
- \sim  P_{host} \left[\theta_r \mathcal{N}_{\ln}\left(\ln{\left(\frac{\alpha_{Ia}}{d_L^2(\theta_{G1})}\right)}, \frac{\ln{10}}{2.5}\sigma_{Ia}\right)
-+\left(1-\theta_r\right)
-\mathcal{N}_{\ln}\left(\ln{\left(\frac{\alpha_{\mathit{non-Ia}}}{d_L^2(\theta_{G1})}\right)}, \frac{\ln{10}}{2.5}\sigma_{\mathit{non-Ia}}\right) \right] \\
- + (1-P_{host})\left[ \theta_r \mathcal{N}_{\ln}\left(\ln{\left(\frac{\alpha_{Ia}}{d_L^2(\theta_{G2})}\right)}, \frac{\ln{10}}{2.5}\sigma_{Ia}\right) 
- + \left(1-\theta_r\right)
-\mathcal{N}_{\ln}\left(\ln{\left(\frac{\alpha_{\mathit{non-Ia}}}{d_L^2(\theta_{G2})}\right)}, \frac{\ln{10}}{2.5}\sigma_{\mathit{non-Ia}}\right) \right],
-\label{adumis2:eqn}
-\end{multline}
-where again we adopt a flat prior in redshift.
+where we take advantage of the fact that
+$P(\theta_{G1}, \theta_{G2} | \ldots) = P(\theta_{G2}, \theta_{G1} | \ldots)$ does
+not have parameter dependence.
 
@@
 underlying distribution.  
-For our analysis, we use the distribution in  Eqn.~\ref{adumis2:eqn} normalized by
+For our analysis, we use the distribution in  Eqn.~\ref{adumis:eqn} normalized by
 the complementary cumulative distribution function
 \begin{equation}
-P(\mathit{ADU}>\mathit{ADU}_0|\ldots) = \int_{\mathit{ADU}_0}^{\infty} p(\mathit{ADU}|\Omega_M, w, \theta_r, \alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}})d\mathit{ADU}
+P(\mathit{ADU}>\mathit{ADU}_0, \theta_{G1}, \theta_{G2}|\ldots) = \int_{\mathit{ADU}_0}^{\infty} p(\mathit{ADU}, \theta_{G1}, \theta_{G2}|\Omega_M, w, \theta_r, \alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}})d\mathit{ADU}
 \end{equation}
@@
 dispersion $\sigma_{non-Ia}=1$.
-\item $\theta_r=r_0 + (r_1-r_0)z/2.1$ for a constant relative fraction of SNe~Ia where $r_1=0.2$,
+\item $\theta_r=r_0 + (r_1-r_0)z/1.54$ for a constant relative fraction of SNe~Ia where $r_1=0.2$,
 $r_0=0.95$.
@@
 
-In our simulated data sets, the
-pdf for the redshift of the second galaxy is approximately uniform in volume:
-\begin{equation}
-\frac{3 z_N^2}{z_{max}^3 - z_{min}^3}.
-\end{equation}
-
-A prior is applied to the SN~Ia absolute magnitude
-\begin{equation}
-\alpha_{SNIa} \sim \ln\mathcal{N}\left(\ln\left(\alpha^0_{SNIa}\right),\frac{\ln{10}}{2.5}0.02\right),
-\end{equation}
+A prior is applied to the SN~Ia absolute magnitude and intrinsic dispersion
+\begin{align}
+\alpha_{SNIa} & \sim \mathcal{N}_{\ln}\left(\ln\left(\alpha^0_{SNIa}\right),\frac{\ln{10}}{2.5}0.02\right)\\
+\sigma_{SNIa} & \sim \mathcal{N}_{\ln}\left(\ln\left(0.1\right),0.1\right),
+\end{align}
 where $\alpha^0_{SNIa}$ is the true input luminosity.
@@
 a probabilistic programming language for
-inference of Bayesian models with Hamiltonian Monte Carlo.  There are
-four chains run, each with 50,000 samples then thinned by 5.  Half the links
-are used for burnin, so ultimately 20,000 links are used as draws from the posterior.
+inference of Bayesian models with Hamiltonian Monte Carlo.
 
-\subsubsection{SN~Ia Only}
-A classical analysis would only include confirmed SNe~Ia with a definitive
-redshift. The realization of simulated data has 415 Type~Ia supernovae.
-Results of the analysis of a pure SN~Ia sample with no
-host misclassification are presented:  Figure~\ref{contour.ia_only:fig}
-shows the posteriors for  $\Omega_M$--$w$ and Table~\ref{ia_only:tab} the
-credible equal-tailed intervals for $w$.  The true $w=-1$ is within
-the 0.58 credible interval. (Note that $w$ is the parameter
-of most interest for the experiment.)
+\subsubsection{Results}
 
@@
    \centering
-   \includegraphics[scale=0.55]{/Users/akim/project/abc/results/{contour..ia_only.500}.pdf} \newline
-\caption{Probability distribution function for $\Omega_M$--$w$ for only SNe~Ia
-   all with spectra.
+   \includegraphics[scale=0.35]{/Users/akim/project/abc/results/temp/{contour..2000..noMalm.1.0}.pdf} \newline
+\caption{Probability distribution function for $\Omega_M$--$w$,
+ 100\% spectroscopy no Malmquist bias.
    Solid lines represent the input cosmology.  Dashed lines in the
    histograms are the 0.16 and 0.86 quantiles. 
-   \label{contour.ia_only:fig}}
+   \label{contour1:fig}}
+\end{figure}
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[scale=0.35]{/Users/akim/project/abc/results/temp/{contour..2000.1.0}.pdf} \newline
+\caption{Probability distribution function for $\Omega_M$--$w$,
+ 100\% spectroscopy with Malmquist bias.
+   \label{contour2:fig}}
+\end{figure}
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[scale=0.35]{/Users/akim/project/abc/results/temp/{contour..2000.0.6}.pdf} \newline
+\caption{Probability distribution function for $\Omega_M$--$w$,
+ 60\% spectroscopy with Malmquist bias.
+   \label{contour3:fig}}
+\end{figure}
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[scale=0.35]{/Users/akim/project/abc/results/temp/{contour..2000.0.2}.pdf} \newline
+\caption{Probability distribution function for $\Omega_M$--$w$,
+ 20\% spectroscopy with Malmquist bias.
+   \label{contour4:fig}}
+\end{figure}
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[scale=0.35]{/Users/akim/project/abc/results/temp/{contour..2000..noMalm.0.2}.pdf} \newline
+\caption{Probability distribution function for $\Omega_M$--$w$,
+ 20\% spectroscopy without Malmquist bias.
+   \label{contour4:fig}}
 \end{figure}
@@
 \centering
-\begin{tabular}{|c|cc|}
+\begin{tabular}{cc|c|cc|}
 \hline
-\%-ile & $w$ range & $\Delta w$\\ \hline
-$0.68$ & $[-1.254, -0.975]$ & $0.279$ \\
-$0.90$ & $[-1.347, -0.889]$ & $0.458$ \\
-$0.95$ & $[-1.396, -0.846]$ & $0.550$ \\
+ADU0&\% Spec&\%-ile & $w$ range & $\Delta w$\\ \hline
+0 & 100 &$0.68$ & $[-1.174, -0.982]$ & $0.192$ \\
+&&$0.90$ & $[-1.239, -0.923]$ & $0.316$ \\
+&&$0.95$ & $[-1.267, -0.894]$ & $0.373$ \\ \hline
+0.2 & 100&$0.68$ & $[-1.156, -0.972]$ & $0.184$ \\
+&&$0.90$ & $[-1.222, -0.912]$ & $0.309$ \\
+&&$0.95$ & $[-1.255, -0.883]$ & $0.372$ \\ \hline
+0.2&60&$0.68$ & $[-1.209, -1.014]$ & $0.195$ \\
+&&$0.90$ & $[-1.275, -0.955]$ & $0.321$ \\
+&&$0.95$ & $[-1.309, -0.924]$ & $0.385$ \\ \hline
+0&20&$0.68$ & $[-1.226, -1.032]$ & $0.194$ \\
+&&$0.90$ & $[-1.289, -0.969]$ & $0.320$ \\
+&&$0.95$ & $[-1.322, -0.942]$ & $0.379$ \\ \hline
+0.2& 20&$0.68$ & $[-1.229, -1.033]$ & $0.196$ \\
+&&$0.90$ & $[-1.294, -0.972]$ & $0.322$ \\
+&&$0.95$ & $[-1.323, -0.943]$ & $0.380$ \\
 \hline
@@
 
-\subsubsection{Full Sample: Varying Spectroscopic Completeness}
-We now turn to the full sample of SNe~Ia and non-Ia's.  Recall that our simple
-model treats the non-Ia's in the sample
-as standard candles with a large (1 mag) intrinsic dispersion.
-
-Results for the $\Omega_M$--$w$ posterior for the
-case of 40\%, 70\%, and 100\% spectroscopic completeness
-are shown in Figures~\ref{contour.200:fig}, \ref{contour.350:fig}, and
-\ref{contour.500:fig} respectively.
-The credible intervals
-of $w$ for are given in Table~\ref{compare:tab}, with
-the input $w=-1$ within the 0.65, 0.49, and 0.47  intervals
-respectively.
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[scale=0.40]{/Users/akim/project/abc/results/{contour.200}.pdf} 
-   \caption{Probability distribution function for $\Omega_M$--$w$ for:
-    SNe~Ia and non-Ia with 40\%  spectroscopic completeness.
-   \label{contour.200:fig}}
-\end{figure}
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[scale=0.40]{/Users/akim/project/abc/results/{contour.350}.pdf} 
-   \caption{Probability distribution function for $\Omega_M$--$w$ for
-    SNe~Ia and non-Ia with 70\%  spectroscopic completeness.
-   \label{contour.350:fig}}
-\end{figure}
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[scale=0.40]{/Users/akim/project/abc/results/{contour.500}.pdf} 
-   %\includegraphics[scale=0.55]{/Users/akim/project/abc/results/{contour.200}.pdf}    
-   \caption{Probability distribution function for $\Omega_M$--$w$ for
-    SNe~Ia and non-Ia with 100\%  spectroscopic completeness.
-   \label{contour.500:fig}}
-\end{figure}
-
-\begin{table}[htbp] 
-\centering
-\begin{tabular}{|cc|cc|}
-\hline
-\# Spectra & \%-ile & $w$ range & $\Delta$\\ \hline
-200& $0.68$ & $[-1.284, -0.991]$ & $0.293$ \\
-200& $0.90$ & $[-1.385, -0.900]$ & $0.485$ \\
-200& $0.95$ & $[-1.435, -0.860]$ & $0.575$ \\
-350& $0.68$ & $[-1.243, -0.952]$ & $0.291$ \\
-350& $0.90$ & $[-1.339, -0.858]$ & $0.481$ \\
-350& $0.95$ & $[-1.390, -0.817]$ & $0.573$ \\
-500& $0.68$ & $[-1.236, -0.948]$ & $0.289$ \\
-500& $0.90$ & $[-1.336, -0.861]$ & $0.475$ \\
-500& $0.95$ & $[-1.385, -0.815]$ & $0.570$ \\
-\hline
-\end{tabular}
-\caption{Credible intervals of $w$ given different levels of spectroscopy.  \label{compare:tab}}
-\end{table}
-
-As would be expected, the better the spectroscopic completeness, the less bias
-and smaller uncertainties that are obtained.
-
+%
+%\subsubsection{SN~Ia Only}
+%A classical analysis would only include confirmed SNe~Ia with a definitive
+%redshift. The realization of simulated data has 415 Type~Ia supernovae.
+%Results of the analysis of a pure SN~Ia sample with no
+%host misclassification are presented:  Figure~\ref{contour.ia_only:fig}
+%shows the posteriors for  $\Omega_M$--$w$ and Table~\ref{ia_only:tab} the
+%credible equal-tailed intervals for $w$.  The true $w=-1$ is within
+%the 0.58 credible interval. (Note that $w$ is the parameter
+%of most interest for the experiment.)
+%
+%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+%   \centering
+%   \includegraphics[scale=0.55]{/Users/akim/project/abc/results/{contour..ia_only.500}.pdf} \newline
+%\caption{Probability distribution function for $\Omega_M$--$w$ for only SNe~Ia
+%   all with spectra.
+%   Solid lines represent the input cosmology.  Dashed lines in the
+%   histograms are the 0.16 and 0.86 quantiles. 
+%   \label{contour.ia_only:fig}}
+%\end{figure}
+%
+%\begin{table}
+%\centering
+%\begin{tabular}{|c|cc|}
+%\hline
+%\%-ile & $w$ range & $\Delta w$\\ \hline
+%$0.68$ & $[-1.254, -0.975]$ & $0.279$ \\
+%$0.90$ & $[-1.347, -0.889]$ & $0.458$ \\
+%$0.95$ & $[-1.396, -0.846]$ & $0.550$ \\
+%\hline
+%\end{tabular}
+%\caption{Credible intervals of $w$ using the SNe~Ia only with spectroscopic
+%observations.\label{ia_only:tab}}
+%\end{table}
+%
+%\subsubsection{Full Sample: Varying Spectroscopic Completeness}
+%We now turn to the full sample of SNe~Ia and non-Ia's.  Recall that our simple
+%model treats the non-Ia's in the sample
+%as standard candles with a large (1 mag) intrinsic dispersion.
+%
+%Results for the $\Omega_M$--$w$ posterior for the
+%case of 40\%, 70\%, and 100\% spectroscopic completeness
+%are shown in Figures~\ref{contour.200:fig}, \ref{contour.350:fig}, and
+%\ref{contour.500:fig} respectively.
+%The credible intervals
+%of $w$ for are given in Table~\ref{compare:tab}, with
+%the input $w=-1$ within the 0.65, 0.49, and 0.47  intervals
+%respectively.
+%
+%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+%   \centering
+%   \includegraphics[scale=0.40]{/Users/akim/project/abc/results/{contour.200}.pdf} 
+%   \caption{Probability distribution function for $\Omega_M$--$w$ for:
+%    SNe~Ia and non-Ia with 40\%  spectroscopic completeness.
+%   \label{contour.200:fig}}
+%\end{figure}
+%
+%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+%   \centering
+%   \includegraphics[scale=0.40]{/Users/akim/project/abc/results/{contour.350}.pdf} 
+%   \caption{Probability distribution function for $\Omega_M$--$w$ for
+%    SNe~Ia and non-Ia with 70\%  spectroscopic completeness.
+%   \label{contour.350:fig}}
+%\end{figure}
+%
+%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+%   \centering
+%   \includegraphics[scale=0.40]{/Users/akim/project/abc/results/{contour.500}.pdf} 
+%   %\includegraphics[scale=0.55]{/Users/akim/project/abc/results/{contour.200}.pdf}    
+%   \caption{Probability distribution function for $\Omega_M$--$w$ for
+%    SNe~Ia and non-Ia with 100\%  spectroscopic completeness.
+%   \label{contour.500:fig}}
+%\end{figure}
+%
+%\begin{table}[htbp] 
+%\centering
+%\begin{tabular}{|cc|cc|}
+%\hline
+%\# Spectra & \%-ile & $w$ range & $\Delta$\\ \hline
+%200& $0.68$ & $[-1.284, -0.991]$ & $0.293$ \\
+%200& $0.90$ & $[-1.385, -0.900]$ & $0.485$ \\
+%200& $0.95$ & $[-1.435, -0.860]$ & $0.575$ \\
+%350& $0.68$ & $[-1.243, -0.952]$ & $0.291$ \\
+%350& $0.90$ & $[-1.339, -0.858]$ & $0.481$ \\
+%350& $0.95$ & $[-1.390, -0.817]$ & $0.573$ \\
+%500& $0.68$ & $[-1.236, -0.948]$ & $0.289$ \\
+%500& $0.90$ & $[-1.336, -0.861]$ & $0.475$ \\
+%500& $0.95$ & $[-1.385, -0.815]$ & $0.570$ \\
+%\hline
+%\end{tabular}
+%\caption{Credible intervals of $w$ given different levels of spectroscopy.  \label{compare:tab}}
+%\end{table}
+%
+%As would be expected, the better the spectroscopic completeness, the less bias
+%and smaller uncertainties that are obtained.
+%
 %

### 2015-09-13 src/des.py
do all for no malmquist bias

@@ -217,60 +217,62 @@ def main():
 	Nchains=4
 	N_sn=2000
 
-	app='.'+str(N_sn)+'.'
 	ia_only=False
 
 	data= Data(N_sn, 2)
 
 	sm = pystan.StanModel(file='des.stan')
 
-	ADU0=0.2 #0.2 #0.2
-	data.found(ADU0)
+	ADU0s = [0.,0.2]
+	for ADU0 in ADU0s:
+		app='.'+str(N_sn)+'.'
+		ADU0=0.2 #0.2 #0.2
+		data.found(ADU0)
 
-	fracspec = numpy.arange(0.2,1.0,0.4)
-	for ns in fracspec:
-		data.spectrum(ns)
+		fracspec = numpy.arange(0.2,1.0,0.4)
+		for ns in fracspec:
+			data.spectrum(ns)
 
-		fit = sm.sampling(data=data.dict(ia_only=ia_only), iter=1000, thin=1, n_jobs=-1, chains=Nchains, init=data.init(Nchains))
+			fit = sm.sampling(data=data.dict(ia_only=ia_only), iter=1000, thin=1, n_jobs=-1, chains=Nchains, init=data.init(Nchains))
 
-		logposterior = fit.get_logposterior()
-
-
-		if ia_only:
-			app+='.ia_only.'
-		if ADU0 == 0.:
-			app+='.noMalm.'
-		with open('../results/temp/model'+app+str(ns)+'.pkl', 'wb') as f:
-			pickle.dump([fit.extract(), logposterior], f)
+			logposterior = fit.get_logposterior()
 
 
-	ADU0=0.
-	ns=1.
-	data.found(ADU0)
-	data.spectrum(ns)
+			if ia_only:
+				app+='.ia_only.'
+			if ADU0 == 0.:
+				app+='noMalm.'
+			with open('../results/temp/model'+app+str(ns)+'.pkl', 'wb') as f:
+				pickle.dump([fit.extract(), logposterior], f)
 
 
-	fit = sm.sampling(data=data.dict(ia_only=ia_only), iter=1000, thin=1, n_jobs=-1, chains=Nchains, init=data.init(Nchains))
-	logposterior = fit.get_logposterior()
-	if ia_only:
-		app+='.ia_only.'
-	if ADU0 == 0.:
-		app+='.noMalm.'
-	with open('../results/temp/model'+app+str(ns)+'.pkl', 'wb') as f:
[…]

### 2015-09-13 src/des.py
fix adu0

@@ -226,7 +226,6 @@ def main():
 	ADU0s = [0.,0.2]
 	for ADU0 in ADU0s:
 		app='.'+str(N_sn)+'.'
-		ADU0=0.2 #0.2 #0.2
 		data.found(ADU0)
 
 		fracspec = numpy.arange(0.2,1.0,0.4)

### 2015-09-14 src/des.py
add bias

@@ -143,7 +143,8 @@ class Data(object):
 				'host_zs_mis': self.host_zs_random[self.s_mis],
 				'host2_zs_mis': self.neighbor_zs_random[self.s_mis],
 
-				'ADU0': self.ADU0
+				'ADU0': self.ADU0, 
+				'bias_anal':0,
 				}
 
 	def init(self, n):
@@ -223,12 +224,15 @@ def main():
 
 	sm = pystan.StanModel(file='des.stan')
 
-	ADU0s = [0.,0.2]
+	ADU0s = [0., 0.2]
 	for ADU0 in ADU0s:
 		app='.'+str(N_sn)+'.'
+		if ADU0 == 0.:
+			app+='noMalm.'
+		
 		data.found(ADU0)
 
-		fracspec = numpy.arange(0.2,1.0,0.4)
+		fracspec = numpy.arange(0.2,1.1,0.4)
 		for ns in fracspec:
 			data.spectrum(ns)
 
@@ -239,8 +243,7 @@ def main():
 
 			if ia_only:
 				app+='.ia_only.'
-			if ADU0 == 0.:
-				app+='noMalm.'
+
 			with open('../results/temp/model'+app+str(ns)+'.pkl', 'wb') as f:
 				pickle.dump([fit.extract(), logposterior], f)
 

### 2015-09-14 doc/model.tex
modified document

@@
 p(\mathit{ADU}, \theta_{G1}, \theta_{G2} | \Omega_M, w, \theta_r, \alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}})  \\
-= \sum_{T}\int_{z,z_N} dz\,dz_N \, p(\mathit{ADU, \theta_{G1}, \theta_{G2}}| z , z_N, T, \ldots)P(T| z, z_N,\ldots) P(z, z_N|\ldots)\\
- =\sum_{T} \int_{z,z_N} dz\,dz_N\, p(\mathit{ADU}| z ,T, \ldots)p(\theta_{G1}, \theta_{G2}| z , z_N) P(T| z, \ldots) P(z, z_N|\ldots)\\
-= \sum_{T} P_{host} p(\mathit{ADU}| z=\theta_{G1} ,T, \ldots) P(T| z=\theta_{G1}, \ldots) P(\theta_{G1},\theta_{G2}|\ldots) \\
- +  (1-P_{host}) p(\mathit{ADU}| z=\theta_{G2} ,T, \ldots) P(T| z=\theta_{G2}, \ldots) P(\theta_{G2},
+= \sum_{T}\int_{z,z_N} dz\,dz_N \, p(\mathit{ADU, \theta_{G1}, \theta_{G2}}| z , z_N, T, \ldots)P(T| z, z_N,\ldots) p(z, z_N|\ldots)\\
+ =\sum_{T} \int_{z,z_N} dz\,dz_N\, p(\mathit{ADU}| z ,T, \ldots)p(\theta_{G1}, \theta_{G2}| z , z_N) P(T| z, \ldots) p(z, z_N|\ldots)\\
+= \sum_{T} P_{host} p(\mathit{ADU}| z=\theta_{G1} ,T, \ldots) P(T| z=\theta_{G1}, \ldots) p(\theta_{G1},\theta_{G2}|\ldots) \\
+ +  (1-P_{host}) p(\mathit{ADU}| z=\theta_{G2} ,T, \ldots) P(T| z=\theta_{G2}, \ldots) p(\theta_{G2},
  \theta_{G1}|\ldots)\\
@@
 where we take advantage of the fact that
-$P(\theta_{G1}, \theta_{G2} | \ldots) = P(\theta_{G2}, \theta_{G1} | \ldots)$ does
+$p(\theta_{G1}, \theta_{G2} | \ldots) = p(\theta_{G2}, \theta_{G1} | \ldots)$ does
 not have parameter dependence.

### 2015-09-14 src/plots.py

@@ -1,0 +1,213 @@
+#!/usr/bin/env python
+
+import matplotlib
+#matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+
+import pystan
+import numpy.random
+from astropy.cosmology import FlatLambdaCDM
+
+import pickle
+import des
+
+import triangle
+
+levels = numpy.array([0.025, 0.05, 0.16, 1-0.16, 1-0.05, 1-.025])
+
+def individual(N_s, ia_only = False, ADU0=None,N_sn=None,dir='temp'):
+	app=''
+	if N_sn is not None:
+		app='.'+str(N_sn)+'.'
+	if ia_only:
+		app+='.ia_only.'
+	if ADU0 == 0.:
+			app+='noMalm.'
+	[extract,logposterior] = pickle.load(file('../results/'+dir+'/model'+app+str(N_s)+'.pkl','rb'))
+#	print numpy.abs((extract['w'] < -1).sum()*1. / len(extract['w'])-0.5)*2
+	n_samples = len(extract[extract.keys()[0]])
+
+
+	samples=numpy.zeros((n_samples,8))
+	samples[:,0] = extract['Omega_M']
+	samples[:,1] = extract['w']
+	samples[:,2] = extract['alpha_Ia']
+	samples[:,3] = extract['sigma_Ia']
+	samples[:,4] = extract['alpha_nonIa']
+	samples[:,5] = extract['sigma_nonIa']
+	samples[:,6] = extract['snIa_rate_0'][:]
+	samples[:,7] = extract['snIa_rate_1'][:]
+
+	kwargs = {'levels':1.0 - numpy.exp(-0.5 * numpy.arange(1, 3.1, 1) ** 2)}
+	figure = triangle.corner(samples, labels=[r"$\Omega_M$", r"$w$", r"$\alpha_{Ia}$", r"$\sigma_{Ia}$", r"$\alpha_{non-Ia}$", r"$\sigma_{non-Ia}$", r"SN Ia Rate 0", r"SN Ia Rate1"],
+		truths=[0.28,-1, 2.,0.1,2*10**(-2./2.5),1,0.95,0.2],
+		quantiles=[0.16, 0.5, 0.84], plot_datapoints=False,plot_density=True, **kwargs)
+	plt.savefig('../results/'+dir+'/contour'+app+str(N_s)+'.pdf')
+	plt.clf()
+
[…]

### 2015-09-14 src/analyze.py
whatever

@@ -181,7 +181,7 @@ def group(nspec):
 
 
 def main():
-	individual(0.6,ia_only=False,ADU0=0.,N_sn=2000)
+	individual(1.0,ia_only=False,ADU0=0.2,N_sn=2000)
 #	individual(500,ia_only=False)
 	wefew
 	group([200,350,500])

### 2015-09-15 src/analyze.py
add second non-Ia population

@@ -15,15 +15,15 @@ import triangle
 
 levels = numpy.array([0.025, 0.05, 0.16, 1-0.16, 1-0.05, 1-.025])
 
-def individual(N_s, ia_only = False, ADU0=None,N_sn=None):
+def individual(N_s, ia_only = False, ADU0=None,N_sn=None,dir='temp'):
 	app=''
 	if N_sn is not None:
-		app='.'+str(N_sn)+'.'
+		app='.'+str(N_sn)
 	if ia_only:
 		app+='.ia_only.'
 	if ADU0 == 0.:
 			app+='.noMalm.'
-	[extract,logposterior] = pickle.load(file('../results/temp/model'+app+str(N_s)+'.pkl','rb'))
+	[extract,logposterior] = pickle.load(file('../results/'+dir+'/model'+app+str(N_s)+'.pkl','rb'))
 #	print numpy.abs((extract['w'] < -1).sum()*1. / len(extract['w'])-0.5)*2
 	n_samples = len(extract[extract.keys()[0]])
 
@@ -35,7 +35,7 @@ def individual(N_s, ia_only = False, ADU0=None,N_sn=None):
 		samples[:,3] = extract['sigma_Ia']
 		figure = triangle.corner(samples, labels=[r"$\Omega_M$", r"$w$", r"$\alpha_{Ia}$", r"$\sigma_{Ia}$"],truths=[0.28,-1, 2.,0.1],
 			quantiles=[0.16, 0.5, 0.84], plot_datapoints=False,plot_density=True)
-		plt.savefig('../results/temp/contour.'+app+str(N_s)+'.pdf')
+		plt.savefig('../results/'+dir+'/contour'+app+str(N_s)+'.pdf')
 		plt.clf()
 	else:
 		samples=numpy.zeros((n_samples,8))
@@ -52,7 +52,7 @@ def individual(N_s, ia_only = False, ADU0=None,N_sn=None):
 		figure = triangle.corner(samples, labels=[r"$\Omega_M$", r"$w$", r"$\alpha_{Ia}$", r"$\sigma_{Ia}$", r"$\alpha_{non-Ia}$", r"$\sigma_{non-Ia}$", r"SN Ia Rate 0", r"SN Ia Rate1"],
 			truths=[0.28,-1, 2.,0.1,2*10**(-2./2.5),1,0.95,0.2],
[…]

### 2015-09-15 src/des.py

@@ -26,11 +26,18 @@ class Data(object):
 
 		self.sigma_snIa=0.1
 		self.sigma_nonIa=1.
+		self.sigma_nonIa_2=0.5
 
 		self.alpha_snIa=2.
 		self.alpha_nonIa=self.alpha_snIa*10**(-2./2.5)
+		self.alpha_nonIa_2=self.alpha_snIa*10**(-0.5/2.5)
+
 		self.frac_Ia_0=.95
 		self.frac_Ia_1=.2
+
+		self.frac_nonIa_0=1.
+		self.frac_nonIa_1=0.2
+
 		numpy.random.seed(seed)
 		self.initialize_()
 
@@ -39,6 +46,7 @@ class Data(object):
 		self.types_()
 		self.adus_()
 		self.hosts_()
+		self.pop2_()
 
 	def redshifts_(self):
 		# zs : the true redshifts
@@ -57,6 +65,8 @@ class Data(object):
 	def types_(self):
 		self.snIa = numpy.random.uniform(size=self.N_sn)
 		self.snIa = numpy.less_equal(self.snIa, self.frac_Ia_0 + (self.frac_Ia_1-self.frac_Ia_0)*self.zs/self.zmax/1.1).astype(int)
+		self.nonIa = numpy.random.uniform(size=self.N_sn)
+		self.nonIa = numpy.less_equal(self.nonIa, self.frac_nonIa_0 + (self.frac_nonIa_1-self.frac_nonIa_0)*(self.zs**2)/((self.zmax/1.1))**2).astype(int)
 
 	def adus_(self):
 		adu = 1/(self.cosmo.luminosity_distance(self.zs).value/self.cosmo.hubble_distance.value)**2
@@ -80,6 +90,13 @@ class Data(object):
 		self.neighbor_zs=numpy.random.uniform((self.zmin/1.1)**3, (self.zmax*1.1)**3,size=self.N_sn)**(1./3)
 		self.host_zs_random = self.zs*self.host_choice + self.neighbor_zs*(1-self.host_choice)
 		self.neighbor_zs_random = self.zs*(1-self.host_choice) + self.neighbor_zs*self.host_choice
+
+	def pop2_(self):
+		adu = 1/(self.cosmo.luminosity_distance(self.zs).value/self.cosmo.hubble_distance.value)**2
[…]

### 2015-09-15 src/plots.py

@@ -54,7 +54,8 @@ def individual(N_s, ia_only = False, ADU0=None,N_sn=None,dir='temp'):
 	for i in xrange(len(levels)/2-1,-1,-1):
 		print '${:4.2f}$ &${:4.2f}$ &${:4.2f}$ & $[{:5.3f}, {:5.3f}]$ & ${:5.3f}$ \\\\'.format(ADU0, N_s, 1-levels[i]*2, ans[i],ans[-1-i], deltas[i])
 
-	fractions = [0.6, 0.2]
+	fractions = [0.6, 0.2, 0.0]
+	#fractions = [0.0]
 
 	for frac in fractions:
 		[extract_,logposterior_] = pickle.load(file('../results/'+dir+'/model'+app+str(frac)+'.pkl','rb'))
@@ -200,7 +201,7 @@ def group(nspec):
 
 
 def main():
-	key='temp'
+	key='seed2'
 	individual(1.0,ia_only=False,ADU0=0.2,N_sn=2000, dir=key)
 	individual(1.0,ia_only=False,ADU0=0.,N_sn=2000, dir=key)
 

### 2015-09-15 src/des.py
remove bad comma

@@ -161,7 +161,7 @@ class Data(object):
 				'host2_zs_mis': self.neighbor_zs_random[self.s_mis],
 
 				'ADU0': self.ADU0, 
-				'bias_anal':0,
+				'bias_anal':0
 				}
 
 	def init(self, n):

### 2015-09-15 src/des.py
ensure consistent random numbers for two non-Ia populations

@@ -38,6 +38,9 @@ class Data(object):
 		self.frac_nonIa_0=1.
 		self.frac_nonIa_1=0.2
 
+		# self.frac_nonIa_0=1.
+		# self.frac_nonIa_1=1.
+
 		numpy.random.seed(seed)
 		self.initialize_()
 
@@ -46,7 +49,6 @@ class Data(object):
 		self.types_()
 		self.adus_()
 		self.hosts_()
-		self.pop2_()
 
 	def redshifts_(self):
 		# zs : the true redshifts
@@ -75,6 +77,8 @@ class Data(object):
 		wnonIa = numpy.where(numpy.logical_not(self.snIa))[0]
 		adu[wsnIa] = self.alpha_snIa*adu[wsnIa]*10**(adu_random[wsnIa]*self.sigma_snIa/2.5)
 		adu[wnonIa] = self.alpha_nonIa*adu[wnonIa]*10**(adu_random[wnonIa]*self.sigma_nonIa/2.5)
+		wpop2 = numpy.where(numpy.logical_and(self.snIa ==0, self.nonIa ==0))[0]
+		adu[wpop2] = self.alpha_nonIa_2*adu[wpop2]*10**(adu_random[wpop2]*self.sigma_nonIa_2/2.5)
 		self.adu = adu
 
 	def hosts_(self):
@@ -90,12 +94,6 @@ class Data(object):
 		self.neighbor_zs=numpy.random.uniform((self.zmin/1.1)**3, (self.zmax*1.1)**3,size=self.N_sn)**(1./3)
 		self.host_zs_random = self.zs*self.host_choice + self.neighbor_zs*(1-self.host_choice)
 		self.neighbor_zs_random = self.zs*(1-self.host_choice) + self.neighbor_zs*self.host_choice
-
-	def pop2_(self):
-		adu = 1/(self.cosmo.luminosity_distance(self.zs).value/self.cosmo.hubble_distance.value)**2
-		wpop2 = numpy.where(numpy.logical_and(self.snIa ==0, self.nonIa ==0))[0]
-		adu_random = numpy.random.normal(size=len(wpop2))
-		self.adu[wpop2] = self.alpha_nonIa_2*adu[wpop2]*10**(adu_random*self.sigma_nonIa_2/2.5)
 
 
 	def found(self, ADU0):

### 2015-09-16 src/des.py
ADU0=0.75 more appropriate for redshift of Malmquist bias

@@ -35,11 +35,11 @@ class Data(object):
 		self.frac_Ia_0=.95
 		self.frac_Ia_1=.2
 
-		self.frac_nonIa_0=1.
-		self.frac_nonIa_1=0.2
-
 		# self.frac_nonIa_0=1.
-		# self.frac_nonIa_1=1.
+		# self.frac_nonIa_1=0.2
+
+		self.frac_nonIa_0=1.
+		self.frac_nonIa_1=1.
 
 		numpy.random.seed(seed)
 		self.initialize_()
@@ -221,10 +221,10 @@ class Data(object):
 
 def dataPlot():
 	N_sn=2000
-	ADU0=.2
+	ADU0=.75
 	ia_only=False
 
-	data= Data(N_sn, 1)
+	data= Data(N_sn, 2)
 	data.found(ADU0)
 	data.spectrum(0.2)
 	data.plot()
@@ -239,7 +239,7 @@ def main():
 
 	sm = pystan.StanModel(file='des.stan')
 
-	ADU0s = [0., 0.2]
+	ADU0s = [0.75]
 	for ADU0 in ADU0s:
 		app='.'+str(N_sn)+'.'
 		if ADU0 == 0.:
@@ -294,5 +294,5 @@ def main():
 
 
 if __name__ == "__main__":
-#	dataPlot()
-    main()
+	dataPlot()
+#    main()

### 2015-09-16 src/des.py
set default to main not plot

@@ -35,11 +35,11 @@ class Data(object):
 		self.frac_Ia_0=.95
 		self.frac_Ia_1=.2
 
-		# self.frac_nonIa_0=1.
-		# self.frac_nonIa_1=0.2
-
 		self.frac_nonIa_0=1.
-		self.frac_nonIa_1=1.
+		self.frac_nonIa_1=0.2
+
+		# self.frac_nonIa_0=1.
+		# self.frac_nonIa_1=1.
 
 		numpy.random.seed(seed)
 		self.initialize_()
@@ -294,5 +294,5 @@ def main():
 
 
 if __name__ == "__main__":
-	dataPlot()
-#    main()
+#	dataPlot()
+    main()

### 2015-09-17 src/des.py
add analysis as if all were Ia

@@ -13,7 +13,7 @@ import pickle
 
 class Data(object):
 	"""docstring for Data"""
-	def __init__(self, N_sn, seed, pop2=False):
+	def __init__(self, N_sn, seed, pop2=False, asifIa = False):
 		super(Data, self).__init__()
 		self.N_sn = N_sn
 		self.seed = seed
@@ -34,6 +34,8 @@ class Data(object):
 
 		self.frac_Ia_0=.95
 		self.frac_Ia_1=.2
+
+		self.asifIa = asifIa
 
 
 		if pop2:
@@ -106,6 +108,8 @@ class Data(object):
 		numpy.random.shuffle(self.s_obs_random)
 
 	def spectrum(self, frac_obs):
+		if self.asifIa:
+			frac_obs=1.
 		self.N_s_obs = frac_obs*self.found_.sum()
 		s_obs=numpy.sort(self.s_obs_random[:self.N_s_obs])
 		s_mis= numpy.sort(self.s_obs_random[self.N_s_obs:])
@@ -143,9 +147,15 @@ class Data(object):
 		else:
 			self.s_obs = self.s_obs.tolist()
 			self.s_mis = self.s_mis.tolist()
+
+			dum= self.snIa[self.s_obs]
+
+			if self.asifIa:
+				dum[:]=1
+
 			return 	{'N_sn': self.found_.sum(),
 				'N_obs': len(self.s_obs),
-				'N_SNIa': self.snIa[self.s_obs].sum(),
+				'N_SNIa': dum.sum(),
 				'N_adu_max':1,
 
 				'zmin':self.zmin,
@@ -155,7 +165,7 @@ class Data(object):
 				'adu_mis': self.adu[self.s_mis],
 
 				'trans_ainv_obs': 1+self.zs[self.s_obs],
-				'snIa_obs': self.snIa[self.s_obs],
+				'snIa_obs': dum,
 
 				'host_zs_obs': self.host_zs_random[self.s_obs], #zs[s_obs],
 				'host_zs_mis': self.host_zs_random[self.s_mis],
@@ -238,6 +248,7 @@ def main():
 	Nchains=4
 	N_sn=2000
 	pop2=False
+	asifIa = False
 
 	ia_only=False ###deprecated
 
@@ -246,7 +257,7 @@ def main():
 	else :
 		dire=''
 
-	data= Data(N_sn, 2, pop2=pop2)
[…]

### 2015-09-18 src/des.py
fix bug in pop2 adu

@@ -30,7 +30,7 @@ class Data(object):
 
 		self.alpha_snIa=2.
 		self.alpha_nonIa=self.alpha_snIa*10**(-2./2.5)
-		self.alpha_nonIa_2=self.alpha_snIa*10**(-1/2.5)
+		self.alpha_nonIa_2=self.alpha_snIa*10**(-0.5/2.5)
 
 		self.frac_Ia_0=.95
 		self.frac_Ia_1=.2
@@ -79,7 +79,7 @@ class Data(object):
 		adu = 1/(self.cosmo.luminosity_distance(self.zs).value/self.cosmo.hubble_distance.value)**2
 		adu_random = numpy.random.normal(size=self.N_sn)
 		wsnIa = numpy.where(self.snIa)[0]
-		wnonIa = numpy.where(numpy.logical_not(self.snIa))[0]
+		wnonIa = numpy.where(numpy.logical_and(self.snIa ==0, self.nonIa ==1))[0]
 		adu[wsnIa] = self.alpha_snIa*adu[wsnIa]*10**(adu_random[wsnIa]*self.sigma_snIa/2.5)
 		adu[wnonIa] = self.alpha_nonIa*adu[wnonIa]*10**(adu_random[wnonIa]*self.sigma_nonIa/2.5)
 		wpop2 = numpy.where(numpy.logical_and(self.snIa ==0, self.nonIa ==0))[0]

### 2015-09-19 doc/model.tex
Nice happy version of things

@@
 \begin{equation}
-\theta_{r}=\frac{\hat{\theta}_{r}}{\hat{\theta}_{r}P_{Ia}(\mathit{ADU} > \mathit{ADU}_0) + (1-\hat{\theta}_{r})P_{non-Ia}(\mathit{ADU} > \mathit{ADU}_0)}.
+\theta_{r}=\frac{\hat{\theta}_{r}P_{Ia}(\mathit{ADU} > \mathit{ADU}_0)}{\hat{\theta}_{r}P_{Ia}(\mathit{ADU} > \mathit{ADU}_0) + (1-\hat{\theta}_{r})P_{non-Ia}(\mathit{ADU} > \mathit{ADU}_0)}.
 \end{equation}
@@
 \item 2000 transients distributed by co-moving volume in the range $0.1<z<1.4$.
-\item Detection threshold at approximately the mean brightness SN~Ia at $z=1.2$.
+\item Detection threshold at approximately the mean brightness SN~Ia at $z=1$.
 \item $z_{min}=0.1/1.1$ and $z_{max}=1.4\times 1.1$ is the range of possible misassigned
@@
 \item $P_{host}=0.98$ for the probability of correct host-galaxy assignment.
-\item Accumulated spectra for 20\%, 60\%, and 100\% of discovered transients.
+\item Accumulated spectra for 0\%, 20\%, 60\%, and 100\% of discovered transients.
 \end{itemize}
+This setup is referred to as Model 1.
 
-A prior is applied to the SN~Ia absolute magnitude and intrinsic dispersion
+The Hubble diagram for a realization drawn from this model is shown in Figure~\ref{hd:fig}.
+Type~Ia's are shown in blue and non-Ia's in red, those that fall below detection threshold
+are faded.  The solid points
+represent those objects spectroscopically typed for the case of 20\% follow-up.
+The green X's represent the 2\% among those without spectroscopy that
+are assigned an incorrect redshift.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[scale=0.4]{/Users/akim/project/abc/doc/seed2.pdf}
+   \includegraphics[scale=0.4]{/Users/akim/project/abc/doc/seed2_pop2.pdf}  
+\caption{Hubble diagrams for a realization drawn from the baseline Model 1 (left)
+and Model 2 with a second non-Ia population (right).
+Type~Ia's are shown in blue and non-Ia's in red, those that fall below detection threshold
+are faded.  The green X's represent the 2\% among those without spectroscopy that
+are assigned an incorrect redshift.
+   \label{hd:fig}}
+\end{figure}
+
+The simulated data are analyzed using 
+\citet{stan-software:2015},
+a probabilistic programming language for
+inference of Bayesian models with Hamiltonian Monte Carlo.
+In addition to the simulated data,
+supplemental priors are applied to the SN~Ia absolute magnitude and intrinsic dispersion
 \begin{align}
@@
 \end{align}
-where $\alpha^0_{SNIa}$ is the true input luminosity.
+where $\alpha^0_{SNIa}$ is the true input luminosity.  This prior is added in lieu of
+a pure large SN~Ia sample at low-redshift.
 
-The simulated data are analyzed using 
-\citet{stan-software:2015}, a
-a probabilistic programming language for
-inference of Bayesian models with Hamiltonian Monte Carlo.
-
-\subsubsection{Results}
+The results of the analyses meet expectations.  As the input data and analyses are
+based on the same model, the input parameters lie in reasonable position
+within the resultant posterior despite the non-trivial appearance of
+the Hubble diagram in Figure~\ref{hd:fig}.
+The parameter pdf's are shown in Figure~\ref{contour1:fig} for the ideal case of 100\% spectroscopic classification.  The input values for all 7 parameters fall within the 68\%
+credible interval.  The same is true for the unideal case of no
+spectroscopic classification.  Table~\ref{seed2:tab} lists the modes
+of the $w$ distribution for varying spectroscopic coverage: there is no appreciable
+bias relative to the statistical uncertainties.
 
@@
    \centering
-   \includegraphics[scale=0.35]{/Users/akim/project/abc/results/temp/{contour..2000..noMalm.1.0}.pdf} \newline
-\caption{Probability distribution function for $\Omega_M$--$w$,
- 100\% spectroscopy no Malmquist bias.
-   Solid lines represent the input cosmology.  Dashed lines in the
-   histograms are the 0.16 and 0.86 quantiles. 
+   \includegraphics[scale=0.17]{/Users/akim/project/abc/results/seed2/{contour.2000.1.0}.pdf}
+   \includegraphics[scale=0.17]{/Users/akim/project/abc/results/seed2_pop2/{contour.2000.1.0}.pdf} 
+\caption{Probability distribution functions of the model parameters for the case of
+ 100\% spectroscopy for Model 1 (left) and Model 2 (right).
+    Solid lines represent the input parameters.  Dashed lines in the
+   histograms are the 0.16 and 0.84 quantiles. 
    \label{contour1:fig}}
-\end{figure}
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[scale=0.35]{/Users/akim/project/abc/results/temp/{contour..2000.1.0}.pdf} \newline
-\caption{Probability distribution function for $\Omega_M$--$w$,
- 100\% spectroscopy with Malmquist bias.
-   \label{contour2:fig}}
-\end{figure}
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[scale=0.35]{/Users/akim/project/abc/results/temp/{contour..2000.0.6}.pdf} \newline
-\caption{Probability distribution function for $\Omega_M$--$w$,
- 60\% spectroscopy with Malmquist bias.
-   \label{contour3:fig}}
-\end{figure}
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[scale=0.35]{/Users/akim/project/abc/results/temp/{contour..2000.0.2}.pdf} \newline
-\caption{Probability distribution function for $\Omega_M$--$w$,
- 20\% spectroscopy with Malmquist bias.
-   \label{contour4:fig}}
-\end{figure}
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[scale=0.35]{/Users/akim/project/abc/results/temp/{contour..2000..noMalm.0.2}.pdf} \newline
-\caption{Probability distribution function for $\Omega_M$--$w$,
- 20\% spectroscopy without Malmquist bias.
-   \label{contour4:fig}}
 \end{figure}
@@
 \centering
-\begin{tabular}{cc|c|cc|}
+\begin{tabular}{|c|c|ccc|}
 \hline
-ADU0&\% Spec&\%-ile & $w$ range & $\Delta w$\\ \hline
-0 & 100 &$0.68$ & $[-1.174, -0.982]$ & $0.192$ \\
-&&$0.90$ & $[-1.239, -0.923]$ & $0.316$ \\
-&&$0.95$ & $[-1.267, -0.894]$ & $0.373$ \\ \hline
-0.2 & 100&$0.68$ & $[-1.156, -0.972]$ & $0.184$ \\
-&&$0.90$ & $[-1.222, -0.912]$ & $0.309$ \\
-&&$0.95$ & $[-1.255, -0.883]$ & $0.372$ \\ \hline
-0.2&60&$0.68$ & $[-1.209, -1.014]$ & $0.195$ \\
-&&$0.90$ & $[-1.275, -0.955]$ & $0.321$ \\
-&&$0.95$ & $[-1.309, -0.924]$ & $0.385$ \\ \hline
-0&20&$0.68$ & $[-1.226, -1.032]$ & $0.194$ \\
-&&$0.90$ & $[-1.289, -0.969]$ & $0.320$ \\
-&&$0.95$ & $[-1.322, -0.942]$ & $0.379$ \\ \hline
-0.2& 20&$0.68$ & $[-1.229, -1.033]$ & $0.196$ \\
-&&$0.90$ & $[-1.294, -0.972]$ & $0.322$ \\
-&&$0.95$ & $[-1.323, -0.943]$ & $0.380$ \\
+Fraction Spec&\%-ile & $w$ &$w$ range & $\Delta w$\\ \hline
+$1.00$ &$0.68$ &$-1.08$ & $[-1.196, -0.914]$ & $0.281$ \\
+$1.00$ &$0.90$ &$-1.08$ & $[-1.292, -0.826]$ & $0.466$ \\
+$1.00$ &$0.95$ &$-1.08$ & $[-1.340, -0.784]$ & $0.556$ \\
+$0.60$ &$0.68$ &$-1.08$ & $[-1.227, -0.933]$ & $0.293$ \\
+$0.60$ &$0.90$ &$-1.08$ & $[-1.331, -0.836]$ & $0.495$ \\
+$0.60$ &$0.95$ &$-1.08$ & $[-1.385, -0.787]$ & $0.598$ \\
+$0.20$ &$0.68$ &$-1.15$ & $[-1.249, -0.943]$ & $0.305$ \\
+$0.20$ &$0.90$ &$-1.15$ & $[-1.354, -0.851]$ & $0.502$ \\
+$0.20$ &$0.95$ &$-1.15$ & $[-1.408, -0.810]$ & $0.597$ \\
+$0.00$ &$0.68$ &$-1.09$ & $[-1.218, -0.909]$ & $0.309$ \\
+$0.00$ &$0.90$ &$-1.09$ & $[-1.320, -0.812]$ & $0.508$ \\
+$0.00$ &$0.95$ &$-1.09$ & $[-1.372, -0.770]$ & $0.602$ \\
 \hline
 \end{tabular}
-\caption{Credible intervals of $w$ using the SNe~Ia only with spectroscopic
-observations.\label{ia_only:tab}}
+\caption{Mode and credible intervals of $w$ for Model 1 for varying
+fractions of spectroscopic coverage. \label{seed2:tab}}
 \end{table}
+
+%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+%   \centering
+%   \includegraphics[scale=0.17]{/Users/akim/project/abc/results/seed2/{contour.2000.0.0}.pdf}
+%   \includegraphics[scale=0.17]{/Users/akim/project/abc/results/seed2_pop2/{contour.2000.0.0}.pdf} 
+%\caption{Probability distribution functions for the difference in parameters
+%with 100\% and 0\% spectroscopic folowup for Model 1 (left) and Model 2 (right).  \label{contour2:fig}}
+%\end{figure}
+
+Though the decrease in spectroscopic coverage produces low bias, it does lead to
+increased parameter uncertainties.
+The credible intervals for $w$ are shown in Table~\ref{seed2:tab}:
+for the case of 100\% follow-up the range of the 68\% $w$ interval is $\Delta w = 0.281$. 
+At the opposite extreme of no spectroscopic classification the $w$ interval inflates to
+$\Delta w = 0.309$, a constraining result nevertheless considering that none of the
+objects are directly typed and redshifted.
+
+As a stress test, we generate a simulated data based on a different model
+referred to as Model 2, which
+has a second non-Ia population with average luminosity 0.5 mag fainter
+than the Ia's and 0.25 mag dispersion.
+The relative rates of the original non-Ia population relative to the second is quadratic:
+\begin{equation}
+1 -\frac{0.8}{1.54}z^2.
+\end{equation}
+A realization of transients from this model, using the same random seeds
+as Model 1, is shown in Figure~\ref{hd:fig}.
+
+When there is 100\% spectroscopic coverage the   $\Omega_M$--$w$  posterior accommodates the input 
+parameters, as shown  in
+Figure~\ref{contour1:fig}.
+A salient feature that contrasts with Model 1 is 
+seen in the modes for $w$ listed in Table~\ref{seed2_pop2:tab}: biases
+larger than the statistical uncertainties appear with decreasing
+spectroscopic coverage.  Note that the Hubble diagrams
+in these analyses are almost identical: there are redshift misassignments
+for 2\% of the transients that lack spectroscopy.
+
+%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+%   \centering
+%   \includegraphics[scale=0.35]{/Users/akim/project/abc/results/seed2_pop2/{contour.2000.1.0}.pdf} \newline
+%\caption{Probability distribution function for $\Omega_M$--$w$,
+% 100\% spectroscopy, biased.
+%    Solid lines represent the input cosmology.  Dashed lines in the
+%   histograms are the 0.16 and 0.84 quantiles. 
+%   \label{contour3:fig}}
+%\end{figure}
+%
+%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+%   \centering
+%   \includegraphics[scale=0.35]{/Users/akim/project/abc/results/seed2_pop2/{contour.2000.0.0}.pdf} \newline
+%\caption{Probability distribution function for $\Omega_M$--$w$,
+% no spectroscopy, biased.
+%   \label{contour4:fig}}
+%\end{figure}
+
+\begin{table}
+\centering
+\begin{tabular}{|c|c|ccc|}
+\hline
+Fraction Spec&\%-ile &$w$ & $w$ range & $\Delta w$\\ \hline
+$1.00$ &$0.68$ &$-0.94$ & $[-1.078, -0.804]$ & $0.274$ \\
+$1.00$ &$0.90$ &$-0.94$ & $[-1.168, -0.720]$ & $0.447$ \\
+$1.00$ &$0.95$ &$-0.94$ & $[-1.214, -0.680]$ & $0.534$ \\
+$0.60$ &$0.68$ &$-1.09$ & $[-1.182, -0.883]$ & $0.298$ \\
+$0.60$ &$0.90$ &$-1.09$ & $[-1.285, -0.791]$ & $0.494$ \\
+$0.60$ &$0.95$ &$-1.09$ & $[-1.332, -0.749]$ & $0.583$ \\
+$0.20$ &$0.68$ &$-1.09$ & $[-1.247, -0.936]$ & $0.311$ \\
+$0.20$ &$0.90$ &$-1.09$ & $[-1.359, -0.840]$ & $0.518$ \\
+$0.20$ &$0.95$ &$-1.09$ & $[-1.413, -0.798]$ & $0.614$ \\
+$0.00$ &$0.68$ &$-1.11$ & $[-1.266, -0.948]$ & $0.317$ \\
+$0.00$ &$0.90$ &$-1.11$ & $[-1.375, -0.850]$ & $0.525$ \\
+$0.00$ &$0.95$ &$-1.11$ & $[-1.428, -0.808]$ & $0.621$ \\
+\hline
+\end{tabular}
+\caption{Mode and credible intervals of $w$ for Model 2  for varying
+fractions of spectroscopic coverage.\label{seed2_pop2:tab}}
+\end{table}
+
+Some initial conclusions.
+\begin{itemize}
+\item Knowing the underlying model that produces data, you should
+get results statistically consistent with the truth.  A tautology?
+\item Typing is important when the non-Ia model is not accurate.
+\end{itemize}
 

### 2015-09-19 src/analyze.py

@@ -18,11 +18,11 @@ levels = numpy.array([0.025, 0.05, 0.16, 1-0.16, 1-0.05, 1-.025])
 def individual(N_s, ia_only = False, ADU0=None,N_sn=None,dir='temp'):
 	app=''
 	if N_sn is not None:
-		app='.'+str(N_sn)
+		app='.'+str(N_sn)+'.'
 	if ia_only:
 		app+='.ia_only.'
 	if ADU0 == 0.:
-			app+='.noMalm.'
+			app+='noMalm.'
 	[extract,logposterior] = pickle.load(file('../results/'+dir+'/model'+app+str(N_s)+'.pkl','rb'))
 #	print numpy.abs((extract['w'] < -1).sum()*1. / len(extract['w'])-0.5)*2
 	n_samples = len(extract[extract.keys()[0]])
@@ -181,7 +181,7 @@ def group(nspec):
 
 
 def main():
-	individual(1.0,ia_only=False,ADU0=0.,N_sn=2000,dir='temp')
+	individual(0.0,ia_only=False,ADU0=0.75,N_sn=2000,dir='seed2_pop2')
 #	individual(500,ia_only=False)
 	wefew
 	group([200,350,500])

### 2015-09-19 src/plots.py

@@ -45,6 +45,9 @@ def individual(N_s, ia_only = False, ADU0=None,N_sn=None,dir='temp'):
 	plt.savefig('../results/'+dir+'/contour'+app+str(N_s)+'.pdf')
 	plt.clf()
 
+
+	n, b = numpy.histogram(samples[:,1], bins=20)
+
 	ans = numpy.zeros(len(levels))
 	deltas = numpy.zeros(len(levels)/2)
 	wsort = numpy.sort(extract['w'])
@@ -52,7 +55,7 @@ def individual(N_s, ia_only = False, ADU0=None,N_sn=None,dir='temp'):
 	for i in xrange(len(levels)/2):
 		deltas[i] = ans[-1-i]-ans[i] 
 	for i in xrange(len(levels)/2-1,-1,-1):
-		print '${:4.2f}$ &${:4.2f}$ &${:4.2f}$ & $[{:5.3f}, {:5.3f}]$ & ${:5.3f}$ \\\\'.format(ADU0, N_s, 1-levels[i]*2, ans[i],ans[-1-i], deltas[i])
+		print '${:4.2f}$ &${:4.2f}$ &${:4.2f}$ & $[{:5.3f}, {:5.3f}]$ & ${:5.3f}$ \\\\'.format(N_s, 1-levels[i]*2, b[numpy.argmax(n)],  ans[i],ans[-1-i], deltas[i])
 
 	fractions = [0.6, 0.2, 0.0]
 	#fractions = [0.0]
@@ -77,6 +80,8 @@ def individual(N_s, ia_only = False, ADU0=None,N_sn=None,dir='temp'):
 		plt.savefig('../results/'+dir+'/contour'+app+str(frac)+'.pdf')
 		plt.clf()
 
+		n, b = numpy.histogram(extract_['w'], bins=20)
+
 		ans = numpy.zeros(len(levels))
 		deltas = numpy.zeros(len(levels)/2)
 		wsort = numpy.sort(extract_['w'])
@@ -84,7 +89,7 @@ def individual(N_s, ia_only = False, ADU0=None,N_sn=None,dir='temp'):
 		for i in xrange(len(levels)/2):
 			deltas[i] = ans[-1-i]-ans[i] 
 		for i in xrange(len(levels)/2-1,-1,-1):
[…]

### 2015-09-19 src/des.py
turn on snia_only

@@ -142,7 +142,8 @@ class Data(object):
 				'host_zs_mis': [],
 				'host2_zs_mis': [],
 
-				'ADU0': self.ADU0
+				'ADU0': self.ADU0,
+				'bias_anal':0
 			}
 		else:
 			self.s_obs = self.s_obs.tolist()
@@ -250,7 +251,7 @@ def main():
 	pop2=False
 	asifIa = False
 
-	ia_only=False ###deprecated
+	ia_only = False
 
 	if pop2:
 		dire='_pop2'
@@ -282,7 +283,7 @@ def main():
 
 
 			if ia_only:
-				app+='.ia_only.'
+				app+='ia_only.'
 
 			with open('../results/temp'+dire+'/model'+app+str(ns)+'.pkl', 'wb') as f:
 				pickle.dump([fit.extract(), logposterior], f)

### 2015-09-20 src/toy_pgm.py
new figure

@@ -1,0 +1,115 @@
+#!/usr/bin/env python
+
+from matplotlib import rc
+from daft import PGM, Node, Plate
+rc("font", family="serif", size=12)
+rc("text", usetex=True)
+
+
+pgm = PGM([6.5, 4.5], origin=[0., 0.2], observed_style='inner')
+
+#pgm.add_node(Node('G',r"$G$", 3,1))
+#pgm.add_node(Node('Coords',r"${RA}_i$/${Dec}_i$", 2,1,fixed=True))
+pgm.add_node(Node('G_i',r"$z_i, z_{Ni}$", 2,2, scale=1.2))
+
+pgm.add_node(Node('mu',r"$\Omega_M$, $w$", 3,4, scale=1.4))
+pgm.add_node(Node('rate',r"$\theta_r$", 5,4))
+pgm.add_node(Node('HD',r"$\mu_i$", 3,2,fixed=True,offset=(0,-22)))
+pgm.add_node(Node('theta_T',r"\center{$\alpha_{Ia}$, $\alpha_{non-Ia}$ \newline $\sigma_{Ia}$, $\sigma_{non-Ia}$}", 4,4,scale=1.65,aspect=1.5))
+#pgm.add_node(Node('theta_Ti',r"$\theta_{Ti}^{Ia}$, $\theta_{Ti}^{non-Ia}$", 2,6,scale=1.5,aspect=1.5))
+
+#pgm.add_node(Node('Host',r"$\theta_{gi}$", 2, 3, fixed=True,offset=(-10,-5)))
+#pgm.add_node(Node('z',r"$z_i$", 2, 2, fixed=True,offset=(-10,-5)))
+
+pgm.add_node(Node('Type',r"$T_i$", 5,3))
+pgm.add_node(Node('Luminosity',r"$L_i(t,\lambda)$", 4,3, scale=1.4))
+#pgm.add_node(Node('Flux',r"$n_i(t,\lambda)$", 5, 5, scale=1.2,fixed=True,offset=(15,0)))
+#pgm.add_node(Node('Flux_g',r"$n_{gi}(\lambda)$", 5, 2,fixed=True,offset=(0,-20)))
+#pgm.add_node(Node('Transmission',r"$\phi(\lambda)$", 7, 7))
+#pgm.add_node(Node('Counts',r"$\overline{\mathit{ADU}}_i$", 8, 5,scale=1.2,fixed=True,offset=(15,0)))
[…]

### 2015-09-23 doc/article.tex
start article

--- 2015-09-19 doc/model.tex
@@
-\documentclass[preprint]{aastex}
+\documentclass[preprint]{elsarticle}
+\usepackage{aas_macros}
 \usepackage{amsmath,amssymb}
@@
 \usepackage{graphicx}
-\usepackage{natbib}
 \usepackage{bm}
-\bibliographystyle{apj}
+\usepackage{hyperref}
 
@@
 
-\title{Model for DES Type Ia Supernova Cosmology Analysis}
-\author{Alex Kim}
+\begin{frontmatter}
+
+\title{Standard Candle Cosmology With Incomplete Spectroscopic Classification}
+\author{A.~G. Kim\corref{cor1}}
+\ead{agkim@lbl.gov}
+\address{Physics Division, Lawrence Berkeley National Laboratory, 1 Cyclotron Road, Berkeley CA, USA 94720}
+
+\begin{abstract}
+\end{abstract}
+\begin{keyword}
+\end{keyword}
+\end{frontmatter}
+
+\section{Introduction}
+A class of astronomical objects who share a common luminosity are called a standard
+candle.  The relative fluxes (or magnitudes) for a set of these objects distributed in space
+provide a measurement of their relative luminosity distances. These data, combined with
+measurements of the standard candle redshifts, constitute a Hubble
+diagram which is used to map the expansion history of the Universe.
+
+Type~Ia supernovae (SNe~Ia) are an example of a standard candle (more precisely a standardizable
+candle), whose redshift-magnitude relation provides an accurate expansion history
+used to measure the Hubble Constant
+\citep{2001ApJ...553...47F} and detect the accelerated expansion of the Universe
+\citep{1998AJ....116.1009R, 1999ApJ...517..565P}.  SN~Ia measurements continue
+to improve 
+\citep{2014A&A...568A..22B} and play a critical role in probing the physics
+responsible for the acceleration \citep{2013PhR...530...87W}.
+Looking at the present and toward the future, SN~Ia cosmology is
+a component of the Dark Energy Survey\footnote{\url{http://www.darkenergysurvey.org}} (DES),
+and a science driver in the design of the
+Large Synoptic Survey Telescope\footnote{\url{http://www.lsst.org}} (LSST)
+and the Wide-Field InfrarRed Survey Telescope
+\citep{2015arXiv150303757S}.
+
+The information necessary to construct a Hubble diagram consists of, per object,
+its classification as a
+member of the standard candle class, its redshift, and its flux.  For SNe~Ia, the flux at
+peak brightness is typically determined from multi-band light curves obtained from repeated
+photometric observations. Traditionally, spectroscopic data is used to classify the transient
+as SN~Ia through the lack of hydrogen and the presence of SiII in its spectrum,
+and determine its redshift either directly through the transient spectrum or that of its host
+galaxy. While the classification and redshift could be determined from the multi-band
+light curves and colors of the host galaxy, the accuracy is insufficient for precision
+cosmology \citep{2011ApJ...738..162S}.  Consequently spectroscopic follow-up
+has played a critical role in cosmological supernova surveys.
+
+While the large focal planes of the Dark Energy Camera (3 square degrees)
+and the LSST (9.6 square degrees) open the
+possibility for the photometric discovery and observation of thousands to millions
+of SNe~Ia out to $z\sim1$, a corresponding multiplex advantage has not been
+achieved for the 10-m
+class telescopes used for the spectroscopic classification of faint discoveries:
+it is unfeasible to obtain a spectrum for all SN~Ia candidates with well-measured
+photometry.
+
+Photometric SN analysis has been developed
+in the hope of taking advantage of the statistical weight imported by the
+availability of light curves
+for large numbers of supernovae, despite their lack of spectroscopy.
+Such analyses have been applied to SDSS-II SN data \citep{2012ApJ...752...79H,
+2013ApJ...763...88C}, and are planned for
+DES \citep{2012ApJ...753..152B} and LSST \citep{2012arXiv1211.0310L}.
 
@@
 \end{equation}
-is examined in this section.
-The measurements: 
+is examined in this section and is sketched in Figure~\ref{toypgm:fig}.
+The measurements are
 \begin{itemize}
-\item $\mathit{ADU}$ are measured counts at peak brightness.
-\item ${{T}}_S$, ${{z}}_S$ are spectroscopic type and redshift for a subset of transients.
-\item $\theta_G$ are the redshift of the galaxy identified as the transient host.
+\item $\mathit{ADU}$: the measured counts at peak brightness;
+\item ${{T}}_S$, ${{z}}_S$: the spectroscopic type and redshift for a subset of transients;
+\item $\theta_{G1}$, $\theta_{G2}$: the redshifts of the identified host and neighbor
+galaxies.
 \end{itemize}
-The model parameters:
+The model parameters are
 \begin{itemize}
-\item $\Omega_M$, $w$ are the parameters of a flat dark-energy cosmology.
-\item $\theta_r$ describe the fraction of transients that are SN~Ia, independent
-of host-galaxy properties.
-\item $\alpha_{Ia}$, $\sigma_{Ia}$, $\alpha_{\mathit{non-Ia}}$, $\sigma_{\mathit{non-Ia}}$ are
+\item $\Omega_M$, $w$: the parameters of a flat dark-energy cosmology;
+\item $\theta_{r1}$, $\theta_{r2}$:  for two redshifts the fraction of transients that are SN~Ia;
+\item $\alpha_{Ia}$, $\sigma_{Ia}$, $\alpha_{\mathit{non-Ia}}$, $\sigma_{\mathit{non-Ia}}$:
 the luminosity (times $4\pi$) and intrinsic dispersion for SNe~Ia and non-Ia at peak.
@@
 
-In addition to the above, there are latent model parameters for each transient used internally
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=5in]{/Users/akim/project/abc/results/toy_pgm.pdf} 
+   \caption{Probabilistic Graphical Model for the simple SN~Ia analysis. The
+   parameters include the cosmological parameters $\Omega_M$ and $w$,
+   the luminosities $\alpha$ and intrinsic dispersions $\sigma$ of SNe~Ia and non-Ia's,
+   and the relative rate parameters $\theta_{r1}$ and $\theta_{r2}$.  Latent parameters
+   include the type $T$ and redshifts of the host and neighboring galaxies $z$ and $z_N$
+   for each transient.  The  parameters for distance modulus $\mu$ and
+   luminosity $L$ are fixed by the other parameters.  The observables include the measured
+   flux $\mathit{ADU}$, spectroscopic type and redshift $T_S$ and $z_S$, and
+   the inferred host and neighbor redshifts $\theta_{G1}$ and $\theta_{G2}$.
+   \label{toypgm:fig}}
+\end{figure}
+
+There are latent model parameters for each transient used internally
 by the model:
 \begin{itemize}
-\item $z$ are the cosmological redshifts.
-\item $T$ are the type, SN~Ia or non-Ia.
+\item $z$: the cosmological redshifts.
+\item $T$: the type, SN~Ia or non-Ia.
 \end{itemize}
@@
 and their analysis is implemented in Python and are available
-on GitHub\footnote{\url{git@github.com:AlexGKim/abc.git}}.
+on GitHub\footnote{{git@github.com:AlexGKim/abc.git}}.
 
@@
 \centering
-\begin{tabular}{|c|c|ccc|}
+\begin{tabular}{|c|c|cccc|}
 \hline
-Fraction Spec&\%-ile & $w$ &$w$ range & $\Delta w$\\ \hline
-$1.00$ &$0.68$ &$-1.08$ & $[-1.196, -0.914]$ & $0.281$ \\
-$1.00$ &$0.90$ &$-1.08$ & $[-1.292, -0.826]$ & $0.466$ \\
-$1.00$ &$0.95$ &$-1.08$ & $[-1.340, -0.784]$ & $0.556$ \\
-$0.60$ &$0.68$ &$-1.08$ & $[-1.227, -0.933]$ & $0.293$ \\
-$0.60$ &$0.90$ &$-1.08$ & $[-1.331, -0.836]$ & $0.495$ \\
-$0.60$ &$0.95$ &$-1.08$ & $[-1.385, -0.787]$ & $0.598$ \\
-$0.20$ &$0.68$ &$-1.15$ & $[-1.249, -0.943]$ & $0.305$ \\
-$0.20$ &$0.90$ &$-1.15$ & $[-1.354, -0.851]$ & $0.502$ \\
-$0.20$ &$0.95$ &$-1.15$ & $[-1.408, -0.810]$ & $0.597$ \\
-$0.00$ &$0.68$ &$-1.09$ & $[-1.218, -0.909]$ & $0.309$ \\
-$0.00$ &$0.90$ &$-1.09$ & $[-1.320, -0.812]$ & $0.508$ \\
-$0.00$ &$0.95$ &$-1.09$ & $[-1.372, -0.770]$ & $0.602$ \\
+Fraction Spec&\%-ile &$<w>$ & $w$ mode  &$w$ range & $\Delta w$\\ \hline
+\multicolumn{6}{|c|}{SN Ia only}\\ \hline
+$1.00$& $0.68$ &$-0.94 \pm 0.09$ &$-0.80$ & $[-1.076, -0.801]$ & $0.275$ \\
+$1.00$& $0.90$ &$-0.94 \pm 0.09$ &$-0.80$ & $[-1.166, -0.718]$ & $0.448$ \\
+$1.00$& $0.95$ &$-0.94 \pm 0.09$ &$-0.80$ & $[-1.208, -0.682]$ & $0.525$ \\
+ \hline
+\multicolumn{6}{|c|}{Model 1}\\ \hline
+$1.00$ &$0.68$ &$-1.06 \pm 0.09$ &$-0.91$ & $[-1.196, -0.914]$ & $0.281$ \\
+$1.00$ &$0.90$ &$-1.06 \pm 0.09$ &$-0.91$ & $[-1.292, -0.826]$ & $0.466$ \\
+$1.00$ &$0.95$ &$-1.06 \pm 0.09$ &$-0.91$ & $[-1.340, -0.784]$ & $0.556$ \\
+$0.60$ &$0.68$ &$-1.08 \pm 0.10$ &$-0.93$ & $[-1.227, -0.933]$ & $0.293$ \\
+$0.60$ &$0.90$ &$-1.08 \pm 0.10$ &$-0.93$ & $[-1.331, -0.836]$ & $0.495$ \\
+$0.60$ &$0.95$ &$-1.08 \pm 0.10$ &$-0.93$ & $[-1.385, -0.787]$ & $0.598$ \\
+$0.20$ &$0.68$ &$-1.10 \pm 0.10$ &$-0.94$ & $[-1.249, -0.943]$ & $0.305$ \\
+$0.20$ &$0.90$ &$-1.10 \pm 0.10$ &$-0.94$ & $[-1.354, -0.851]$ & $0.502$ \\
+$0.20$ &$0.95$ &$-1.10 \pm 0.10$ &$-0.94$ & $[-1.408, -0.810]$ & $0.597$ \\
+$0.00$ &$0.68$ &$-1.07 \pm 0.10$ &$-0.91$ & $[-1.218, -0.909]$ & $0.309$ \\
+$0.00$ &$0.90$ &$-1.07 \pm 0.10$ &$-0.91$ & $[-1.320, -0.812]$ & $0.508$ \\
+$0.00$ &$0.95$ &$-1.07 \pm 0.10$ &$-0.91$ & $[-1.372, -0.770]$ & $0.602$ \\
+ \hline
+\multicolumn{6}{|c|}{Model 2}\\ \hline
+$1.00$ &$0.68$ &$-0.94 \pm 0.09$ &$-0.80$ & $[-1.078, -0.804]$ & $0.274$ \\
+$1.00$ &$0.90$ &$-0.94 \pm 0.09$ &$-0.80$ & $[-1.168, -0.720]$ & $0.447$ \\
+$1.00$ &$0.95$ &$-0.94 \pm 0.09$ &$-0.80$ & $[-1.214, -0.680]$ & $0.534$ \\
+$0.60$ &$0.68$ &$-1.04 \pm 0.10$ &$-0.88$ & $[-1.182, -0.883]$ & $0.298$ \\
+$0.60$ &$0.90$ &$-1.04 \pm 0.10$ &$-0.88$ & $[-1.285, -0.791]$ & $0.494$ \\
+$0.60$ &$0.95$ &$-1.04 \pm 0.10$ &$-0.88$ & $[-1.332, -0.749]$ & $0.583$ \\
+$0.20$ &$0.68$ &$-1.10 \pm 0.10$ &$-0.94$ & $[-1.247, -0.936]$ & $0.311$ \\
+$0.20$ &$0.90$ &$-1.10 \pm 0.10$ &$-0.94$ & $[-1.359, -0.840]$ & $0.518$ \\
+$0.20$ &$0.95$ &$-1.10 \pm 0.10$ &$-0.94$ & $[-1.413, -0.798]$ & $0.614$ \\
+$0.00$ &$0.68$ &$-1.11 \pm 0.10$ &$-0.95$ & $[-1.266, -0.948]$ & $0.317$ \\
+$0.00$ &$0.90$ &$-1.11 \pm 0.10$ &$-0.95$ & $[-1.375, -0.850]$ & $0.525$ \\
+$0.00$ &$0.95$ &$-1.11 \pm 0.10$ &$-0.95$ & $[-1.428, -0.808]$ & $0.621$ \\
 \hline
 \end{tabular}
-\caption{Mode and credible intervals of $w$ for Model 1 for varying
+\caption{Mode and credible intervals of $w$ for only the SNe~Ia, Model 1, and Model 2 for varying
 fractions of spectroscopic coverage. \label{seed2:tab}}
@@
 A salient feature that contrasts with Model 1 is 
-seen in the modes for $w$ listed in Table~\ref{seed2_pop2:tab}: biases
+seen in the modes for $w$ listed in Table~\ref{seed2:tab}: biases
 larger than the statistical uncertainties appear with decreasing
@@
 
-\begin{table}
-\centering
-\begin{tabular}{|c|c|ccc|}
-\hline
-Fraction Spec&\%-ile &$w$ & $w$ range & $\Delta w$\\ \hline
-$1.00$ &$0.68$ &$-0.94$ & $[-1.078, -0.804]$ & $0.274$ \\
-$1.00$ &$0.90$ &$-0.94$ & $[-1.168, -0.720]$ & $0.447$ \\
-$1.00$ &$0.95$ &$-0.94$ & $[-1.214, -0.680]$ & $0.534$ \\
-$0.60$ &$0.68$ &$-1.09$ & $[-1.182, -0.883]$ & $0.298$ \\
-$0.60$ &$0.90$ &$-1.09$ & $[-1.285, -0.791]$ & $0.494$ \\
-$0.60$ &$0.95$ &$-1.09$ & $[-1.332, -0.749]$ & $0.583$ \\
-$0.20$ &$0.68$ &$-1.09$ & $[-1.247, -0.936]$ & $0.311$ \\
-$0.20$ &$0.90$ &$-1.09$ & $[-1.359, -0.840]$ & $0.518$ \\
-$0.20$ &$0.95$ &$-1.09$ & $[-1.413, -0.798]$ & $0.614$ \\
-$0.00$ &$0.68$ &$-1.11$ & $[-1.266, -0.948]$ & $0.317$ \\
-$0.00$ &$0.90$ &$-1.11$ & $[-1.375, -0.850]$ & $0.525$ \\
-$0.00$ &$0.95$ &$-1.11$ & $[-1.428, -0.808]$ & $0.621$ \\
-\hline
-\end{tabular}
-\caption{Mode and credible intervals of $w$ for Model 2  for varying
-fractions of spectroscopic coverage.\label{seed2_pop2:tab}}
-\end{table}
-
 Some initial conclusions.
@@
 \item Typing is important when the non-Ia model is not accurate.
+\item Better than only using SNe~Ia with spectra.
 \end{itemize}
@@
 
+\bibliographystyle{elsarticle-num} 
 \bibliography{/Users/akim/Documents/alex}

### 2015-09-23 src/analyze.py

@@ -20,7 +20,7 @@ def individual(N_s, ia_only = False, ADU0=None,N_sn=None,dir='temp'):
 	if N_sn is not None:
 		app='.'+str(N_sn)+'.'
 	if ia_only:
-		app+='.ia_only.'
+		app+='ia_only.'
 	if ADU0 == 0.:
 			app+='noMalm.'
 	[extract,logposterior] = pickle.load(file('../results/'+dir+'/model'+app+str(N_s)+'.pkl','rb'))
@@ -112,6 +112,8 @@ def individual(N_s, ia_only = False, ADU0=None,N_sn=None,dir='temp'):
 	# 	for i in xrange(len(levels)/2-1,-1,-1):
 	# 		print '{}& ${:4.2f}$ & $[{:5.3f}, {:5.3f}]$ & ${:5.3f}$ \\\\'.format(label[j],1-levels[i]*2, ans[j,i],ans[j,-1-i], deltas[j,i])
 
+	n, b = numpy.histogram(samples[:,1], bins=20)
+
 	ans = numpy.zeros(len(levels))
 	deltas = numpy.zeros(len(levels)/2)
 	wsort = numpy.sort(extract['w'])
@@ -119,7 +121,7 @@ def individual(N_s, ia_only = False, ADU0=None,N_sn=None,dir='temp'):
 	for i in xrange(len(levels)/2):
 		deltas[i] = ans[-1-i]-ans[i] 
 	for i in xrange(len(levels)/2-1,-1,-1):
-		print '${:4.2f}$ & $[{:5.3f}, {:5.3f}]$ & ${:5.3f}$ \\\\'.format(1-levels[i]*2, ans[i],ans[-1-i], deltas[i])
+		print '1.0& ${:4.2f}$ &${:4.2f}$ & $[{:5.3f}, {:5.3f}]$ & ${:5.3f}$ \\\\'.format(1-levels[i]*2, b[numpy.argmax(n)],  ans[i],ans[-1-i], deltas[i])
 
 
 
@@ -181,7 +183,7 @@ def group(nspec):
 
 
 def main():
-	individual(0.0,ia_only=False,ADU0=0.75,N_sn=2000,dir='seed2_pop2')
+	individual(1.0,ia_only=True,ADU0=0.75,N_sn=2000,dir='seed2')
 #	individual(500,ia_only=False)
 	wefew
 	group([200,350,500])

### 2015-09-23 src/toy_pgm.py

@@ -13,7 +13,7 @@ pgm = PGM([6.5, 4.5], origin=[0., 0.2], observed_style='inner')
 pgm.add_node(Node('G_i',r"$z_i, z_{Ni}$", 2,2, scale=1.2))
 
 pgm.add_node(Node('mu',r"$\Omega_M$, $w$", 3,4, scale=1.4))
-pgm.add_node(Node('rate',r"$\theta_r$", 5,4))
+pgm.add_node(Node('rate',r"$\theta_{r1}$, $\theta_{r2}$", 5,4,scale=1.4))
 pgm.add_node(Node('HD',r"$\mu_i$", 3,2,fixed=True,offset=(0,-22)))
 pgm.add_node(Node('theta_T',r"\center{$\alpha_{Ia}$, $\alpha_{non-Ia}$ \newline $\sigma_{Ia}$, $\sigma_{non-Ia}$}", 4,4,scale=1.65,aspect=1.5))
 #pgm.add_node(Node('theta_Ti',r"$\theta_{Ti}^{Ia}$, $\theta_{Ti}^{non-Ia}$", 2,6,scale=1.5,aspect=1.5))
@@ -22,7 +22,7 @@ pgm.add_node(Node('theta_T',r"\center{$\alpha_{Ia}$, $\alpha_{non-Ia}$ \newline 
 #pgm.add_node(Node('z',r"$z_i$", 2, 2, fixed=True,offset=(-10,-5)))
 
 pgm.add_node(Node('Type',r"$T_i$", 5,3))
-pgm.add_node(Node('Luminosity',r"$L_i(t,\lambda)$", 4,3, scale=1.4))
+pgm.add_node(Node('Luminosity',r"$L_i(t,\lambda)$", 4,3, fixed=True, scale=1.4, offset=(-22,-22)))
 #pgm.add_node(Node('Flux',r"$n_i(t,\lambda)$", 5, 5, scale=1.2,fixed=True,offset=(15,0)))
 #pgm.add_node(Node('Flux_g',r"$n_{gi}(\lambda)$", 5, 2,fixed=True,offset=(0,-20)))
 #pgm.add_node(Node('Transmission',r"$\phi(\lambda)$", 7, 7))
@@ -37,7 +37,7 @@ pgm.add_node(Node('Spars',r"${T}_{Si}$, ${z}_{Si}$", 4,1, scale=1.4,aspect=1.2, 
[…]

### 2015-09-28 doc/article.tex
adding to paper and reformatting of table

--- 2015-09-14 doc/model.tex
@@
-\documentclass[preprint]{aastex}
+\documentclass[preprint,3p]{elsarticle}
+\usepackage{aas_macros}
 \usepackage{amsmath,amssymb}
@@
 
-\title{Model for DES Type Ia Supernova Cosmology Analysis}
-\author{Alex Kim}
+\begin{frontmatter}
 
-\section{Model}
-We infer a Hubble diagram based on measurements of discovered transients
-that have passed some selection criteria (e.g.\ classified as Type~Ia supernovae).  The posterior
-of the Hubble diagram is denoted as
+\title{Standard Candle Cosmology With Incomplete Spectroscopic Classification}
+\author{A.~G. Kim\corref{cor1}}
+\ead{agkim@lbl.gov}
+\address{Physics Division, Lawrence Berkeley National Laboratory, 1 Cyclotron Road, Berkeley CA, USA 94720}
+
+\begin{abstract}
+\end{abstract}
+\begin{keyword}
+\end{keyword}
+\end{frontmatter}
+
+\section{Introduction}
+A class of astronomical objects who share a common luminosity are called a standard
+candle.  The relative fluxes (or magnitudes) for a set of these objects distributed in space
+provide a measurement of their relative luminosity distances. These data, combined with
+measurements of the standard candle redshifts, constitute a Hubble
+diagram which is used to map the expansion history of the Universe.
+
+Type~Ia supernovae (SNe~Ia) are an example of a standard candle (more precisely a standardizable
+candle), whose redshift-magnitude relation provides an accurate expansion history
+used to measure the Hubble Constant
+\citep{2001ApJ...553...47F} and detect the accelerated expansion of the Universe
+\citep{1998AJ....116.1009R, 1999ApJ...517..565P}.  SN~Ia measurements continue
+to improve 
+\citep{2014A&A...568A..22B} and play a critical role in probing the physics
+responsible for the acceleration \citep{2013PhR...530...87W}.
+Looking at the present and toward the future, SN~Ia cosmology is
+a component of the Dark Energy Survey\footnote{\url{http://www.darkenergysurvey.org}} (DES),
+and a science driver in the design of the
+Large Synoptic Survey Telescope\footnote{\url{http://www.lsst.org}} (LSST)
+and the Wide-Field InfrarRed Survey Telescope
+\citep{2015arXiv150303757S}.
+
+The information necessary to construct a Hubble diagram consists of, per object,
+its classification as a
+member of the standard candle class, its redshift, and its flux.  For SNe~Ia, the flux at
+peak brightness is typically determined from multi-band light curves obtained from repeated
+photometric observations. Traditionally, spectroscopic data is used to classify the transient
+as SN~Ia through the lack of hydrogen and the presence of SiII in its spectrum,
+and determine its redshift either directly through the transient spectrum or that of its host
+galaxy. While the classification and redshift could be determined from the multi-band
+light curves and colors of the host galaxy, the accuracy is insufficient for precision
+cosmology \citep{2011ApJ...738..162S}.  Consequently spectroscopic follow-up
+has played a critical role in cosmological supernova surveys.
+
+While the large focal planes of the Dark Energy Camera (3 square degrees)
+and the LSST (9.6 square degrees) open the
+possibility for the photometric discovery and observation of thousands to millions
+of SNe~Ia out to $z\sim1$, a corresponding multiplex advantage has not been
+achieved for the 10-m
+class telescopes used for the spectroscopic classification of faint discoveries:
+it is unfeasible to obtain a spectrum for all SN~Ia candidates with well-measured
+photometry.
+
+Photometric supernova analysis has been proposed to  take advantage of the statistical weight imported by large numbers of supernova light curves, despite the lack of spectroscopy.
+An example of such a program would proceed as follows: A rolling wide-field imaging
+survey generates light curves for all transients in the survey area.  In near real-time,
+a subset 
+of transients from those images are selected for triggered spectroscopic observations
+to obtain classifications and redshifts.  At the end of the survey, the
+analysis sample is the subset of likely SN~Ia
+candidates based on photometric data;  the analysis sample and its subset
+with triggered spectroscopy are constructed so as to be drawn from the same parent distribution.
+Spectroscopic redshifts are obtained for likely host galaxies.  The Hubble diagram of the
+analysis sample is analyzed with the understanding that it may contain multiple populations.
+
+The Sloan Digital Sky Survey-II Supernova Survey is an example of a program
+that produced significant numbers of transients
+with light curves but without spectroscopic typing \citep{2014arXiv1401.3317S}:
+photometric SN analysis has been developed applied to these data \citep{2012ApJ...752...79H,
+2013ApJ...763...88C}.   Such analyses are anticipated in the projected
+supernova programs of 
+DES \citep{2012ApJ...753..152B} and LSST \citep{2012arXiv1211.0310L}.
+
+Current models used for supernova cosmology analysis account for unobserved quantities.
+SNe~Ia are not standard but are ``standardizable'' candles, implying that the class may be composed of distinct subpopulations each with its own redshift-dependent rates, magnitude distributions, and secondary
+observable (e.g.\ light-curve shape, color) distributions.  Bayesian hierarchical modeling is 
+used to account for this extra layer of complexity  to determine characteristics of the SN~Ia population simultaneously
+with the cosmology \citep{2011MNRAS.418.2308M,
+2015arXiv150701602R}.  Consideration of missing classification is addressed
+by
+BEAMS \citep{2007PhRvD..75j3508K}, which  includes a non-Ia population in sample, whose luminosity distribution
+is inferred along with the cosmology:
+BEAMS was used in the analysis of SDSS-II SN data \citep{2012ApJ...752...79H}.
+
+This article addresses the affect of missing spectroscopic typing in
+a transient standard candle analysis, with the eventual goal of quantifying
+requirements for the spectroscopic subsample in a broader photometric analysis.
+The lack of spectroscopy leads to ambiguity in both the transient class and
+in the host galaxy due to projected galaxies that appear close to the transient or
+the relative low-surface brightness of the host.  The subsample with
+spectroscopic typing informs the interpretation of objects lacking spectroscopy.
+Differences between observed and
+intrinsic distributions in a flux-limited sample can have important effects on the Hubble
+diagram  (e.g.\ Malmquist bias) so are accounted for explicitly.
+Though motivated by SNe~Ia, this article makes the simplifying assumption that they
+are standard candles with random dispersion; the motivation of this article is to understand
+the general effects of spectroscopic completeness in a manner that is not specific to
+the choice of model for the underlying supernova heterogeneity.
+
+\section{Data Model}
+\label{model:sec}
+The data in constructing a Hubble diagram and the fundamental parameters of the
+model used to describe those data in this article are succinctly summarized in the notation
+for the likelihood 
 \begin{equation}
-p({\mu},{z} |  {{ADU}}, {{T}}_S,{{z}}_S,
-{{\theta}}_S, \theta_G, \tau).
-\label{hd:eqn}
+p(f, {{T}}_S,{{z}}_S, \theta_G|  \Omega_M, w, \theta_r,\alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}}),
+\label{likelihood:eqn}
 \end{equation}
-The set of distance moduli
-and redshifts $(\mu, z)$ contains the points that constitute the Hubble diagram.  The
-data
-from which the Hubble diagram is inferred include:
-the transient photometry ${ADU}$; spectral measurements of
-transient
-type, redshift and SN-parameters ${T}_S$, ${z}_S$, ${\theta}_S$;
-host-galaxy parameter measurements $\theta_H$ (including redshift,
-mass, sSFR, etc.).  
-The subset transients that enter the cosmology
-analysis is based on the sample-selection criteria $\tau$: for example
-the classification score from PSNID (a classifier based on multi-band
-light curves).
-
-The posterior of $\mu$ and $z$ is an efficient way
-to distribute supernova results in is a way that is independent of cosmological model,
-facilitating joint-probe analysis or consideration of non-standard models.  Choosing
-a specific cosmological model, the posterior of the model parameters $\theta_\mu$
-is of interest.  The model presented here accommodates both options.
-
-A sketch of a more extensive model that includes the
-model of Equation~\ref{hd:eqn} is depicted in the Probabilistic Graphical Model
-(PGM)
-shown in Figure~\ref{pgm:fig}.
-The fundamental parameters are those with no incoming arrows;  most are
-used to model the universe: 
-the background cosmology, transients that could enter the sample, and their host galaxies.
+and are sketched as the probabilistic graphical model in Figure~\ref{toypgm:fig}.
+The measurements are
 \begin{itemize}
-\item  $g$ labels the  galaxy that hosts the transient.
-\item $\theta_\mu$ are the parameters that specify that distance modulus.  They could
-be the parameters of a specific cosmological
-parameters, or an empirical model independent of physics.
-\item $\theta_\tau$ govern the relative rates of supernovae of different types in galaxies.
-\item $\theta_T^{Ia}$, $\theta_{Ti}^{Ia}$.  The model parameters for SNe~Ia, including
-parameters that describe distributions.
-Different SN~Ia models could be considered.  The treatment of SALT2
-has been presented in \citet{2011MNRAS.418.2308M}:
-in this model each supernova
-has individual $c$ and $x_1$ parameters that constitute $\theta_{Ti}^{Ia}$;
-global SN~Ia properties
-$\alpha$, $\beta$, $\sigma_{int}$ 
- and  underlying  $c$ and $x_1$ distributions   constitute $\theta_T^{Ia}$.
-\item $\theta_T^{\mathit{non-Ia}}$, $\theta_{Ti}^{\mathit{non-Ia}}$.  False-positive non-Ia transients
-that enter the analysis are described by a parameterized model.
-\item The transmission functions $\phi(\lambda)$ describe the optical path from the
-atmosphere to counts.  Calibration solutions are generally provided
-but are included in Figure~\ref{pgm:fig} to encompass the case of self-calibration.
+\item $f$: the flux at peak brightness, taken 
+to be bolometric to facilitate the treatment of
+standard candles at different redshift;
+\item ${{T}}_S$, ${{z}}_S$: the spectroscopic type and redshift available for a subset of transients;
+\item $\theta_{G1}$, $\theta_{G2}$: the spectroscopic redshifts of the galaxies identified
+as host and neighbor from imaging.
+\end{itemize}
+The model parameters are
+\begin{itemize}
+\item $\Omega_M$, $w$: the mass density and dark-energy equation of state parameters of a flat,
+constant-$w$ dark-energy cosmology;
+\item $\theta_{r1}$, $\theta_{r2}$:  the parameters
+that describe the redshift-dependent relative fraction of SN~Ia's and non-Ia's;
+\item $\alpha_{Ia}$, $\sigma_{Ia}$, $\alpha_{\mathit{non-Ia}}$, $\sigma_{\mathit{non-Ia}}$:
+the luminosity (times $4\pi$) and intrinsic dispersion for SNe~Ia and non-Ia at peak brightness.
+\end{itemize}
+Not listed explicitly in Eqn.~\ref{likelihood:eqn} but shown in Figure~\ref{toypgm:fig} are latent model parameters for each transient:
+\begin{itemize}
+\item $z$: the cosmological redshifts of the host and neighboring galaxies;
+\item $T$: the class of the objects, SN~Ia or non-Ia.
 \end{itemize}
@@
    \centering
-   \includegraphics[width=7in]{/Users/akim/project/abc/results/hdpgm.pdf} 
-   \caption{Probabilistic Graphical Model for the SN~Ia analysis.  
-   The forward modeling
-   flow goes from left to right, starting with the description of the universe, observatory,
-   and data.    A transient has host galaxy $g_i$, which determines its redshift $z_i$
-   and galaxy parameters $\theta_{gi}$.
-   A model with parameters $\theta_\mu$ fix the distance modulus $\mu_i$.
-   The transient type $T$ depends on the host-galaxy parameters  $\theta_{gi}$
-   and rates $\theta_r$.   The transient
-   parameters $\theta_T^X$, $\theta_{Ti}^X$ (and perhaps the host galaxy) determine the luminosity $L$.       The 
-   incoming photon flux $n$, $n_g$  are then fixed
-   with redshift and distance modulus.
-   The instrumental transmission function $\phi$ is calibrated with data ${Z}$ and
-   gives the expected
-   counts $\overline{\mathit{ADU}}$, $\overline{\mathit{ADU}}_g$. 
-   The transient has realized light curves (${ADU}$) and passes selection criteria
-   through $\tau_i$ to be included in the sample.  Some transients have spectral data
-   ${X}_S$.  The properties of the galaxy identified as the host galaxy is $\theta_G$. 
-   \label{pgm:fig}}
+   \includegraphics[width=4.5in]{/Users/akim/project/abc/results/toy_pgm.pdf} 
+   \caption{Probabilistic Graphical Model for the  SN~Ia standard candle analysis. The
+   parameters include the cosmological parameters $\Omega_M$ and $w$,
+   the luminosities $\alpha$ and intrinsic dispersions $\sigma$ of SNe~Ia and non-Ia's,
+   and the relative fraction parameters $\theta_{r1}$ and $\theta_{r2}$.  Latent parameters
+   include the type $T$ and redshifts of the host and neighboring galaxies $z$ and $z_N$
+   for each transient.  The  distance modulus $\mu$ and
+   luminosity $L$ are fixed by the other parameters.  The observables include the measured
+   flux $f$, spectroscopic type and redshift $T_S$ and $z_S$, and
+   the inferred host and neighbor redshifts $\theta_{G1}$ and $\theta_{G2}$.
+   The host and neighbor galaxies of all transients are inferred based a common galaxy catalog, 
+   and so strictly are not independent from supernova to supernova.
+   \label{toypgm:fig}}
 \end{figure}
 
-From these fundamental parameters we can determine the expected
-signals
-through a series of intermediary parameters,
-some of which are deterministic (points in Figure~\ref{pgm:fig}) and others
-probabilistic (ovals).
-\begin{itemize}
-\item $z_i$, $\theta_{gi}$ are the galaxy redshift and parameters (e.g.\ mass, sSFR, metallicity).
-Each galaxy $g_i$ has its values for these quantities.
-\item $\mu_i=\mu(z_i; \theta_\mu)$.  The distance modulus is a function of redshift,
-Unspecified at the moment,  it could
-be a $\Lambda$CDM prediction with cosmological parameters, a spline with knot values
-as parameters.
-The redshift of the galaxy is used in the Hubble diagram, peculiar velocities are not considered.
-\item $P(T_i | \theta_r, \theta_{gi})$.  The transient type $T_i$, SN~Ia or non-Ia, depends
-on the relative rates given the host properties.
-\item $P(L_i(t,\lambda)| T_i, \theta_T^{Ia}, \theta_{Ti}^{Ia}, \theta_T^{\mathit{non-Ia}}, \theta_{Ti}^{\mathit{non-Ia}},
-\theta_{gi})$.  The source model determines
-the luminosity; the model may include intrinsic dispersion to make the luminosity
-probabilistic. The  model includes  information on the
-source and line-of-sight effects, which specify the effective SED.   Only the
-parameters of the model of the appropriate type $T$ are relevant.  The galaxy parameters
-$\theta_{gi}$ are included if correlations with host-galaxy properties are to be modeled.
-\item $n_i(t,\lambda; L_i, \mu_i, z_i)$, $n_{gi}(t; g_i, \mu_i, z_i)$.  The  fluxes of
-the transient and host that are incident at Earth
-are fixed by the luminosity, distance modulus, and redshift.
-The supernova redshift is required for this calculation,
-for simplicity the supernova and host-galaxy redshift are assumed to be equal.
-\item $\overline{\mathit{ADU}}$ and
-$\overline{\mathit{ADU}}_g$ are the expected counts of the transient and galaxy respectively,
-coming from $\int n_i \phi d\lambda$.  
-\end{itemize}
+The analysis sample consists of transients that are discovered and pass some sample-selection criteria, for example a photometric-classification score.  While the studies in this
+article  explicitly account for
+the discovery criterion, they do not do so for the subsequent sample selection.
+In other words, sample selection is assumed not to alter the shape of any of the pdf's.
 
-The observations are as follows:
-\begin{itemize}
-\item ${\mathit{ADU}}$ is the realized flux.  It depends on the underlying flux and
-the photometric noise.
-\item $\theta_G$ represents the galaxy parameters of the
-galaxy catalog used to identify prospective host galaxies.
-\item ${T}_S$, ${z}_S$, ${\theta}_S$ are the transient type, redshift and properties from
-spectroscopic data. Details of the actual measurement are ignored and a direct association
-is made with the fluxes of the transient and underlying galaxy $n$, $n_g$.
-\item $\tau$ is the score used to decide if the transient is used in the analysis.  It is
-determined based on other measurements $\tau(\mathit{ADU},T_S)$.
-\item ${Z}$ represents the calibration measurements.   Although this may be given
-by the Calibration Task Force, the PGM is written for the more general case where the calibration
-is modeled within our analysis.
-\end{itemize}
-
-%The likelihood for the model is
-%\begin{multline}
-%p(\mathit{ADU}, {{T}}_S,{{z}}_S,
-%{{\theta}}_S, \theta_G, \tau, Z | g, \theta_\mu, \theta_r, \theta_T^{Ia}, \theta_{Ti}^{Ia}, \theta_T^{non-Ia}, \theta_{Ti}^{non-Ia}, \phi) = \\
-%p(\theta_G|g)p(Z|\phi)p(\mathit{ADU}, {{T}}_S,{{z}}_S,
-%{{\theta}}_S, \tau | g, \theta_\mu, \theta_r, \theta_T^{Ia}, \theta_{Ti}^{Ia}, \theta_T^{non-Ia}, \theta_{Ti}^{non-Ia}, \phi).
-%\label{likelihood:eqn}
-%\end{multline}
-
-\section{Simple Example}
-\subsection{Model}
-\label{example:sec}
-A simplified version of the above model,
-\begin{equation}
-p(\mathit{ADU}, {{T}}_S,{{z}}_S, \theta_G|  \Omega_M, w, \theta_r,\alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}}),
-\end{equation}
-is examined in this section.
-The measurements: 
-\begin{itemize}
-\item $\mathit{ADU}$ are measured counts at peak brightness.
-\item ${{T}}_S$, ${{z}}_S$ are spectroscopic type and redshift for a subset of transients.
-\item $\theta_G$ are the redshift of the galaxy identified as the transient host.
-\end{itemize}
-The model parameters:
-\begin{itemize}
-\item $\Omega_M$, $w$ are the parameters of a flat dark-energy cosmology.
-\item $\theta_r$ describe the fraction of transients that are SN~Ia, independent
-of host-galaxy properties.
-\item $\alpha_{Ia}$, $\sigma_{Ia}$, $\alpha_{\mathit{non-Ia}}$, $\sigma_{\mathit{non-Ia}}$ are
-the luminosity (times $4\pi$) and intrinsic dispersion for SNe~Ia and non-Ia at peak.
-Light-curve shape and color are not considered in this simple model.
-\end{itemize}
-
-In addition to the above, there are latent model parameters for each transient used internally
-by the model:
-\begin{itemize}
-\item $z$ are the cosmological redshifts.
-\item $T$ are the type, SN~Ia or non-Ia.
-\end{itemize}
-
-The transients are divided into samples defined by available data: {\it obs} are transients observed spectroscopically while active, from which $T_S=1$ are those typed
+The data for each transient
+is modeled according to the following subsets:
+{\it obs} are transients observed spectroscopically while active, from which $T_S=1$ are those typed
 as SN~Ia and $T_S=0$ as non-Ia.  {\it mis} transients are not observed
@@
 
-\subsubsection{Model for the {\it obs} set data}
-The modeling of data from the {\it obs} set, which has
+\subsection{Model for the {\it obs} set data}
+\label{obs:sec}
+The likelihood of data from the {\it obs} set, which has
 spectroscopic observations $T_S$ and redshift
-$z_S$, is described as follows.  We are interested in
+$z_S$, is described as follow.  The likelihood is
 \begin{align}
-p(\mathit{ADU}, {{T}}_S,{{z}}_S|  \Omega_M, w, \theta_r,\alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}})  &=\sum_T \int_z dz\,
-p(\mathit{ADU}, {{T}}_S,{{z}}_S, T, z| \ldots)\\
+p(f, {{T}}_S,{{z}}_S|  \Omega_M, w, \theta_r,\alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}})  &=\sum_T \int_z dz\,
+p(f, {{T}}_S,{{z}}_S, T, z| \ldots)\\
 &= \sum_T \int_z dz\,
-p(\mathit{ADU}, {{T}}_S,{{z}}_S| T, z,\dots) p(T,z | \ldots)
+p(f, {{T}}_S,{{z}}_S| T, z,\dots) p(T,z | \ldots).
 \end{align}
 
-A direct association of spectroscopic redshift and type are made so that
+A direct association of spectroscopic redshift and type are made
 \begin{align}
@@
 \begin{align}
-p(\mathit{ADU}, {{T}}_S,{{z}}_S|  \ldots) &= 
-p(\mathit{ADU}| T=T_S, z=z_s,\dots) P(T_S| z= z_S , \ldots) p(z_S|\ldots).
+p(f, {{T}}_S,{{z}}_S|  \ldots) &= 
+p(f| T=T_S, z=z_s,\dots) P(T_S| z= z_S , \ldots) p(z_S|\ldots).
 \label{obs:eqn}
 \end{align}
-We remark that in a flux limited survey, the pdf's for the data are truncated versions of the universal
-pdf's of the observables.
 
@@
 is modeled as being drawn from a standard candle
-with luminosity $4\pi\alpha_X$ and intrinsic magnitude dispersion  $\sigma_X$:
+with mean luminosity $4\pi\alpha_X$ and a normal distribution in magnitude
+space with intrinsic dispersion  $\sigma_X$:
 \begin{equation}
-\mathit{ADU}| T_S, z_S, \Omega_M, w, \theta_r, \alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}} \sim \mathcal{N}_{\ln}\left(\ln{\left(\frac{\alpha_{T_S}}{d_L^2(z_S;\Omega_M, w)}\right)}, \frac{\ln{10}}{2.5}\sigma_{T_S}\right),
+f| T_S, z_S, \Omega_M, w, \theta_r, \alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}} \sim \mathcal{N}_{\ln}\left(\ln{\left(\frac{\alpha_{T_S}}{d_L^2(z_S;\Omega_M, w)}\right)}, \frac{\ln{10}}{2.5}\sigma_{T_S}\right),
+\label{flux:eqn}
 \end{equation}
 where $\mathcal{N}_{\ln}$ is the log-normal distribution and $d_L$ is the luminosity distance.
-
-The subset of objects that enters our analysis comes from a truncated distribution:
+Measurement uncertainty is taken to be negligible.
+In a flux limited survey, the pdf's for the data are truncated versions of the underlying
+pdf's.
 \begin{itemize}
-\item For transients in set $T_S=1$:
+\item For SNe~Ia  $T_S=1$:
 \begin{equation}
-\mathit{ADU} | T_S=1, z_S, \Omega_M, w, \alpha_{Ia},\sigma_{Ia} \sim
-\frac{\mathcal{N}_{\ln}\left(\ln{\left(\frac{\alpha_{Ia}}{d_L^2(z_S;\Omega_M, w)}\right)}, \frac{\ln{10}}{2.5}\sigma_{Ia}\right)}{P_{Ia}(\mathit{ADU} > \mathit{ADU}_0)}.
+f | T_S=1, z_S, \Omega_M, w, \alpha_{Ia},\sigma_{Ia} \sim
+\frac{\mathcal{N}_{\ln}\left(\ln{\left(\frac{\alpha_{Ia}}{d_L^2(z_S;\Omega_M, w)}\right)}, \frac{\ln{10}}{2.5}\sigma_{Ia}\right)}{P_{Ia}(f > f_0)}.
 \label{adusnIa:eqn}
 \end{equation}
-\item For transients in set $T_S=0$:
+\item For non-Ia's in set $T_S=0$:
 \begin{equation}
-\mathit{ADU} | T_S=0, z_S, \Omega_M, w, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}}\sim 
-\frac{\mathcal{N}_{\ln}\left(\ln{\left(\frac{\alpha_{\mathit{non-Ia}}}{d_L^2(z_S;\Omega_M, w)}\right)}, \frac{\ln{10}}{2.5}\sigma_{\mathit{non-Ia}}\right)}{P_{non-Ia}(\mathit{ADU} > \mathit{ADU}_0)},
+f | T_S=0, z_S, \Omega_M, w, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}}\sim 
+\frac{\mathcal{N}_{\ln}\left(\ln{\left(\frac{\alpha_{\mathit{non-Ia}}}{d_L^2(z_S;\Omega_M, w)}\right)}, \frac{\ln{10}}{2.5}\sigma_{\mathit{non-Ia}}\right)}{P_{non-Ia}(f > f_0)},
 \label{adunonIa:eqn}
@@
 for the corresponding log-normal distribution.
-It is understood that $p(\mathit{ADU}<\mathit{ADU}_0)=0$ is never evaluated.
+It is understood implicitly that as all objects must pass the detection threshold,
+the case of $f<f_0$ is never confronted in the analysis.
 
@@
  parameterized by the
-its value at $z=0$ and $1.1 \times z_{max}$, 
+its values at $z=0$ and $1.1 \times z_{max}$, 
 \begin{equation}
-\hat{\theta}_{r}=\theta_{r0}+z\left(\frac{\theta_{r1}-\theta_{r0}}{1.1 \times z_{max}}\right).
+\hat{\theta}_r=\theta_{r0}+z\left(\frac{\theta_{r1}-\theta_{r0}}{1.1 \times z_{max}}\right).
+\label{rate:eqn}
 \end{equation}
-The relative rate for SN~Ia discovery for the truncated distribution is
+The relative rate for SN~Ia discovery for the discovered (truncated) distribution is
 \begin{equation}
-\theta_{r}=\frac{\hat{\theta}_{r}}{\hat{\theta}_{r}P_{Ia}(\mathit{ADU} > \mathit{ADU}_0) + (1-\hat{\theta}_{r})P_{non-Ia}(\mathit{ADU} > \mathit{ADU}_0)}.
+\theta_r=\frac{\hat{\theta}_rP_{Ia}(f > f_0)}{\hat{\theta}_{r}P_{Ia}(f > f_0) + (1-\hat{\theta}_{r})P_{non-Ia}(f > f_0)}.
 \end{equation}
@@
 Although the underlying type distribution depends only on $ \theta_{r0}$ and $ \theta_{r1}$,  
-the observed truncated distribution does depend on the other parameters through 
-$P_{X}(\mathit{ADU} > \mathit{ADU}_0)$.
+the observed distribution does depend on the other parameters through $\theta_r$'s dependence on
+the two normalization factors
+$P_{X}(f > f_0)$.
 
 The third term is the redshift distribution of transient discoveries.
-In our model we adopt
-a redshift distribution of transients in the universe
+The model takes an underlying redshift distribution of transients in the universe
 \begin{equation}
-P(z) \propto z^2.
+p(z) \propto z^2.
 \end{equation}
@@
 \begin{equation}
-P(z) = \left(\int_{z_{min}}^{z_{max}} dz'\, z'^2\left( 
-\hat{\theta}_{r}P_{Ia}(\mathit{ADU} > \mathit{ADU}_0) + (1-\hat{\theta}_{r})P_{non-Ia}(\mathit{ADU} > \mathit{ADU}_0)
-\right)\right)^{-1}z^2.
+p(z) = \frac{z^2\left(\hat{\theta}_{r}P_{Ia}(f > f_0) + (1-\hat{\theta}_{r})P_{non-Ia}(f > f_0)
+\right)}{\int_{z_{min}}^{z_{max}} dz'\, z'^2\left( 
+\hat{\theta}_{r}P_{Ia}(f > f_0) + (1-\hat{\theta}_{r})P_{non-Ia}(f > f_0)
+\right)}.
 \end{equation}
 
-In the presented model, the data from different transients are independent.
+\subsection{Model for the {\it mis} set data}
 
-\subsubsection{Model for the {\it mis} set data}
-
-We now consider the modeling of data from the  {\it mis}
-set that has no spectroscopic confirmation.
-The redshift measurement is treated as follows:
-For each transient there are two galaxies identified as
-the potential host, one ($\theta_{G1}$) with high probability $P_{host}$
+Transients in the {\it mis}
+set have no spectroscopic confirmation, and their data are treated as follows:
+With no redshift from the transient itself, 
+the redshift measurement is inferred from potential host galaxies.
+In the analysis of this article each transient is associated with two galaxies, one 
+with redshift $\theta_{G1}$
+that has high probability $\pi_{host}$
 of being the host and the other
-($\theta_{G2}$) at lower $(1-P_{host})$ probability.
+with redshift $\theta_{G2}$ that has probability $(1-\pi_{host})$.
 In the model, the
@@
 P(\theta_{G1},\theta_{G2}|z, z_N) =
-	P_{host}\delta(z-\theta_{G1})\delta(z_N-\theta_{G2}) +
-	(1-P_{host}) \delta(z-\theta_{G2})\delta(z_N-\theta_{G1}).
+	\pi_{host}\delta(z-\theta_{G1})\delta(z_N-\theta_{G2}) +
+	(1-\pi_{host}) \delta(z-\theta_{G2})\delta(z_N-\theta_{G1}).
 \end{equation}
 As for the {\it obs} set, the redshifts of the supernova
- and neighbor are drawn from distributions $P(z) \propto z^2$, $P(z_N) \propto z^2_N$.
+ and neighbor are drawn from underlying distributions $p(z) \propto z^2$, $p(z_N) \propto z^2_N$.
 
-The data likelihood is 
+The underlying distribution is 
 \begin{multline}
-p(\mathit{ADU}, \theta_{G1}, \theta_{G2} | \Omega_M, w, \theta_r, \alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}})  \\
+p(f, \theta_{G1}, \theta_{G2} | \Omega_M, w, \theta_r, \alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}})  \\
 = \sum_{T}\int_{z,z_N} dz\,dz_N \, p(\mathit{ADU, \theta_{G1}, \theta_{G2}}| z , z_N, T, \ldots)P(T| z, z_N,\ldots) p(z, z_N|\ldots)\\
- =\sum_{T} \int_{z,z_N} dz\,dz_N\, p(\mathit{ADU}| z ,T, \ldots)p(\theta_{G1}, \theta_{G2}| z , z_N) P(T| z, \ldots) p(z, z_N|\ldots)\\
-= \sum_{T} P_{host} p(\mathit{ADU}| z=\theta_{G1} ,T, \ldots) P(T| z=\theta_{G1}, \ldots) p(\theta_{G1},\theta_{G2}|\ldots) \\
- +  (1-P_{host}) p(\mathit{ADU}| z=\theta_{G2} ,T, \ldots) P(T| z=\theta_{G2}, \ldots) p(\theta_{G2},
+ =\sum_{T} \int_{z,z_N} dz\,dz_N\, p(f| z ,T, \ldots)p(\theta_{G1}, \theta_{G2}| z , z_N) P(T| z, \ldots) p(z, z_N|\ldots)\\
+= \sum_{T} \pi_{host} p(f| z=\theta_{G1} ,T, \ldots) P(T| z=\theta_{G1}, \ldots) p(\theta_{G1},\theta_{G2}|\ldots) \\
+ +  (1-\pi_{host}) p(f| z=\theta_{G2} ,T, \ldots) P(T| z=\theta_{G2}, \ldots) p(\theta_{G2},
  \theta_{G1}|\ldots)\\
-\propto \sum_{T} P_{host} p(\mathit{ADU}| z=\theta_{G1} ,T, \ldots) P(T| z=\theta_{G1}, \ldots) \\
- +  (1-P_{host}) p(\mathit{ADU}| z=\theta_{G2} ,T, \ldots) P(T| z=\theta_{G2}, \ldots),
+\propto \sum_{T} \pi_{host} p(f| z=\theta_{G1} ,T, \ldots) P(T| z=\theta_{G1}, \ldots) \\
+ +  (1-\pi_{host}) p(f| z=\theta_{G2} ,T, \ldots) P(T| z=\theta_{G2}, \ldots),
 \label{adumis:eqn}
@@
 where we take advantage of the fact that
-$p(\theta_{G1}, \theta_{G2} | \ldots) = p(\theta_{G2}, \theta_{G1} | \ldots)$ does
-not have parameter dependence.
+$p(\theta_{G1}, \theta_{G2} | \ldots) = p(\theta_{G2}, \theta_{G1} | \ldots)$ has
+no parameter dependence.  The probabilities  for the underlying flux and
+relative rate distributions
+ Eqns.~\ref{flux:eqn} and \ref{rate:eqn} introduced in \S\ref{obs:sec} apply.
 
-The distribution of $\mathit{ADU}$ for our sample is a truncated version of the
+The data likelihood is a truncated version of the
 underlying distribution.  
@@
 \begin{equation}
-P(\mathit{ADU}>\mathit{ADU}_0, \theta_{G1}, \theta_{G2}|\ldots) = \int_{\mathit{ADU}_0}^{\infty} p(\mathit{ADU}, \theta_{G1}, \theta_{G2}|\Omega_M, w, \theta_r, \alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}})d\mathit{ADU}
+p(f>f_0, \theta_{G1}, \theta_{G2}|\ldots) = \int_{f_0}^{\infty} p(f, \theta_{G1}, \theta_{G2}|\Omega_M, w, \theta_r, \alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}})df
 \end{equation}
-for a detection threshold of $\mathit{ADU}_0$.
+for a detection threshold of $f_0$.
 
@@
 
-\subsection{Analysis of Simulated Data}
-The simulation of data from the model presented in \S\ref{example:sec}
-and their analysis is implemented in Python and are available
-on GitHub\footnote{\url{git@github.com:AlexGKim/abc.git}}.
-
-The results that follow are based on the parameter
-choices:
+\section{Instantiation and Analysis of Simulated Data}
+\subsection{Simulated Data}
+Simulated data sets are realized and analyzed with the model of
+ \S\ref{model:sec}.  The generative model of the first data set (Set 1) is
+ identical to the model used for analysis, with the following parameter choices:
 \begin{itemize}
@@
 dispersion $\sigma_{non-Ia}=1$.
-\item $\theta_r=r_0 + (r_1-r_0)z/1.54$ for a constant relative fraction of SNe~Ia where $r_1=0.2$,
-$r_0=0.95$.
-\item 2000 transients distributed by co-moving volume in the range $0.1<z<1.4$.
-\item Detection threshold at approximately the mean brightness SN~Ia at $z=1.2$.
-\item $z_{min}=0.1/1.1$ and $z_{max}=1.4\times 1.1$ is the range of possible misassigned
-host redshift.
-\item $P_{host}=0.98$ for the probability of correct host-galaxy assignment.
-\item Accumulated spectra for 20\%, 60\%, and 100\% of discovered transients.
+\item $z_{max}=1.4$.
+\item $\theta_{r0}=0.95$, $\theta_{r1}=0.2$ for the relative fraction of SNe~Ia
+at $z=0$ and $z=1.1 \times z_{max}$ respectively.
+\item 2000 transients total, including discovered and non-discovered,
+in the range $0.1<z<z_{max}$.
+\item Detection threshold at approximately the mean brightness SN~Ia at $z=1$.
+\item Limits of neighbor-galaxy redshifts of $0.1/1.1$ and $1.1\times z_{max}$.
+\item $\pi_{host}=0.98$ for the probability of correct host-galaxy assignment.
+\item Accumulated spectra for 0\%, 20\%, 60\%, and 100\% of discovered transients.
 \end{itemize}
 
-A prior is applied to the SN~Ia absolute magnitude and intrinsic dispersion
+The Hubble diagram for a realization drawn from this model is shown in Figure~\ref{hd:fig}
+and a histogram of redshifts for discovered SNe~Ia and non-Ia in Figure~\ref{hist:fig}.
+SNe~Ia's are shown in blue and non-Ia's in red, those that fall below detection threshold
+are transparent.  The solid points
+represent those objects spectroscopically typed for the case of 20\% follow-up.
+The green X's represent the 2\% among those without spectroscopy that
+are assigned an incorrect redshift.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[scale=0.4]{/Users/akim/project/abc/doc/seed2.pdf}
+   \includegraphics[scale=0.4]{/Users/akim/project/abc/doc/seed2_pop2.pdf}  
+\caption{Hubble diagrams for a realization drawn from Set 1 (left)
+and Set 2 which contains  a second non-Ia population (right).
+Type~Ia's are shown in blue and non-Ia's in red, those that fall below detection threshold
+are transparent.  The green X's represent the 2\% among those without spectroscopy that
+are assigned an incorrect redshift.
+   \label{hd:fig}}
+\end{figure}
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[scale=0.4]{/Users/akim/project/abc/doc/seed2_hist.pdf}
+   \includegraphics[scale=0.4]{/Users/akim/project/abc/doc/seed2_pop2_hist.pdf}  
+\caption{Histogram of redshifts of discovered SNe~Ia and non-Ia from Set 1 (left)
+and Set 2  (right).
+   \label{hist:fig}}
+\end{figure}
+
+The generative model for the second realized data set (Set 2)
+is a perturbed version of that used to make Set 1, and is different from the analysis model.
+A second non-Ia population is introduced with average luminosity 0.5 mag fainter
+than the Ia's and with 0.25 mag dispersion.
+The relative rate of the original non-Ia population relative to the second is quadratic
+in redshift:
+\begin{equation}
+1 -\frac{0.8}{\left(1.1\times z_{max}\right)^2}z^2.
+\end{equation}
+A realization of Set 2 is shown in Figure~\ref{hd:fig}.
+The same seeds used in the construction of Set 1 are used:  The salient differences
+between the two realizations are that a fraction of non-Ia's have absolute magnitude
+based on the second population's average luminosity and intrinsic dispersion; from
+that population different transients pass detection threshold; spectroscopic follow-up is redistributed
+for the new set that is detected.
+
+Sets 1 and 2 share identical discovered SNe~Ia.  For reference, this pure SN~Ia
+set is analyzed with 100\% spectroscopic typing.
+
+\subsection{Analysis Results}
+The simulated data Sets 1 and 2 are analyzed using the model described
+in \S\ref{model:sec}.  The analysis is performed using STAN 
+\citep{stan-software:2015},
+a probabilistic programming language for
+inference of Bayesian models with Hamiltonian Monte Carlo
+using the No-U-Turn sampler \citep{Homan:2014:NSA:2627435.2638586}.  Each run of the analysis
+uses 24 chains each with 1000 links.  In warmup, the first half of the links are used to
+determine parameters for the integration step size and the ``mass''
+parameters of the Hamiltonian. The complementary
+12,000 links represent draws from the model-parameter posterior.
+
+In lieu of including data of
+a pure large SN~Ia sample at low-redshift.
+supplemental priors are applied to the SN~Ia absolute magnitude and intrinsic dispersion
 \begin{align}
@@
 
-The simulated data are analyzed using 
-\citet{stan-software:2015}, a
-a probabilistic programming language for
-inference of Bayesian models with Hamiltonian Monte Carlo.
-
-\subsubsection{Results}
+The output of the analyses are presented as contours of the model
+parameter pdf's for the case of 100\% spectroscopic
+typing in Figure~\ref{hd:fig}, and as the mean, median, and
+credible intervals of $w$ for different fractions of
+spectroscopic completeness in Table~\ref{seed2:tab}.
+For Set 1 the generative and analysis models
+are identical. Consequently the input parameters lie 
+within the 68\% credible intervals of the resultant posterior despite the non-trivial appearance of
+the Hubble diagram in Figure~\ref{hd:fig}.
+The decrease in spectroscopic coverage leads to shifts in $w$ of 0.04 relative to the 100\%-coverage case, which is small
+relative to the credible interval range of 0.281.  However, there is an
+increase in parameter uncertainties, going from $\Delta w= 0.281$ to 0.309
+when there is no spectroscopy.
+At the opposite extreme of no spectroscopic classification the $w$ interval inflates to
+$\Delta w = 0.309$, a constraining result considering that none of the
+objects are directly typed and redshifted.
+The Set 1 analysis gives a best-fit $w$ marginally smaller than $-1$ while its
+subset of SNe~Ia gives a results marginally larger than $-1$.  The addition of the extra non-Ia's provides no appreciable leverage on the uncertainty of $w$.
 
@@
 \centering
-\begin{tabular}{cc|c|cc|}
+\begin{tabular}{|c|cc|ccc|}
 \hline
-ADU0&\% Spec&\%-ile & $w$ range & $\Delta w$\\ \hline
-0 & 100 &$0.68$ & $[-1.174, -0.982]$ & $0.192$ \\
-&&$0.90$ & $[-1.239, -0.923]$ & $0.316$ \\
-&&$0.95$ & $[-1.267, -0.894]$ & $0.373$ \\ \hline
-0.2 & 100&$0.68$ & $[-1.156, -0.972]$ & $0.184$ \\
-&&$0.90$ & $[-1.222, -0.912]$ & $0.309$ \\
-&&$0.95$ & $[-1.255, -0.883]$ & $0.372$ \\ \hline
-0.2&60&$0.68$ & $[-1.209, -1.014]$ & $0.195$ \\
-&&$0.90$ & $[-1.275, -0.955]$ & $0.321$ \\
-&&$0.95$ & $[-1.309, -0.924]$ & $0.385$ \\ \hline
-0&20&$0.68$ & $[-1.226, -1.032]$ & $0.194$ \\
-&&$0.90$ & $[-1.289, -0.969]$ & $0.320$ \\
-&&$0.95$ & $[-1.322, -0.942]$ & $0.379$ \\ \hline
-0.2& 20&$0.68$ & $[-1.229, -1.033]$ & $0.196$ \\
-&&$0.90$ & $[-1.294, -0.972]$ & $0.322$ \\
-&&$0.95$ & $[-1.323, -0.943]$ & $0.380$ \\
+Fraction Spec&$<w>$ & $w$ median &\%-ile  &$w$ range & $\Delta w$\\ \hline
+\multicolumn{6}{|c|}{SN Ia only}\\ \hline
+$1.00$& $-0.94 \pm 0.09$ &$-0.94$ &$0.68$ & $[-1.076, -0.801]$ & $0.275$ \\
+&  &  & $0.90$ & $[-1.166, -0.718]$ & $0.448$ \\
+&  &  & $0.95$ & $[-1.208, -0.682]$ & $0.525$ \\
+ \hline
+\multicolumn{6}{|c|}{Set 1}\\ \hline
+$1.00$ &$-1.06 \pm  0.09$ &$-1.05$ &$0.68$ & $[-1.196, -0.914]$ & $0.281$ \\
+&&&$0.90$ & $[-1.292, -0.826]$ & $0.466$ \\
+&&&$0.95$ & $[-1.340, -0.784]$ & $0.556$ \\
+\hline
+$0.60$ &$-1.08 \pm  0.10$ & $-1.08$ &$0.68$ & $[-1.227, -0.933]$ & $0.293$ \\
+& & &$0.90$ & $[-1.331, -0.836]$ & $0.495$ \\
+& & &$0.95$ & $[-1.385, -0.787]$ & $0.598$ \\
+\hline
+$0.20$ &$-1.10 \pm  0.10$ & $-1.09$ &$0.68$ & $[-1.249, -0.943]$ & $0.305$ \\
+& & &$0.90$ & $[-1.354, -0.851]$ & $0.502$ \\
+& & &$0.95$ & $[-1.408, -0.810]$ & $0.597$ \\
+\hline
+$0.00$ &$-1.07 \pm  0.10$ & $-1.06$ &$0.68$ & $[-1.218, -0.909]$ & $0.309$ \\
+& & &$0.90$ & $[-1.320, -0.812]$ & $0.508$ \\
+& & &$0.95$ & $[-1.372, -0.770]$ & $0.602$ \\
+\hline
+\multicolumn{6}{|c|}{Set 2}\\ \hline
+$1.00$ &$-0.94 \pm  0.09$ &$-0.94$ &$0.68$ & $[-1.078, -0.804]$ & $0.274$ \\
+&&&$0.90$ & $[-1.168, -0.720]$ & $0.447$ \\
+&&&$0.95$ & $[-1.214, -0.680]$ & $0.534$ \\
+\hline
+$0.60$ &$-1.04 \pm  0.10$ & $-1.03$ &$0.68$ & $[-1.182, -0.883]$ & $0.298$ \\
+& & &$0.90$ & $[-1.285, -0.791]$ & $0.494$ \\
+& & &$0.95$ & $[-1.332, -0.749]$ & $0.583$ \\
+\hline
+$0.20$ &$-1.10 \pm  0.10$ & $-1.09$ &$0.68$ & $[-1.247, -0.936]$ & $0.311$ \\
+& & &$0.90$ & $[-1.359, -0.840]$ & $0.518$ \\
+& & &$0.95$ & $[-1.413, -0.798]$ & $0.614$ \\
+\hline
+$0.00$ &$-1.11 \pm  0.10$ & $-1.10$ &$0.68$ & $[-1.266, -0.948]$ & $0.317$ \\
+& & &$0.90$ & $[-1.375, -0.850]$ & $0.525$ \\
+& & &$0.95$ & $[-1.428, -0.808]$ & $0.621$ \\
 \hline
 \end{tabular}
-\caption{Credible intervals of $w$ using the SNe~Ia only with spectroscopic
-observations.\label{ia_only:tab}}
+\caption{Mean, median, and credible intervals of $w$ for the SNe~Ia only,
+Model 1, and Model 2 for varying
+fractions of spectroscopic coverage. \label{seed2:tab}}
 \end{table}
+
+The generative model for Set 2 differs from the analysis model.
+While it is expected for the input and resultant non-Ia parameters not to match, 
+when there is 100\% spectroscopic coverage the posteriors of the other
+parameters accommodate the input with the $w$ posterior matching
+closely that of the SN~Ia-only analysis.  Unlike Model~1, which exhibits no bias
+in $w$ with decreasing spectroscopy, Model~2 does have a shift in the $w$
+credible region.  
+The values of the mean and median values of
+$w$ for both 20\% and 0\% coverage are no outside the 68\%
+credible region of the ideal 100\% coverage.
+The Set 2 $\Delta w$ increases quicker with decreasing spectroscopy
+relative to Set 1.
+
+These results are consistent with the trivial expectation that when generative
+and analysis models are identical statistically correct parameter determinations
+occur, and that analysis with an incorrect non-Ia model can lead to bias.
+The latter case is mitigated with complete spectroscopic typing, though then
+the non-Ia's contribute little to the $w$ constraints.
 
@@
 
+\section{Model}
+We infer a Hubble diagram based on measurements of discovered transients
+that have passed some selection criteria (e.g.\ classified as Type~Ia supernovae).  The posterior
+of the Hubble diagram is denoted as
+\begin{equation}
+p({\mu},{z} |  {{ADU}}, {{T}}_S,{{z}}_S,
+{{\theta}}_S, \theta_G, \tau).
+\label{hd:eqn}
+\end{equation}
+The set of distance moduli
+and redshifts $(\mu, z)$ contains the points that constitute the Hubble diagram.  The
+data
+from which the Hubble diagram is inferred include:
+the transient photometry ${ADU}$; spectral measurements of
+transient
+type, redshift and SN-parameters ${T}_S$, ${z}_S$, ${\theta}_S$;
+host-galaxy parameter measurements $\theta_H$ (including redshift,
+mass, sSFR, etc.).  
+The subset transients that enter the cosmology
+analysis is based on the sample-selection criteria $\tau$: for example
+the classification score from PSNID (a classifier based on multi-band
+light curves).
+
+The posterior of $\mu$ and $z$ is an efficient way
+to distribute supernova results in is a way that is independent of cosmological model,
+facilitating joint-probe analysis or consideration of non-standard models.  Choosing
+a specific cosmological model, the posterior of the model parameters $\theta_\mu$
+is of interest.  The model presented here accommodates both options.
+
+A sketch of a more extensive model that includes the
+model of Equation~\ref{hd:eqn} is depicted in the Probabilistic Graphical Model
+(PGM)
+shown in Figure~\ref{pgm:fig}.
+The fundamental parameters are those with no incoming arrows;  most are
+used to model the universe: 
+the background cosmology, transients that could enter the sample, and their host galaxies.
+\begin{itemize}
+\item  $g$ labels the  galaxy that hosts the transient.
+\item $\theta_\mu$ are the parameters that specify that distance modulus.  They could
+be the parameters of a specific cosmological
+parameters, or an empirical model independent of physics.
+\item $\theta_\tau$ govern the relative rates of supernovae of different types in galaxies.
+\item $\theta_T^{Ia}$, $\theta_{Ti}^{Ia}$.  The model parameters for SNe~Ia, including
+parameters that describe distributions.
+Different SN~Ia models could be considered.  The treatment of SALT2
+has been presented in \citet{2011MNRAS.418.2308M}:
+in this model each supernova
+has individual $c$ and $x_1$ parameters that constitute $\theta_{Ti}^{Ia}$;
+global SN~Ia properties
+$\alpha$, $\beta$, $\sigma_{int}$ 
+ and  underlying  $c$ and $x_1$ distributions   constitute $\theta_T^{Ia}$.
+\item $\theta_T^{\mathit{non-Ia}}$, $\theta_{Ti}^{\mathit{non-Ia}}$.  False-positive non-Ia transients
+that enter the analysis are described by a parameterized model.
+\item The transmission functions $\phi(\lambda)$ describe the optical path from the
+atmosphere to counts.  Calibration solutions are generally provided
+but are included in Figure~\ref{pgm:fig} to encompass the case of self-calibration.
+\end{itemize}
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=7in]{/Users/akim/project/abc/results/hdpgm.pdf} 
+   \caption{Probabilistic Graphical Model for the SN~Ia analysis.  
+   The forward modeling
+   flow goes from left to right, starting with the description of the universe, observatory,
+   and data.    A transient has host galaxy $g_i$, which determines its redshift $z_i$
+   and galaxy parameters $\theta_{gi}$.
+   A model with parameters $\theta_\mu$ fix the distance modulus $\mu_i$.
+   The transient type $T$ depends on the host-galaxy parameters  $\theta_{gi}$
+   and rates $\theta_r$.   The transient
+   parameters $\theta_T^X$, $\theta_{Ti}^X$ (and perhaps the host galaxy) determine the luminosity $L$.       The 
+   incoming photon flux $n$, $n_g$  are then fixed
+   with redshift and distance modulus.
+   The instrumental transmission function $\phi$ is calibrated with data ${Z}$ and
+   gives the expected
+   counts $\overline{f}$, $\overline{f}_g$. 
+   The transient has realized light curves (${ADU}$) and passes selection criteria
+   through $\tau_i$ to be included in the sample.  Some transients have spectral data
+   ${X}_S$.  The properties of the galaxy identified as the host galaxy is $\theta_G$. 
+   \label{pgm:fig}}
+\end{figure}
+
+From these fundamental parameters we can determine the expected
+signals
+through a series of intermediary parameters,
+some of which are deterministic (points in Figure~\ref{pgm:fig}) and others
+probabilistic (ovals).
+\begin{itemize}
+\item $z_i$, $\theta_{gi}$ are the galaxy redshift and parameters (e.g.\ mass, sSFR, metallicity).
+Each galaxy $g_i$ has its values for these quantities.
+\item $\mu_i=\mu(z_i; \theta_\mu)$.  The distance modulus is a function of redshift,
+Unspecified at the moment,  it could
+be a $\Lambda$CDM prediction with cosmological parameters, a spline with knot values
+as parameters.
+The redshift of the galaxy is used in the Hubble diagram, peculiar velocities are not considered.
+\item $P(T_i | \theta_r, \theta_{gi})$.  The transient type $T_i$, SN~Ia or non-Ia, depends
+on the relative rates given the host properties.
+\item $P(L_i(t,\lambda)| T_i, \theta_T^{Ia}, \theta_{Ti}^{Ia}, \theta_T^{\mathit{non-Ia}}, \theta_{Ti}^{\mathit{non-Ia}},
+\theta_{gi})$.  The source model determines
+the luminosity; the model may include intrinsic dispersion to make the luminosity
+probabilistic. The  model includes  information on the
+source and line-of-sight effects, which specify the effective SED.   Only the
+parameters of the model of the appropriate type $T$ are relevant.  The galaxy parameters
+$\theta_{gi}$ are included if correlations with host-galaxy properties are to be modeled.
+\item $n_i(t,\lambda; L_i, \mu_i, z_i)$, $n_{gi}(t; g_i, \mu_i, z_i)$.  The  fluxes of
+the transient and host that are incident at Earth
+are fixed by the luminosity, distance modulus, and redshift.
+The supernova redshift is required for this calculation,
+for simplicity the supernova and host-galaxy redshift are assumed to be equal.
+\item $\overline{f}$ and
+$\overline{f}_g$ are the expected counts of the transient and galaxy respectively,
+coming from $\int n_i \phi d\lambda$.  
+\end{itemize}
+
+The observations are as follows:
+\begin{itemize}
+\item ${f}$ is the realized flux.  It depends on the underlying flux and
+the photometric noise.
+\item $\theta_G$ represents the galaxy parameters of the
+galaxy catalog used to identify prospective host galaxies.
+\item ${T}_S$, ${z}_S$, ${\theta}_S$ are the transient type, redshift and properties from
+spectroscopic data. Details of the actual measurement are ignored and a direct association
+is made with the fluxes of the transient and underlying galaxy $n$, $n_g$.
+\item $\tau$ is the score used to decide if the transient is used in the analysis.  It is
+determined based on other measurements $\tau(f,T_S)$.
+\item ${Z}$ represents the calibration measurements.   Although this may be given
+by the Calibration Task Force, the PGM is written for the more general case where the calibration
+is modeled within our analysis.
+\end{itemize}
+
+%The likelihood for the model is
+%\begin{multline}
+%p(\mathit{ADU}, {{T}}_S,{{z}}_S,
+%{{\theta}}_S, \theta_G, \tau, Z | g, \theta_\mu, \theta_r, \theta_T^{Ia}, \theta_{Ti}^{Ia}, \theta_T^{non-Ia}, \theta_{Ti}^{non-Ia}, \phi) = \\
+%p(\theta_G|g)p(Z|\phi)p(\mathit{ADU}, {{T}}_S,{{z}}_S,
+%{{\theta}}_S, \tau | g, \theta_\mu, \theta_r, \theta_T^{Ia}, \theta_{Ti}^{Ia}, \theta_T^{non-Ia}, \theta_{Ti}^{non-Ia}, \phi).
+%\label{likelihood:eqn}
+%\end{multline}
+
+The simulation of data from the model presented in
+and their analysis is implemented in Python and are available
+on GitHub\footnote{{git@github.com:AlexGKim/abc.git}}.
+
+\bibliographystyle{elsarticle-num} 
 \bibliography{/Users/akim/Documents/alex}

### 2015-09-28 src/analyze.py

@@ -118,11 +118,22 @@ def individual(N_s, ia_only = False, ADU0=None,N_sn=None,dir='temp'):
 	deltas = numpy.zeros(len(levels)/2)
 	wsort = numpy.sort(extract['w'])
 	ans = wsort[numpy.round(levels*len(wsort)).astype(int)]
+	median  = wsort[len(wsort)/2]
+	mean = numpy.mean(ans)
+	std = numpy.std(ans)
 	for i in xrange(len(levels)/2):
 		deltas[i] = ans[-1-i]-ans[i] 
-	for i in xrange(len(levels)/2-1,-1,-1):
-		print '1.0& ${:4.2f}$ &${:4.2f}$ & $[{:5.3f}, {:5.3f}]$ & ${:5.3f}$ \\\\'.format(1-levels[i]*2, b[numpy.argmax(n)],  ans[i],ans[-1-i], deltas[i])
 
+	index = 0
+
+	for i in xrange(len(levels)/2-1,-1,-1):
+#		print '1.0& ${:4.2f}$ &${:4.2f}$ & $[{:5.3f}, {:5.3f}]$ & ${:5.3f}$ \\\\'.format(1-levels[i]*2, b[numpy.argmax(n)],  ans[i],ans[-1-i], deltas[i])
+		if index ==0:
+			print '$1.00$& ${:4.2f} \pm {:4.2f}$ &${:4.2f}$ &${:4.2f}$ & $[{:5.3f}, {:5.3f}]$ & ${:5.3f}$ \\\\'.format(mean, std/numpy.sqrt(len(ans)), median, 1-levels[i]*2,  ans[i],ans[-1-i], deltas[i])
+		else:
+			print '&  &  & ${:4.2f}$ & $[{:5.3f}, {:5.3f}]$ & ${:5.3f}$ \\\\'.format(1-levels[i]*2,  ans[i],ans[-1-i], deltas[i])
+
+		index +=1
 
 
 	# for j in xrange(len(nspec)):

### 2015-09-28 src/plots.py

@@ -52,10 +52,20 @@ def individual(N_s, ia_only = False, ADU0=None,N_sn=None,dir='temp'):
 	deltas = numpy.zeros(len(levels)/2)
 	wsort = numpy.sort(extract['w'])
 	ans = wsort[numpy.round(levels*len(wsort)).astype(int)]
+	median  = wsort[len(wsort)/2]
+	mean = numpy.mean(ans)
+	std = numpy.std(ans)
 	for i in xrange(len(levels)/2):
 		deltas[i] = ans[-1-i]-ans[i] 
+	index = 0
 	for i in xrange(len(levels)/2-1,-1,-1):
-		print '${:4.2f}$ &${:4.2f}$ &${:4.2f}$ & $[{:5.3f}, {:5.3f}]$ & ${:5.3f}$ \\\\'.format(N_s, 1-levels[i]*2, b[numpy.argmax(n)],  ans[i],ans[-1-i], deltas[i])
+#		print '${:4.2f}$ &${:4.2f}$ &${:4.2f}$ & $[{:5.3f}, {:5.3f}]$ & ${:5.3f}$ \\\\'.format(N_s, 1-levels[i]*2, b[numpy.argmax(n)],  ans[i],ans[-1-i], deltas[i])
+		if index ==0:
+			print '${:4.2f}$ &${:5.2f} \pm {:5.2f}$ &${:4.2f}$ &${:4.2f}$ & $[{:5.3f}, {:5.3f}]$ & ${:5.3f}$ \\\\'.format(N_s,mean, std/numpy.sqrt(len(ans)), median,  1-levels[i]*2,  ans[i],ans[-1-i], deltas[i])
+		else:
+			print '&&&${:4.2f}$ & $[{:5.3f}, {:5.3f}]$ & ${:5.3f}$ \\\\'.format(1-levels[i]*2,  ans[i],ans[-1-i], deltas[i])
+		index +=1
+	print "\hline"
 
 	fractions = [0.6, 0.2, 0.0]
 	#fractions = [0.0]
@@ -86,11 +96,21 @@ def individual(N_s, ia_only = False, ADU0=None,N_sn=None,dir='temp'):
 		deltas = numpy.zeros(len(levels)/2)
 		wsort = numpy.sort(extract_['w'])
 		ans = wsort[numpy.round(levels*len(wsort)).astype(int)]
+		median  = wsort[len(wsort)/2]
[…]

### 2015-09-28 src/toy_pgm.py

@@ -26,10 +26,10 @@ pgm.add_node(Node('Luminosity',r"$L_i(t,\lambda)$", 4,3, fixed=True, scale=1.4, 
 #pgm.add_node(Node('Flux',r"$n_i(t,\lambda)$", 5, 5, scale=1.2,fixed=True,offset=(15,0)))
 #pgm.add_node(Node('Flux_g',r"$n_{gi}(\lambda)$", 5, 2,fixed=True,offset=(0,-20)))
 #pgm.add_node(Node('Transmission',r"$\phi(\lambda)$", 7, 7))
-#pgm.add_node(Node('Counts',r"$\overline{\mathit{ADU}}_i$", 8, 5,scale=1.2,fixed=True,offset=(15,0)))
-#pgm.add_node(Node('Counts_g',r"$\overline{\mathit{ADU}}_{gi}$", 8, 4,scale=1.2,fixed=True,offset=(10,-25)))
+#pgm.add_node(Node('Counts',r"$\overline{f}_i$", 8, 5,scale=1.2,fixed=True,offset=(15,0)))
+#pgm.add_node(Node('Counts_g',r"$\overline{f}_{gi}$", 8, 4,scale=1.2,fixed=True,offset=(10,-25)))
 #pgm.add_node(Node('Zeropoints',r"${Z}$", 9, 7, observed=True))
-pgm.add_node(Node('^Counts',r"${\mathit{ADU}_i}$", 4, 2, observed=True,scale=1.2,aspect=1.2))
+pgm.add_node(Node('^Counts',r"${f_i}$", 4, 2, observed=True))
 
 pgm.add_node(Node('Spars',r"${T}_{Si}$, ${z}_{Si}$", 4,1, scale=1.4,aspect=1.2, observed=True))
 #pgm.add_node(Node('^Host',r"${z}_{Hi},{\theta}_{Hi}$", 7, 2, scale=1.5,observed=True))

### 2015-09-29 src/hd_pgm.py
fix diagrams

@@ -8,65 +8,73 @@ rc("text", usetex=True)
 
 pgm = PGM([10.5, 7.5], origin=[0., 0.2], observed_style='inner')
 
-#pgm.add_node(Node('G',r"$G$", 3,1))
-#pgm.add_node(Node('Coords',r"${RA}_i$/${Dec}_i$", 2,1,fixed=True))
-pgm.add_node(Node('G_i',r"$g_i$", 2,2))
+pgm.add_node(Node('dispersion',r"\center{$\sigma_{Ia}$ \newline $\sigma_{non-Ia}$}", 1,7,scale=1.2,aspect=1.8))
+pgm.add_node(Node('rate',r"$\theta_r$",2,7))
+pgm.add_node(Node('theta_T',r"\center{$\alpha_{Ia}$, $\alpha_{non-Ia}$ \newline $\theta_{Ia}$, $\theta_{non-Ia}$}", 5,7,scale=1.4,aspect=1.8))
+pgm.add_node(Node('mu',r"$\Omega_M$, $w$", 6,7, scale=1.4))
+pgm.add_node(Node('Transmission',r"$Z$", 7, 7))
 
-pgm.add_node(Node('mu',r"$\theta_\mu$", 1,4))
-pgm.add_node(Node('rate',r"$\theta_r$", 1,5))
-pgm.add_node(Node('HD',r"$\mu_i$", 4,4,fixed=True))
-pgm.add_node(Node('theta_T',r"$\theta_T^{Ia}$, $\theta_T^{non-Ia}$", 2,7,scale=1.5,aspect=1.5))
-pgm.add_node(Node('theta_Ti',r"$\theta_{Ti}^{Ia}$, $\theta_{Ti}^{non-Ia}$", 2,6,scale=1.5,aspect=1.5))
+pgm.add_node(Node('G_i',r"$g_i$", 3,6))
+pgm.add_node(Node('G_Ni',r"$g_{Ni}$", 4,1))
 
-pgm.add_node(Node('Host',r"$\theta_{gi}$", 2, 3, fixed=True,offset=(-10,-5)))
-pgm.add_node(Node('z',r"$z_i$", 3, 3, fixed=True,offset=(-10,-5)))
+pgm.add_node(Node('Gals',r"$\theta_G$", 10,6, observed=True))
+
+
+pgm.add_node(Node('theta_Ti',r"\center{$\theta_{Ia,i}$ \newline $\theta_{non-Ia,i}$}", 1,5,scale=1.5,aspect=1.2))
 
[…]

### 2015-09-29 src/toy_pgm.py

@@ -22,7 +22,7 @@ pgm.add_node(Node('theta_T',r"\center{$\alpha_{Ia}$, $\alpha_{non-Ia}$ \newline 
 #pgm.add_node(Node('z',r"$z_i$", 2, 2, fixed=True,offset=(-10,-5)))
 
 pgm.add_node(Node('Type',r"$T_i$", 5,3))
-pgm.add_node(Node('Luminosity',r"$L_i(t,\lambda)$", 4,3, fixed=True, scale=1.4, offset=(-22,-22)))
+pgm.add_node(Node('Luminosity',r"$L_i(t,\lambda)$", 4,3, scale=1.4))
 #pgm.add_node(Node('Flux',r"$n_i(t,\lambda)$", 5, 5, scale=1.2,fixed=True,offset=(15,0)))
 #pgm.add_node(Node('Flux_g',r"$n_{gi}(\lambda)$", 5, 2,fixed=True,offset=(0,-20)))
 #pgm.add_node(Node('Transmission',r"$\phi(\lambda)$", 7, 7))

### 2015-09-30 src/analyze.py
fix hd_pgm, change output for analyze

@@ -52,7 +52,7 @@ def individual(N_s, ia_only = False, ADU0=None,N_sn=None,dir='temp'):
 		figure = triangle.corner(samples, labels=[r"$\Omega_M$", r"$w$", r"$\alpha_{Ia}$", r"$\sigma_{Ia}$", r"$\alpha_{non-Ia}$", r"$\sigma_{non-Ia}$", r"SN Ia Rate 0", r"SN Ia Rate1"],
 			truths=[0.28,-1, 2.,0.1,2*10**(-2./2.5),1,0.95,0.2],
 			quantiles=[0.16, 0.5, 0.84], plot_datapoints=False,plot_density=True, **kwargs)
-		plt.savefig('../results/'+dir+'/contour'+app+str(N_s)+'.pdf')
+		plt.savefig('../results/'+dir+'/contour'+app+str(N_s)+'.analyze.pdf')
 		plt.clf()
 
 
@@ -194,7 +194,7 @@ def group(nspec):
 
 
 def main():
-	individual(1.0,ia_only=True,ADU0=0.75,N_sn=2000,dir='seed2')
+	individual(0.0,ia_only=False,ADU0=0.75,N_sn=2000,dir='seed2_pop2')
 #	individual(500,ia_only=False)
 	wefew
 	group([200,350,500])

### 2015-09-30 src/hd_pgm.py

@@ -15,30 +15,30 @@ pgm.add_node(Node('mu',r"$\Omega_M$, $w$", 6,7, scale=1.4))
 pgm.add_node(Node('Transmission',r"$Z$", 7, 7))
 
 pgm.add_node(Node('G_i',r"$g_i$", 3,6))
-pgm.add_node(Node('G_Ni',r"$g_{Ni}$", 4,1))
-
 pgm.add_node(Node('Gals',r"$\theta_G$", 10,6, observed=True))
 
-
 pgm.add_node(Node('theta_Ti',r"\center{$\theta_{Ia,i}$ \newline $\theta_{non-Ia,i}$}", 1,5,scale=1.5,aspect=1.2))
-
 pgm.add_node(Node('Type',r"$T_i$", 2, 5))
+
+pgm.add_node(Node('G_Ni',r"$g_{Ni}$", 4,5))
+
 pgm.add_node(Node('z',r"$z_i$", 3, 3, fixed=True,offset=(-10,-5)))
 
+
+
+pgm.add_node(Node('Stheta',r"${\theta}_{Si}$", 1, 1,  observed=True))
 pgm.add_node(Node('ST',r"${T}_{Si}$", 2, 1, observed=True))
 pgm.add_node(Node('Sz',r"${z}_{Si}$", 3, 1, observed=True))
-pgm.add_node(Node('Stheta',r"${\theta}_{Si}$", 1, 1,  observed=True))
 
 
 pgm.add_node(Node('HD',r"$\mu_i$", 5,3,fixed=True,offset=(10,-5)))
 pgm.add_node(Node('Luminosity',r"$L_i(t,\lambda)$", 5, 4, fixed=True, scale=1.2, offset=(20,-22)))
-pgm.add_node(Node('Flux_g',r"$f_{gi}(\lambda)$", 5, 1,fixed=True,offset=(0,-25)))
 pgm.add_node(Node('Flux',r"$f_i(t,\lambda)$", 5, 2, scale=1.2,fixed=True,offset=(20,-25)))
-
-pgm.add_node(Node('Counts_g',r"$\overline{\mathit{ADU}}_{gi}$", 8, 1,scale=1.2,fixed=True,offset=(10,-25)))
 pgm.add_node(Node('Counts',r"$\overline{\mathit{ADU}}_i$", 8, 2,scale=1.2,fixed=True,offset=(15,0)))
[…]

### 2015-10-01 src/hd_pgm.py
add summary statistics

@@ -19,96 +19,57 @@ pgm.add_node(Node('Gals',r"$\theta_G$", 10,6, observed=True))
 
 pgm.add_node(Node('theta_Ti',r"\center{$\theta_{Ia,i}$ \newline $\theta_{non-Ia,i}$}", 1,5,scale=1.5,aspect=1.2))
 pgm.add_node(Node('Type',r"$T_i$", 2, 5))
-
 pgm.add_node(Node('G_Ni',r"$g_{Ni}$", 4,5))
 
+pgm.add_node(Node('Luminosity',r"$L_i(t,\lambda)$", 5, 4, fixed=True, scale=1.2, offset=(-20,8)))
+
 pgm.add_node(Node('z',r"$z_i$", 3, 3, fixed=True,offset=(-10,-5)))
-
-
+pgm.add_node(Node('HD',r"$\mu_i$", 5,3,fixed=True,offset=(10,-5)))
 
 pgm.add_node(Node('Stheta',r"${\theta}_{Si}$", 1, 1,  observed=True))
 pgm.add_node(Node('ST',r"${T}_{Si}$", 2, 1, observed=True))
 pgm.add_node(Node('Sz',r"${z}_{Si}$", 3, 1, observed=True))
 
 
-pgm.add_node(Node('HD',r"$\mu_i$", 5,3,fixed=True,offset=(10,-5)))
-pgm.add_node(Node('Luminosity',r"$L_i(t,\lambda)$", 5, 4, fixed=True, scale=1.2, offset=(20,-22)))
 pgm.add_node(Node('Flux',r"$f_i(t,\lambda)$", 5, 2, scale=1.2,fixed=True,offset=(20,-25)))
 pgm.add_node(Node('Counts',r"$\overline{\mathit{ADU}}_i$", 8, 2,scale=1.2,fixed=True,offset=(15,0)))
-pgm.add_node(Node('Counts_g',r"$\overline{\mathit{ADU}}_{gi}$", 8, 1,scale=1.2,fixed=True,offset=(10,-25)))
+pgm.add_node(Node('^Counts',r"${\mathit{ADU}_i}$", 9, 2, observed=True,scale=1.2,aspect=1.2))
+
 pgm.add_node(Node('Flux_g',r"$f_{gi}(\lambda)$", 5, 1,fixed=True,offset=(0,-25)))
-#pgm.add_node(Node('^Type',r"$\tau_i$", 9, 1, fixed=True,offset=(10,-10)))
[…]

### 2015-10-09 doc/article.tex
fix hd_pgm, change output for analyze
fixes to z prior

@@
 diagram  (e.g.\ Malmquist bias) so are accounted for explicitly.
-Though motivated by SNe~Ia, this article makes the simplifying assumption that they
-are standard candles with random dispersion; the motivation of this article is to understand
-the general effects of spectroscopic completeness in a manner that is not specific to
-the choice of model for the underlying supernova heterogeneity.
 
-\section{Data Model}
+\section{Standard Candle}
+To introduce basic model elements, this Section considers a
+simplified view of SNe~Ia
+as transients that are bolometric standard candles with an intrinsic random
+dispersion
+at peak brightness, and assumes data with negligible measurement uncertainties.
+For convenience,
+the transients
+in this Section are  referred to as SNe~Ia.
+The added complexity of correlations between absolute magnitude
+and multi-band light curves, and measurement uncertainties
+are discussed in
+\S\ref{snIamodel:sec}.
+
+\subsection{Base Model}
 \label{model:sec}
-The data in constructing a Hubble diagram and the fundamental parameters of the
-model used to describe those data in this article are succinctly summarized in the notation
+This Section presents a model that is used both for generating simulated data, and for analysis.
+The data used to construct a Hubble diagram and the fundamental parameters of the
+model used to describe those data are succinctly summarized in the notation
 for the likelihood 
@@
 \end{equation}
-and are sketched as the probabilistic graphical model in Figure~\ref{toypgm:fig}.
+whose relations are sketched in the probabilistic graphical model in Figure~\ref{toypgm:fig}.
 The measurements are
@@
 \item $\theta_{r1}$, $\theta_{r2}$:  the parameters
-that describe the redshift-dependent relative fraction of SN~Ia's and non-Ia's;
+that describe the redshift-dependent relative fraction of SNe~Ia and non-Ia's;
 \item $\alpha_{Ia}$, $\sigma_{Ia}$, $\alpha_{\mathit{non-Ia}}$, $\sigma_{\mathit{non-Ia}}$:
@@
 \item $z$: the cosmological redshifts of the host and neighboring galaxies;
-\item $T$: the class of the objects, SN~Ia or non-Ia.
+\item $T$: the class of the objects, SN~Ia or non-Ia;
+\item $L$: the luminosity of the transient.
+\end{itemize}
+There is a  fixed parameter
+\begin{itemize}
+\item $\mu$: the distance modulus given the cosmological parameters and the redshift.
 \end{itemize}
@@
    \includegraphics[width=4.5in]{/Users/akim/project/abc/results/toy_pgm.pdf} 
-   \caption{Probabilistic Graphical Model for the  SN~Ia standard candle analysis. The
+   \caption{Probabilistic Graphical Model for the standard candle analysis. The
    parameters include the cosmological parameters $\Omega_M$ and $w$,
@@
    and the relative fraction parameters $\theta_{r1}$ and $\theta_{r2}$.  Latent parameters
-   include the type $T$ and redshifts of the host and neighboring galaxies $z$ and $z_N$
-   for each transient.  The  distance modulus $\mu$ and
+   include 
+   for each transient the type $T$ and redshifts of the host and neighboring galaxies $z$ and $z_N$.  The  distance modulus $\mu$ and
    luminosity $L$ are fixed by the other parameters.  The observables include the measured
@@
 
-The analysis sample consists of transients that are discovered and pass some sample-selection criteria, for example a photometric-classification score.  While the studies in this
-article  explicitly account for
-the discovery criterion, they do not do so for the subsequent sample selection.
-In other words, sample selection is assumed not to alter the shape of any of the pdf's.
+The transients being analyzed have passed some detection threshold
+and thus are drawn from
+distributions that have different shapes than the underlying population of both discovered and
+non-discovered objects. A  threshold flux of $f_0$ is adopted for the detection criterion.
+Otherwise, no other sample-selection criteria are assumed.
 
-The data for each transient
-is modeled according to the following subsets:
+The transients are divided into
+the following subsets:
 {\it obs} are transients observed spectroscopically while active, from which $T_S=1$ are those typed
 as SN~Ia and $T_S=0$ as non-Ia.  {\it mis} transients are not observed
-spectroscopically when active.  The  {\it obs} and {\it mis} samples
-are assumed to be drawn from the same underlying distribution, so that 
-same SN~Ia and non-Ia parameters apply for both sets.
+spectroscopically when active.  The data from each subset have different forms for their likelihood.
+The  {\it obs} sample constrains and specifies the parameter distributions of the 
+parameters missing from the {\it mis} sample; both samples
+are assumed to be drawn from the same underlying distribution.
 
-\subsection{Model for the {\it obs} set data}
+\subsubsection{Likelihood for the {\it obs} set data}
 \label{obs:sec}
@@
 \begin{align}
-p(f, {{T}}_S,{{z}}_S|  \Omega_M, w, \theta_r,\alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}})  &=\sum_T \int_z dz\,
-p(f, {{T}}_S,{{z}}_S, T, z| \ldots)\\
-&= \sum_T \int_z dz\,
-p(f, {{T}}_S,{{z}}_S| T, z,\dots) p(T,z | \ldots).
+p(f, {{T}}_S,{{z}}_S|  \Omega_M, w, \theta_r,\alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}}, z)  &=\sum_T
+p(f, {{T}}_S,{{z}}_S, T| \ldots)\\
+&= \sum_T 
+p(f, {{T}}_S,{{z}}_S| T,\dots) p(T | \ldots).
 \end{align}
 
-A direct association of spectroscopic redshift and type are made
+Direct associations between model and spectroscopic redshift and type are made
 \begin{align}
@@
 p(f, {{T}}_S,{{z}}_S|  \ldots) &= 
-p(f| T=T_S, z=z_s,\dots) P(T_S| z= z_S , \ldots) p(z_S|\ldots).
+p(f| T=T_S, z=z_s,\dots) p(T_S|z=z_s, \ldots).
 \label{obs:eqn}
@@
 \begin{equation}
-f| T_S, z_S, \Omega_M, w, \theta_r, \alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}} \sim \mathcal{N}_{\ln}\left(\ln{\left(\frac{\alpha_{T_S}}{d_L^2(z_S;\Omega_M, w)}\right)}, \frac{\ln{10}}{2.5}\sigma_{T_S}\right),
+f| T=T_S, z=z_S, \Omega_M, w, \theta_r, \alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}} \sim \mathcal{N}_{\ln}\left(\ln{\left(\frac{\alpha_{T_S}}{d_L^2(z_S;\Omega_M, w)}\right)}, \frac{\ln{10}}{2.5}\sigma_{T_S}\right),
 \label{flux:eqn}
@@
 Measurement uncertainty is taken to be negligible.
-In a flux limited survey, the pdf's for the data are truncated versions of the underlying
+In a flux-limited survey, the pdf's for the data are truncated versions of the underlying
 pdf's.
@@
 \begin{equation}
-f | T_S=1, z_S, \Omega_M, w, \alpha_{Ia},\sigma_{Ia} \sim
+f | T=1, z=z_S, \Omega_M, w, \alpha_{Ia},\sigma_{Ia} \sim
 \frac{\mathcal{N}_{\ln}\left(\ln{\left(\frac{\alpha_{Ia}}{d_L^2(z_S;\Omega_M, w)}\right)}, \frac{\ln{10}}{2.5}\sigma_{Ia}\right)}{P_{Ia}(f > f_0)}.
@@
 \begin{equation}
-f | T_S=0, z_S, \Omega_M, w, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}}\sim 
+f | T=0, z=z_S, \Omega_M, w, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}}\sim 
 \frac{\mathcal{N}_{\ln}\left(\ln{\left(\frac{\alpha_{\mathit{non-Ia}}}{d_L^2(z_S;\Omega_M, w)}\right)}, \frac{\ln{10}}{2.5}\sigma_{\mathit{non-Ia}}\right)}{P_{non-Ia}(f > f_0)},
@@
 where the normalization factor is the complementary cumulative distribution function
-for the corresponding log-normal distribution.
+for the corresponding log-normal distribution that accounts for the truncated
+distribution of the detected sample.
 It is understood implicitly that as all objects must pass the detection threshold,
@@
 The second term gives the type probability. In our model,
-the underlying relative rates between SNe~Ia and non-Ia is linear in redshift,
+the underlying relative rates between SNe~Ia and non-Ia are linear in redshift,
  parameterized by the
@@
 \begin{equation}
-T_S | \Omega_M, w, \theta_{r0}, \theta_{r1} , \alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}} \sim \text{Bernoulli}(\theta_r).
+T_S | z=z_S, \Omega_M, w, \theta_{r0}, \theta_{r1} , \alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}} \sim \text{Bernoulli}(\theta_r).
 \end{equation}
@@
 
-The third term is the redshift distribution of transient discoveries.
-The model takes an underlying redshift distribution of transients in the universe
-\begin{equation}
-p(z) \propto z^2.
-\end{equation}
-The redshift distribution of discovered transients is then
-\begin{equation}
-p(z) = \frac{z^2\left(\hat{\theta}_{r}P_{Ia}(f > f_0) + (1-\hat{\theta}_{r})P_{non-Ia}(f > f_0)
-\right)}{\int_{z_{min}}^{z_{max}} dz'\, z'^2\left( 
-\hat{\theta}_{r}P_{Ia}(f > f_0) + (1-\hat{\theta}_{r})P_{non-Ia}(f > f_0)
-\right)}.
-\end{equation}
+%The third term is the redshift distribution of transient discoveries.
+%The model takes an underlying redshift distribution of transients in the universe
+%\begin{equation}
+%p(z) \propto z^2.
+%\end{equation}
+%The redshift distribution of discovered transients is then
+%\begin{equation}
+%p(z) = \frac{z^2\left(\hat{\theta}_{r}P_{Ia}(f > f_0) + (1-\hat{\theta}_{r})P_{non-Ia}(f > f_0)
+%\right)}{\int_{z_{min}}^{z_{max}} dz'\, z'^2\left( 
+%\hat{\theta}_{r}P_{Ia}(f > f_0) + (1-\hat{\theta}_{r})P_{non-Ia}(f > f_0)
+%\right)}.
+%\end{equation}
 
-\subsection{Model for the {\it mis} set data}
+\subsubsection{Likelihood for the {\it mis} set data}
 
@@
 the redshift measurement is inferred from potential host galaxies.
-In the analysis of this article each transient is associated with two galaxies, one 
+In this Section, each transient is associated with two galaxies, one 
 with redshift $\theta_{G1}$
@@
 true host redshift is $z$ and that of the interloping galaxy is $z_N$.
+The likelihood for the galaxy redshifts is
 \begin{equation}
@@
 \end{equation}
-As for the {\it obs} set, the redshifts of the supernova
- and neighbor are drawn from underlying distributions $p(z) \propto z^2$, $p(z_N) \propto z^2_N$.
+As with the transients, the redshifts of the host
+ and neighbor galaxies are drawn from underlying distributions $p(z) \propto z^2$, $p(z_N) \propto z^2_N$.
 
-The underlying distribution is 
+The distribution of the underlying distribution is 
 \begin{multline}
-p(f, \theta_{G1}, \theta_{G2} | \Omega_M, w, \theta_r, \alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}})  \\
-= \sum_{T}\int_{z,z_N} dz\,dz_N \, p(\mathit{ADU, \theta_{G1}, \theta_{G2}}| z , z_N, T, \ldots)P(T| z, z_N,\ldots) p(z, z_N|\ldots)\\
- =\sum_{T} \int_{z,z_N} dz\,dz_N\, p(f| z ,T, \ldots)p(\theta_{G1}, \theta_{G2}| z , z_N) P(T| z, \ldots) p(z, z_N|\ldots)\\
-= \sum_{T} \pi_{host} p(f| z=\theta_{G1} ,T, \ldots) P(T| z=\theta_{G1}, \ldots) p(\theta_{G1},\theta_{G2}|\ldots) \\
- +  (1-\pi_{host}) p(f| z=\theta_{G2} ,T, \ldots) P(T| z=\theta_{G2}, \ldots) p(\theta_{G2},
- \theta_{G1}|\ldots)\\
-\propto \sum_{T} \pi_{host} p(f| z=\theta_{G1} ,T, \ldots) P(T| z=\theta_{G1}, \ldots) \\
- +  (1-\pi_{host}) p(f| z=\theta_{G2} ,T, \ldots) P(T| z=\theta_{G2}, \ldots),
+p(f, \theta_{G1}, \theta_{G2} | \Omega_M, w, \theta_r, \alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}}, z, z_N)  \\
+= \sum_{T} p(f, \theta_{G1}, \theta_{G2}| T, \ldots)P(T| \ldots)\\
+ =\sum_{T} p(f| T, \ldots)p(\theta_{G1}, \theta_{G2}| T, \ldots) P(T| \ldots) \\
+= \sum_{T} \pi_{host} p(f| T, z=\theta_{G1} ,z_N=\theta_{G2}, \ldots) P(T| z=\theta_{G1}, ,z_N=\theta_{G2}, \ldots)  \\
+ +  (1-\pi_{host}) p(f| T, z=\theta_{G2}, z_N=\theta_{G1}, \ldots) P(T| z=\theta_{G2}, z_N=\theta_{G1}, \ldots).
 \label{adumis:eqn}
 \end{multline}
-where we take advantage of the fact that
-$p(\theta_{G1}, \theta_{G2} | \ldots) = p(\theta_{G2}, \theta_{G1} | \ldots)$ has
-no parameter dependence.  The probabilities  for the underlying flux and
+The probabilities  for the underlying flux and
 relative rate distributions
@@
 The data likelihood is a truncated version of the
-underlying distribution.  
-For our analysis, we use the distribution in  Eqn.~\ref{adumis:eqn} normalized by
+underlying distribution: the distribution in  Eqn.~\ref{adumis:eqn} normalized by
 the complementary cumulative distribution function
 \begin{equation}
-p(f>f_0, \theta_{G1}, \theta_{G2}|\ldots) = \int_{f_0}^{\infty} p(f, \theta_{G1}, \theta_{G2}|\Omega_M, w, \theta_r, \alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}})df
+p(f>f_0, \theta_{G1}, \theta_{G2}|\ldots) = \int_{f_0}^{\infty} p(f, \theta_{G1}, \theta_{G2}|\ldots)df
 \end{equation}
@@
 
-%I highlight the treatment of redshift in this model; the cosmological redshift
-%$z$ is set to the values of the
-%observed redshifts through $\delta$-functions.  This choice was made specifically to aid
-%in the convergence of the Monte Carlo: the discrete possibilities for redshift allow
-%for their marginalized likelihood to be used in the calculation of the posterior.
-%A more general model would replace the $\delta$-functions
-%with coming from a continuous PDF's.
-%Peculiar velocities, redshift measurement errors (particularly from
-%photometric redshifts) justify this generalization.
-%A transient
-%without a spectrum has uncertain type and redshift: the redshift
-%of the associated host galaxy, and redshifts expected based on the
-%flux of the SN~Ia and non-Ia standard candles,
-%are viable but disjoint possibilities for the posterior of
-%the true underlying redshift. My runs of this scenario produce chains
-%that do not mix so I resorted to the simplified treatment presented here.
-
-\section{Instantiation and Analysis of Simulated Data}
-\subsection{Simulated Data}
-Simulated data sets are realized and analyzed with the model of
- \S\ref{model:sec}.  The generative model of the first data set (Set 1) is
- identical to the model used for analysis, with the following parameter choices:
+\subsection{Instantiation of Simulated Data}
+Two simulated data sets are realized.
+The generative model of the first data set (Set 1) is
+ identical to the model described in \S\ref{model:sec} with the following parameter choices:
 \begin{itemize}
 \item Cosmological parameters $\Omega_M=0.28$, $w=-1$.
-\item Type~Ia supernovae with intrinsic dispersion $\sigma_{SNIa}=0.1$.
+\item Type~Ia supernovae with intrinsic dispersion $\sigma_{SNIa}=0.1$ mag.
 \item Non-Ia supernovae 2 magnitudes fainter than SNe~Ia with intrinsic
-dispersion $\sigma_{non-Ia}=1$.
+dispersion $\sigma_{non-Ia}=1$ mag.
 \item $z_{max}=1.4$.
@@
 in the range $0.1<z<z_{max}$.
-\item Detection threshold at approximately the mean brightness SN~Ia at $z=1$.
+\item Detection threshold $f_0$ at approximately the mean brightness SN~Ia at $z=1$.
 \item Limits of neighbor-galaxy redshifts of $0.1/1.1$ and $1.1\times z_{max}$.
@@
 
-The Hubble diagram for a realization drawn from this model is shown in Figure~\ref{hd:fig}
-and a histogram of redshifts for discovered SNe~Ia and non-Ia in Figure~\ref{hist:fig}.
+Figures~\ref{hd:fig} and \ref{hist:fig} show
+the Hubble diagram 
+and redshift histogram for discovered SNe~Ia and non-Ia respectively
+for a realization drawn from this model.
 SNe~Ia's are shown in blue and non-Ia's in red, those that fall below detection threshold
@@
 \caption{Hubble diagrams for a realization drawn from Set 1 (left)
-and Set 2 which contains  a second non-Ia population (right).
+and Set 2 that contains  a second non-Ia population (right).
 Type~Ia's are shown in blue and non-Ia's in red, those that fall below detection threshold
@@
 The generative model for the second realized data set (Set 2)
-is a perturbed version of that used to make Set 1, and is different from the analysis model.
+is a perturbed version of that used to make Set 1.
 A second non-Ia population is introduced with average luminosity 0.5 mag fainter
@@
 \end{equation}
-A realization of Set 2 is shown in Figure~\ref{hd:fig}.
-The same seeds used in the construction of Set 1 are used:  The salient differences
+A Hubble diagram realization for Set 2 is shown in Figure~\ref{hd:fig} and its redshift histogram
+is in Figure~\ref{hist:fig}.  Sets 1 and 2 are realized using the same seeds:
+The salient differences
 between the two realizations are that a fraction of non-Ia's have absolute magnitude
 based on the second population's average luminosity and intrinsic dispersion; from
-that population different transients pass detection threshold; spectroscopic follow-up is redistributed
+that population different transients satisfy the detection threshold; spectroscopic follow-up is redistributed
 for the new set that is detected.
@@
 The simulated data Sets 1 and 2 are analyzed using the model described
-in \S\ref{model:sec}.  The analysis is performed using STAN 
+in \S\ref{model:sec}.  The generative model for Set 1 and the analysis model are 
+identical, but for Set 2 they differ.
+The analysis is performed using STAN 
 \citep{stan-software:2015},
@@
 In lieu of including data of
-a pure large SN~Ia sample at low-redshift.
-supplemental priors are applied to the SN~Ia absolute magnitude and intrinsic dispersion
+a pure large SN~Ia sample at low-redshift,
+priors are applied to the SN~Ia absolute magnitude and intrinsic dispersion
 \begin{align}
@@
 spectroscopic completeness in Table~\ref{seed2:tab}.
-For Set 1 the generative and analysis models
-are identical. Consequently the input parameters lie 
+For Set 1  the input parameters lie 
 within the 68\% credible intervals of the resultant posterior despite the non-trivial appearance of
@@
 increase in parameter uncertainties, going from $\Delta w= 0.281$ to 0.309
-when there is no spectroscopy.
-At the opposite extreme of no spectroscopic classification the $w$ interval inflates to
-$\Delta w = 0.309$, a constraining result considering that none of the
+when there is no spectroscopy; the latter is a constraining result considering that none of the
 objects are directly typed and redshifted.
-The Set 1 analysis gives a best-fit $w$ marginally smaller than $-1$ while its
-subset of SNe~Ia gives a results marginally larger than $-1$.  The addition of the extra non-Ia's provides no appreciable leverage on the uncertainty of $w$.
+Relative to Set 1 with 100\% spectrosocopy,
+the subset of SNe~Ia-only has a shift in the mean $w$ of 0.12
+and no appreciable increase in the uncertainty of $w$.
 
@@
 The values of the mean and median values of
-$w$ for both 20\% and 0\% coverage are no outside the 68\%
+$w$ for both 20\% and 0\% coverage are outside the 68\%
 credible region of the ideal 100\% coverage.
@@
 The latter case is mitigated with complete spectroscopic typing, though then
-the non-Ia's contribute little to the $w$ constraints.
+the non-Ia's contribute little statistically to the $w$ constraints.
+
+\section{SN~Ia Model}
+\label{snIamodel:sec}
+\subsection{Base Model}
+SNe~Ia are not perfect standard candles but rather are calibrated candles whose
+peak brightnesses are a
+function of their internal properties discerned from their colors and light-curve evolution.
+Measurement uncertainty, particularly from photometric flux
+calibration and galaxy photometric redshifts, can play an important role in the statistical
+reach of experiments.  This Section contains a model that expands upon the one
+presented in \S\ref{snIamodel:sec} to have the fidelity needed for the photometric
+supernova analysis of the Dark Energy Survey and the Large Synoptic Survey Telescope.
+
+The likelihood is written as
+\begin{equation}
+p(\mathit{ADU}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G |  \Omega_M, w, \theta_r,\alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}}, \theta_{Ia}, \theta_{non-Ia}, Z, g, g_N),
+\label{likelihood2:eqn}
+\end{equation}
+whose relations are sketched in the probabilistic graphical model in Figure~\ref{pgm:fig}.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=6.5in]{/Users/akim/project/abc/results/hdpgm.pdf} 
+   \caption{Probabilistic Graphical Model for the SN~Ia analysis.  
+   The forward modeling
+   flow goes from left to right, starting with the description of the universe, observatory,
+   and data.    A transient has host galaxy $g_i$, which determines its redshift $z_i$
+   and galaxy parameters $\theta_{gi}$.
+   A model with parameters $\theta_\mu$ fix the distance modulus $\mu_i$.
+   The transient type $T$ depends on the host-galaxy parameters  $\theta_{gi}$
+   and rates $\theta_r$.   The transient
+   parameters $\theta_T^X$, $\theta_{Ti}^X$ (and perhaps the host galaxy) determine the luminosity $L$.       The 
+   incoming photon flux $n$, $n_g$  are then fixed
+   with redshift and distance modulus.
+   The instrumental transmission function $\phi$ is calibrated with data ${Z}$ andflux
+   gives the expected
+   counts $\overline{f}$, $\overline{f}_g$. 
+   The transient has realized light curves (${ADU}$) and passes selection criteria
+   through $\tau_i$ to be included in the sample.  Some transients have spectral data
+   ${X}_S$.  The properties of the galaxy identified as the host galaxy is $\theta_G$. 
+   \label{pgm:fig}}
+\end{figure}
+
+The new measurement that differs from  \S\ref{model:sec} is
+\begin{itemize}
+\item $\mathit{ADU}$: the measured counts for each photometric observation takes
+the place of flux;
+\end{itemize}
+The new model parameters are
+\begin{itemize}
+\item $\theta_{Ia}$, $\theta_{non-Ia}$: the parameters for the internal diversity within SNe~Ia and
+non-Ia's respectively;
+\item $Z$: the parameters that describe the transmission functions, i.e.\ photometric calibration.
+\end{itemize}
+New latent model parameters for each transient:
+\begin{itemize}
+\item $\theta_{Ia,i}$, $\theta_{non-Ia,i}$: the underlying parameters that describe the transient;
+\item $g$: the parameters that describe the candidate host and neighbor galaxies including redshift
+is a more general replacement for $z$.
+\end{itemize}
+The new fixed parameters are
+\begin{itemize}
+\item{$z$}: the cosmological transient redshift given the host galaxy;
+\item{$L$}: the luminosity of the transient with specified parameters;
+\item{$f$, $f_g$}: the flux of the transient and foreground hosts;
+\item{$\overline{\mathit{ADU}}$, $\overline{\mathit{ADU}}_g$}: the expected counts of the
+transient and foreground galaxies.
+\end{itemize}
+
+\subsubsection{Likelihood for the obs set data}
+The likelihood of data from the {\it obs} set is
+\begin{equation}
+p(\mathit{ADU}, {{T}}_S,{{z}}_S, \theta_S, \theta_G|  \Omega_M, w, \theta_r,\alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}}, \theta_{Ia}, \theta_{non-Ia}, Z, g, g_N).
+\end{equation}
+Again assuming that spectroscopy gives an unambiguous redshift, type and now adding
+host-galaxy properties 
+\begin{align}
+p(\theta_S, \theta_G|g) &= \delta(\{\theta_S, \theta_G\} -g)
+\end{align}
+then
+\begin{multline}
+p(\mathit{ADU}, {{T}}_S,{{z}}_S, \theta_S, \theta_G|  \ldots) = \\
+p(\mathit{ADU} | T=T_S, z=z_s, g=\{\theta_S, \theta_G\},  \dots) P(T_S| z= z_S , g=\{\theta_S, \theta_G\}, \ldots).
+\label{obs3:eqn}
+\end{multline}
+
+The first term is the likelihood for the light curve.  The dependence of the light curve depends
+on transient properties, cosmology, calibration, and the experiment.  For convenience. the
+construction of the likelihood is broken up into several steps, with intermediary points
+at the determination of the time and wavelength-dependent luminosity $L$,
+the flux $f$, the expected counts $\overline{\mathit{ADU}}$ of the transient and background, and
+finally the observed light curve $\mathit{ADU}$.  Figure~\ref{pgm:fig} shows how these
+parameters are related to the intrinsic parameters and to each other.
+
+The pdf of the luminosity $L$ can be expressed as follows:
+\begin{multline}
+p(L|  \theta_r,\alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}}, \theta_{Ia}, \theta_{non-Ia}, g)  \\
+= \sum_T \int d\theta_{Ia}\, d\theta_{non-Ia}\, P(L, T, \theta_{Ia} \theta_{non-Ia}|\ldots) \\
+= \sum_T \int d\theta_{Ia}\, d\theta_{non-Ia}\, P(L| T, \theta_{Ia} \theta_{non-Ia} \ldots) p(T,
+\theta_{Ia}\, \theta_{non-Ia} | \ldots)
+\end{multline}
+
+\subsubsection{Likelihood for the mis set data}
+
+%The likelihood for the model is
+%\begin{multline}
+%p(\mathit{ADU}, {{T}}_S,{{z}}_S,
+%{{\theta}}_S, \theta_G, \tau, Z | g, \theta_\mu, \theta_r, \theta_T^{Ia}, \theta_{Ti}^{Ia}, \theta_T^{non-Ia}, \theta_{Ti}^{non-Ia}, \phi) = \\
+%p(\theta_G|g)p(Z|\phi)p(\mathit{ADU}, {{T}}_S,{{z}}_S,
+%{{\theta}}_S, \tau | g, \theta_\mu, \theta_r, \theta_T^{Ia}, \theta_{Ti}^{Ia}, \theta_T^{non-Ia}, \theta_{Ti}^{non-Ia}, \phi).
+%\label{likelihood:eqn}
+%\end{multline}
+
+The simulation of data from the model presented in
+and their analysis is implemented in Python and are available
+on GitHub\footnote{{git@github.com:AlexGKim/abc.git}}.
+
+\bibliographystyle{elsarticle-num} 
+\bibliography{/Users/akim/Documents/alex}
+
+\end{document}
 
@@
 %that are mistaken for Ia and not all discovered transients.
-
-\section{Model}
-We infer a Hubble diagram based on measurements of discovered transients
-that have passed some selection criteria (e.g.\ classified as Type~Ia supernovae).  The posterior
-of the Hubble diagram is denoted as
-\begin{equation}
-p({\mu},{z} |  {{ADU}}, {{T}}_S,{{z}}_S,
-{{\theta}}_S, \theta_G, \tau).
-\label{hd:eqn}
-\end{equation}
-The set of distance moduli
-and redshifts $(\mu, z)$ contains the points that constitute the Hubble diagram.  The
-data
-from which the Hubble diagram is inferred include:
-the transient photometry ${ADU}$; spectral measurements of
-transient
-type, redshift and SN-parameters ${T}_S$, ${z}_S$, ${\theta}_S$;
-host-galaxy parameter measurements $\theta_H$ (including redshift,
-mass, sSFR, etc.).  
-The subset transients that enter the cosmology
-analysis is based on the sample-selection criteria $\tau$: for example
-the classification score from PSNID (a classifier based on multi-band
-light curves).
-
-The posterior of $\mu$ and $z$ is an efficient way
-to distribute supernova results in is a way that is independent of cosmological model,
-facilitating joint-probe analysis or consideration of non-standard models.  Choosing
-a specific cosmological model, the posterior of the model parameters $\theta_\mu$
-is of interest.  The model presented here accommodates both options.
-
-A sketch of a more extensive model that includes the
-model of Equation~\ref{hd:eqn} is depicted in the Probabilistic Graphical Model
-(PGM)
-shown in Figure~\ref{pgm:fig}.
-The fundamental parameters are those with no incoming arrows;  most are
-used to model the universe: 
-the background cosmology, transients that could enter the sample, and their host galaxies.
-\begin{itemize}
-\item  $g$ labels the  galaxy that hosts the transient.
-\item $\theta_\mu$ are the parameters that specify that distance modulus.  They could
-be the parameters of a specific cosmological
-parameters, or an empirical model independent of physics.
-\item $\theta_\tau$ govern the relative rates of supernovae of different types in galaxies.
-\item $\theta_T^{Ia}$, $\theta_{Ti}^{Ia}$.  The model parameters for SNe~Ia, including
-parameters that describe distributions.
-Different SN~Ia models could be considered.  The treatment of SALT2
-has been presented in \citet{2011MNRAS.418.2308M}:
-in this model each supernova
-has individual $c$ and $x_1$ parameters that constitute $\theta_{Ti}^{Ia}$;
-global SN~Ia properties
-$\alpha$, $\beta$, $\sigma_{int}$ 
- and  underlying  $c$ and $x_1$ distributions   constitute $\theta_T^{Ia}$.
-\item $\theta_T^{\mathit{non-Ia}}$, $\theta_{Ti}^{\mathit{non-Ia}}$.  False-positive non-Ia transients
-that enter the analysis are described by a parameterized model.
-\item The transmission functions $\phi(\lambda)$ describe the optical path from the
-atmosphere to counts.  Calibration solutions are generally provided
-but are included in Figure~\ref{pgm:fig} to encompass the case of self-calibration.
-\end{itemize}
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=7in]{/Users/akim/project/abc/results/hdpgm.pdf} 
-   \caption{Probabilistic Graphical Model for the SN~Ia analysis.  
-   The forward modeling
-   flow goes from left to right, starting with the description of the universe, observatory,
-   and data.    A transient has host galaxy $g_i$, which determines its redshift $z_i$
-   and galaxy parameters $\theta_{gi}$.
-   A model with parameters $\theta_\mu$ fix the distance modulus $\mu_i$.
-   The transient type $T$ depends on the host-galaxy parameters  $\theta_{gi}$
-   and rates $\theta_r$.   The transient
-   parameters $\theta_T^X$, $\theta_{Ti}^X$ (and perhaps the host galaxy) determine the luminosity $L$.       The 
-   incoming photon flux $n$, $n_g$  are then fixed
-   with redshift and distance modulus.
-   The instrumental transmission function $\phi$ is calibrated with data ${Z}$ and
-   gives the expected
-   counts $\overline{f}$, $\overline{f}_g$. 
-   The transient has realized light curves (${ADU}$) and passes selection criteria
-   through $\tau_i$ to be included in the sample.  Some transients have spectral data
-   ${X}_S$.  The properties of the galaxy identified as the host galaxy is $\theta_G$. 
-   \label{pgm:fig}}
-\end{figure}
-
-From these fundamental parameters we can determine the expected
-signals
-through a series of intermediary parameters,
-some of which are deterministic (points in Figure~\ref{pgm:fig}) and others
-probabilistic (ovals).
-\begin{itemize}
-\item $z_i$, $\theta_{gi}$ are the galaxy redshift and parameters (e.g.\ mass, sSFR, metallicity).
-Each galaxy $g_i$ has its values for these quantities.
-\item $\mu_i=\mu(z_i; \theta_\mu)$.  The distance modulus is a function of redshift,
-Unspecified at the moment,  it could
-be a $\Lambda$CDM prediction with cosmological parameters, a spline with knot values
-as parameters.
-The redshift of the galaxy is used in the Hubble diagram, peculiar velocities are not considered.
-\item $P(T_i | \theta_r, \theta_{gi})$.  The transient type $T_i$, SN~Ia or non-Ia, depends
-on the relative rates given the host properties.
-\item $P(L_i(t,\lambda)| T_i, \theta_T^{Ia}, \theta_{Ti}^{Ia}, \theta_T^{\mathit{non-Ia}}, \theta_{Ti}^{\mathit{non-Ia}},
-\theta_{gi})$.  The source model determines
-the luminosity; the model may include intrinsic dispersion to make the luminosity
-probabilistic. The  model includes  information on the
-source and line-of-sight effects, which specify the effective SED.   Only the
-parameters of the model of the appropriate type $T$ are relevant.  The galaxy parameters
-$\theta_{gi}$ are included if correlations with host-galaxy properties are to be modeled.
-\item $n_i(t,\lambda; L_i, \mu_i, z_i)$, $n_{gi}(t; g_i, \mu_i, z_i)$.  The  fluxes of
-the transient and host that are incident at Earth
-are fixed by the luminosity, distance modulus, and redshift.
-The supernova redshift is required for this calculation,
-for simplicity the supernova and host-galaxy redshift are assumed to be equal.
-\item $\overline{f}$ and
-$\overline{f}_g$ are the expected counts of the transient and galaxy respectively,
-coming from $\int n_i \phi d\lambda$.  
-\end{itemize}
-
-The observations are as follows:
-\begin{itemize}
-\item ${f}$ is the realized flux.  It depends on the underlying flux and
-the photometric noise.
-\item $\theta_G$ represents the galaxy parameters of the
-galaxy catalog used to identify prospective host galaxies.
-\item ${T}_S$, ${z}_S$, ${\theta}_S$ are the transient type, redshift and properties from
-spectroscopic data. Details of the actual measurement are ignored and a direct association
-is made with the fluxes of the transient and underlying galaxy $n$, $n_g$.
-\item $\tau$ is the score used to decide if the transient is used in the analysis.  It is
-determined based on other measurements $\tau(f,T_S)$.
-\item ${Z}$ represents the calibration measurements.   Although this may be given
-by the Calibration Task Force, the PGM is written for the more general case where the calibration
-is modeled within our analysis.
-\end{itemize}
-
-%The likelihood for the model is
-%\begin{multline}
-%p(\mathit{ADU}, {{T}}_S,{{z}}_S,
-%{{\theta}}_S, \theta_G, \tau, Z | g, \theta_\mu, \theta_r, \theta_T^{Ia}, \theta_{Ti}^{Ia}, \theta_T^{non-Ia}, \theta_{Ti}^{non-Ia}, \phi) = \\
-%p(\theta_G|g)p(Z|\phi)p(\mathit{ADU}, {{T}}_S,{{z}}_S,
-%{{\theta}}_S, \tau | g, \theta_\mu, \theta_r, \theta_T^{Ia}, \theta_{Ti}^{Ia}, \theta_T^{non-Ia}, \theta_{Ti}^{non-Ia}, \phi).
-%\label{likelihood:eqn}
-%\end{multline}
-
-The simulation of data from the model presented in
-and their analysis is implemented in Python and are available
-on GitHub\footnote{{git@github.com:AlexGKim/abc.git}}.
-
-\bibliographystyle{elsarticle-num} 
-\bibliography{/Users/akim/Documents/alex}
-
-\end{document}

### 2015-10-09 src/hd_pgm.py

@@ -70,6 +70,7 @@ pgm.add_edge("Transmission","Counts_g")
 pgm.add_edge("Type","ST")
 pgm.add_edge("theta_Ti","Stheta")
 pgm.add_edge("Counts_g","^Counts")
+
 # Big Plate: Galaxy
 pgm.add_plate(Plate([0.5, 0.5, 9, 6.],
                     label=r"SNe $i = 1, \cdots, N_{SN}$",

### 2015-10-16 doc/article.tex
Keep on writing article

@@
 \section{Standard Candle}
+\label{toy:sec}
 To introduce basic model elements, this Section considers a
@@
 
-\section{SN~Ia Model}
+\section{DES SN Survey Model}
 \label{snIamodel:sec}
-\subsection{Base Model}
+\subsection{Model}
 SNe~Ia are not perfect standard candles but rather are calibrated candles whose
@@
 
-The likelihood is written as
+The notation for the likelihood presents the data and fundamental model parameters
 \begin{equation}
-p(\mathit{ADU}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G |  \Omega_M, w, \theta_r,\alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}}, \theta_{Ia}, \theta_{non-Ia}, Z, g, g_N),
+p(\mathit{ADU}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G |  \Omega_M, w, \theta_r, \alpha_{Ia}, \beta_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\beta_{\mathit{non-Ia}}, \sigma_{\mathit{non-Ia}},  Z, g, g_N, f_g),
 \label{likelihood2:eqn}
@@
 \begin{itemize}
-\item $\mathit{ADU}$: the measured counts for each photometric observation takes
-the place of flux;
+\item $\mathit{ADU}$: the measured counts for each photometric observation.
+This takes
+the place of flux as calibration is now considered.
 \end{itemize}
@@
 \begin{itemize}
-\item $\theta_{Ia}$, $\theta_{non-Ia}$: the parameters for the internal diversity within SNe~Ia and
-non-Ia's respectively;
 \item $Z$: the parameters that describe the transmission functions, i.e.\ photometric calibration.
+\item $\beta_{Ia}$, $\beta_{non-Ia}$: the parameters for the internal diversity within SNe~Ia and
+non-Ia's respectively, e.g.\ SALT2's  $\alpha$ and $\beta$;
+\item $f_g$: the surface brightness of the background light at the location of the transient
+needed for to extract the photometry of the point-source transient.
 \end{itemize}
@@
 \begin{itemize}
-\item $\theta_{Ia,i}$, $\theta_{non-Ia,i}$: the underlying parameters that describe the transient;
-\item $g$: the parameters that describe the candidate host and neighbor galaxies including redshift
-is a more general replacement for $z$.
+\item $\theta_{Ia}$, $\theta_{non-Ia}$: the transient parameters that describe individual
+transients, e.g.\ SALT2's $x_1$, $c$;
+\item $g$: the parameters that describe the candidate host and neighbor galaxies,
+to be more expansive than the previous $z$ parameter.
 \end{itemize}
@@
 \begin{itemize}
-\item{$z$}: the cosmological transient redshift given the host galaxy;
-\item{$L$}: the luminosity of the transient with specified parameters;
-\item{$f$, $f_g$}: the flux of the transient and foreground hosts;
-\item{$\overline{\mathit{ADU}}$, $\overline{\mathit{ADU}}_g$}: the expected counts of the
-transient and foreground galaxies.
+\item{$f$}: the flux of the transient;
+\item{$\overline{\mathit{ADU}}_X$}: the expected counts of the transient and background light.
 \end{itemize}
 
-\subsubsection{Likelihood for the obs set data}
-The likelihood of data from the {\it obs} set is
+The relationships between the parameters for the underlying population are now described.  What follows is an initial proposal
+based on current supernova analyses, but many different models need to be
+considered as the understanding of transients improve
+and for probing systematics by comparing the
+performance of competing models.
+
+\begin{itemize}
+\item Intrinsic transient parameters are dependent on their distributions and the host galaxy.
+The SNe~Ia parameters are drawn as
 \begin{equation}
-p(\mathit{ADU}, {{T}}_S,{{z}}_S, \theta_S, \theta_G|  \Omega_M, w, \theta_r,\alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}}, \theta_{Ia}, \theta_{non-Ia}, Z, g, g_N).
+\theta_{Ia} | \sigma_{Ia}, g \sim \mathcal{N}(0, \sigma_{Ia}),
 \end{equation}
-Again assuming that spectroscopy gives an unambiguous redshift, type and now adding
-host-galaxy properties 
-\begin{align}
-p(\theta_S, \theta_G|g) &= \delta(\{\theta_S, \theta_G\} -g)
-\end{align}
-then
+where $\theta_{Ia} =\{x_1, c, \delta_M\}$, the SALT2 light-curve shape and color parameters.
+A more complex model can be based on non-Normal distributions
+and/or including SN properties directly tied to characteristics (e.g.\ mass, star formation
+rate) of the host galaxy.
+
+The non-Ia parameters are drawn as
+\begin{equation}
+\theta_{non-Ia} | \sigma_{non-Ia}, g  \sim \mathcal{N}(0, \sigma_{non-Ia}),
+\end{equation}
+where the parameter is the realization of an intrinsic magnitude dispersion.
+A more complex model can include multiple non-Ia populations each with its own
+intrinsic parameters.
+\item Spectroscopically observed transient parameters depend on the intrinsic transient
+parameters and type.  $\theta_{Si}$ may be ignored in a zero'th order analysis that
+does not relate spectral features with SN~Ia absolute magnitudes.   If spectral
+features are considered, the simple model
+\begin{equation}
+\theta_{Si} | \theta_{Ia}, \theta_{non-Ia}, T = \delta(\theta_{Si}-\theta_T)
+\end{equation}
+assumes an unambiguous mapping between supernova parameters and spectral signal.
+\item The type is drawn from the host-dependent relative rate between SNe~Ia and non-Ia's 
+\begin{equation}
+T | \theta_r, g \sim \rm{Bernoulli}(\pi(g,\theta_r)),
+\end{equation}
+where $\pi$ is a model for the relative rates of the different types as a
+function of galaxy parameters and redshift.  A reasonable choice for $\pi$ needs to be
+selected, any volunteers?
+\item Supernova type is assumed to be unambiguously encoded in the
+spectrum:
+\begin{equation}
+T_S | T  = \delta(T_S - T).
+\end{equation}
+\item The observed redshift is taken to be the host galaxy redshift
+\begin{equation}
+z_S = g_z,
+\end{equation}
+where $g_z$ is the element in $g$ that corresponds to redshift.
+Added sophistication includes redshift
+measurement uncertainty and random peculiar velocities. The study of coherent
+flow requires added model complexity.
+\item The underlying SED of transients are modeled.  For SNe~Ia the SALT2 model
+is an option, although new models that separate dust and intrinsic color or
+identify new SN~Ia parameters are expected in the near future.  Absolute magnitudes
+that depend on host-galaxy properties need to be considered. 
+For SNe~Ia $T=1$
+\begin{equation}
+L(t,\lambda; \alpha_{Ia}, \beta_{Ia}, \theta_{Ia}, g)  =10^{-\left(\frac{\alpha x_1 + \beta c}{2.5}\right)}L_{SALT2}(t-t_0; \alpha_{Ia}, x_1, c, \delta_m) \gamma(g, \beta) ,
+\end{equation}
+where the first two terms is the SALT2 model with a realized error snake,
+and $\gamma(g, \beta)$ a step function with free parameters in $\beta$ that
+describe the step size.
+
+For non-Ia's $T=0$ a set of light curve templates or a model can be used.
+An initial candidate is the treatment of non-Ia's implemented in PSNID.
+\item The theoretical distance modulus
+\begin{equation}
+\mu(g_z; \Omega_M, w)
+\end{equation}
+is the predicted distance modulus of a flat dark energy cosmology.
+\item The flux incident on Earth is the redshifted and time-dilated SED scaled
+by the distance modulus.
+\begin{equation}
+f(t,\lambda) = 10^{-\mu/2.5} L\left(t/(1+g_z),\lambda/(1+g_z)\right)
+\end{equation}
+\item The expected light curve in counts depends on the flux and throughput of the
+optical chain.  A first model encapsulates flux calibration through a zeropoint
+\begin{equation}
+\overline{\mathit{ADU}}(f, Z) = 10^{Z/2.5} \int  f(\lambda) T_0(\lambda)d\lambda,
+\end{equation}
+where $T_0$ is a fiducial transmission function for the appropriate filter.  A more sophisticated
+analysis can have a transmission function specific to each observation.
+\item The measured surface brightness of the host galaxy depends on the underlying
+surface brightness convolved with the point spread function and integrated
+over the transmission
+\begin{equation}
+\overline{\mathit{ADU}}_g =    \int (f_g(\lambda, RA, Dec) \otimes PSF) T(\lambda;Z)d\lambda.
+\end{equation}
+\item The measurement $\mathit{ADU}$ is the superposition of transient and background
+light $\overline{\mathit{ADU}} + \overline{\mathit{ADU}}_g$.
+\end{itemize}
+
+\subsection{Likelihood}
+
+\subsubsection{Measurements}
+In the following discussion,
+spectroscopic and galaxy measurements are assumed
+to provide prefect determinations of transient type and parameters, and
+galaxy redshifts and parameters.  The working group is striving to get spectroscopic
+redshifts of all potential hosts.
+
+The measured counts depend on the expected counts and measurement uncertainty
+$C_P$ as a Poisson (or considering the high sky background Normal) distribution
+\begin{equation}
+\mathit{ADU} \sim \mathcal{N} (\overline{\mathit{ADU}}+\overline{\mathit{ADU}}_g ,C_P).
+\label{ADU:eqn}
+\end{equation}
+
+Practically, the photometric extraction is handled by independent software, which calculates
+the pdf of $\mathit{ADU}_{\mathit{SN}}$, the realized contribution of supernova light,
+replacing this and the previous two bullet points.  Dillon is providing this.
+For the rest of the discussion, $\mathit{ADU}_{\mathit{SN}}$ is treated a measurement
+directly connected to the expected mean signal of the supernova
+$\overline{\mathit{ADU}}$.
+
+\subsubsection{Likelihood}
+
+The above describes the model for the underlying distribution.  Needed
+is the distribution for the population that enter the analysis; detection and spectroscopic
+follow-up have parameter-dependent selection efficiencies.  For the analysis sample
+imposing slightly more stringent criteria at the expense
+of losing a few captured transients may be more convenient than reconstructing
+the live-time decision making process.
+
+%The likelihood for the analysis sample is related to the underlying likelihood through
+%\begin{multline}
+%p(\mathit{ADU}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G |  \Omega_M, w, \theta_r, \alpha_{Ia}, \beta_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\beta_{\mathit{non-Ia}}, \sigma_{\mathit{non-Ia}},  Z, g, g_N, f_g)\\
+%= \frac{\epsilon(\mathit{ADU}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G) p_U(\mathit{ADU}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G | \ldots)}
+%{\sum_{T_S} \int d\mathit{ADU}\, dz_S\, d\theta_S\, d\theta_G\, \epsilon(\mathit{ADU}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G) p_U(\mathit{ADU}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G | \ldots)},
+%\end{multline} 
+%where $p_U$ is the underlying likelihood  and $\epsilon$ is the efficiency for inclusion
+%in the sample (more precisely subsample as spectroscopic
+%selection should produce different efficiencies for the {\it obs} and {\it mis} sets.)
+
+%The efficiencies for photometric and spectroscopic selection are taken to be independent.
+%The efficiency  to pass photometric selection is denoted as $\epsilon_P$.
+The acceptance criteria based on photometry has not yet defined; the following is a sketch
+of how it would be considered for a criterion of $\ge N$ photometric points
+above a signal-to-noise threshold (translating to a distinct limiting signal $ADU_0$
+for each measurement of each transient) given $M$ available measurements. 
+The fail/pass status of each of the measurements is denoted as
+$b$ of 0/1, and there are $\sum_{k=N}^M \binom{M}{k}$ 
+distinct $b$'s that allow acceptance of the light curve.
+
+\subsubsection{Likelihood for the {\it obs} Set}
+The likelihood for the {\it obs} set is
 \begin{multline}
-p(\mathit{ADU}, {{T}}_S,{{z}}_S, \theta_S, \theta_G|  \ldots) = \\
-p(\mathit{ADU} | T=T_S, z=z_s, g=\{\theta_S, \theta_G\},  \dots) P(T_S| z= z_S , g=\{\theta_S, \theta_G\}, \ldots).
-\label{obs3:eqn}
+p(\mathit{ADU}_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G |  \Omega_M, w, \theta_r, \alpha_{Ia}, \beta_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\beta_{\mathit{non-Ia}}, \sigma_{\mathit{non-Ia}},  Z, g, g_N, f_g)\\
+= \sum_i \int_L dL\, p(\mathit{ADU}_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G | b_i, L, \ldots)
+P(b_{i} |L, \ldots) P(L|\ldots) ,
 \end{multline} 
+where $L$ are the latent parameters.
+The first term is the likelihood for the data given the condition for the  $b_i$ configuration
+of threshold pass/fails  and all parameters.  The second term and
+third terms are the probabilities of achieving the configuration
+and latent parameters
+respectively.
 
-The first term is the likelihood for the light curve.  The dependence of the light curve depends
-on transient properties, cosmology, calibration, and the experiment.  For convenience. the
-construction of the likelihood is broken up into several steps, with intermediary points
-at the determination of the time and wavelength-dependent luminosity $L$,
-the flux $f$, the expected counts $\overline{\mathit{ADU}}$ of the transient and background, and
-finally the observed light curve $\mathit{ADU}$.  Figure~\ref{pgm:fig} shows how these
-parameters are related to the intrinsic parameters and to each other.
+The likelihood for one of the $b$ configurations is derived from the likelihood without the configuration condition
+\begin{equation}
+p(\mathit{ADU}_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G | b_i, L, \ldots)
+%=\frac{
+% \epsilon(\mathit{ADU}_{SN}; b_i)
+%  p(\mathit{ADU}_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G | L, \ldots)}
+%  {\sum_{T_S} \int d\mathit{ADU}_{SN}\, dz_S\, d\theta_S\, d\theta_G\, 
+% \epsilon(\mathit{ADU}_{SN}; b_i)
+%  p(\mathit{ADU}_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G | L, \ldots)}\\
+  =  \frac{ \prod_j
+ \epsilon(\mathit{ADU}_{SN,j}; b_{ij})
+  p(\mathit{ADU}_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G | L, \ldots)}
+  {\prod_j P(b_{ij}{ |L,\dots)}} ,
+\label{obsconf:eqn}
+\end{equation}
+where $j$ indexes photometric points and
+$\epsilon$ is the efficiency of acceptance of that point from the underlying distribution.
+For flux thresholds, the efficiency is
+\begin{equation}
+\epsilon(\mathit{ADU}_{SN,j}; b_{ij})= \mathcal{H}\left((-1)^{b_{ij}+1}(ADU_{SN,j}-ADU_{0,j})\right),
+\end{equation}
+where $\mathcal{H}$ is the Heaviside step function; when $b_{ij}=1$ the step in the efficiency
+is up and for $b_{ij}=0$ the step is down.
 
-The pdf of the luminosity $L$ can be expressed as follows:
+The likelihood without the configuration condition is
 \begin{multline}
-p(L|  \theta_r,\alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}}, \theta_{Ia}, \theta_{non-Ia}, g)  \\
-= \sum_T \int d\theta_{Ia}\, d\theta_{non-Ia}\, P(L, T, \theta_{Ia} \theta_{non-Ia}|\ldots) \\
-= \sum_T \int d\theta_{Ia}\, d\theta_{non-Ia}\, P(L| T, \theta_{Ia} \theta_{non-Ia} \ldots) p(T,
-\theta_{Ia}\, \theta_{non-Ia} | \ldots)
+p(\mathit{ADU}_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G | L, \ldots) \\
+= \delta(z_S - g_z) \delta(\theta_S-\theta_T) \delta(\theta_G -g) \delta(T_S-T)  \mathcal{N}
+\left(\mathit{ADU}_{SN} -\overline{\mathit{ADU}}_j(L ,\ldots), \sigma \right),
 \end{multline}
+where $\mathcal{N}$ is an $M$-dimensional Normal distribution
+and $\sigma$ is the photometric uncertainty.
 
-\subsubsection{Likelihood for the mis set data}
+The probability for failing (passing) the selection criterion for a single point is
+\begin{equation}
+P(b_{ij} | L, \ldots) = b_{ij} + (-1)^{b_{ij}}\int_{-\infty}^{ADU_0} d\mathit{ADU}_{SN,i}  \mathcal{N}\left(\mathit{ADU}_{SN} - \overline{\mathit{ADU}}_j(L ,\ldots), \sigma_T \right),
+\end{equation}
+the (complementary) cumulative distribution function for a normal distribution
+with variable
+$\mathit{ADU}_0$.
 
-%The likelihood for the model is
-%\begin{multline}
-%p(\mathit{ADU}, {{T}}_S,{{z}}_S,
-%{{\theta}}_S, \theta_G, \tau, Z | g, \theta_\mu, \theta_r, \theta_T^{Ia}, \theta_{Ti}^{Ia}, \theta_T^{non-Ia}, \theta_{Ti}^{non-Ia}, \phi) = \\
-%p(\theta_G|g)p(Z|\phi)p(\mathit{ADU}, {{T}}_S,{{z}}_S,
-%{{\theta}}_S, \tau | g, \theta_\mu, \theta_r, \theta_T^{Ia}, \theta_{Ti}^{Ia}, \theta_T^{non-Ia}, \theta_{Ti}^{non-Ia}, \phi).
-%\label{likelihood:eqn}
-%\end{multline}
+\subsubsection{Likelihood for the {\it mis} Set}
+The likelihood for the {\it mis} set does not have to account for spectroscopic data
+\begin{multline}
+p(\mathit{ADU}_{SN}, \theta_G |  \Omega_M, w, \theta_r, \alpha_{Ia}, \beta_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\beta_{\mathit{non-Ia}}, \sigma_{\mathit{non-Ia}},  Z, g, g_N, f_g)\\
+= \sum_i \int_L dL\, p(\mathit{ADU}_{SN}, \theta_G | b_i, L, \ldots)
+P(b_{i} |L, \ldots) P(L|\ldots) ,
+\end{multline} 
+\begin{equation}
+p(\mathit{ADU}_{SN}, \theta_G | b_i, L, \ldots)
+  =  \frac{ \prod_j
+ \epsilon(\mathit{ADU}_{SN,j}; b_{ij})
+  p(\mathit{ADU}_{SN}, \theta_G | L, \ldots)}
+  {\prod_j P(b_{ij}{ |L,\dots)}}.
+\label{misconf:eqn}
+\end{equation}
 
+Suppose Ravi provides for each transient a set of potential host galaxies
+each with an associated probability.  For the case of two potential hosts,
+the likelihood without the configuration condition is
+\begin{multline}
+p(\mathit{ADU}_{SN}, \theta_{G}| L, \ldots) = \\
+ \left(\pi_{host} p(z-\theta_{G1})\delta(z_N-\theta_{G2}) +
+	(1-\pi_{host}) \delta(z-\theta_{G2})\delta(z_N-\theta_{G1})
+\right) \mathcal{N}
+\left(\mathit{ADU}_{SN} -\overline{\mathit{ADU}}_j(L ,\ldots), \sigma \right);
+\end{multline}
+this is trivially generalized for only one or more than two potential hosts.
+FIX FOR PHOTO-Z.
+
+All other terms are as for the {\it obs} Set case.
+
+\subsubsection{Spectroscopic Selection}
+The efficiency for a successful spectroscopic observation $\epsilon_S$ has
+to be determined.  There are volunteers.
+
+\subsubsection{Measurement Uncertainties}
+The measurements $\mathit{ADU}$
+
+Measurement uncertainties.
+$Z$ has a prior for calibration.
+
+\section{Misc}
 The simulation of data from the model presented in

### 2015-10-16 src/hd_pgm.py

@@ -6,59 +6,59 @@ rc("font", family="serif", size=12)
 rc("text", usetex=True)
 
 
-pgm = PGM([10.5, 7.5], origin=[0., 0.2], observed_style='inner')
+pgm = PGM([9.5, 6.5], origin=[0., 0.2], observed_style='inner')
 
-pgm.add_node(Node('dispersion',r"\center{$\sigma_{Ia}$ \newline $\sigma_{non-Ia}$}", 1,7,scale=1.2,aspect=1.8))
-pgm.add_node(Node('rate',r"$\theta_r$",2,7))
-pgm.add_node(Node('theta_T',r"\center{$\alpha_{Ia}$, $\alpha_{non-Ia}$ \newline $\theta_{Ia}$, $\theta_{non-Ia}$}", 5,7,scale=1.4,aspect=1.8))
-pgm.add_node(Node('mu',r"$\Omega_M$, $w$", 6,7, scale=1.4))
-pgm.add_node(Node('Transmission',r"$Z$", 7, 7))
+pgm.add_node(Node('dispersion',r"\center{$\sigma_{Ia}$ \newline $\sigma_{non-Ia}$}", 1,6,scale=1.2,aspect=1.8))
+pgm.add_node(Node('rate',r"$\theta_r$",2,6))
+pgm.add_node(Node('theta_T',r"\center{$\alpha_{Ia}$, $\alpha_{non-Ia}$ \newline $\beta_{Ia}$, $\beta_{non-Ia}$}", 4,6,scale=1.4,aspect=1.8))
+pgm.add_node(Node('mu',r"$\Omega_M$, $w$", 5,6, scale=1.4))
+pgm.add_node(Node('Transmission',r"$Z$", 7, 6))
 
-pgm.add_node(Node('G_i',r"$g_i$", 3,6))
-pgm.add_node(Node('Gals',r"$\theta_G$", 10,6, observed=True))
+pgm.add_node(Node('G_i',r"$g_i$", 3,5))
+pgm.add_node(Node('G_Ni',r"$g_{Ni}$", 8,5))
 
-pgm.add_node(Node('theta_Ti',r"\center{$\theta_{Ia,i}$ \newline $\theta_{non-Ia,i}$}", 1,5,scale=1.5,aspect=1.2))
-pgm.add_node(Node('Type',r"$T_i$", 2, 5))
-pgm.add_node(Node('G_Ni',r"$g_{Ni}$", 4,5))
[…]

### 2015-10-16 doc/article.tex
version sent to Danny

@@
 galaxy redshifts and parameters.  The working group is striving to get spectroscopic
-redshifts of all potential hosts.
+redshifts of all potential hosts.  People who are interested in SN spectral features
+or host-galaxy correlations (Chris, Rachel, Mat) can develop these models.
 
@@
 \end{equation}
-
 Practically, the photometric extraction is handled by independent software, which calculates
@@
 directly connected to the expected mean signal of the supernova
-$\overline{\mathit{ADU}}$.
-
-\subsubsection{Likelihood}
-
-The above describes the model for the underlying distribution.  Needed
-is the distribution for the population that enter the analysis; detection and spectroscopic
-follow-up have parameter-dependent selection efficiencies.  For the analysis sample
-imposing slightly more stringent criteria at the expense
-of losing a few captured transients may be more convenient than reconstructing
-the live-time decision making process.
+$\overline{\mathit{ADU}}$
+\begin{equation}
+\mathit{ADU}_{SN} \sim \mathcal{N} (\overline{\mathit{ADU}} ,C_P).
+\end{equation}
+
+\subsubsection{Constructing the Likelihood}
+
+The analysis sample satisfy certain photometric and no successful spectroscopy
+({\it mis} Set)  and photometric
+and successful spectroscopic classification ({\it obs} Set) selection criteria, which for convenience
+probably should  be chosen to be stringent than the live-time decisions made during the survey.
+Neither the photometric nor spectroscopic selection criteria have been defined.
+Identifying good spectroscopic criteria needs to be done: the OzDES folks and Ryan are natural
+candidates.
 
@@
 %The efficiency  to pass photometric selection is denoted as $\epsilon_P$.
-The acceptance criteria based on photometry has not yet defined; the following is a sketch
-of how it would be considered for a criterion of $\ge N$ photometric points
-above a signal-to-noise threshold (translating to a distinct limiting signal $ADU_0$
-for each measurement of each transient) given $M$ available measurements. 
-The fail/pass status of each of the measurements is denoted as
-$b$ of 0/1, and there are $\sum_{k=N}^M \binom{M}{k}$ 
+
+The following is a sketch of the likelihood calculation for an example 
+photometric selection criterion, which should serve as a useful guide once the criteria are fixed.
+The criterion is for $\ge N$ photometric points
+above a signal-to-noise threshold (translating to a distinct limiting signal $ADU_{0i}$
+for measurement $i$ of a given transient) given $M$ available measurements. 
+The fail/pass status of the measurements are stored as 0/1 in an array $b$.
+There are $\sum_{k=N}^M \binom{M}{k}$ 
 distinct $b$'s that allow acceptance of the light curve.
@@
 = \delta(z_S - g_z) \delta(\theta_S-\theta_T) \delta(\theta_G -g) \delta(T_S-T)  \mathcal{N}
-\left(\mathit{ADU}_{SN} -\overline{\mathit{ADU}}_j(L ,\ldots), \sigma \right),
+\left(\mathit{ADU}_{SN} -\overline{\mathit{ADU}}_j(L ,\ldots), C_P \right),
 \end{multline}
@@
 
-The probability for failing (passing) the selection criterion for a single point is
-\begin{equation}
-P(b_{ij} | L, \ldots) = b_{ij} + (-1)^{b_{ij}}\int_{-\infty}^{ADU_0} d\mathit{ADU}_{SN,i}  \mathcal{N}\left(\mathit{ADU}_{SN} - \overline{\mathit{ADU}}_j(L ,\ldots), \sigma_T \right),
-\end{equation}
-the (complementary) cumulative distribution function for a normal distribution
-with variable
-$\mathit{ADU}_0$.
+%
+%The probability for failing (passing) the selection criterion for a single point is
+%\begin{equation}
+%P(b_{ij} | L, \ldots) = b_{ij} + (-1)^{b_{ij}}\int_{-\infty}^{ADU_0} d\mathit{ADU}_{SN,i}  \mathcal{N}\left(\mathit{ADU}_{SN} - \overline{\mathit{ADU}}_j(L ,\ldots), C_P \right),
+%\end{equation}
+%the (complementary) cumulative distribution function for a normal distribution
+%with variable
+%$\mathit{ADU}_0$, i.e.\ 2 times the error function.
+
+Assembling this together, the likelihood for the {\it obs} Set is
+\begin{multline}
+p(\mathit{ADU}_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G |  \Omega_M, w, \theta_r, \alpha_{Ia}, \beta_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\beta_{\mathit{non-Ia}}, \sigma_{\mathit{non-Ia}},  Z, g, g_N, f_g)\\
+= \sum_i \int_L dL\, 
+\prod_j
+ \epsilon(\mathit{ADU}_{SN,j}; b_{ij}) 
+\mathcal{N}\left(\mathit{ADU}_{SN} - \overline{\mathit{ADU}}_j(L ,
+g_z=z_S, \theta_T=\theta_S, g=\theta_G, T=T_S, \ldots), C_P \right)\\
+P(L|g_z=z_S, \theta_T=\theta_S, g=\theta_G, T=T_S, \ldots),
+\end{multline} 
+where the latent parameters $T$, $\theta_T$ are not integrated over.
 
 \subsubsection{Likelihood for the {\it mis} Set}
-The likelihood for the {\it mis} set does not have to account for spectroscopic data
+The likelihood for the {\it mis} set follow the same pattern as that of the
+{\it obs} set except for not having to account for spectroscopic data.
 \begin{multline}
-p(\mathit{ADU}_{SN}, \theta_G |  \Omega_M, w, \theta_r, \alpha_{Ia}, \beta_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\beta_{\mathit{non-Ia}}, \sigma_{\mathit{non-Ia}},  Z, g, g_N, f_g)\\
-= \sum_i \int_L dL\, p(\mathit{ADU}_{SN}, \theta_G | b_i, L, \ldots)
-P(b_{i} |L, \ldots) P(L|\ldots) ,
+p(\mathit{ADU}_{SN}, \theta_{G_1} |  \Omega_M, w, \theta_r, \alpha_{Ia}, \beta_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\beta_{\mathit{non-Ia}}, \sigma_{\mathit{non-Ia}},  Z, g, g_N, f_g) \\
+ = \sum_i \int_L dL\, 
+\prod_j
+ \epsilon(\mathit{ADU}_{SN,j}; b_{ij}) \sum_k 
+\pi_k\mathcal{N}\left(\mathit{ADU}_{SN} - \overline{\mathit{ADU}}_j(L ,
+g=\theta_{G_k}, \ldots), C_P \right)
+P(L|g=\theta_{G_k}, \ldots), 
 \end{multline} 
-\begin{equation}
-p(\mathit{ADU}_{SN}, \theta_G | b_i, L, \ldots)
-  =  \frac{ \prod_j
- \epsilon(\mathit{ADU}_{SN,j}; b_{ij})
-  p(\mathit{ADU}_{SN}, \theta_G | L, \ldots)}
-  {\prod_j P(b_{ij}{ |L,\dots)}}.
-\label{misconf:eqn}
-\end{equation}
-
-Suppose Ravi provides for each transient a set of potential host galaxies
-each with an associated probability.  For the case of two potential hosts,
-the likelihood without the configuration condition is
-\begin{multline}
-p(\mathit{ADU}_{SN}, \theta_{G}| L, \ldots) = \\
- \left(\pi_{host} p(z-\theta_{G1})\delta(z_N-\theta_{G2}) +
-	(1-\pi_{host}) \delta(z-\theta_{G2})\delta(z_N-\theta_{G1})
-\right) \mathcal{N}
-\left(\mathit{ADU}_{SN} -\overline{\mathit{ADU}}_j(L ,\ldots), \sigma \right);
-\end{multline}
-this is trivially generalized for only one or more than two potential hosts.
-FIX FOR PHOTO-Z.
-
-All other terms are as for the {\it obs} Set case.
-
-\subsubsection{Spectroscopic Selection}
-The efficiency for a successful spectroscopic observation $\epsilon_S$ has
-to be determined.  There are volunteers.
-
-\subsubsection{Measurement Uncertainties}
-The measurements $\mathit{ADU}$
-
-Measurement uncertainties.
-$Z$ has a prior for calibration.
+where $\pi_k$ is the probability that the $k$'th galaxy is the host, provided by Ravi.
+
+%\begin{multline}
+%p(\mathit{ADU}_{SN}, \theta_G |  \Omega_M, w, \theta_r, \alpha_{Ia}, \beta_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\beta_{\mathit{non-Ia}}, \sigma_{\mathit{non-Ia}},  Z, g, g_N, f_g)\\
+%= \sum_i \int_L dL\, p(\mathit{ADU}_{SN}, \theta_G | b_i, L, \ldots)
+%P(b_{i} |L, \ldots) P(L|\ldots) ,
+%\end{multline} 
+%\begin{equation}
+%p(\mathit{ADU}_{SN}, \theta_G | b_i, L, \ldots)
+%  =  \frac{ \prod_j
+% \epsilon(\mathit{ADU}_{SN,j}; b_{ij})
+%  p(\mathit{ADU}_{SN}, \theta_G | L, \ldots)}
+%  {\prod_j P(b_{ij}{ |L,\dots)}}.
+%\label{misconf:eqn}
+%\end{equation}
+
+\section{Tasks}
+\begin{table}[htdp]
+\caption{default}
+\begin{center}
+\begin{tabular}{|c|c|}
+\hline
+Task/Deliverable & Responsible \\ \hline
+Model Design & \\
+Sampler &\\
+Photometric Selection &\\
+Spectroscopy Selection &\\
+Host Galaxy Association &\\
+Host Galaxy Parameters &\\
+SN~Ia Models Selection &\\
+Non-Ia Models Selection &\\
+SN light curves (ADU) &\\
+Photometric Zeropoints &\\
+\hline
+\end{tabular}
+\end{center}
+\label{Tasks and Responsible Parties}
+\end{table}%
 

### 2015-10-18 doc/article.tex
fix errors in likelihood

@@
 \documentclass[preprint,3p]{elsarticle}
+%\documentclass[preprint]{aastex}
 \usepackage{aas_macros}
@@
 
-\subsection{Likelihood}
-
-\subsubsection{Measurements}
+\subsection{Measurements}
+\label{measurements:sec}
 In the following discussion,
@@
 to provide prefect determinations of transient type and parameters, and
-galaxy redshifts and parameters.  The working group is striving to get spectroscopic
+galaxy redshifts and parameters. 
+\begin{align}
+p(T_S|T) &= \delta(T_S-T),\\
+p(\theta_S|\theta_T) &= \delta(\theta_S|\theta_T),\\
+p(\theta_G|g) &= \delta(\theta_G-g)\\
+p(z_S|g_z) &= \delta(z_S-g_z)\\.
+\label{specz:eqn}
+\end{align}
+The working group is striving to get spectroscopic
 redshifts of all potential hosts.  People who are interested in SN spectral features
@@
 
-\subsubsection{Constructing the Likelihood}
+\subsection{Constructing the Likelihood}
 
@@
 There are $\sum_{k=N}^M \binom{M}{k}$ 
-distinct $b$'s that allow acceptance of the light curve.
+distinct $b$'s that allow acceptance of the light curve.  In the notation $b_{ijk}$, $i$ indexes
+the configuration, $j$ the transient, and $k$ the photometric point of transient $j$.
 
@@
 p(\mathit{ADU}_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G |  \Omega_M, w, \theta_r, \alpha_{Ia}, \beta_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\beta_{\mathit{non-Ia}}, \sigma_{\mathit{non-Ia}},  Z, g, g_N, f_g)\\
-= \sum_i \int_L dL\, p(\mathit{ADU}_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G | b_i, L, \ldots)
-P(b_{i} |L, \ldots) P(L|\ldots) ,
+= \sum_i \int_L dL\, p(\mathit{ADU}_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G , b_i|  L, \ldots)
+ P(L|\ldots) \\
+ \propto \sum_i  \epsilon(\mathit{ADU}_{SN}; b_{i}) \int_L dL\, p(\mathit{ADU}_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G|  L, \ldots)P(L|\ldots).
 \end{multline} 
-where $L$ are the latent parameters.
-The first term is the likelihood for the data given the condition for the  $b_i$ configuration
-of threshold pass/fails  and all parameters.  The second term and
-third terms are the probabilities of achieving the configuration
-and latent parameters
-respectively.
-
-The likelihood for one of the $b$ configurations is derived from the likelihood without the configuration condition
-\begin{equation}
-p(\mathit{ADU}_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G | b_i, L, \ldots)
-%=\frac{
-% \epsilon(\mathit{ADU}_{SN}; b_i)
-%  p(\mathit{ADU}_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G | L, \ldots)}
-%  {\sum_{T_S} \int d\mathit{ADU}_{SN}\, dz_S\, d\theta_S\, d\theta_G\, 
-% \epsilon(\mathit{ADU}_{SN}; b_i)
-%  p(\mathit{ADU}_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G | L, \ldots)}\\
-  =  \frac{ \prod_j
- \epsilon(\mathit{ADU}_{SN,j}; b_{ij})
-  p(\mathit{ADU}_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G | L, \ldots)}
-  {\prod_j P(b_{ij}{ |L,\dots)}} ,
-\label{obsconf:eqn}
-\end{equation}
-where $j$ indexes photometric points and
-$\epsilon$ is the efficiency of acceptance of that point from the underlying distribution.
-For flux thresholds, the efficiency is
-\begin{equation}
-\epsilon(\mathit{ADU}_{SN,j}; b_{ij})= \mathcal{H}\left((-1)^{b_{ij}+1}(ADU_{SN,j}-ADU_{0,j})\right),
-\end{equation}
-where $\mathcal{H}$ is the Heaviside step function; when $b_{ij}=1$ the step in the efficiency
-is up and for $b_{ij}=0$ the step is down.
-
-The likelihood without the configuration condition is
-\begin{multline}
-p(\mathit{ADU}_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G | L, \ldots) \\
-= \delta(z_S - g_z) \delta(\theta_S-\theta_T) \delta(\theta_G -g) \delta(T_S-T)  \mathcal{N}
-\left(\mathit{ADU}_{SN} -\overline{\mathit{ADU}}_j(L ,\ldots), C_P \right),
-\end{multline}
-where $\mathcal{N}$ is an $M$-dimensional Normal distribution
-and $\sigma$ is the photometric uncertainty.
+It is proportional to the truncated likelihood of the underlying sample, where the truncation
+is achieved through $\epsilon(\mathit{ADU}_{SN}; b_{i})$, the efficiency that a light curve is 
+selected in for a given configuration.  For the limiting flux criteria
+\begin{equation}
+\epsilon(\mathit{ADU}_{SN}; b_{i})= \prod_{jk}\mathcal{H}\left((-1)^{b_{ijk}+1}(ADU_{SN,jk}-ADU_{0,jk})\right),
+\end{equation}
+where $\mathcal{H}$ is the Heaviside step function; when $b_{ijk}=1$ the step in the efficiency
+is up and for $b_{ijk}=0$ the step is down.
+
+%The likelihood without the configuration condition for our measurements is
+%\begin{multline}
+%p(\mathit{ADU}_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G | L, \ldots) \\
+%= \delta(z_S - g_z) \delta(\theta_S-\theta_T) \delta(\theta_G -g) \delta(T_S-T)  \mathcal{N}
+%\left(\mathit{ADU}_{SN} -\overline{\mathit{ADU}}_j(L ,\ldots), C_P \right).
+%\end{multline}. 
+%
 
@@
 
-Assembling this together, the likelihood for the {\it obs} Set is
+For measurements described in \S\ref{measurements:sec}, the likelihood for the {\it obs} Set is
 \begin{multline}
 p(\mathit{ADU}_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G |  \Omega_M, w, \theta_r, \alpha_{Ia}, \beta_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\beta_{\mathit{non-Ia}}, \sigma_{\mathit{non-Ia}},  Z, g, g_N, f_g)\\
-= \sum_i \int_L dL\, 
-\prod_j
- \epsilon(\mathit{ADU}_{SN,j}; b_{ij}) 
+\propto \sum_i  \epsilon(\mathit{ADU}_{SN}; b_{i})  \int_L dL\, 
 \mathcal{N}\left(\mathit{ADU}_{SN} - \overline{\mathit{ADU}}_j(L ,
@@
 where the latent parameters $T$, $\theta_T$ are not integrated over.
+The normalization factor is parameter-dependent and is set by the condition
+\begin{equation}
+\sum_{T_S} \int d\mathit{ADU}_{SN}\,d{{z}}_S\,d\theta_{S}\,d\theta_G\,p(\mathit{ADU}_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G |  \ldots)=1.
+\end{equation}
 
@@
 p(\mathit{ADU}_{SN}, \theta_{G_1} |  \Omega_M, w, \theta_r, \alpha_{Ia}, \beta_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\beta_{\mathit{non-Ia}}, \sigma_{\mathit{non-Ia}},  Z, g, g_N, f_g) \\
- = \sum_i \int_L dL\, 
-\prod_j
- \epsilon(\mathit{ADU}_{SN,j}; b_{ij}) \sum_k 
+ \propto \sum_i  \epsilon(\mathit{ADU}_{SN}; b_{i}) 
+\int_L dL\, 
+\sum_k 
 \pi_k\mathcal{N}\left(\mathit{ADU}_{SN} - \overline{\mathit{ADU}}_j(L ,

### 2015-10-18 doc/article.tex
more fixes

@@
 diagram  (e.g.\ Malmquist bias) so are accounted for explicitly.
+
+\section{DES SN Survey Model}
+\label{snIamodel:sec}
+\subsection{Model}
+This Section presents a candidate model
+for supernova surveys that has the fidelity needed for the photometric
+supernova analysis of the Dark Energy Survey and the Large Synoptic Survey Telescope.
+%SNe~Ia are not perfect standard candles but rather are calibrated candles whose
+%peak brightnesses are a
+%function of their internal properties discerned from their colors and light-curve evolution.
+%Measurement uncertainty, particularly from photometric flux
+%calibration and galaxy photometric redshifts, can play an important role in the statistical
+%reach of experiments. 
+The notation for the likelihood presents the data and fundamental model parameters
+\begin{equation}
+p(n, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G |  \Omega_M, w, r, \alpha_{Ia}, \beta_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\beta_{\mathit{non-Ia}}, \sigma_{\mathit{non-Ia}},  \sigma_\beta, Z, g, g_N, f_g),
+\label{likelihood2:eqn}
+\end{equation}
+whose relations are sketched in the probabilistic graphical model in Figure~\ref{pgm:fig}.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=6.5in]{/Users/akim/project/abc/results/hdpgm.pdf} 
+   \caption{Probabilistic Graphical Model for the SN~Ia analysis.  
+   The forward modeling
+   flow goes from left to right, starting with the description of the universe, observatory,
+   and data.    A transient has host galaxy $g_i$, which determines its redshift $z_i$
+   and galaxy parameters $\theta_{gi}$.
+   A model with parameters $\theta_\mu$ fix the distance modulus $\mu_i$.
+   The transient type $T$ depends on the host-galaxy parameters  $\theta_{gi}$
+   and rates $r$.   The transient
+   parameters $\theta_T^X$, $\theta_{Ti}^X$ (and perhaps the host galaxy) determine the luminosity $L$.       The 
+   incoming photon flux $n$, $n_g$  are then fixed
+   with redshift and distance modulus.
+   The instrumental transmission function $\phi$ is calibrated with data ${Z}$ andflux
+   gives the expected
+   counts $\overline{f}$, $\overline{f}_g$. 
+   The transient has realized light curves ($n$) and passes selection criteria
+   through $\tau_i$ to be included in the sample.  Some transients have spectral data
+   ${X}_S$.  The properties of the galaxy identified as the host galaxy is $\theta_G$. 
+   \label{pgm:fig}}
+\end{figure}
+
+The measurements are
+\begin{itemize}
+\item $n$: the measured counts for each photometric observation;
+\item ${{T}}_S$, ${{z}}_S$, $\theta_S$: the spectroscopic type, redshift, and transient parameters available for a subset of transients;
+\item $\theta_{G1}$, $\theta_{G2}$: the spectroscopic redshifts of the galaxies identified
+as host and neighbor from imaging.
+\end{itemize}
+The model parameters are
+\begin{itemize}
+\item $\Omega_M$, $w$: the mass density and dark-energy equation of state parameters of a flat,
+constant-$w$ dark-energy cosmology;
+\item $r_1$, $r_2$:  the parameters
+that describe the redshift-dependent relative fraction of SNe~Ia and non-Ia's;
+\item $\alpha_{Ia}$, $\sigma_{Ia}$, $\alpha_{\mathit{non-Ia}}$, $\sigma_{\mathit{non-Ia}}$:
+the luminosity (times $4\pi$) and intrinsic dispersion for SNe~Ia and non-Ia at peak brightness;
+\item $\beta_{Ia}$, $\beta_{non-Ia}$: the parameters for the internal diversity within SNe~Ia and
+non-Ia's respectively, e.g.\ SALT2's  $\alpha$ and $\beta$;
+\item $\sigma_\beta$: parameters that describe the distribution of intrinsic supernova
+parameters of SNe~Ia and non-Ia;
+\item $Z$: the parameters that describe the transmission functions, i.e.\ photometric calibration;
+\item $g$, $g_N$: the parameters that describe the candidate host and neighbor galaxies,
+to be more expansive than the previous $z$ parameter;
+\item $f_g$: the surface brightness of the background light at the location of the transient
+needed for to extract the photometry of the point-source transient.
+\end{itemize}
+Not listed explicitly in Eqn.~\ref{likelihood:eqn} but shown in Figure~\ref{toypgm:fig} are latent model parameters for each transient:
+\begin{itemize}
+%\item $z$: the cosmological redshifts of the host and neighboring galaxies;
+\item $T$: the class of the objects, SN~Ia or non-Ia;
+\item $\theta_{Ia}$, $\theta_{non-Ia}$: the transient parameters that describe individual
+transients, e.g.\ SALT2's $x_1$, $c$;
+\item $L$: the luminosity of the transient.
+\end{itemize}
+There are  fixed parameters
+\begin{itemize}
+\item $\mu$: the distance modulus given the cosmological parameters and the redshift;
+\item{$f$}: the flux of the transient given the luminosity, distance modulus, and
+redshift;
+\item{$\overline{n}_X$}: the expected counts of the transient and background light given
+the flux and transmission.
+\end{itemize}
+
+The relationships between the parameters for the underlying population are now described.  What follows is an initial proposal
+based on current supernova analyses, but many different models need to be
+considered as the understanding of transients improve
+and for probing systematics by comparing the
+performance of competing models.
+
+\begin{itemize}
+\item Intrinsic transient parameters are dependent on their distributions and the host galaxy.
+The SNe~Ia parameters are drawn as
+\begin{equation}
+\theta_{Ia} | \sigma_\beta, g \sim \mathcal{N}(0, \sigma_{\beta,Ia}),
+\end{equation}
+where $\theta_{Ia} =\{x_1, c\}$ are the SALT2 light-curve shape and color parameters.
+A more complex model can be based on non-Normal distributions
+and/or including SN properties directly tied to characteristics (e.g.\ mass, star formation
+rate) of the host galaxy.
+
+{\bf The non-Ia parameters, their underlying distributions, and SED's need to chosen.}
+The prime candidate
+is their description used in PSNID.
+
+%\begin{equation}
+%\theta_{non-Ia} | \sigma_\beta, g  \sim \mathcal{N}(0, \sigma_{\beta, non-Ia}),
+%\end{equation}
+%where the parameter is the realization of an intrinsic magnitude dispersion.
+%A more complex model can include multiple non-Ia populations each with its own
+%intrinsic parameters.
+\item Spectroscopically observed transient parameters depend on the intrinsic transient
+parameters and type.  $\theta_{Si}$ may be ignored in a zero'th order analysis that
+does not relate spectral features with SN~Ia absolute magnitudes.   If spectral
+features are considered, the simple model
+\begin{equation}
+\theta_{Si} (\theta_{Ia}, \theta_{non-Ia}, T)=\theta_T
+\end{equation}
+assumes an unambiguous mapping between supernova parameters and spectral signal.
+{\bf We need to decide what SN spectral parameters, if any, we will consider in our analysis.}
+\item The type is drawn from the host-dependent relative rate between SNe~Ia and non-Ia's 
+\begin{equation}
+T | r, g \sim \rm{Bernoulli}(\pi(g,r)),
+\end{equation}
+where $\pi$ is a model for the relative rates of the different types as a
+function of galaxy parameters and redshift.  {\bf A reasonable choice for $\pi$ needs to be
+selected, any volunteers?}
+\item Supernova type is assumed to be unambiguously encoded in the
+spectrum:
+\begin{equation}
+T_S (T)  = T.
+\end{equation}
+\item The observed redshift is taken to be the host galaxy redshift
+\begin{equation}
+z_S (g_z) =g_z
+\end{equation}
+where $g_z$ is the element in $g$ that corresponds to redshift.
+Added sophistication includes redshift
+measurement uncertainty and random peculiar velocities. The study of coherent
+flow requires added model complexity.
+\item The underlying SED of transients are modeled.  For SNe~Ia the SALT2 model
+is an option, although new models that separate dust and intrinsic color or
+identify new SN~Ia parameters are expected in the near future.  Absolute magnitudes
+that depend on host-galaxy properties need to be considered. 
+For SNe~Ia $T=1$
+\begin{equation}
+L(t,\lambda) |  \alpha_{Ia}, \beta_{Ia}, \sigma_{Ia},  \theta_{Ia}, g, x_1, c \sim L_{SALT2}(t-t_0; \alpha_{Ia}, x_1, c) \gamma(g, \beta) \mathcal{N}(0,\sigma_{Ia}),
+\end{equation}
+where the first  term is the SALT2 light-curve and absolute magnitude
+model with a realized error snake,
+and $\gamma(g, \beta)$ a step function with free parameters in $\beta$ that
+describe the step size.
+
+{\bf The non-Ia model needs to be identified.}
+\item The theoretical distance modulus
+\begin{equation}
+\mu(g_z; \Omega_M, w) = \mu_{wCDM}(g_z; \Omega_M, w)
+\end{equation}
+is the predicted distance modulus of a flat dark energy cosmology.
+\item The flux incident on Earth is the redshifted and time-dilated SED scaled
+by the distance modulus.
+\begin{equation}
+f(t,\lambda; L) = 10^{-\mu/2.5} L\left(t/(1+g_z),\lambda/(1+g_z)\right)
+\end{equation}
+\item The expected light curve in counts depends on the flux and throughput of the
+optical chain.  A first model encapsulates flux calibration through a zeropoint
+\begin{equation}
+\overline{n}(f, Z) = 10^{Z/2.5} \int  f(\lambda) T_0(\lambda)d\lambda,
+\end{equation}
+where $T_0$ is a fiducial transmission function for the appropriate filter.  A more sophisticated
+analysis can have a transmission function specific to each observation.
+\item The measured surface brightness of the host galaxy depends on the underlying
+surface brightness convolved with the point spread function and integrated
+over the transmission
+\begin{equation}
+\overline{n}_g =    \int (f_g(\lambda, RA, Dec) \otimes PSF) T(\lambda;Z)d\lambda.
+\end{equation}
+\item The measurement $n$ is the superposition of transient and background
+light $\overline{n} + \overline{n}_g$.
+\end{itemize}
+
+\subsection{Measurements}
+\label{measurements:sec}
+In the following discussion,
+spectroscopic and galaxy measurements are assumed
+to provide prefect determinations of transient type and parameters, and
+galaxy redshifts and parameters. 
+\begin{align}
+p(T_S|T) &= \delta(T_S-T),\\
+p(\theta_S|\theta_T) &= \delta(\theta_S-\theta_T),\\
+p(\theta_G|g) &= \delta(\theta_G-g),\\
+p(z_S|g_z) &= \delta(z_S-g_z)
+\label{specz:eqn}
+\end{align}
+The working group is striving to get spectroscopic
+redshifts of all potential hosts.  People who are interested in SN spectral features
+or host-galaxy correlations (Chris, Rachel, Mat) can develop these models.
+
+The measured counts depend on the expected counts and measurement uncertainty
+$C_P$ as a Poisson (or considering the high sky background Normal) distribution
+\begin{equation}
+n \sim \mathcal{N} (\overline{n}+\overline{n}_g ,C_P).
+\label{ADU:eqn}
+\end{equation}
+Practically, the photometric extraction is handled by independent software, which calculates
+the pdf of $n_{\mathit{SN}}$, the realized contribution of supernova light,
+replacing this and the previous two bullet points.  Dillon is providing this.
+For the rest of the discussion, $n_{\mathit{SN}}$ is treated a measurement
+directly connected to the expected mean signal of the supernova
+$\overline{n}$
+\begin{equation}
+n_{SN} \sim \mathcal{N} (\overline{n} ,C_P).
+\end{equation}
+
+Prior on $Z$.
+\subsection{Constructing the Likelihood}
+
+The analysis sample satisfy certain photometric and no successful spectroscopy
+({\it mis} Set)  and photometric
+and successful spectroscopic classification ({\it obs} Set) selection criteria, which for convenience
+probably should  be chosen to be stringent than the live-time decisions made during the survey.
+Neither the photometric nor spectroscopic selection criteria have been defined.
+Identifying good spectroscopic criteria needs to be done: the OzDES folks and Ryan are natural
+candidates.
+
+%The likelihood for the analysis sample is related to the underlying likelihood through
+%\begin{multline}
+%p(n, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G |  \Omega_M, w, \theta_r, \alpha_{Ia}, \beta_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\beta_{\mathit{non-Ia}}, \sigma_{\mathit{non-Ia}},  Z, g, g_N, f_g)\\
+%= \frac{\epsilon(n, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G) p_U(n, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G | \ldots)}
+%{\sum_{T_S} \int dn\, dz_S\, d\theta_S\, d\theta_G\, \epsilon(n, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G) p_U(n, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G | \ldots)},
+%\end{multline} 
+%where $p_U$ is the underlying likelihood  and $\epsilon$ is the efficiency for inclusion
+%in the sample (more precisely subsample as spectroscopic
+%selection should produce different efficiencies for the {\it obs} and {\it mis} sets.)
+
+%The efficiencies for photometric and spectroscopic selection are taken to be independent.
+%The efficiency  to pass photometric selection is denoted as $\epsilon_P$.
+
+The following is a sketch of the likelihood calculation for an example 
+photometric selection criterion, which should serve as a useful guide once the criteria are fixed.
+The criterion is for $\ge N$ photometric points
+above a signal-to-noise threshold (translating to a distinct limiting signal $n_{0i}$
+for measurement $i$ of a given transient) given $M$ available measurements. 
+The fail/pass status of the measurements are stored as 0/1 in an array $b$.
+There are $\sum_{k=N}^M \binom{M}{k}$ 
+distinct $b$'s that allow acceptance of the light curve.  In the notation $b_{ijk}$, $i$ indexes
+the configuration, $j$ the transient, and $k$ the photometric point of transient $j$.
+
+The transients are divided into
+the following subsets:
+{\it obs} are transients observed spectroscopically while active, from which $T_S=1$ are those typed
+as SN~Ia and $T_S=0$ as non-Ia.  {\it mis} transients are not observed
+spectroscopically when active.  The data from each subset have different forms for their likelihood.
+The  {\it obs} sample constrains and specifies the parameter distributions of the 
+parameters missing from the {\it mis} sample; both samples
+are assumed to be drawn from the same underlying distribution.
+
+\subsubsection{Likelihood for the {\it obs} Set}
+The likelihood for the {\it obs} set is
+\begin{multline}
+p(n_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G |  \Omega_M, w, r, \alpha_{Ia}, \beta_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\beta_{\mathit{non-Ia}}, \sigma_{\mathit{non-Ia}},  \sigma_\beta, Z, g, g_N, f_g)\\
+= \sum_i \int_L dL\, p(n_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G , b_i|  L, \ldots)
+ P(L|\ldots) \\
+ \propto \sum_i  \epsilon(n_{SN}; b_{i}) \int_L dL\, p(n_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G|  L, \ldots)P(L|\ldots).
+\end{multline} 
+It is proportional to the truncated likelihood of the underlying sample, where the truncation
+is achieved through $\epsilon(n_{SN}; b_{i})$, the efficiency that a light curve is 
+selected in for a given configuration.  For the limiting flux criteria
+\begin{equation}
+\epsilon(n_{SN}; b_{i})= \prod_{jk}\mathcal{H}\left((-1)^{b_{ijk}+1}(n_{SN,jk}-n_{0,jk})\right),
+\end{equation}
+where $\mathcal{H}$ is the Heaviside step function; when $b_{ijk}=1$ the step in the efficiency
+is up and for $b_{ijk}=0$ the step is down.
+
+%The likelihood without the configuration condition for our measurements is
+%\begin{multline}
+%p(n_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G | L, \ldots) \\
+%= \delta(z_S - g_z) \delta(\theta_S-\theta_T) \delta(\theta_G -g) \delta(T_S-T)  \mathcal{N}
+%\left(n_{SN} -\overline{n}_j(L ,\ldots), C_P \right).
+%\end{multline}. 
+%
+
+%
+%The probability for failing (passing) the selection criterion for a single point is
+%\begin{equation}
+%P(b_{ij} | L, \ldots) = b_{ij} + (-1)^{b_{ij}}\int_{-\infty}^{ADU_0} dn_{SN,i}  \mathcal{N}\left(n_{SN} - \overline{n}_j(L ,\ldots), C_P \right),
+%\end{equation}
+%the (complementary) cumulative distribution function for a normal distribution
+%with variable
+%$n_0$, i.e.\ 2 times the error function.
+
+For measurements described in \S\ref{measurements:sec}, the likelihood for the {\it obs} Set is
+\begin{multline}
+p(n_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G |  \Omega_M, w, r, \alpha_{Ia}, \beta_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\beta_{\mathit{non-Ia}}, \sigma_{\mathit{non-Ia}},  \sigma_\beta, Z, g, g_N, f_g)\\
+\propto \sum_i  \epsilon(n_{SN}; b_{i})  \int_L dL\, 
+\mathcal{N}\left(n_{SN} - \overline{n}_j(L ,
+g_z=z_S, \theta_T=\theta_S, g=\theta_G, T=T_S, \ldots), C_P \right)\\
+P(L|g_z=z_S, \theta_T=\theta_S, g=\theta_G, T=T_S, \ldots),
+\end{multline} 
+where the latent parameters $T$, $\theta_T$ are not integrated over.
+The normalization factor is parameter-dependent and is set by the condition
+\begin{equation}
+\sum_{T_S} \int dn_{SN}\,d{{z}}_S\,d\theta_{S}\,d\theta_G\,p(n_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G |  \ldots)=1.
+\end{equation}
+
+\subsubsection{Likelihood for the {\it mis} Set}
+The likelihood for the {\it mis} set follow the same pattern as that of the
+{\it obs} set except for not having to account for spectroscopic data.
+\begin{multline}
+p(n_{SN}, \theta_{G_1} |  \Omega_M, w, r, \alpha_{Ia}, \beta_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\beta_{\mathit{non-Ia}}, \sigma_{\mathit{non-Ia}},  \sigma_\beta, Z, g, g_N, f_g) \\
+ \propto \sum_i  \epsilon(n_{SN}; b_{i}) 
+\int_L dL\, 
+\sum_k 
+\pi_k\mathcal{N}\left(n_{SN} - \overline{n}_j(L ,
+g=\theta_{G_k}, \ldots), C_P \right)
+P(L|g=\theta_{G_k}, \ldots), 
+\end{multline} 
+where $\pi_k$ is the probability that the $k$'th galaxy is the host, provided by Ravi.
+
+%\begin{multline}
+%p(n_{SN}, \theta_G |  \Omega_M, w, \theta_r, \alpha_{Ia}, \beta_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\beta_{\mathit{non-Ia}}, \sigma_{\mathit{non-Ia}},  Z, g, g_N, f_g)\\
+%= \sum_i \int_L dL\, p(n_{SN}, \theta_G | b_i, L, \ldots)
+%P(b_{i} |L, \ldots) P(L|\ldots) ,
+%\end{multline} 
+%\begin{equation}
+%p(n_{SN}, \theta_G | b_i, L, \ldots)
+%  =  \frac{ \prod_j
+% \epsilon(n_{SN,j}; b_{ij})
+%  p(n_{SN}, \theta_G | L, \ldots)}
+%  {\prod_j P(b_{ij}{ |L,\dots)}}.
+%\label{misconf:eqn}
+%\end{equation}
+
+\section{Tasks}
+\begin{table}[htdp]
+\caption{default}
+\begin{center}
+\begin{tabular}{|c|c|}
+\hline
+Task/Deliverable & Responsible \\ \hline
+Model Design & \\
+Sampler &\\
+Photometric Selection &\\
+Spectroscopy Selection &\\
+Host Galaxy Association &\\
+Host Galaxy Parameters &\\
+SN~Ia Models Selection &\\
+Non-Ia Models Selection &\\
+SN light curves ($n$) &\\
+Photometric Zeropoints &\\
+\hline
+\end{tabular}
+\end{center}
+\label{Tasks and Responsible Parties}
+\end{table}%
+
+\section{Misc}
+The simulation of data from the model presented in
+and their analysis is implemented in Python and are available
+on GitHub\footnote{{git@github.com:AlexGKim/abc.git}}.
 
@@
 
-The transients are divided into
-the following subsets:
-{\it obs} are transients observed spectroscopically while active, from which $T_S=1$ are those typed
-as SN~Ia and $T_S=0$ as non-Ia.  {\it mis} transients are not observed
-spectroscopically when active.  The data from each subset have different forms for their likelihood.
-The  {\it obs} sample constrains and specifies the parameter distributions of the 
-parameters missing from the {\it mis} sample; both samples
-are assumed to be drawn from the same underlying distribution.
-
 \subsubsection{Likelihood for the {\it obs} set data}
@@
 
-\section{DES SN Survey Model}
-\label{snIamodel:sec}
-\subsection{Model}
-SNe~Ia are not perfect standard candles but rather are calibrated candles whose
-peak brightnesses are a
-function of their internal properties discerned from their colors and light-curve evolution.
-Measurement uncertainty, particularly from photometric flux
-calibration and galaxy photometric redshifts, can play an important role in the statistical
-reach of experiments.  This Section contains a model that expands upon the one
-presented in \S\ref{snIamodel:sec} to have the fidelity needed for the photometric
-supernova analysis of the Dark Energy Survey and the Large Synoptic Survey Telescope.
-
-The notation for the likelihood presents the data and fundamental model parameters
-\begin{equation}
-p(\mathit{ADU}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G |  \Omega_M, w, \theta_r, \alpha_{Ia}, \beta_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\beta_{\mathit{non-Ia}}, \sigma_{\mathit{non-Ia}},  Z, g, g_N, f_g),
-\label{likelihood2:eqn}
-\end{equation}
-whose relations are sketched in the probabilistic graphical model in Figure~\ref{pgm:fig}.
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=6.5in]{/Users/akim/project/abc/results/hdpgm.pdf} 
-   \caption{Probabilistic Graphical Model for the SN~Ia analysis.  
-   The forward modeling
-   flow goes from left to right, starting with the description of the universe, observatory,
-   and data.    A transient has host galaxy $g_i$, which determines its redshift $z_i$
-   and galaxy parameters $\theta_{gi}$.
-   A model with parameters $\theta_\mu$ fix the distance modulus $\mu_i$.
-   The transient type $T$ depends on the host-galaxy parameters  $\theta_{gi}$
-   and rates $\theta_r$.   The transient
-   parameters $\theta_T^X$, $\theta_{Ti}^X$ (and perhaps the host galaxy) determine the luminosity $L$.       The 
-   incoming photon flux $n$, $n_g$  are then fixed
-   with redshift and distance modulus.
-   The instrumental transmission function $\phi$ is calibrated with data ${Z}$ andflux
-   gives the expected
-   counts $\overline{f}$, $\overline{f}_g$. 
-   The transient has realized light curves (${ADU}$) and passes selection criteria
-   through $\tau_i$ to be included in the sample.  Some transients have spectral data
-   ${X}_S$.  The properties of the galaxy identified as the host galaxy is $\theta_G$. 
-   \label{pgm:fig}}
-\end{figure}
-
-The new measurement that differs from  \S\ref{model:sec} is
-\begin{itemize}
-\item $\mathit{ADU}$: the measured counts for each photometric observation.
-This takes
-the place of flux as calibration is now considered.
-\end{itemize}
-The new model parameters are
-\begin{itemize}
-\item $Z$: the parameters that describe the transmission functions, i.e.\ photometric calibration.
-\item $\beta_{Ia}$, $\beta_{non-Ia}$: the parameters for the internal diversity within SNe~Ia and
-non-Ia's respectively, e.g.\ SALT2's  $\alpha$ and $\beta$;
-\item $f_g$: the surface brightness of the background light at the location of the transient
-needed for to extract the photometry of the point-source transient.
-\end{itemize}
-New latent model parameters for each transient:
-\begin{itemize}
-\item $\theta_{Ia}$, $\theta_{non-Ia}$: the transient parameters that describe individual
-transients, e.g.\ SALT2's $x_1$, $c$;
-\item $g$: the parameters that describe the candidate host and neighbor galaxies,
-to be more expansive than the previous $z$ parameter.
-\end{itemize}
-The new fixed parameters are
-\begin{itemize}
-\item{$f$}: the flux of the transient;
-\item{$\overline{\mathit{ADU}}_X$}: the expected counts of the transient and background light.
-\end{itemize}
-
-The relationships between the parameters for the underlying population are now described.  What follows is an initial proposal
-based on current supernova analyses, but many different models need to be
-considered as the understanding of transients improve
-and for probing systematics by comparing the
-performance of competing models.
-
-\begin{itemize}
-\item Intrinsic transient parameters are dependent on their distributions and the host galaxy.
-The SNe~Ia parameters are drawn as
-\begin{equation}
-\theta_{Ia} | \sigma_{Ia}, g \sim \mathcal{N}(0, \sigma_{Ia}),
-\end{equation}
-where $\theta_{Ia} =\{x_1, c, \delta_M\}$, the SALT2 light-curve shape and color parameters.
-A more complex model can be based on non-Normal distributions
-and/or including SN properties directly tied to characteristics (e.g.\ mass, star formation
-rate) of the host galaxy.
-
-The non-Ia parameters are drawn as
-\begin{equation}
-\theta_{non-Ia} | \sigma_{non-Ia}, g  \sim \mathcal{N}(0, \sigma_{non-Ia}),
-\end{equation}
-where the parameter is the realization of an intrinsic magnitude dispersion.
-A more complex model can include multiple non-Ia populations each with its own
-intrinsic parameters.
-\item Spectroscopically observed transient parameters depend on the intrinsic transient
-parameters and type.  $\theta_{Si}$ may be ignored in a zero'th order analysis that
-does not relate spectral features with SN~Ia absolute magnitudes.   If spectral
-features are considered, the simple model
-\begin{equation}
-\theta_{Si} | \theta_{Ia}, \theta_{non-Ia}, T = \delta(\theta_{Si}-\theta_T)
-\end{equation}
-assumes an unambiguous mapping between supernova parameters and spectral signal.
-\item The type is drawn from the host-dependent relative rate between SNe~Ia and non-Ia's 
-\begin{equation}
-T | \theta_r, g \sim \rm{Bernoulli}(\pi(g,\theta_r)),
-\end{equation}
-where $\pi$ is a model for the relative rates of the different types as a
-function of galaxy parameters and redshift.  A reasonable choice for $\pi$ needs to be
-selected, any volunteers?
-\item Supernova type is assumed to be unambiguously encoded in the
-spectrum:
-\begin{equation}
-T_S | T  = \delta(T_S - T).
-\end{equation}
-\item The observed redshift is taken to be the host galaxy redshift
-\begin{equation}
-z_S = g_z,
-\end{equation}
-where $g_z$ is the element in $g$ that corresponds to redshift.
-Added sophistication includes redshift
-measurement uncertainty and random peculiar velocities. The study of coherent
-flow requires added model complexity.
-\item The underlying SED of transients are modeled.  For SNe~Ia the SALT2 model
-is an option, although new models that separate dust and intrinsic color or
-identify new SN~Ia parameters are expected in the near future.  Absolute magnitudes
-that depend on host-galaxy properties need to be considered. 
-For SNe~Ia $T=1$
-\begin{equation}
-L(t,\lambda; \alpha_{Ia}, \beta_{Ia}, \theta_{Ia}, g)  =10^{-\left(\frac{\alpha x_1 + \beta c}{2.5}\right)}L_{SALT2}(t-t_0; \alpha_{Ia}, x_1, c, \delta_m) \gamma(g, \beta) ,
-\end{equation}
-where the first two terms is the SALT2 model with a realized error snake,
-and $\gamma(g, \beta)$ a step function with free parameters in $\beta$ that
-describe the step size.
-
-For non-Ia's $T=0$ a set of light curve templates or a model can be used.
-An initial candidate is the treatment of non-Ia's implemented in PSNID.
-\item The theoretical distance modulus
-\begin{equation}
-\mu(g_z; \Omega_M, w)
-\end{equation}
-is the predicted distance modulus of a flat dark energy cosmology.
-\item The flux incident on Earth is the redshifted and time-dilated SED scaled
-by the distance modulus.
-\begin{equation}
-f(t,\lambda) = 10^{-\mu/2.5} L\left(t/(1+g_z),\lambda/(1+g_z)\right)
-\end{equation}
-\item The expected light curve in counts depends on the flux and throughput of the
-optical chain.  A first model encapsulates flux calibration through a zeropoint
-\begin{equation}
-\overline{\mathit{ADU}}(f, Z) = 10^{Z/2.5} \int  f(\lambda) T_0(\lambda)d\lambda,
-\end{equation}
-where $T_0$ is a fiducial transmission function for the appropriate filter.  A more sophisticated
-analysis can have a transmission function specific to each observation.
-\item The measured surface brightness of the host galaxy depends on the underlying
-surface brightness convolved with the point spread function and integrated
-over the transmission
-\begin{equation}
-\overline{\mathit{ADU}}_g =    \int (f_g(\lambda, RA, Dec) \otimes PSF) T(\lambda;Z)d\lambda.
-\end{equation}
-\item The measurement $\mathit{ADU}$ is the superposition of transient and background
-light $\overline{\mathit{ADU}} + \overline{\mathit{ADU}}_g$.
-\end{itemize}
-
-\subsection{Measurements}
-\label{measurements:sec}
-In the following discussion,
-spectroscopic and galaxy measurements are assumed
-to provide prefect determinations of transient type and parameters, and
-galaxy redshifts and parameters. 
-\begin{align}
-p(T_S|T) &= \delta(T_S-T),\\
-p(\theta_S|\theta_T) &= \delta(\theta_S|\theta_T),\\
-p(\theta_G|g) &= \delta(\theta_G-g)\\
-p(z_S|g_z) &= \delta(z_S-g_z)\\.
-\label{specz:eqn}
-\end{align}
-The working group is striving to get spectroscopic
-redshifts of all potential hosts.  People who are interested in SN spectral features
-or host-galaxy correlations (Chris, Rachel, Mat) can develop these models.
-
-The measured counts depend on the expected counts and measurement uncertainty
-$C_P$ as a Poisson (or considering the high sky background Normal) distribution
-\begin{equation}
-\mathit{ADU} \sim \mathcal{N} (\overline{\mathit{ADU}}+\overline{\mathit{ADU}}_g ,C_P).
-\label{ADU:eqn}
-\end{equation}
-Practically, the photometric extraction is handled by independent software, which calculates
-the pdf of $\mathit{ADU}_{\mathit{SN}}$, the realized contribution of supernova light,
-replacing this and the previous two bullet points.  Dillon is providing this.
-For the rest of the discussion, $\mathit{ADU}_{\mathit{SN}}$ is treated a measurement
-directly connected to the expected mean signal of the supernova
-$\overline{\mathit{ADU}}$
-\begin{equation}
-\mathit{ADU}_{SN} \sim \mathcal{N} (\overline{\mathit{ADU}} ,C_P).
-\end{equation}
-
-\subsection{Constructing the Likelihood}
-
-The analysis sample satisfy certain photometric and no successful spectroscopy
-({\it mis} Set)  and photometric
-and successful spectroscopic classification ({\it obs} Set) selection criteria, which for convenience
-probably should  be chosen to be stringent than the live-time decisions made during the survey.
-Neither the photometric nor spectroscopic selection criteria have been defined.
-Identifying good spectroscopic criteria needs to be done: the OzDES folks and Ryan are natural
-candidates.
-
-%The likelihood for the analysis sample is related to the underlying likelihood through
-%\begin{multline}
-%p(\mathit{ADU}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G |  \Omega_M, w, \theta_r, \alpha_{Ia}, \beta_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\beta_{\mathit{non-Ia}}, \sigma_{\mathit{non-Ia}},  Z, g, g_N, f_g)\\
-%= \frac{\epsilon(\mathit{ADU}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G) p_U(\mathit{ADU}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G | \ldots)}
-%{\sum_{T_S} \int d\mathit{ADU}\, dz_S\, d\theta_S\, d\theta_G\, \epsilon(\mathit{ADU}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G) p_U(\mathit{ADU}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G | \ldots)},
-%\end{multline} 
-%where $p_U$ is the underlying likelihood  and $\epsilon$ is the efficiency for inclusion
-%in the sample (more precisely subsample as spectroscopic
-%selection should produce different efficiencies for the {\it obs} and {\it mis} sets.)
-
-%The efficiencies for photometric and spectroscopic selection are taken to be independent.
-%The efficiency  to pass photometric selection is denoted as $\epsilon_P$.
-
-The following is a sketch of the likelihood calculation for an example 
-photometric selection criterion, which should serve as a useful guide once the criteria are fixed.
-The criterion is for $\ge N$ photometric points
-above a signal-to-noise threshold (translating to a distinct limiting signal $ADU_{0i}$
-for measurement $i$ of a given transient) given $M$ available measurements. 
-The fail/pass status of the measurements are stored as 0/1 in an array $b$.
-There are $\sum_{k=N}^M \binom{M}{k}$ 
-distinct $b$'s that allow acceptance of the light curve.  In the notation $b_{ijk}$, $i$ indexes
-the configuration, $j$ the transient, and $k$ the photometric point of transient $j$.
-
-\subsubsection{Likelihood for the {\it obs} Set}
-The likelihood for the {\it obs} set is
-\begin{multline}
-p(\mathit{ADU}_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G |  \Omega_M, w, \theta_r, \alpha_{Ia}, \beta_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\beta_{\mathit{non-Ia}}, \sigma_{\mathit{non-Ia}},  Z, g, g_N, f_g)\\
-= \sum_i \int_L dL\, p(\mathit{ADU}_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G , b_i|  L, \ldots)
- P(L|\ldots) \\
- \propto \sum_i  \epsilon(\mathit{ADU}_{SN}; b_{i}) \int_L dL\, p(\mathit{ADU}_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G|  L, \ldots)P(L|\ldots).
-\end{multline} 
-It is proportional to the truncated likelihood of the underlying sample, where the truncation
-is achieved through $\epsilon(\mathit{ADU}_{SN}; b_{i})$, the efficiency that a light curve is 
-selected in for a given configuration.  For the limiting flux criteria
-\begin{equation}
-\epsilon(\mathit{ADU}_{SN}; b_{i})= \prod_{jk}\mathcal{H}\left((-1)^{b_{ijk}+1}(ADU_{SN,jk}-ADU_{0,jk})\right),
-\end{equation}
-where $\mathcal{H}$ is the Heaviside step function; when $b_{ijk}=1$ the step in the efficiency
-is up and for $b_{ijk}=0$ the step is down.
-
-%The likelihood without the configuration condition for our measurements is
-%\begin{multline}
-%p(\mathit{ADU}_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G | L, \ldots) \\
-%= \delta(z_S - g_z) \delta(\theta_S-\theta_T) \delta(\theta_G -g) \delta(T_S-T)  \mathcal{N}
-%\left(\mathit{ADU}_{SN} -\overline{\mathit{ADU}}_j(L ,\ldots), C_P \right).
-%\end{multline}. 
-%
-
-%
-%The probability for failing (passing) the selection criterion for a single point is
-%\begin{equation}
-%P(b_{ij} | L, \ldots) = b_{ij} + (-1)^{b_{ij}}\int_{-\infty}^{ADU_0} d\mathit{ADU}_{SN,i}  \mathcal{N}\left(\mathit{ADU}_{SN} - \overline{\mathit{ADU}}_j(L ,\ldots), C_P \right),
-%\end{equation}
-%the (complementary) cumulative distribution function for a normal distribution
-%with variable
-%$\mathit{ADU}_0$, i.e.\ 2 times the error function.
-
-For measurements described in \S\ref{measurements:sec}, the likelihood for the {\it obs} Set is
-\begin{multline}
-p(\mathit{ADU}_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G |  \Omega_M, w, \theta_r, \alpha_{Ia}, \beta_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\beta_{\mathit{non-Ia}}, \sigma_{\mathit{non-Ia}},  Z, g, g_N, f_g)\\
-\propto \sum_i  \epsilon(\mathit{ADU}_{SN}; b_{i})  \int_L dL\, 
-\mathcal{N}\left(\mathit{ADU}_{SN} - \overline{\mathit{ADU}}_j(L ,
-g_z=z_S, \theta_T=\theta_S, g=\theta_G, T=T_S, \ldots), C_P \right)\\
-P(L|g_z=z_S, \theta_T=\theta_S, g=\theta_G, T=T_S, \ldots),
-\end{multline} 
-where the latent parameters $T$, $\theta_T$ are not integrated over.
-The normalization factor is parameter-dependent and is set by the condition
-\begin{equation}
-\sum_{T_S} \int d\mathit{ADU}_{SN}\,d{{z}}_S\,d\theta_{S}\,d\theta_G\,p(\mathit{ADU}_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G |  \ldots)=1.
-\end{equation}
-
-\subsubsection{Likelihood for the {\it mis} Set}
-The likelihood for the {\it mis} set follow the same pattern as that of the
-{\it obs} set except for not having to account for spectroscopic data.
-\begin{multline}
-p(\mathit{ADU}_{SN}, \theta_{G_1} |  \Omega_M, w, \theta_r, \alpha_{Ia}, \beta_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\beta_{\mathit{non-Ia}}, \sigma_{\mathit{non-Ia}},  Z, g, g_N, f_g) \\
- \propto \sum_i  \epsilon(\mathit{ADU}_{SN}; b_{i}) 
-\int_L dL\, 
-\sum_k 
-\pi_k\mathcal{N}\left(\mathit{ADU}_{SN} - \overline{\mathit{ADU}}_j(L ,
-g=\theta_{G_k}, \ldots), C_P \right)
-P(L|g=\theta_{G_k}, \ldots), 
-\end{multline} 
-where $\pi_k$ is the probability that the $k$'th galaxy is the host, provided by Ravi.
-
-%\begin{multline}
-%p(\mathit{ADU}_{SN}, \theta_G |  \Omega_M, w, \theta_r, \alpha_{Ia}, \beta_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\beta_{\mathit{non-Ia}}, \sigma_{\mathit{non-Ia}},  Z, g, g_N, f_g)\\
-%= \sum_i \int_L dL\, p(\mathit{ADU}_{SN}, \theta_G | b_i, L, \ldots)
-%P(b_{i} |L, \ldots) P(L|\ldots) ,
-%\end{multline} 
-%\begin{equation}
-%p(\mathit{ADU}_{SN}, \theta_G | b_i, L, \ldots)
-%  =  \frac{ \prod_j
-% \epsilon(\mathit{ADU}_{SN,j}; b_{ij})
-%  p(\mathit{ADU}_{SN}, \theta_G | L, \ldots)}
-%  {\prod_j P(b_{ij}{ |L,\dots)}}.
-%\label{misconf:eqn}
-%\end{equation}
-
-\section{Tasks}
-\begin{table}[htdp]
-\caption{default}
-\begin{center}
-\begin{tabular}{|c|c|}
-\hline
-Task/Deliverable & Responsible \\ \hline
-Model Design & \\
-Sampler &\\
-Photometric Selection &\\
-Spectroscopy Selection &\\
-Host Galaxy Association &\\
-Host Galaxy Parameters &\\
-SN~Ia Models Selection &\\
-Non-Ia Models Selection &\\
-SN light curves (ADU) &\\
-Photometric Zeropoints &\\
-\hline
-\end{tabular}
-\end{center}
-\label{Tasks and Responsible Parties}
-\end{table}%
-
-\section{Misc}
-The simulation of data from the model presented in
-and their analysis is implemented in Python and are available
-on GitHub\footnote{{git@github.com:AlexGKim/abc.git}}.
-
 \bibliographystyle{elsarticle-num} 

### 2015-10-20 doc/article.tex
New version

@@
 supernova analysis of the Dark Energy Survey and the Large Synoptic Survey Telescope.
+This model captures the current treatment in current analysis but expanded to include
+photometry-only transients.  This may not be the ultimate model used, indeed many models
+need to be considered for model testing.
+
 %SNe~Ia are not perfect standard candles but rather are calibrated candles whose
@@
 The notation for the likelihood presents the data and fundamental model parameters
-\begin{equation}
-p(n, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G |  \Omega_M, w, r, \alpha_{Ia}, \beta_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\beta_{\mathit{non-Ia}}, \sigma_{\mathit{non-Ia}},  \sigma_\beta, Z, g, g_N, f_g),
+\begin{multline}
+\sum_T \int d\theta_{Ia}\, d\theta_{!Ia}\, dL\, p(n, {{T}}_S,{{z}}_S, \theta_{S}, G | T, \theta_{Ia},
+\theta_{!Ia}, L, \mathcal{S}, \Omega_M, w, r, \Theta_{Ia}, \Theta_{\mathit{!Ia}}, Z, g) \\
+p(L|T, \theta_{Ia},
+\theta_{!Ia},  \mathcal{S}, \Omega_M, w, r, \Theta_{Ia},\Theta_{\mathit{!Ia}}, Z, g)
+p(T, \theta_{Ia},
+\theta_{!Ia}|  \mathcal{S}, \Omega_M, w, r, \Theta_{Ia},\Theta_{\mathit{!Ia}}, Z, g),
 \label{likelihood2:eqn}
-\end{equation}
+\end{multline}
 whose relations are sketched in the probabilistic graphical model in Figure~\ref{pgm:fig}.
+$\mathcal{S}$ indicates that this likelihood corresponds to the analysis sample. 
+For shorthand we asign $A=\{n, {{T}}_S,{{z}}_S, \theta_{S}, G \}$, $B=\{T, \theta_{Ia},
+\theta_{!Ia}, L\}$, and $C=\{\Omega_M, w, r, \Theta_{Ia}, \Theta_{\mathit{!Ia}}, Z, \}$
+so that the likelihood is more compactly expressed as $\int dB\, p(AB| \mathcal{S}, C)p(B| \mathcal{S}, C)$.
 
@@
    through $\tau_i$ to be included in the sample.  Some transients have spectral data
-   ${X}_S$.  The properties of the galaxy identified as the host galaxy is $\theta_G$. 
+   ${X}_S$.  The properties of the galaxy identified as the host galaxy is $G$. 
    \label{pgm:fig}}
@@
 \begin{itemize}
-\item $n$: the measured counts for each photometric observation;
+\item $n$: the measured counts for each photometric observation for all transients in the sample;
 \item ${{T}}_S$, ${{z}}_S$, $\theta_S$: the spectroscopic type, redshift, and transient parameters available for a subset of transients;
-\item $\theta_{G1}$, $\theta_{G2}$: the spectroscopic redshifts of the galaxies identified
-as host and neighbor from imaging.
+\item $G$: measured properties of the galaxy identified
+as the host.
 \end{itemize}
-The model parameters are
+The top-level model parameters are
 \begin{itemize}
@@
 constant-$w$ dark-energy cosmology;
-\item $r_1$, $r_2$:  the parameters
+\item $r$:  the parameters
 that describe the redshift-dependent relative fraction of SNe~Ia and non-Ia's;
-\item $\alpha_{Ia}$, $\sigma_{Ia}$, $\alpha_{\mathit{non-Ia}}$, $\sigma_{\mathit{non-Ia}}$:
-the luminosity (times $4\pi$) and intrinsic dispersion for SNe~Ia and non-Ia at peak brightness;
-\item $\beta_{Ia}$, $\beta_{non-Ia}$: the parameters for the internal diversity within SNe~Ia and
-non-Ia's respectively, e.g.\ SALT2's  $\alpha$ and $\beta$;
-\item $\sigma_\beta$: parameters that describe the distribution of intrinsic supernova
-parameters of SNe~Ia and non-Ia;
+\item $\Theta_{Ia}$, $\Theta_{\mathit{!Ia}}$:  All the fundamental parameters used to describe
+the SN~Ia and non-Ia populations respectively, such as the mean
+absolute magnitude, intrinsic magnitude dispersion, the distribution of internal parameters
+(i,e,\ the distributions of SALT2's $x_1$ and $c$), the relationship between internal
+parameters and magnitude (i.e.\ SALT2's $\alpha$, $\beta$);
 \item $Z$: the parameters that describe the transmission functions, i.e.\ photometric calibration;
-\item $g$, $g_N$: the parameters that describe the candidate host and neighbor galaxies,
-to be more expansive than the previous $z$ parameter;
-\item $f_g$: the surface brightness of the background light at the location of the transient
-needed for to extract the photometry of the point-source transient.
+\item $g$: the parameters that describe the candidate host and neighbor galaxies
+including redshift $g_z$.
 \end{itemize}
-Not listed explicitly in Eqn.~\ref{likelihood:eqn} but shown in Figure~\ref{toypgm:fig} are latent model parameters for each transient:
+The second-level parameters are
 \begin{itemize}
@@
 \item $T$: the class of the objects, SN~Ia or non-Ia;
-\item $\theta_{Ia}$, $\theta_{non-Ia}$: the transient parameters that describe individual
-transients, e.g.\ SALT2's $x_1$, $c$;
-\item $L$: the luminosity of the transient.
+\item $\theta_{Ia}$, $\theta_{!Ia}$: the transient parameters that describe individual
+transients (i.e..\ SALT2's $x_1$, $c$);
+\item $L(t,\lambda)$: the luminosity of the transient.
 \end{itemize}
@@
 \item{$f$}: the flux of the transient given the luminosity, distance modulus, and
-redshift;
-\item{$\overline{n}_X$}: the expected counts of the transient and background light given
-the flux and transmission.
+redshift.
+%\item{$\overline{n}$}: the expected counts of the transient given
+%the flux and transmission.
 \end{itemize}
 
-The relationships between the parameters for the underlying population are now described.  What follows is an initial proposal
-based on current supernova analyses, but many different models need to be
-considered as the understanding of transients improve
-and for probing systematics by comparing the
-performance of competing models.
-
+The relationships between the parameters are now described:
 \begin{itemize}
@@
 \begin{equation}
-\theta_{Ia} | \sigma_\beta, g \sim \mathcal{N}(0, \sigma_{\beta,Ia}),
-\end{equation}
-where $\theta_{Ia} =\{x_1, c\}$ are the SALT2 light-curve shape and color parameters.
+\theta_{Ia} | \Theta_{Ia}, g \sim \mathcal{N}(0, \Theta_{ia, \theta}),
+\end{equation}
+where $\theta_{Ia} =\{x_1, c\}$ are the SALT2 light-curve shape and color parameters
+and $\Theta_{ia, \theta}$ describes the covariance of their distributions.
 A more complex model can be based on non-Normal distributions
@@
 \begin{equation}
-\theta_{Si} (\theta_{Ia}, \theta_{non-Ia}, T)=\theta_T
+\theta_{S} (\theta_{Ia}, \theta_{!Ia}, T)=\theta_{T}
 \end{equation}
@@
 \begin{equation}
-T | r, g \sim \rm{Bernoulli}(\pi(g,r)),
-\end{equation}
-where $\pi$ is a model for the relative rates of the different types as a
+T | r, g \sim \rm{Bernoulli}(\pi(r,g,T)),
+\end{equation}
+where $\pi$ is a model for the relative rate of SNe~Ia as a
 function of galaxy parameters and redshift.  {\bf A reasonable choice for $\pi$ needs to be
-selected, any volunteers?}
+selected.}
 \item Supernova type is assumed to be unambiguously encoded in the
@@
 that depend on host-galaxy properties need to be considered. 
-For SNe~Ia $T=1$
-\begin{equation}
-L(t,\lambda) |  \alpha_{Ia}, \beta_{Ia}, \sigma_{Ia},  \theta_{Ia}, g, x_1, c \sim L_{SALT2}(t-t_0; \alpha_{Ia}, x_1, c) \gamma(g, \beta) \mathcal{N}(0,\sigma_{Ia}),
+\begin{equation}
+L(t,\lambda) |  \Theta_{Ia}, \theta_{Ia}, g \sim L_{SALT2}(t-t_0; \alpha, \beta, x_1, c) \gamma(g, \Theta_{Ia,g}) \mathcal{N}(0,\sigma_{Ia}),
 \end{equation}
@@
 model with a realized error snake,
-and $\gamma(g, \beta)$ a step function with free parameters in $\beta$ that
-describe the step size.
-
-{\bf The non-Ia model needs to be identified.}
+and $\gamma(g, \Theta_{Ia})$ a step function to model the ``mass step''.  Recall that the  fundamental SALT2 parameters 
+$\alpha$, $\beta$, and intrinsic dispersion $\sigma_{Ia}$, and the parameters that
+relate SN magnitude and host,
+are included in $\Theta_{Ia}$; the parameters in the SALT2 fit $t_0$, $x_1$, $c$
+are included in $\theta_{Ia}$.
+
+{\bf The non-Ia model needs to be identified.  Perhaps PSNID.}
 \item The theoretical distance modulus
@@
 \begin{equation}
-\overline{n}(f, Z) = 10^{Z/2.5} \int  f(\lambda) T_0(\lambda)d\lambda,
+n(f, Z) = 10^{Z/2.5} \int  f(\lambda) T_0(\lambda)d\lambda,
 \end{equation}
@@
 analysis can have a transmission function specific to each observation.
-\item The measured surface brightness of the host galaxy depends on the underlying
-surface brightness convolved with the point spread function and integrated
-over the transmission
-\begin{equation}
-\overline{n}_g =    \int (f_g(\lambda, RA, Dec) \otimes PSF) T(\lambda;Z)d\lambda.
-\end{equation}
-\item The measurement $n$ is the superposition of transient and background
-light $\overline{n} + \overline{n}_g$.
+\item The host-galaxy information is directly encoded in the measurements
+\begin{equation}
+G(g)=g.
+\end{equation}
 \end{itemize}
@@
 \label{measurements:sec}
-In the following discussion,
-spectroscopic and galaxy measurements are assumed
+Spectroscopic measurements are assumed
 to provide prefect determinations of transient type and parameters, and
@@
 p(\theta_S|\theta_T) &= \delta(\theta_S-\theta_T),\\
-p(\theta_G|g) &= \delta(\theta_G-g),\\
-p(z_S|g_z) &= \delta(z_S-g_z)
+p(z_S|g_z) &= \delta(z_S-g_z).
 \label{specz:eqn}
 \end{align}
+People who are interested in SN spectral features
+or host-galaxy correlations (Chris, Rachel, Mat) can develop these models.
+
+For the photometric sample, there is uncertainty in the identity of the host galaxy.
+From a set of potential host galaxies $\hat{G}$ each with probability $\pi$ of being the correct host,
+\begin{equation}
+G \sim \prod_i \delta(G-\hat{G}_i) \pi_i.
+\end{equation}
+Ravi can provide for each transient a list of candidate hosts and their probabilities.
 The working group is striving to get spectroscopic
-redshifts of all potential hosts.  People who are interested in SN spectral features
-or host-galaxy correlations (Chris, Rachel, Mat) can develop these models.
-
-The measured counts depend on the expected counts and measurement uncertainty
-$C_P$ as a Poisson (or considering the high sky background Normal) distribution
-\begin{equation}
-n \sim \mathcal{N} (\overline{n}+\overline{n}_g ,C_P).
-\label{ADU:eqn}
-\end{equation}
-Practically, the photometric extraction is handled by independent software, which calculates
-the pdf of $n_{\mathit{SN}}$, the realized contribution of supernova light,
-replacing this and the previous two bullet points.  Dillon is providing this.
-For the rest of the discussion, $n_{\mathit{SN}}$ is treated a measurement
-directly connected to the expected mean signal of the supernova
-$\overline{n}$
-\begin{equation}
-n_{SN} \sim \mathcal{N} (\overline{n} ,C_P).
-\end{equation}
-
-Prior on $Z$.
-\subsection{Constructing the Likelihood}
-
-The analysis sample satisfy certain photometric and no successful spectroscopy
-({\it mis} Set)  and photometric
-and successful spectroscopic classification ({\it obs} Set) selection criteria, which for convenience
-probably should  be chosen to be stringent than the live-time decisions made during the survey.
-Neither the photometric nor spectroscopic selection criteria have been defined.
-Identifying good spectroscopic criteria needs to be done: the OzDES folks and Ryan are natural
-candidates.
-
-%The likelihood for the analysis sample is related to the underlying likelihood through
-%\begin{multline}
-%p(n, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G |  \Omega_M, w, \theta_r, \alpha_{Ia}, \beta_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\beta_{\mathit{non-Ia}}, \sigma_{\mathit{non-Ia}},  Z, g, g_N, f_g)\\
-%= \frac{\epsilon(n, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G) p_U(n, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G | \ldots)}
-%{\sum_{T_S} \int dn\, dz_S\, d\theta_S\, d\theta_G\, \epsilon(n, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G) p_U(n, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G | \ldots)},
-%\end{multline} 
-%where $p_U$ is the underlying likelihood  and $\epsilon$ is the efficiency for inclusion
-%in the sample (more precisely subsample as spectroscopic
-%selection should produce different efficiencies for the {\it obs} and {\it mis} sets.)
-
-%The efficiencies for photometric and spectroscopic selection are taken to be independent.
-%The efficiency  to pass photometric selection is denoted as $\epsilon_P$.
-
-The following is a sketch of the likelihood calculation for an example 
-photometric selection criterion, which should serve as a useful guide once the criteria are fixed.
-The criterion is for $\ge N$ photometric points
-above a signal-to-noise threshold (translating to a distinct limiting signal $n_{0i}$
-for measurement $i$ of a given transient) given $M$ available measurements. 
-The fail/pass status of the measurements are stored as 0/1 in an array $b$.
-There are $\sum_{k=N}^M \binom{M}{k}$ 
-distinct $b$'s that allow acceptance of the light curve.  In the notation $b_{ijk}$, $i$ indexes
-the configuration, $j$ the transient, and $k$ the photometric point of transient $j$.
-
+redshifts of all potential hosts, which is included in $G$.
+For the spectroscopic sample the host is unambigous
+\begin{equation}
+G = g.
+\end{equation}
+
+Practically the photometric extraction is handled by independent software, which calculates
+the $n$ with uncertainties $C_P$
+by modeling and separating out polluting background light from the transient
+signal
+\begin{equation}
+n \sim \mathcal{N}\left(10^{Z/2.5} \int  f(\lambda;A, B) T_0(\lambda)d\lambda,C_P\right).
+\end{equation}
+Dillon is providing this.
+Note that the model has explicit calibration parameters that are to be fit.  An alternative
+approach is to include calibration uncertainties in $C_P$.
+
+\subsection{Sample Selection}
+The transients that enter the analysis satisfy some selection criteria.  Trivially, they
+have to be discovered in the first place and often more stringent photometric signal-to-noise
+requirements are applied.  Additionally, the probability for a transient to have successful
+spectroscopy may depend on parameters.  These criteria have not yet been determined/selected
+(Argonne for photometry, OzDES/Ryan for spectroscopy are candidates to do this);
+presented here is a sketch of the likelihood calculation for a reasonable
+photometric selection criterion.
+For each transient $\nu$, the criterion is to have $\ge N$ photometric points
+above a signal-to-noise threshold there  given $M_\nu$ available measurements:
+the signal-to-noise threshold corresponding to a flux threshold
+ $n_{0,\nu i}$.
+
+Call the likelihood of the underlying distribution without sample selection $P(A|C)$.
+Let the array $b_{\nu}$ be an array that contains $0$ or $1$ based on
+whether the corresponding photometric point is below or passes threshold. 
+Let the larger array $b$ be a combination of the $b_\nu$ from all transients.
+There are $2^{\sum_\nu M_\nu}$ possible permutations of $b$, and the underlying
+likelihood can be broken up into the sum of all possible combinations
+\begin{align}
+p(A|C) &= \sum_k p(A, b_k| C)\\
+& = \sum_k \epsilon(n, b_k)p(A| C),
+\end{align}
+where
+\begin{equation}
+\epsilon(n; b_{k})= \prod_{\nu i}\mathcal{H}\left((-1)^{b_{k\nu i}+1}(n_{k\nu i}-n_{0,\nu i})\right),
+\end{equation}
+where $\mathcal{H}$ is the Heaviside step function; when $b_{k\nu i}=1/0$ the step in the efficiency
+is up/down.  The indices correspond to configuration $k$,
+transient $\nu$, and photometric point $i$.
+
+For the analysis sample, are a smaller number of combinations of $b$ that satisfy
+the selection criteria;
+instead of $2^{M_\nu}$ there are $\sum_{k=N}^{M_{\nu}} \binom{M_{\nu}}{k}$ 
+distinct $b_{\nu}$'s that allow acceptance of transient $\nu$.  The selection efficiency
+for the complement set of possible $b$'s is zero.
+The sample likelihood is then as
+\begin{equation}
+p(A|\mathcal{S}, C) = \frac{\sum_k \epsilon(n, b_k)p(A| C)}{\int dA\, \sum_k \epsilon(n, b_k)p(A| C)},
+\end{equation}
+where the sum is
+over only the configurations that meet the selection criteria.
+
+The measurement uncertainties in the light curves $n$ are independent of the other
+measurements, and the measurement uncertainties are drawn from a Normal distribution:
+the likelihood is assembled from truncated Gaussians with the integrals over $n$ in the numerator
+proportional to error functions.
+
+\subsection{Likelihoods}
 The transients are divided into
@@
 The  {\it obs} sample constrains and specifies the parameter distributions of the 
-parameters missing from the {\it mis} sample; both samples
-are assumed to be drawn from the same underlying distribution.
+parameters missing from the {\it mis} sample.
 
@@
 \begin{multline}
-p(n_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G |  \Omega_M, w, r, \alpha_{Ia}, \beta_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\beta_{\mathit{non-Ia}}, \sigma_{\mathit{non-Ia}},  \sigma_\beta, Z, g, g_N, f_g)\\
-= \sum_i \int_L dL\, p(n_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G , b_i|  L, \ldots)
- P(L|\ldots) \\
- \propto \sum_i  \epsilon(n_{SN}; b_{i}) \int_L dL\, p(n_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G|  L, \ldots)P(L|\ldots).
+p(A|\mathcal{S},C) \propto
+\sum_k \epsilon(n, b_k) 
+\sum_T \int d\theta_{Ia}\, d\theta_{!Ia}\, dL\, p(n, {{T}}_S,{{z}}_S, \theta_{S}, G | T,  L, \Omega_M, w, r, \Theta_{Ia}, \Theta_{\mathit{!Ia}}, Z, g) \\
+p(L| T, \theta_{Ia},
+\theta_{!Ia},  \Omega_M, w, r, \Theta_{Ia},\Theta_{\mathit{!Ia}}, Z, g)
+p(T, \theta_{Ia}
+\theta_{!Ia}|  \Omega_M, w, r, \Theta_{Ia},\Theta_{\mathit{!Ia}}, Z, g).
 \end{multline}
-It is proportional to the truncated likelihood of the underlying sample, where the truncation
-is achieved through $\epsilon(n_{SN}; b_{i})$, the efficiency that a light curve is 
-selected in for a given configuration.  For the limiting flux criteria
-\begin{equation}
-\epsilon(n_{SN}; b_{i})= \prod_{jk}\mathcal{H}\left((-1)^{b_{ijk}+1}(n_{SN,jk}-n_{0,jk})\right),
-\end{equation}
-where $\mathcal{H}$ is the Heaviside step function; when $b_{ijk}=1$ the step in the efficiency
-is up and for $b_{ijk}=0$ the step is down.
-
-%The likelihood without the configuration condition for our measurements is
+
+For our model and measurements
+\begin{multline}
+p(A|\mathcal{S},C) \propto 
+\sum_k \epsilon(n, b_k) \int dL\,
+p(n |  T= T_S, \theta_{T}=\theta_S, g=G, L, C)
+p(L| T, \theta_{T_S}, r, \Theta_{T_S}, g)\\
+\pi(r, z_S, T_S)p( \theta_{T_S}|  \Theta_{T_S},g=G) .
+\end{multline}
+
+\subsubsection{Likelihood for the {\it mis} Set}
+The likelihood for the {\it mis} set follows the same pattern as that of the
+{\it obs} set except for not having to account for spectroscopic data
+\begin{multline}
+p(n, \theta_{G} |  \mathcal{S}, C) 
+ \propto \sum_k \epsilon(n; b_{k}) 
+\sum_T \int d\theta_{Ia}\, d\theta_{!Ia}\, dL\, 
+\sum_l
+\pi_l
+p(n |  g=\hat{G}_l, B, C)
+p(L| T, \theta_{Ia}, \theta_{!Ia}, r, \Theta_{Ia}, \Theta_{!Ia}, g)\\
+\pi(r, \hat{G}_l, T)p( \theta_{Ia},
+\theta_{!Ia}|  \Theta_{Ia},\Theta_{\mathit{!Ia}}, g=\hat{G}_l).
+\end{multline}
+
 %\begin{multline}
-%p(n_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G | L, \ldots) \\
-%= \delta(z_S - g_z) \delta(\theta_S-\theta_T) \delta(\theta_G -g) \delta(T_S-T)  \mathcal{N}
-%\left(n_{SN} -\overline{n}_j(L ,\ldots), C_P \right).
-%\end{multline}. 
-%
-
-%
-%The probability for failing (passing) the selection criterion for a single point is
-%\begin{equation}
-%P(b_{ij} | L, \ldots) = b_{ij} + (-1)^{b_{ij}}\int_{-\infty}^{ADU_0} dn_{SN,i}  \mathcal{N}\left(n_{SN} - \overline{n}_j(L ,\ldots), C_P \right),
-%\end{equation}
-%the (complementary) cumulative distribution function for a normal distribution
-%with variable
-%$n_0$, i.e.\ 2 times the error function.
-
-For measurements described in \S\ref{measurements:sec}, the likelihood for the {\it obs} Set is
-\begin{multline}
-p(n_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G |  \Omega_M, w, r, \alpha_{Ia}, \beta_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\beta_{\mathit{non-Ia}}, \sigma_{\mathit{non-Ia}},  \sigma_\beta, Z, g, g_N, f_g)\\
-\propto \sum_i  \epsilon(n_{SN}; b_{i})  \int_L dL\, 
-\mathcal{N}\left(n_{SN} - \overline{n}_j(L ,
-g_z=z_S, \theta_T=\theta_S, g=\theta_G, T=T_S, \ldots), C_P \right)\\
-P(L|g_z=z_S, \theta_T=\theta_S, g=\theta_G, T=T_S, \ldots),
-\end{multline} 
-where the latent parameters $T$, $\theta_T$ are not integrated over.
-The normalization factor is parameter-dependent and is set by the condition
-\begin{equation}
-\sum_{T_S} \int dn_{SN}\,d{{z}}_S\,d\theta_{S}\,d\theta_G\,p(n_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G |  \ldots)=1.
-\end{equation}
-
-\subsubsection{Likelihood for the {\it mis} Set}
-The likelihood for the {\it mis} set follow the same pattern as that of the
-{\it obs} set except for not having to account for spectroscopic data.
-\begin{multline}
-p(n_{SN}, \theta_{G_1} |  \Omega_M, w, r, \alpha_{Ia}, \beta_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\beta_{\mathit{non-Ia}}, \sigma_{\mathit{non-Ia}},  \sigma_\beta, Z, g, g_N, f_g) \\
- \propto \sum_i  \epsilon(n_{SN}; b_{i}) 
-\int_L dL\, 
-\sum_k 
-\pi_k\mathcal{N}\left(n_{SN} - \overline{n}_j(L ,
-g=\theta_{G_k}, \ldots), C_P \right)
-P(L|g=\theta_{G_k}, \ldots), 
-\end{multline} 
-where $\pi_k$ is the probability that the $k$'th galaxy is the host, provided by Ravi.
-
-%\begin{multline}
-%p(n_{SN}, \theta_G |  \Omega_M, w, \theta_r, \alpha_{Ia}, \beta_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\beta_{\mathit{non-Ia}}, \sigma_{\mathit{non-Ia}},  Z, g, g_N, f_g)\\
-%= \sum_i \int_L dL\, p(n_{SN}, \theta_G | b_i, L, \ldots)
+%p(n_{SN}, G |  \Omega_M, w, \theta_r, \alpha_{Ia}, \beta_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\beta_{\mathit{non-Ia}}, \sigma_{\mathit{non-Ia}},  Z, g, g_N, f_g)\\
+%= \sum_i \int_L dL\, p(n_{SN}, G | b_i, L, \ldots)
 %P(b_{i} |L, \ldots) P(L|\ldots) ,
@@
 %\begin{equation}
-%p(n_{SN}, \theta_G | b_i, L, \ldots)
+%p(n_{SN}, G | b_i, L, \ldots)
 %  =  \frac{ \prod_j
 % \epsilon(n_{SN,j}; b_{ij})
-%  p(n_{SN}, \theta_G | L, \ldots)}
+%  p(n_{SN}, G | L, \ldots)}
 %  {\prod_j P(b_{ij}{ |L,\dots)}}.
@@
 
-\section{Standard Candle}
-\label{toy:sec}
-To introduce basic model elements, this Section considers a
-simplified view of SNe~Ia
-as transients that are bolometric standard candles with an intrinsic random
-dispersion
-at peak brightness, and assumes data with negligible measurement uncertainties.
-For convenience,
-the transients
-in this Section are  referred to as SNe~Ia.
-The added complexity of correlations between absolute magnitude
-and multi-band light curves, and measurement uncertainties
-are discussed in
-\S\ref{snIamodel:sec}.
-
-\subsection{Base Model}
-\label{model:sec}
-This Section presents a model that is used both for generating simulated data, and for analysis.
-The data used to construct a Hubble diagram and the fundamental parameters of the
-model used to describe those data are succinctly summarized in the notation
-for the likelihood 
-\begin{equation}
-p(f, {{T}}_S,{{z}}_S, \theta_G|  \Omega_M, w, \theta_r,\alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}}),
-\label{likelihood:eqn}
-\end{equation}
-whose relations are sketched in the probabilistic graphical model in Figure~\ref{toypgm:fig}.
-The measurements are
-\begin{itemize}
-\item $f$: the flux at peak brightness, taken 
-to be bolometric to facilitate the treatment of
-standard candles at different redshift;
-\item ${{T}}_S$, ${{z}}_S$: the spectroscopic type and redshift available for a subset of transients;
-\item $\theta_{G1}$, $\theta_{G2}$: the spectroscopic redshifts of the galaxies identified
-as host and neighbor from imaging.
-\end{itemize}
-The model parameters are
-\begin{itemize}
-\item $\Omega_M$, $w$: the mass density and dark-energy equation of state parameters of a flat,
-constant-$w$ dark-energy cosmology;
-\item $\theta_{r1}$, $\theta_{r2}$:  the parameters
-that describe the redshift-dependent relative fraction of SNe~Ia and non-Ia's;
-\item $\alpha_{Ia}$, $\sigma_{Ia}$, $\alpha_{\mathit{non-Ia}}$, $\sigma_{\mathit{non-Ia}}$:
-the luminosity (times $4\pi$) and intrinsic dispersion for SNe~Ia and non-Ia at peak brightness.
-\end{itemize}
-Not listed explicitly in Eqn.~\ref{likelihood:eqn} but shown in Figure~\ref{toypgm:fig} are latent model parameters for each transient:
-\begin{itemize}
-\item $z$: the cosmological redshifts of the host and neighboring galaxies;
-\item $T$: the class of the objects, SN~Ia or non-Ia;
-\item $L$: the luminosity of the transient.
-\end{itemize}
-There is a  fixed parameter
-\begin{itemize}
-\item $\mu$: the distance modulus given the cosmological parameters and the redshift.
-\end{itemize}
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=4.5in]{/Users/akim/project/abc/results/toy_pgm.pdf} 
-   \caption{Probabilistic Graphical Model for the standard candle analysis. The
-   parameters include the cosmological parameters $\Omega_M$ and $w$,
-   the luminosities $\alpha$ and intrinsic dispersions $\sigma$ of SNe~Ia and non-Ia's,
-   and the relative fraction parameters $\theta_{r1}$ and $\theta_{r2}$.  Latent parameters
-   include 
-   for each transient the type $T$ and redshifts of the host and neighboring galaxies $z$ and $z_N$.  The  distance modulus $\mu$ and
-   luminosity $L$ are fixed by the other parameters.  The observables include the measured
-   flux $f$, spectroscopic type and redshift $T_S$ and $z_S$, and
-   the inferred host and neighbor redshifts $\theta_{G1}$ and $\theta_{G2}$.
-   The host and neighbor galaxies of all transients are inferred based a common galaxy catalog, 
-   and so strictly are not independent from supernova to supernova.
-   \label{toypgm:fig}}
-\end{figure}
-
-The transients being analyzed have passed some detection threshold
-and thus are drawn from
-distributions that have different shapes than the underlying population of both discovered and
-non-discovered objects. A  threshold flux of $f_0$ is adopted for the detection criterion.
-Otherwise, no other sample-selection criteria are assumed.
-
-\subsubsection{Likelihood for the {\it obs} set data}
-\label{obs:sec}
-The likelihood of data from the {\it obs} set, which has
-spectroscopic observations $T_S$ and redshift
-$z_S$, is described as follow.  The likelihood is
-\begin{align}
-p(f, {{T}}_S,{{z}}_S|  \Omega_M, w, \theta_r,\alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}}, z)  &=\sum_T
-p(f, {{T}}_S,{{z}}_S, T| \ldots)\\
-&= \sum_T 
-p(f, {{T}}_S,{{z}}_S| T,\dots) p(T | \ldots).
-\end{align}
-
-Direct associations between model and spectroscopic redshift and type are made
-\begin{align}
-p(z_S|z) &= \delta(z_S-z)\\
-p(T_S|T) &= \delta(T_S-T),
-\label{specz:eqn}
-\end{align}
-so that
-\begin{align}
-p(f, {{T}}_S,{{z}}_S|  \ldots) &= 
-p(f| T=T_S, z=z_s,\dots) p(T_S|z=z_s, \ldots).
-\label{obs:eqn}
-\end{align}
-
-The first term describes the expected counts. Given the redshift
-and transient type, the brightness of the underlying population
-is modeled as being drawn from a standard candle
-with mean luminosity $4\pi\alpha_X$ and a normal distribution in magnitude
-space with intrinsic dispersion  $\sigma_X$:
-\begin{equation}
-f| T=T_S, z=z_S, \Omega_M, w, \theta_r, \alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}} \sim \mathcal{N}_{\ln}\left(\ln{\left(\frac{\alpha_{T_S}}{d_L^2(z_S;\Omega_M, w)}\right)}, \frac{\ln{10}}{2.5}\sigma_{T_S}\right),
-\label{flux:eqn}
-\end{equation}
-where $\mathcal{N}_{\ln}$ is the log-normal distribution and $d_L$ is the luminosity distance.
-Measurement uncertainty is taken to be negligible.
-In a flux-limited survey, the pdf's for the data are truncated versions of the underlying
-pdf's.
-\begin{itemize}
-\item For SNe~Ia  $T_S=1$:
-\begin{equation}
-f | T=1, z=z_S, \Omega_M, w, \alpha_{Ia},\sigma_{Ia} \sim
-\frac{\mathcal{N}_{\ln}\left(\ln{\left(\frac{\alpha_{Ia}}{d_L^2(z_S;\Omega_M, w)}\right)}, \frac{\ln{10}}{2.5}\sigma_{Ia}\right)}{P_{Ia}(f > f_0)}.
-\label{adusnIa:eqn}
-\end{equation}
-\item For non-Ia's in set $T_S=0$:
-\begin{equation}
-f | T=0, z=z_S, \Omega_M, w, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}}\sim 
-\frac{\mathcal{N}_{\ln}\left(\ln{\left(\frac{\alpha_{\mathit{non-Ia}}}{d_L^2(z_S;\Omega_M, w)}\right)}, \frac{\ln{10}}{2.5}\sigma_{\mathit{non-Ia}}\right)}{P_{non-Ia}(f > f_0)},
-\label{adunonIa:eqn}
-\end{equation}
-\end{itemize}
-where the normalization factor is the complementary cumulative distribution function
-for the corresponding log-normal distribution that accounts for the truncated
-distribution of the detected sample.
-It is understood implicitly that as all objects must pass the detection threshold,
-the case of $f<f_0$ is never confronted in the analysis.
-
-The second term gives the type probability. In our model,
-the underlying relative rates between SNe~Ia and non-Ia are linear in redshift,
- parameterized by the
-its values at $z=0$ and $1.1 \times z_{max}$, 
-\begin{equation}
-\hat{\theta}_r=\theta_{r0}+z\left(\frac{\theta_{r1}-\theta_{r0}}{1.1 \times z_{max}}\right).
-\label{rate:eqn}
-\end{equation}
-The relative rate for SN~Ia discovery for the discovered (truncated) distribution is
-\begin{equation}
-\theta_r=\frac{\hat{\theta}_rP_{Ia}(f > f_0)}{\hat{\theta}_{r}P_{Ia}(f > f_0) + (1-\hat{\theta}_{r})P_{non-Ia}(f > f_0)}.
-\end{equation}
-The spectroscopic classifications are drawn from
-\begin{equation}
-T_S | z=z_S, \Omega_M, w, \theta_{r0}, \theta_{r1} , \alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}} \sim \text{Bernoulli}(\theta_r).
-\end{equation}
-Although the underlying type distribution depends only on $ \theta_{r0}$ and $ \theta_{r1}$,  
-the observed distribution does depend on the other parameters through $\theta_r$'s dependence on
-the two normalization factors
-$P_{X}(f > f_0)$.
-
-%The third term is the redshift distribution of transient discoveries.
-%The model takes an underlying redshift distribution of transients in the universe
-%\begin{equation}
-%p(z) \propto z^2.
-%\end{equation}
-%The redshift distribution of discovered transients is then
-%\begin{equation}
-%p(z) = \frac{z^2\left(\hat{\theta}_{r}P_{Ia}(f > f_0) + (1-\hat{\theta}_{r})P_{non-Ia}(f > f_0)
-%\right)}{\int_{z_{min}}^{z_{max}} dz'\, z'^2\left( 
-%\hat{\theta}_{r}P_{Ia}(f > f_0) + (1-\hat{\theta}_{r})P_{non-Ia}(f > f_0)
-%\right)}.
-%\end{equation}
-
-\subsubsection{Likelihood for the {\it mis} set data}
-
-Transients in the {\it mis}
-set have no spectroscopic confirmation, and their data are treated as follows:
-With no redshift from the transient itself, 
-the redshift measurement is inferred from potential host galaxies.
-In this Section, each transient is associated with two galaxies, one 
-with redshift $\theta_{G1}$
-that has high probability $\pi_{host}$
-of being the host and the other
-with redshift $\theta_{G2}$ that has probability $(1-\pi_{host})$.
-In the model, the
-true host redshift is $z$ and that of the interloping galaxy is $z_N$.
-The likelihood for the galaxy redshifts is
-\begin{equation}
-P(\theta_{G1},\theta_{G2}|z, z_N) =
-	\pi_{host}\delta(z-\theta_{G1})\delta(z_N-\theta_{G2}) +
-	(1-\pi_{host}) \delta(z-\theta_{G2})\delta(z_N-\theta_{G1}).
-\end{equation}
-As with the transients, the redshifts of the host
- and neighbor galaxies are drawn from underlying distributions $p(z) \propto z^2$, $p(z_N) \propto z^2_N$.
-
-The distribution of the underlying distribution is 
-\begin{multline}
-p(f, \theta_{G1}, \theta_{G2} | \Omega_M, w, \theta_r, \alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}}, z, z_N)  \\
-= \sum_{T} p(f, \theta_{G1}, \theta_{G2}| T, \ldots)P(T| \ldots)\\
- =\sum_{T} p(f| T, \ldots)p(\theta_{G1}, \theta_{G2}| T, \ldots) P(T| \ldots) \\
-= \sum_{T} \pi_{host} p(f| T, z=\theta_{G1} ,z_N=\theta_{G2}, \ldots) P(T| z=\theta_{G1}, ,z_N=\theta_{G2}, \ldots)  \\
- +  (1-\pi_{host}) p(f| T, z=\theta_{G2}, z_N=\theta_{G1}, \ldots) P(T| z=\theta_{G2}, z_N=\theta_{G1}, \ldots).
-\label{adumis:eqn}
-\end{multline}
-The probabilities  for the underlying flux and
-relative rate distributions
- Eqns.~\ref{flux:eqn} and \ref{rate:eqn} introduced in \S\ref{obs:sec} apply.
-
-The data likelihood is a truncated version of the
-underlying distribution: the distribution in  Eqn.~\ref{adumis:eqn} normalized by
-the complementary cumulative distribution function
-\begin{equation}
-p(f>f_0, \theta_{G1}, \theta_{G2}|\ldots) = \int_{f_0}^{\infty} p(f, \theta_{G1}, \theta_{G2}|\ldots)df
-\end{equation}
-for a detection threshold of $f_0$.
-
-\subsection{Instantiation of Simulated Data}
-Two simulated data sets are realized.
-The generative model of the first data set (Set 1) is
- identical to the model described in \S\ref{model:sec} with the following parameter choices:
-\begin{itemize}
-\item Cosmological parameters $\Omega_M=0.28$, $w=-1$.
-\item Type~Ia supernovae with intrinsic dispersion $\sigma_{SNIa}=0.1$ mag.
-\item Non-Ia supernovae 2 magnitudes fainter than SNe~Ia with intrinsic
-dispersion $\sigma_{non-Ia}=1$ mag.
-\item $z_{max}=1.4$.
-\item $\theta_{r0}=0.95$, $\theta_{r1}=0.2$ for the relative fraction of SNe~Ia
-at $z=0$ and $z=1.1 \times z_{max}$ respectively.
-\item 2000 transients total, including discovered and non-discovered,
-in the range $0.1<z<z_{max}$.
-\item Detection threshold $f_0$ at approximately the mean brightness SN~Ia at $z=1$.
-\item Limits of neighbor-galaxy redshifts of $0.1/1.1$ and $1.1\times z_{max}$.
-\item $\pi_{host}=0.98$ for the probability of correct host-galaxy assignment.
-\item Accumulated spectra for 0\%, 20\%, 60\%, and 100\% of discovered transients.
-\end{itemize}
-
-Figures~\ref{hd:fig} and \ref{hist:fig} show
-the Hubble diagram 
-and redshift histogram for discovered SNe~Ia and non-Ia respectively
-for a realization drawn from this model.
-SNe~Ia's are shown in blue and non-Ia's in red, those that fall below detection threshold
-are transparent.  The solid points
-represent those objects spectroscopically typed for the case of 20\% follow-up.
-The green X's represent the 2\% among those without spectroscopy that
-are assigned an incorrect redshift.
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[scale=0.4]{/Users/akim/project/abc/doc/seed2.pdf}
-   \includegraphics[scale=0.4]{/Users/akim/project/abc/doc/seed2_pop2.pdf}  
-\caption{Hubble diagrams for a realization drawn from Set 1 (left)
-and Set 2 that contains  a second non-Ia population (right).
-Type~Ia's are shown in blue and non-Ia's in red, those that fall below detection threshold
-are transparent.  The green X's represent the 2\% among those without spectroscopy that
-are assigned an incorrect redshift.
-   \label{hd:fig}}
-\end{figure}
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[scale=0.4]{/Users/akim/project/abc/doc/seed2_hist.pdf}
-   \includegraphics[scale=0.4]{/Users/akim/project/abc/doc/seed2_pop2_hist.pdf}  
-\caption{Histogram of redshifts of discovered SNe~Ia and non-Ia from Set 1 (left)
-and Set 2  (right).
-   \label{hist:fig}}
-\end{figure}
-
-The generative model for the second realized data set (Set 2)
-is a perturbed version of that used to make Set 1.
-A second non-Ia population is introduced with average luminosity 0.5 mag fainter
-than the Ia's and with 0.25 mag dispersion.
-The relative rate of the original non-Ia population relative to the second is quadratic
-in redshift:
-\begin{equation}
-1 -\frac{0.8}{\left(1.1\times z_{max}\right)^2}z^2.
-\end{equation}
-A Hubble diagram realization for Set 2 is shown in Figure~\ref{hd:fig} and its redshift histogram
-is in Figure~\ref{hist:fig}.  Sets 1 and 2 are realized using the same seeds:
-The salient differences
-between the two realizations are that a fraction of non-Ia's have absolute magnitude
-based on the second population's average luminosity and intrinsic dispersion; from
-that population different transients satisfy the detection threshold; spectroscopic follow-up is redistributed
-for the new set that is detected.
-
-Sets 1 and 2 share identical discovered SNe~Ia.  For reference, this pure SN~Ia
-set is analyzed with 100\% spectroscopic typing.
-
-\subsection{Analysis Results}
-The simulated data Sets 1 and 2 are analyzed using the model described
-in \S\ref{model:sec}.  The generative model for Set 1 and the analysis model are 
-identical, but for Set 2 they differ.
-The analysis is performed using STAN 
-\citep{stan-software:2015},
-a probabilistic programming language for
-inference of Bayesian models with Hamiltonian Monte Carlo
-using the No-U-Turn sampler \citep{Homan:2014:NSA:2627435.2638586}.  Each run of the analysis
-uses 24 chains each with 1000 links.  In warmup, the first half of the links are used to
-determine parameters for the integration step size and the ``mass''
-parameters of the Hamiltonian. The complementary
-12,000 links represent draws from the model-parameter posterior.
-
-In lieu of including data of
-a pure large SN~Ia sample at low-redshift,
-priors are applied to the SN~Ia absolute magnitude and intrinsic dispersion
-\begin{align}
-\alpha_{SNIa} & \sim \mathcal{N}_{\ln}\left(\ln\left(\alpha^0_{SNIa}\right),\frac{\ln{10}}{2.5}0.02\right)\\
-\sigma_{SNIa} & \sim \mathcal{N}_{\ln}\left(\ln\left(0.1\right),0.1\right),
-\end{align}
-where $\alpha^0_{SNIa}$ is the true input luminosity.
-
-The output of the analyses are presented as contours of the model
-parameter pdf's for the case of 100\% spectroscopic
-typing in Figure~\ref{hd:fig}, and as the mean, median, and
-credible intervals of $w$ for different fractions of
-spectroscopic completeness in Table~\ref{seed2:tab}.
-For Set 1  the input parameters lie 
-within the 68\% credible intervals of the resultant posterior despite the non-trivial appearance of
-the Hubble diagram in Figure~\ref{hd:fig}.
-The decrease in spectroscopic coverage leads to shifts in $w$ of 0.04 relative to the 100\%-coverage case, which is small
-relative to the credible interval range of 0.281.  However, there is an
-increase in parameter uncertainties, going from $\Delta w= 0.281$ to 0.309
-when there is no spectroscopy; the latter is a constraining result considering that none of the
-objects are directly typed and redshifted.
-Relative to Set 1 with 100\% spectrosocopy,
-the subset of SNe~Ia-only has a shift in the mean $w$ of 0.12
-and no appreciable increase in the uncertainty of $w$.
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[scale=0.17]{/Users/akim/project/abc/results/seed2/{contour.2000.1.0}.pdf}
-   \includegraphics[scale=0.17]{/Users/akim/project/abc/results/seed2_pop2/{contour.2000.1.0}.pdf} 
-\caption{Probability distribution functions of the model parameters for the case of
- 100\% spectroscopy for Model 1 (left) and Model 2 (right).
-    Solid lines represent the input parameters.  Dashed lines in the
-   histograms are the 0.16 and 0.84 quantiles. 
-   \label{contour1:fig}}
-\end{figure}
-
-\begin{table}
-\centering
-\begin{tabular}{|c|cc|ccc|}
-\hline
-Fraction Spec&$<w>$ & $w$ median &\%-ile  &$w$ range & $\Delta w$\\ \hline
-\multicolumn{6}{|c|}{SN Ia only}\\ \hline
-$1.00$& $-0.94 \pm 0.09$ &$-0.94$ &$0.68$ & $[-1.076, -0.801]$ & $0.275$ \\
-&  &  & $0.90$ & $[-1.166, -0.718]$ & $0.448$ \\
-&  &  & $0.95$ & $[-1.208, -0.682]$ & $0.525$ \\
- \hline
-\multicolumn{6}{|c|}{Set 1}\\ \hline
-$1.00$ &$-1.06 \pm  0.09$ &$-1.05$ &$0.68$ & $[-1.196, -0.914]$ & $0.281$ \\
-&&&$0.90$ & $[-1.292, -0.826]$ & $0.466$ \\
-&&&$0.95$ & $[-1.340, -0.784]$ & $0.556$ \\
-\hline
-$0.60$ &$-1.08 \pm  0.10$ & $-1.08$ &$0.68$ & $[-1.227, -0.933]$ & $0.293$ \\
-& & &$0.90$ & $[-1.331, -0.836]$ & $0.495$ \\
-& & &$0.95$ & $[-1.385, -0.787]$ & $0.598$ \\
-\hline
-$0.20$ &$-1.10 \pm  0.10$ & $-1.09$ &$0.68$ & $[-1.249, -0.943]$ & $0.305$ \\
-& & &$0.90$ & $[-1.354, -0.851]$ & $0.502$ \\
-& & &$0.95$ & $[-1.408, -0.810]$ & $0.597$ \\
-\hline
-$0.00$ &$-1.07 \pm  0.10$ & $-1.06$ &$0.68$ & $[-1.218, -0.909]$ & $0.309$ \\
-& & &$0.90$ & $[-1.320, -0.812]$ & $0.508$ \\
-& & &$0.95$ & $[-1.372, -0.770]$ & $0.602$ \\
-\hline
-\multicolumn{6}{|c|}{Set 2}\\ \hline
-$1.00$ &$-0.94 \pm  0.09$ &$-0.94$ &$0.68$ & $[-1.078, -0.804]$ & $0.274$ \\
-&&&$0.90$ & $[-1.168, -0.720]$ & $0.447$ \\
-&&&$0.95$ & $[-1.214, -0.680]$ & $0.534$ \\
-\hline
-$0.60$ &$-1.04 \pm  0.10$ & $-1.03$ &$0.68$ & $[-1.182, -0.883]$ & $0.298$ \\
-& & &$0.90$ & $[-1.285, -0.791]$ & $0.494$ \\
-& & &$0.95$ & $[-1.332, -0.749]$ & $0.583$ \\
-\hline
-$0.20$ &$-1.10 \pm  0.10$ & $-1.09$ &$0.68$ & $[-1.247, -0.936]$ & $0.311$ \\
-& & &$0.90$ & $[-1.359, -0.840]$ & $0.518$ \\
-& & &$0.95$ & $[-1.413, -0.798]$ & $0.614$ \\
-\hline
-$0.00$ &$-1.11 \pm  0.10$ & $-1.10$ &$0.68$ & $[-1.266, -0.948]$ & $0.317$ \\
-& & &$0.90$ & $[-1.375, -0.850]$ & $0.525$ \\
-& & &$0.95$ & $[-1.428, -0.808]$ & $0.621$ \\
-\hline
-\end{tabular}
-\caption{Mean, median, and credible intervals of $w$ for the SNe~Ia only,
-Model 1, and Model 2 for varying
-fractions of spectroscopic coverage. \label{seed2:tab}}
-\end{table}
-
-The generative model for Set 2 differs from the analysis model.
-While it is expected for the input and resultant non-Ia parameters not to match, 
-when there is 100\% spectroscopic coverage the posteriors of the other
-parameters accommodate the input with the $w$ posterior matching
-closely that of the SN~Ia-only analysis.  Unlike Model~1, which exhibits no bias
-in $w$ with decreasing spectroscopy, Model~2 does have a shift in the $w$
-credible region.  
-The values of the mean and median values of
-$w$ for both 20\% and 0\% coverage are outside the 68\%
-credible region of the ideal 100\% coverage.
-The Set 2 $\Delta w$ increases quicker with decreasing spectroscopy
-relative to Set 1.
-
-These results are consistent with the trivial expectation that when generative
-and analysis models are identical statistically correct parameter determinations
-occur, and that analysis with an incorrect non-Ia model can lead to bias.
-The latter case is mitigated with complete spectroscopic typing, though then
-the non-Ia's contribute little statistically to the $w$ constraints.
+%
+%\section{Standard Candle}
+%\label{toy:sec}
+%To introduce basic model elements, this Section considers a
+%simplified view of SNe~Ia
+%as transients that are bolometric standard candles with an intrinsic random
+%dispersion
+%at peak brightness, and assumes data with negligible measurement uncertainties.
+%For convenience,
+%the transients
+%in this Section are  referred to as SNe~Ia.
+%The added complexity of correlations between absolute magnitude
+%and multi-band light curves, and measurement uncertainties
+%are discussed in
+%\S\ref{snIamodel:sec}. 
+%
+%\subsection{Base Model}
+%\label{model:sec}
+%This Section presents a model that is used both for generating simulated data, and for analysis.
+%The data used to construct a Hubble diagram and the fundamental parameters of the
+%model used to describe those data are succinctly summarized in the notation
+%for the likelihood 
+%\begin{equation}
+%p(f, {{T}}_S,{{z}}_S, G|  \Omega_M, w, \theta_r,\alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{!Ia}},\sigma_{\mathit{!Ia}}),
+%\label{likelihood:eqn}
+%\end{equation}
+%whose relations are sketched in the probabilistic graphical model in Figure~\ref{toypgm:fig}.
+%The measurements are
+%\begin{itemize}
+%\item $f$: the flux at peak brightness, taken 
+%to be bolometric to facilitate the treatment of
+%standard candles at different redshift;
+%\item ${{T}}_S$, ${{z}}_S$: the spectroscopic type and redshift available for a subset of transients;
+%\item $\theta_{G1}$, $\theta_{G2}$: the spectroscopic redshifts of the galaxies identified
+%as host and neighbor from imaging.
+%\end{itemize}
+%The model parameters are
+%\begin{itemize}
+%\item $\Omega_M$, $w$: the mass density and dark-energy equation of state parameters of a flat,
+%constant-$w$ dark-energy cosmology;
+%\item $\theta_{r1}$, $\theta_{r2}$:  the parameters
+%that describe the redshift-dependent relative fraction of SNe~Ia and non-Ia's;
+%\item $\alpha_{Ia}$, $\sigma_{Ia}$, $\alpha_{\mathit{!Ia}}$, $\sigma_{\mathit{!Ia}}$:
+%the luminosity (times $4\pi$) and intrinsic dispersion for SNe~Ia and non-Ia at peak brightness.
+%\end{itemize}
+%Not listed explicitly in Eqn.~\ref{likelihood:eqn} but shown in Figure~\ref{toypgm:fig} are latent model parameters for each transient:
+%\begin{itemize}
+%\item $z$: the cosmological redshifts of the host and neighboring galaxies;
+%\item $T$: the class of the objects, SN~Ia or non-Ia;
+%\item $L$: the luminosity of the transient.
+%\end{itemize}
+%There is a  fixed parameter
+%\begin{itemize}
+%\item $\mu$: the distance modulus given the cosmological parameters and the redshift.
+%\end{itemize}
+%
+%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+%   \centering
+%   \includegraphics[width=4.5in]{/Users/akim/project/abc/results/toy_pgm.pdf} 
+%   \caption{Probabilistic Graphical Model for the standard candle analysis. The
+%   parameters include the cosmological parameters $\Omega_M$ and $w$,
+%   the luminosities $\alpha$ and intrinsic dispersions $\sigma$ of SNe~Ia and non-Ia's,
+%   and the relative fraction parameters $\theta_{r1}$ and $\theta_{r2}$.  Latent parameters
+%   include 
+%   for each transient the type $T$ and redshifts of the host and neighboring galaxies $z$ and $z_N$.  The  distance modulus $\mu$ and
+%   luminosity $L$ are fixed by the other parameters.  The observables include the measured
+%   flux $f$, spectroscopic type and redshift $T_S$ and $z_S$, and
+%   the inferred host and neighbor redshifts $\theta_{G1}$ and $\theta_{G2}$.
+%   The host and neighbor galaxies of all transients are inferred based a common galaxy catalog, 
+%   and so strictly are not independent from supernova to supernova.
+%   \label{toypgm:fig}}
+%\end{figure}
+%
+%
+%The transients being analyzed have passed some detection threshold
+%and thus are drawn from
+%distributions that have different shapes than the underlying population of both discovered and
+%non-discovered objects. A  threshold flux of $f_0$ is adopted for the detection criterion.
+%Otherwise, no other sample-selection criteria are assumed.
+%
+%\subsubsection{Likelihood for the {\it obs} set data}
+%\label{obs:sec}
+%The likelihood of data from the {\it obs} set, which has
+%spectroscopic observations $T_S$ and redshift
+%$z_S$, is described as follow.  The likelihood is
+%\begin{align}
+%p(f, {{T}}_S,{{z}}_S|  \Omega_M, w, \theta_r,\alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{!Ia}},\sigma_{\mathit{!Ia}}, z)  &=\sum_T
+%p(f, {{T}}_S,{{z}}_S, T| \ldots)\\
+%&= \sum_T 
+%p(f, {{T}}_S,{{z}}_S| T,\dots) p(T | \ldots).
+%\end{align}
+%
+%Direct associations between model and spectroscopic redshift and type are made
+%\begin{align}
+%p(z_S|z) &= \delta(z_S-z)\\
+%p(T_S|T) &= \delta(T_S-T),
+%\label{specz:eqn}
+%\end{align}
+%so that
+%\begin{align}
+%p(f, {{T}}_S,{{z}}_S|  \ldots) &= 
+%p(f| T=T_S, z=z_s,\dots) p(T_S|z=z_s, \ldots).
+%\label{obs:eqn}
+%\end{align}
+%
+%
+%The first term describes the expected counts. Given the redshift
+%and transient type, the brightness of the underlying population
+%is modeled as being drawn from a standard candle
+%with mean luminosity $4\pi\alpha_X$ and a normal distribution in magnitude
+%space with intrinsic dispersion  $\sigma_X$:
+%\begin{equation}
+%f| T=T_S, z=z_S, \Omega_M, w, \theta_r, \alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{!Ia}},\sigma_{\mathit{!Ia}} \sim \mathcal{N}_{\ln}\left(\ln{\left(\frac{\alpha_{T_S}}{d_L^2(z_S;\Omega_M, w)}\right)}, \frac{\ln{10}}{2.5}\sigma_{T_S}\right),
+%\label{flux:eqn}
+%\end{equation}
+%where $\mathcal{N}_{\ln}$ is the log-normal distribution and $d_L$ is the luminosity distance.
+%Measurement uncertainty is taken to be negligible.
+%In a flux-limited survey, the pdf's for the data are truncated versions of the underlying
+%pdf's.
+%\begin{itemize}
+%\item For SNe~Ia  $T_S=1$:
+%\begin{equation}
+%f | T=1, z=z_S, \Omega_M, w, \alpha_{Ia},\sigma_{Ia} \sim
+%\frac{\mathcal{N}_{\ln}\left(\ln{\left(\frac{\alpha_{Ia}}{d_L^2(z_S;\Omega_M, w)}\right)}, \frac{\ln{10}}{2.5}\sigma_{Ia}\right)}{P_{Ia}(f > f_0)}.
+%\label{adusnIa:eqn}
+%\end{equation}
+%\item For non-Ia's in set $T_S=0$:
+%\begin{equation}
+%f | T=0, z=z_S, \Omega_M, w, \alpha_{\mathit{!Ia}},\sigma_{\mathit{!Ia}}\sim 
+%\frac{\mathcal{N}_{\ln}\left(\ln{\left(\frac{\alpha_{\mathit{!Ia}}}{d_L^2(z_S;\Omega_M, w)}\right)}, \frac{\ln{10}}{2.5}\sigma_{\mathit{!Ia}}\right)}{P_{!Ia}(f > f_0)},
+%\label{adunonIa:eqn}
+%\end{equation}
+%\end{itemize}
+%where the normalization factor is the complementary cumulative distribution function
+%for the corresponding log-normal distribution that accounts for the truncated
+%distribution of the detected sample.
+%It is understood implicitly that as all objects must pass the detection threshold,
+%the case of $f<f_0$ is never confronted in the analysis.
+%
+%The second term gives the type probability. In our model,
+%the underlying relative rates between SNe~Ia and non-Ia are linear in redshift,
+% parameterized by the
+%its values at $z=0$ and $1.1 \times z_{max}$, 
+%\begin{equation}
+%\hat{\theta}_r=\theta_{r0}+z\left(\frac{\theta_{r1}-\theta_{r0}}{1.1 \times z_{max}}\right).
+%\label{rate:eqn}
+%\end{equation}
+%The relative rate for SN~Ia discovery for the discovered (truncated) distribution is
+%\begin{equation}
+%\theta_r=\frac{\hat{\theta}_rP_{Ia}(f > f_0)}{\hat{\theta}_{r}P_{Ia}(f > f_0) + (1-\hat{\theta}_{r})P_{!Ia}(f > f_0)}.
+%\end{equation}
+%The spectroscopic classifications are drawn from
+%\begin{equation}
+%T_S | z=z_S, \Omega_M, w, \theta_{r0}, \theta_{r1} , \alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{!Ia}},\sigma_{\mathit{!Ia}} \sim \text{Bernoulli}(\theta_r).
+%\end{equation}
+%Although the underlying type distribution depends only on $ \theta_{r0}$ and $ \theta_{r1}$,  
+%the observed distribution does depend on the other parameters through $\theta_r$'s dependence on
+%the two normalization factors
+%$P_{X}(f > f_0)$.
+%
+%%The third term is the redshift distribution of transient discoveries.
+%%The model takes an underlying redshift distribution of transients in the universe
+%%\begin{equation}
+%%p(z) \propto z^2.
+%%\end{equation}
+%%The redshift distribution of discovered transients is then
+%%\begin{equation}
+%%p(z) = \frac{z^2\left(\hat{\theta}_{r}P_{Ia}(f > f_0) + (1-\hat{\theta}_{r})P_{non-Ia}(f > f_0)
+%%\right)}{\int_{z_{min}}^{z_{max}} dz'\, z'^2\left( 
+%%\hat{\theta}_{r}P_{Ia}(f > f_0) + (1-\hat{\theta}_{r})P_{non-Ia}(f > f_0)
+%%\right)}.
+%%\end{equation}
+%
+%
+%\subsubsection{Likelihood for the {\it mis} set data}
+%
+%Transients in the {\it mis}
+%set have no spectroscopic confirmation, and their data are treated as follows:
+%With no redshift from the transient itself, 
+%the redshift measurement is inferred from potential host galaxies.
+%In this Section, each transient is associated with two galaxies, one 
+%with redshift $\theta_{G1}$
+%that has high probability $\pi_{host}$
+%of being the host and the other
+%with redshift $\theta_{G2}$ that has probability $(1-\pi_{host})$.
+%In the model, the
+%true host redshift is $z$ and that of the interloping galaxy is $z_N$.
+%The likelihood for the galaxy redshifts is
+%\begin{equation}
+%P(\theta_{G1},\theta_{G2}|z, z_N) =
+%	\pi_{host}\delta(z-\theta_{G1})\delta(z_N-\theta_{G2}) +
+%	(1-\pi_{host}) \delta(z-\theta_{G2})\delta(z_N-\theta_{G1}).
+%\end{equation}
+%As with the transients, the redshifts of the host
+% and neighbor galaxies are drawn from underlying distributions $p(z) \propto z^2$, $p(z_N) \propto z^2_N$.
+%
+%
+%The distribution of the underlying distribution is 
+%\begin{multline}
+%p(f, \theta_{G1}, \theta_{G2} | \Omega_M, w, \theta_r, \alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{!Ia}},\sigma_{\mathit{!Ia}}, z, z_N)  \\
+%= \sum_{T} p(f, \theta_{G1}, \theta_{G2}| T, \ldots)P(T| \ldots)\\
+% =\sum_{T} p(f| T, \ldots)p(\theta_{G1}, \theta_{G2}| T, \ldots) P(T| \ldots) \\
+%= \sum_{T} \pi_{host} p(f| T, z=\theta_{G1} ,z_N=\theta_{G2}, \ldots) P(T| z=\theta_{G1}, ,z_N=\theta_{G2}, \ldots)  \\
+% +  (1-\pi_{host}) p(f| T, z=\theta_{G2}, z_N=\theta_{G1}, \ldots) P(T| z=\theta_{G2}, z_N=\theta_{G1}, \ldots).
+%\label{adumis:eqn}
+%\end{multline}
+%The probabilities  for the underlying flux and
+%relative rate distributions
+% Eqns.~\ref{flux:eqn} and \ref{rate:eqn} introduced in \S\ref{obs:sec} apply.
+%
+%The data likelihood is a truncated version of the
+%underlying distribution: the distribution in  Eqn.~\ref{adumis:eqn} normalized by
+%the complementary cumulative distribution function
+%\begin{equation}
+%p(f>f_0, \theta_{G1}, \theta_{G2}|\ldots) = \int_{f_0}^{\infty} p(f, \theta_{G1}, \theta_{G2}|\ldots)df
+%\end{equation}
+%for a detection threshold of $f_0$.
+%
+%\subsection{Instantiation of Simulated Data}
+%Two simulated data sets are realized.
+%The generative model of the first data set (Set 1) is
+% identical to the model described in \S\ref{model:sec} with the following parameter choices:
+%\begin{itemize}
+%\item Cosmological parameters $\Omega_M=0.28$, $w=-1$.
+%\item Type~Ia supernovae with intrinsic dispersion $\sigma_{SNIa}=0.1$ mag.
+%\item Non-Ia supernovae 2 magnitudes fainter than SNe~Ia with intrinsic
+%dispersion $\sigma_{!Ia}=1$ mag.
+%\item $z_{max}=1.4$.
+%\item $\theta_{r0}=0.95$, $\theta_{r1}=0.2$ for the relative fraction of SNe~Ia
+%at $z=0$ and $z=1.1 \times z_{max}$ respectively.
+%\item 2000 transients total, including discovered and non-discovered,
+%in the range $0.1<z<z_{max}$.
+%\item Detection threshold $f_0$ at approximately the mean brightness SN~Ia at $z=1$.
+%\item Limits of neighbor-galaxy redshifts of $0.1/1.1$ and $1.1\times z_{max}$.
+%\item $\pi_{host}=0.98$ for the probability of correct host-galaxy assignment.
+%\item Accumulated spectra for 0\%, 20\%, 60\%, and 100\% of discovered transients.
+%\end{itemize}
+%
+%Figures~\ref{hd:fig} and \ref{hist:fig} show
+%the Hubble diagram 
+%and redshift histogram for discovered SNe~Ia and non-Ia respectively
+%for a realization drawn from this model.
+%SNe~Ia's are shown in blue and non-Ia's in red, those that fall below detection threshold
+%are transparent.  The solid points
+%represent those objects spectroscopically typed for the case of 20\% follow-up.
+%The green X's represent the 2\% among those without spectroscopy that
+%are assigned an incorrect redshift.
+%
+%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+%   \centering
+%   \includegraphics[scale=0.4]{/Users/akim/project/abc/doc/seed2.pdf}
+%   \includegraphics[scale=0.4]{/Users/akim/project/abc/doc/seed2_pop2.pdf}  
+%\caption{Hubble diagrams for a realization drawn from Set 1 (left)
+%and Set 2 that contains  a second non-Ia population (right).
+%Type~Ia's are shown in blue and non-Ia's in red, those that fall below detection threshold
+%are transparent.  The green X's represent the 2\% among those without spectroscopy that
+%are assigned an incorrect redshift.
+%   \label{hd:fig}}
+%\end{figure}
+%
+%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+%   \centering
+%   \includegraphics[scale=0.4]{/Users/akim/project/abc/doc/seed2_hist.pdf}
+%   \includegraphics[scale=0.4]{/Users/akim/project/abc/doc/seed2_pop2_hist.pdf}  
+%\caption{Histogram of redshifts of discovered SNe~Ia and non-Ia from Set 1 (left)
+%and Set 2  (right).
+%   \label{hist:fig}}
+%\end{figure}
+%
+%The generative model for the second realized data set (Set 2)
+%is a perturbed version of that used to make Set 1.
+%A second non-Ia population is introduced with average luminosity 0.5 mag fainter
+%than the Ia's and with 0.25 mag dispersion.
+%The relative rate of the original non-Ia population relative to the second is quadratic
+%in redshift:
+%\begin{equation}
+%1 -\frac{0.8}{\left(1.1\times z_{max}\right)^2}z^2.
+%\end{equation}
+%A Hubble diagram realization for Set 2 is shown in Figure~\ref{hd:fig} and its redshift histogram
+%is in Figure~\ref{hist:fig}.  Sets 1 and 2 are realized using the same seeds:
+%The salient differences
+%between the two realizations are that a fraction of non-Ia's have absolute magnitude
+%based on the second population's average luminosity and intrinsic dispersion; from
+%that population different transients satisfy the detection threshold; spectroscopic follow-up is redistributed
+%for the new set that is detected.
+%
+%Sets 1 and 2 share identical discovered SNe~Ia.  For reference, this pure SN~Ia
+%set is analyzed with 100\% spectroscopic typing. 
+%
+%
+%\subsection{Analysis Results}
+%The simulated data Sets 1 and 2 are analyzed using the model described
+%in \S\ref{model:sec}.  The generative model for Set 1 and the analysis model are 
+%identical, but for Set 2 they differ.
+%The analysis is performed using STAN 
+%\citep{stan-software:2015},
+%a probabilistic programming language for
+%inference of Bayesian models with Hamiltonian Monte Carlo
+%using the No-U-Turn sampler \citep{Homan:2014:NSA:2627435.2638586}.  Each run of the analysis
+%uses 24 chains each with 1000 links.  In warmup, the first half of the links are used to
+%determine parameters for the integration step size and the ``mass''
+%parameters of the Hamiltonian. The complementary
+%12,000 links represent draws from the model-parameter posterior.
+%
+%In lieu of including data of
+%a pure large SN~Ia sample at low-redshift,
+%priors are applied to the SN~Ia absolute magnitude and intrinsic dispersion
+%\begin{align}
+%\alpha_{SNIa} & \sim \mathcal{N}_{\ln}\left(\ln\left(\alpha^0_{SNIa}\right),\frac{\ln{10}}{2.5}0.02\right)\\
+%\sigma_{SNIa} & \sim \mathcal{N}_{\ln}\left(\ln\left(0.1\right),0.1\right),
+%\end{align}
+%where $\alpha^0_{SNIa}$ is the true input luminosity.
+%
+%The output of the analyses are presented as contours of the model
+%parameter pdf's for the case of 100\% spectroscopic
+%typing in Figure~\ref{hd:fig}, and as the mean, median, and
+%credible intervals of $w$ for different fractions of
+%spectroscopic completeness in Table~\ref{seed2:tab}.
+%For Set 1  the input parameters lie 
+%within the 68\% credible intervals of the resultant posterior despite the non-trivial appearance of
+%the Hubble diagram in Figure~\ref{hd:fig}.
+%The decrease in spectroscopic coverage leads to shifts in $w$ of 0.04 relative to the 100\%-coverage case, which is small
+%relative to the credible interval range of 0.281.  However, there is an
+%increase in parameter uncertainties, going from $\Delta w= 0.281$ to 0.309
+%when there is no spectroscopy; the latter is a constraining result considering that none of the
+%objects are directly typed and redshifted.
+%Relative to Set 1 with 100\% spectrosocopy,
+%the subset of SNe~Ia-only has a shift in the mean $w$ of 0.12
+%and no appreciable increase in the uncertainty of $w$.
+%
+%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+%   \centering
+%   \includegraphics[scale=0.17]{/Users/akim/project/abc/results/seed2/{contour.2000.1.0}.pdf}
+%   \includegraphics[scale=0.17]{/Users/akim/project/abc/results/seed2_pop2/{contour.2000.1.0}.pdf} 
+%\caption{Probability distribution functions of the model parameters for the case of
+% 100\% spectroscopy for Model 1 (left) and Model 2 (right).
+%    Solid lines represent the input parameters.  Dashed lines in the
+%   histograms are the 0.16 and 0.84 quantiles. 
+%   \label{contour1:fig}}
+%\end{figure}
+%
+%\begin{table}
+%\centering
+%\begin{tabular}{|c|cc|ccc|}
+%\hline
+%Fraction Spec&$<w>$ & $w$ median &\%-ile  &$w$ range & $\Delta w$\\ \hline
+%\multicolumn{6}{|c|}{SN Ia only}\\ \hline
+%$1.00$& $-0.94 \pm 0.09$ &$-0.94$ &$0.68$ & $[-1.076, -0.801]$ & $0.275$ \\
+%&  &  & $0.90$ & $[-1.166, -0.718]$ & $0.448$ \\
+%&  &  & $0.95$ & $[-1.208, -0.682]$ & $0.525$ \\
+% \hline
+%\multicolumn{6}{|c|}{Set 1}\\ \hline
+%$1.00$ &$-1.06 \pm  0.09$ &$-1.05$ &$0.68$ & $[-1.196, -0.914]$ & $0.281$ \\
+%&&&$0.90$ & $[-1.292, -0.826]$ & $0.466$ \\
+%&&&$0.95$ & $[-1.340, -0.784]$ & $0.556$ \\
+%\hline
+%$0.60$ &$-1.08 \pm  0.10$ & $-1.08$ &$0.68$ & $[-1.227, -0.933]$ & $0.293$ \\
+%& & &$0.90$ & $[-1.331, -0.836]$ & $0.495$ \\
+%& & &$0.95$ & $[-1.385, -0.787]$ & $0.598$ \\
+%\hline
+%$0.20$ &$-1.10 \pm  0.10$ & $-1.09$ &$0.68$ & $[-1.249, -0.943]$ & $0.305$ \\
+%& & &$0.90$ & $[-1.354, -0.851]$ & $0.502$ \\
+%& & &$0.95$ & $[-1.408, -0.810]$ & $0.597$ \\
+%\hline
+%$0.00$ &$-1.07 \pm  0.10$ & $-1.06$ &$0.68$ & $[-1.218, -0.909]$ & $0.309$ \\
+%& & &$0.90$ & $[-1.320, -0.812]$ & $0.508$ \\
+%& & &$0.95$ & $[-1.372, -0.770]$ & $0.602$ \\
+%\hline
+%\multicolumn{6}{|c|}{Set 2}\\ \hline
+%$1.00$ &$-0.94 \pm  0.09$ &$-0.94$ &$0.68$ & $[-1.078, -0.804]$ & $0.274$ \\
+%&&&$0.90$ & $[-1.168, -0.720]$ & $0.447$ \\
+%&&&$0.95$ & $[-1.214, -0.680]$ & $0.534$ \\
+%\hline
+%$0.60$ &$-1.04 \pm  0.10$ & $-1.03$ &$0.68$ & $[-1.182, -0.883]$ & $0.298$ \\
+%& & &$0.90$ & $[-1.285, -0.791]$ & $0.494$ \\
+%& & &$0.95$ & $[-1.332, -0.749]$ & $0.583$ \\
+%\hline
+%$0.20$ &$-1.10 \pm  0.10$ & $-1.09$ &$0.68$ & $[-1.247, -0.936]$ & $0.311$ \\
+%& & &$0.90$ & $[-1.359, -0.840]$ & $0.518$ \\
+%& & &$0.95$ & $[-1.413, -0.798]$ & $0.614$ \\
+%\hline
+%$0.00$ &$-1.11 \pm  0.10$ & $-1.10$ &$0.68$ & $[-1.266, -0.948]$ & $0.317$ \\
+%& & &$0.90$ & $[-1.375, -0.850]$ & $0.525$ \\
+%& & &$0.95$ & $[-1.428, -0.808]$ & $0.621$ \\
+%\hline
+%\end{tabular}
+%\caption{Mean, median, and credible intervals of $w$ for the SNe~Ia only,
+%Model 1, and Model 2 for varying
+%fractions of spectroscopic coverage. \label{seed2:tab}}
+%\end{table}
+%
+%The generative model for Set 2 differs from the analysis model.
+%While it is expected for the input and resultant non-Ia parameters not to match, 
+%when there is 100\% spectroscopic coverage the posteriors of the other
+%parameters accommodate the input with the $w$ posterior matching
+%closely that of the SN~Ia-only analysis.  Unlike Model~1, which exhibits no bias
+%in $w$ with decreasing spectroscopy, Model~2 does have a shift in the $w$
+%credible region.  
+%The values of the mean and median values of
+%$w$ for both 20\% and 0\% coverage are outside the 68\%
+%credible region of the ideal 100\% coverage.
+%The Set 2 $\Delta w$ increases quicker with decreasing spectroscopy
+%relative to Set 1.
+%
+%These results are consistent with the trivial expectation that when generative
+%and analysis models are identical statistically correct parameter determinations
+%occur, and that analysis with an incorrect non-Ia model can lead to bias.
+%The latter case is mitigated with complete spectroscopic typing, though then
+%the non-Ia's contribute little statistically to the $w$ constraints. 
+%
+%
 

### 2015-10-20 src/hd_pgm.py

@@ -6,49 +6,50 @@ rc("font", family="serif", size=12)
 rc("text", usetex=True)
 
 
-pgm = PGM([9.5, 6.5], origin=[0., 0.2], observed_style='inner')
+pgm = PGM([8.5, 6.5], origin=[0., 0.2], observed_style='inner')
 
-pgm.add_node(Node('dispersion',r"\center{$\sigma_{Ia}$ \newline $\sigma_{non-Ia}$}", 1,6,scale=1.2,aspect=1.8))
-pgm.add_node(Node('rate',r"$\theta_r$",2,6))
-pgm.add_node(Node('theta_T',r"\center{$\alpha_{Ia}$, $\alpha_{non-Ia}$ \newline $\beta_{Ia}$, $\beta_{non-Ia}$}", 4,6,scale=1.4,aspect=1.8))
+#pgm.add_node(Node('dispersion',r"\center{$\sigma_{Ia}$ \newline $\sigma_{!Ia}$}", 1,6,scale=1.2,aspect=1.8))
+pgm.add_node(Node('rate',r"$r$",2,6))
+#pgm.add_node(Node('theta_T',r"\center{$\alpha_{Ia}$, $\alpha_{!Ia}$ \newline $\beta_{Ia}$, $\beta_{!Ia}$}", 4,6,scale=1.4,aspect=1.8))
+pgm.add_node(Node('theta_T',r"\center{$\Theta_{Ia}$ \newline $\Theta_{!Ia}$}", 4,6,scale=1.5,aspect=1.2))
 pgm.add_node(Node('mu',r"$\Omega_M$, $w$", 5,6, scale=1.4))
 pgm.add_node(Node('Transmission',r"$Z$", 7, 6))
 
 pgm.add_node(Node('G_i',r"$g_i$", 3,5))
-pgm.add_node(Node('G_Ni',r"$g_{Ni}$", 8,5))
+#pgm.add_node(Node('G_Ni',r"$g_{Ni}$", 8,5))
 
-pgm.add_node(Node('theta_Ti',r"\center{$\theta_{Ia,i}$ \newline $\theta_{non-Ia,i}$}", 1,4,scale=1.5,aspect=1.2))
+pgm.add_node(Node('theta_Ti',r"\center{$\theta_{Ia,i}$ \newline $\theta_{!Ia,i}$}", 1,4,scale=1.5,aspect=1.2))
 pgm.add_node(Node('Type',r"$T_i$", 2, 4))
[…]

### 2015-10-22 doc/article.tex
new version

@@
 
-%SNe~Ia are not perfect standard candles but rather are calibrated candles whose
-%peak brightnesses are a
-%function of their internal properties discerned from their colors and light-curve evolution.
-%Measurement uncertainty, particularly from photometric flux
-%calibration and galaxy photometric redshifts, can play an important role in the statistical
-%reach of experiments. 
-The notation for the likelihood presents the data and fundamental model parameters
-\begin{multline}
-\sum_T \int d\theta_{Ia}\, d\theta_{!Ia}\, dL\, p(n, {{T}}_S,{{z}}_S, \theta_{S}, G | T, \theta_{Ia},
-\theta_{!Ia}, L, \mathcal{S}, \Omega_M, w, r, \Theta_{Ia}, \Theta_{\mathit{!Ia}}, Z, g) \\
-p(L|T, \theta_{Ia},
-\theta_{!Ia},  \mathcal{S}, \Omega_M, w, r, \Theta_{Ia},\Theta_{\mathit{!Ia}}, Z, g)
-p(T, \theta_{Ia},
-\theta_{!Ia}|  \mathcal{S}, \Omega_M, w, r, \Theta_{Ia},\Theta_{\mathit{!Ia}}, Z, g),
-\label{likelihood2:eqn}
-\end{multline}
-whose relations are sketched in the probabilistic graphical model in Figure~\ref{pgm:fig}.
-$\mathcal{S}$ indicates that this likelihood corresponds to the analysis sample. 
-For shorthand we asign $A=\{n, {{T}}_S,{{z}}_S, \theta_{S}, G \}$, $B=\{T, \theta_{Ia},
-\theta_{!Ia}, L\}$, and $C=\{\Omega_M, w, r, \Theta_{Ia}, \Theta_{\mathit{!Ia}}, Z, \}$
-so that the likelihood is more compactly expressed as $\int dB\, p(AB| \mathcal{S}, C)p(B| \mathcal{S}, C)$.
+The Probabilistic Graphical Model is shown in Figure~\ref{pgm:fig}. The underlying behavior of the universe is described by the following elements:
+\begin{description}
+\item [Cosmology] Luminosity distance for the cosmological model being considered,
+e.g.\ a $wCDM$ universe parameterized by $\Omega_M$, $\Omega_w$, $w_0$, $w_a$.
+\item[SNe~Ia, Non-Ia Populations] Time-dependent luminosity for all transient populations
+that may enter
+the analysis.  The SALT2 model is a candidate for SNe~Ia, with parameters $\alpha$, $\beta$,
+and pdf's for $x_1$ and $c$.  The PSNID treatment of non-Ia's is a candidate for the other
+transients.
+\item [Relative Rates] Relative rates of all the transients populations under consideration.  The
+model could be extended to measure absolute rates, but that is unnecessary if
+the cosmological parameters are the goal.
+\end{description}
+Each transient is described by the following elements:
+\begin{description}
+\item[Host Galaxy] The host galaxy, or more generally for the case of hostless supernovae,
+the environment from which the transient arises.  The host is described by its redshift
+and parameters that may be correlated with Hubble diagram residuals, such as mass,
+specific star formation rate, metallicity.
+\item[Type Subtype] Specification of the the transient: which population to which it belongs
+and its internal parameters.  For example, an object could be SN~Ia with specific
+values for its SALT2 parameters $c$, $x_1$, $t_0$ and its realization
+from the error snake.  This dependent on the relative rates and
+its host galaxy including redshift.
+\item[Distance] Distance modulus or equivalently the luminosity distance of the host galaxy,
+which in our model corresponds to the cosmological redshift of the transient.  The value
+is fixed based on the cosmological model and redshift.
+\end{description}
+The individual photometric measurements of a transient are described by the following
+elements:
+\begin{description}
+\item[Luminosity]  Luminosity as a function of wavelength
+corresponding to the date of observation.   This depends on the population, type,
+and subtype.  Given evidence for correlations between host properties and Hubble
+residuals, a direction connection between host galaxy and luminosity is made.
+\item[Flux] Flux of the transient incident to earth at the date of observation.  It is 
+fixed based on the luminosity, redshift, and distance.
+\end{description}
+The observatory is described by the following element:
+\begin{description}
+\item[Throughput] The transmission function for the band at that date appropriate
+for the transient.  A simple parameterization could be calibration zeropoints; more
+sophisticated descriptions can vary the shape, not only the normalization, of the
+transmission.
+\end{description}
+The data subscripted by ``o'' are
+\begin{description}
+\item[$\text{Photometry}_o$] Photometric flux measurement.  The expected measurement
+is the incident flux integrated over the throughput.  Typically the measurement
+uncertainties are from a Poisson distribution.  In practice, photometric data extraction
+is performed in an independent analysis that isolates the transient flux
+from contaminating background light. 
+\item[$\text{Type Subtype}_o$] Measurement of the intrinsic transient type.  This is done
+through spectroscopy.
+\item[$\text{Redshift}_o$] Measurement of the host redshift.  The redshift can be
+spectroscopic or photometric.  Uncertain host galaxy identification contribute
+to measurement errors.
+\item[$\text{Host Properties}_o$] Measurement of the host properties such
+as mass, sSFR, metallicity. Uncertain host galaxy identification contribute
+to measurement errors.
+\end{description}
 
@@
    The forward modeling
-   flow goes from left to right, starting with the description of the universe, observatory,
-   and data.    A transient has host galaxy $g_i$, which determines its redshift $z_i$
-   and galaxy parameters $\theta_{gi}$.
-   A model with parameters $\theta_\mu$ fix the distance modulus $\mu_i$.
-   The transient type $T$ depends on the host-galaxy parameters  $\theta_{gi}$
-   and rates $r$.   The transient
-   parameters $\theta_T^X$, $\theta_{Ti}^X$ (and perhaps the host galaxy) determine the luminosity $L$.       The 
-   incoming photon flux $n$, $n_g$  are then fixed
-   with redshift and distance modulus.
-   The instrumental transmission function $\phi$ is calibrated with data ${Z}$ andflux
-   gives the expected
-   counts $\overline{f}$, $\overline{f}_g$. 
-   The transient has realized light curves ($n$) and passes selection criteria
-   through $\tau_i$ to be included in the sample.  Some transients have spectral data
-   ${X}_S$.  The properties of the galaxy identified as the host galaxy is $G$. 
+   flow goes from top to bottom, starting with the description of the universe, observatory,
+   and data.    A transient occurs in host galaxy $g_i$.  The type $T$ depends on the
+   host and relative rates $r$.  The transient parameters $\theta$ depend on the
+   transient model $\Theta$ and the host.  The luminosity $L$ depends on the preceding
+   parameters.  
+   A model with parameters $\Omega_M$ and $w$ fix the distance modulus $\mu_i$.
+   The 
+   incoming photon flux $f$  are then fixed
+   with host redshift and distance modulus.
+   The measured light curve depends on the instrumental throughput $Z$.  There are
+   spectroscopic
+   measurements $\theta_S$, $T_S$, $z_S$ of the transient parameters, type, and
+   redshift.  $G$ is the determination of the host galaxy from photometric data.
    \label{pgm:fig}}
@@
 
-The measurements are
+This hierarchical model has several features worth noting.  Transients with and without
+spectroscopic classification are treated together: those with classification help constrain
+the properties of the underlying population to inform the treatment of those without.
+Photometric classification is treated internally, through the
+latent Type.  The system throughput is treated as a probabilistic variable
+allowing for self-calibration; this could be omitted from the model with calibration applied
+to the Photometry measurements.  Host-galaxy misclassification enters as measurement
+uncertainties.  Malmquist bias and other selection effects do not appear explicitly, but are accounted
+for in the likelihoods.  The model could be extended to include summary statistics,
+for example the results of an external supernova classifier; the use
+of summary statistics would affect the manner in which the model is evaluated
+due to our inability to write their likelihoods.
+
+\subsection{Sample Selection}
+The transients that enter the analysis satisfy some selection criteria.  Trivially, they
+have to be discovered in the first place and often more stringent photometric signal-to-noise
+requirements are applied.  Additionally, the probability for a transient to have successful
+spectroscopy may depend on parameters.
+These criteria have not yet been determined/selected
+(Argonne for photometry, OzDES/Ryan for spectroscopy are candidates to do this);
+presented here is a sketch of the likelihood calculation for a reasonable
+photometric selection criterion.
+
+For each transient $\nu$, the criterion is to have $\ge N$ photometric points
+above a signal-to-noise threshold given $M_\nu$ available measurements:
+every photometric point is associated with a flux threshold that it either passes
+or fails.  Given a total $M=\sum_\nu M_\nu$ data points, there are
+$2^M$ possible combinations
+of passing or failing theshold, of which only
+$\prod_\nu \sum_{k=N}^{M_{\nu}} \binom{M_{\nu}}{k}$  combinations would lead to
+the inclusion of the transients in the sample.
+
+The probability distribution function for all possible data realizations can be written
+as the sum of the pdf's of all possible permutations
+\begin{equation}
+p(data|model) = \sum_{k=1}^{2^M} p(data, b_k| model),
+\label{likelihood_u:eqn}
+\end{equation}
+where $b$ contains all possible combinations.
+The probability distribution function for all possible data realizations that pass
+our selection criteria is a conditional pdf. It is proportional to the underlying
+pdf after removal of conditions that are not achieved, i.e.\ removal from the sum
+in Eqn.~\ref{likelihood_u:eqn} of all combinations that do not meet the sample
+selection criteria. This leaves a reduced set $b$ of
+possible permutations
+\begin{equation}
+\mathcal{L}(data|\mathcal{S}, model) \propto \sum_{k=1}^{\prod_\nu \sum_{k=N}^{M_{\nu}} \binom{M_{\nu}}{k}} p(data, b_k| model),
+\end{equation}
+where $\mathcal{S}$ is the sample-selection condition.
+
+The probability for the data to be in a specific configuration $b_k$ of
+being below or above flux threshold is expressed
+as
+\begin{equation}
+p(data, b_k| model)  = \epsilon(Photometry_o, b_k)p(data| model)\\
+\end{equation}
+where
+\begin{equation}
+\epsilon(Photometry_o; b_{k})= \prod_{\nu i}\mathcal{H}\left((-1)^{b_{k\nu i}+1}(Photometry_{o,k\nu i}-Threshold_{\nu i})\right),
+\end{equation}
+where $\mathcal{H}$ is the Heaviside step function; when $b_{k\nu i}=1/0$ the step in the efficiency
+is up/down.  The indices correspond to configuration $k$,
+transient $\nu$, and photometric point $i$.
+
+Assembling this together, the likelihood is
+\begin{equation}
+\mathcal{L}(data|\mathcal{S}, model) = \frac{\sum_{k=1}^{\prod_\nu \sum_{k=N}^{M_{\nu}} \binom{M_{\nu}}{k}} \epsilon(Photometry_o, b_k)p(data| model)}{\int ddata\,
+\sum_{k=1}^{\prod_\nu \sum_{k=N}^{M_{\nu}} \binom{M_{\nu}}{k}} \epsilon(Photometry_o, b_k)p(data| model)
+}
+\end{equation}
+where the normalizing factor is included explicitly as a reminder that it has 
+parameter dependence and must not be neglected in calculations.
+
+Consider the traditional case of Malmquist bias of a single object,
+where a single measurement has
+to be above flux threshold.  For the underlying distribution with no flux threshold there
+are $2^1=2$ possible configurations, the flux is either above or below threshold.  For
+the sample distribution, there is $\binom{1}{1}=1$ possible configuration: the flux
+is above threshold.   The likelihood for the measured flux is the truncated version
+of the underlying distribution.
+
+For the case of a single object with two measurements and a single threshold requirement,
+there are $2^2=4$ possible configurations of which $\sum_{k=1}^{2} \binom{2}{k}=3$
+would allow sample selection, the exception being when both measurements fall below threshold.
+The likelihood for each flux is composed from
+the sum of three truncated distributions of which one accepts faint fluxes,
+resulting in resultant likelihoods that do not fall to zero below detection threshold.
+
+\subsection{Underlying Likelihood}
+The likelihood of the analysis sample is calculated from the underlying pdf of data.  Based on Figure~\ref{pgm:fig},
+\begin{align}
+p(data|model) &=\int dType\, dLuminosity\, p(Photometry_o |  Luminosity, Cosmology,Host,Throughput)  \nonumber\\
+& p(Luminosity| Type
+, Host, Population) p(Type | Rates, Host)  \nonumber\\
+& \times \int dType\, p(Type_0|Type) p(Type|Rates, Host) \nonumber \\
+& \times p(Redshift_o, Host_o| Host)
+\label{like:eqn}
+\end{align}
+where $data=\{Photometry_o, Type_o, Redshift_o, Host_o\}$,
+$model=\{Cosmology, Populations, Rates\}$, and we anticipate the independence
+of photometric and spectroscopic typing measurements.
+
+Now for specificity candidate models for the pdf's that enter Eqn.~\ref{like:eqn}
+are presented.
 \begin{itemize}
-\item $n$: the measured counts for each photometric observation for all transients in the sample;
-\item ${{T}}_S$, ${{z}}_S$, $\theta_S$: the spectroscopic type, redshift, and transient parameters available for a subset of transients;
-\item $G$: measured properties of the galaxy identified
-as the host.
-\end{itemize}
-The top-level model parameters are
-\begin{itemize}
-\item $\Omega_M$, $w$: the mass density and dark-energy equation of state parameters of a flat,
-constant-$w$ dark-energy cosmology;
-\item $r$:  the parameters
-that describe the redshift-dependent relative fraction of SNe~Ia and non-Ia's;
-\item $\Theta_{Ia}$, $\Theta_{\mathit{!Ia}}$:  All the fundamental parameters used to describe
-the SN~Ia and non-Ia populations respectively, such as the mean
-absolute magnitude, intrinsic magnitude dispersion, the distribution of internal parameters
-(i,e,\ the distributions of SALT2's $x_1$ and $c$), the relationship between internal
-parameters and magnitude (i.e.\ SALT2's $\alpha$, $\beta$);
-\item $Z$: the parameters that describe the transmission functions, i.e.\ photometric calibration;
-\item $g$: the parameters that describe the candidate host and neighbor galaxies
-including redshift $g_z$.
-\end{itemize}
-The second-level parameters are
-\begin{itemize}
-%\item $z$: the cosmological redshifts of the host and neighboring galaxies;
-\item $T$: the class of the objects, SN~Ia or non-Ia;
-\item $\theta_{Ia}$, $\theta_{!Ia}$: the transient parameters that describe individual
-transients (i.e..\ SALT2's $x_1$, $c$);
-\item $L(t,\lambda)$: the luminosity of the transient.
-\end{itemize}
-There are  fixed parameters
-\begin{itemize}
-\item $\mu$: the distance modulus given the cosmological parameters and the redshift;
-\item{$f$}: the flux of the transient given the luminosity, distance modulus, and
-redshift.
-%\item{$\overline{n}$}: the expected counts of the transient given
-%the flux and transmission.
-\end{itemize}
-
-The relationships between the parameters are now described:
-\begin{itemize}
-\item Intrinsic transient parameters are dependent on their distributions and the host galaxy.
-The SNe~Ia parameters are drawn as
-\begin{equation}
-\theta_{Ia} | \Theta_{Ia}, g \sim \mathcal{N}(0, \Theta_{ia, \theta}),
-\end{equation}
-where $\theta_{Ia} =\{x_1, c\}$ are the SALT2 light-curve shape and color parameters
-and $\Theta_{ia, \theta}$ describes the covariance of their distributions.
-A more complex model can be based on non-Normal distributions
-and/or including SN properties directly tied to characteristics (e.g.\ mass, star formation
-rate) of the host galaxy.
-
-{\bf The non-Ia parameters, their underlying distributions, and SED's need to chosen.}
-The prime candidate
-is their description used in PSNID.
-
-%\begin{equation}
-%\theta_{non-Ia} | \sigma_\beta, g  \sim \mathcal{N}(0, \sigma_{\beta, non-Ia}),
-%\end{equation}
-%where the parameter is the realization of an intrinsic magnitude dispersion.
-%A more complex model can include multiple non-Ia populations each with its own
-%intrinsic parameters.
-\item Spectroscopically observed transient parameters depend on the intrinsic transient
-parameters and type.  $\theta_{Si}$ may be ignored in a zero'th order analysis that
-does not relate spectral features with SN~Ia absolute magnitudes.   If spectral
-features are considered, the simple model
-\begin{equation}
-\theta_{S} (\theta_{Ia}, \theta_{!Ia}, T)=\theta_{T}
-\end{equation}
-assumes an unambiguous mapping between supernova parameters and spectral signal.
-{\bf We need to decide what SN spectral parameters, if any, we will consider in our analysis.}
 \item The type is drawn from the host-dependent relative rate between SNe~Ia and non-Ia's 
 \begin{equation}
-T | r, g \sim \rm{Bernoulli}(\pi(r,g,T)),
+Type | Rates, Host \sim {\rm Bernoulli}(\pi(z;r)),
 \end{equation}
 where $\pi$ is a model for the relative rate of SNe~Ia as a
-function of galaxy parameters and redshift.  {\bf A reasonable choice for $\pi$ needs to be
+function of galaxy redshift $z$.  {\bf A reasonable choice for $\pi$ needs to be
 selected.}
-\item Supernova type is assumed to be unambiguously encoded in the
-spectrum:
-\begin{equation}
-T_S (T)  = T.
-\end{equation}
-\item The observed redshift is taken to be the host galaxy redshift
-\begin{equation}
-z_S (g_z) =g_z
-\end{equation}
-where $g_z$ is the element in $g$ that corresponds to redshift.
-Added sophistication includes redshift
-measurement uncertainty and random peculiar velocities. The study of coherent
-flow requires added model complexity.
-\item The underlying SED of transients are modeled.  For SNe~Ia the SALT2 model
+
+Type~Ia supernovae have values of SALT2 parameters
+$x_1$ and $c$ drawn from Normal distributions
+with parameters for the variance
+\begin{equation}
+x_1, c \sim \mathcal{N}(0, (\sigma_{x_1}, \sigma_c)).
+\end{equation}
+
+Models for non-Ia supernovae need to be selected.  The model used in PSNID is a good
+place to start.
+\item The underlying SED of transients.  For SNe~Ia the SALT2 model
 is an option, although new models that separate dust and intrinsic color or
@@
 \begin{equation}
-L(t,\lambda) |  \Theta_{Ia}, \theta_{Ia}, g \sim L_{SALT2}(t-t_0; \alpha, \beta, x_1, c) \gamma(g, \Theta_{Ia,g}) \mathcal{N}(0,\sigma_{Ia}),
+Luminosity| Type
+, Host, Population \sim L_{SALT2}\left(\frac{t-t_0}{1+z}; \alpha, \beta, x_1, c\right) \exp{\left(\delta_G\mathcal{H}(g)\right)},
 \end{equation}
 where the first  term is the SALT2 light-curve and absolute magnitude
-model with a realized error snake,
-and $\gamma(g, \Theta_{Ia})$ a step function to model the ``mass step''.  Recall that the  fundamental SALT2 parameters 
-$\alpha$, $\beta$, and intrinsic dispersion $\sigma_{Ia}$, and the parameters that
-relate SN magnitude and host,
-are included in $\Theta_{Ia}$; the parameters in the SALT2 fit $t_0$, $x_1$, $c$
-are included in $\theta_{Ia}$.
+model with error snake.  Possible host-galaxy effects like the ``mass step'' are
+accounted in $\mathcal{H}(g)$ where $g$ is the corresponding host parameter
+and $\delta_G$ is the size of the offset.  The host redshift is $z$.
 
 {\bf The non-Ia model needs to be identified.  Perhaps PSNID.}
-\item The theoretical distance modulus
-\begin{equation}
-\mu(g_z; \Omega_M, w) = \mu_{wCDM}(g_z; \Omega_M, w)
-\end{equation}
-is the predicted distance modulus of a flat dark energy cosmology.
-\item The flux incident on Earth is the redshifted and time-dilated SED scaled
-by the distance modulus.
-\begin{equation}
-f(t,\lambda; L) = 10^{-\mu/2.5} L\left(t/(1+g_z),\lambda/(1+g_z)\right)
-\end{equation}
-\item The expected light curve in counts depends on the flux and throughput of the
+\item The theoretical distance modulus is
+\begin{equation}
+\mu(Host, Cosmology) = \mu_{wCDM}(z; \Omega_M, w)
+\end{equation}
+is the predicted distance modulus of a flat dark energy cosmology
+with parameters $\Omega_M$ and $w$, and host redshift $z$.
+
+The flux incident on Earth is the redshifted and time-dilated SED scaled
+by the distance modulus
+\begin{equation}
+f(Luminosity, Host, \mu) = 10^{-\mu/2.5} Luminosity(\lambda/(1+z)).
+\end{equation}
+
+The expected photometric signal in counts depends on the flux and throughput of the
 optical chain.  A first model encapsulates flux calibration through a zeropoint
 \begin{equation}
-n(f, Z) = 10^{Z/2.5} \int  f(\lambda) T_0(\lambda)d\lambda,
+counts(Throughput, f) = 10^{Z/2.5} \int  f(\lambda) T_0(\lambda)d\lambda,
 \end{equation}
@@
 analysis can have a transmission function specific to each observation.
-\item The host-galaxy information is directly encoded in the measurements
-\begin{equation}
-G(g)=g.
-\end{equation}
-\end{itemize}
-
-\subsection{Measurements}
-\label{measurements:sec}
-Spectroscopic measurements are assumed
-to provide prefect determinations of transient type and parameters, and
-galaxy redshifts and parameters. 
-\begin{align}
-p(T_S|T) &= \delta(T_S-T),\\
-p(\theta_S|\theta_T) &= \delta(\theta_S-\theta_T),\\
-p(z_S|g_z) &= \delta(z_S-g_z).
-\label{specz:eqn}
-\end{align}
-People who are interested in SN spectral features
-or host-galaxy correlations (Chris, Rachel, Mat) can develop these models.
-
-For the photometric sample, there is uncertainty in the identity of the host galaxy.
-From a set of potential host galaxies $\hat{G}$ each with probability $\pi$ of being the correct host,
-\begin{equation}
-G \sim \prod_i \delta(G-\hat{G}_i) \pi_i.
-\end{equation}
-Ravi can provide for each transient a list of candidate hosts and their probabilities.
-The working group is striving to get spectroscopic
-redshifts of all potential hosts, which is included in $G$.
-For the spectroscopic sample the host is unambigous
-\begin{equation}
-G = g.
-\end{equation}
 
@@
 \begin{equation}
-n \sim \mathcal{N}\left(10^{Z/2.5} \int  f(\lambda;A, B) T_0(\lambda)d\lambda,C_P\right).
+Photometry_o |  Luminosity, Cosmology,Host,Throughput \sim \mathcal{N}(counts,C_P).
 \end{equation}
@@
 
-\subsection{Sample Selection}
-The transients that enter the analysis satisfy some selection criteria.  Trivially, they
-have to be discovered in the first place and often more stringent photometric signal-to-noise
-requirements are applied.  Additionally, the probability for a transient to have successful
-spectroscopy may depend on parameters.  These criteria have not yet been determined/selected
-(Argonne for photometry, OzDES/Ryan for spectroscopy are candidates to do this);
-presented here is a sketch of the likelihood calculation for a reasonable
-photometric selection criterion.
-For each transient $\nu$, the criterion is to have $\ge N$ photometric points
-above a signal-to-noise threshold there  given $M_\nu$ available measurements:
-the signal-to-noise threshold corresponding to a flux threshold
- $n_{0,\nu i}$.
-
-Call the likelihood of the underlying distribution without sample selection $P(A|C)$.
-Let the array $b_{\nu}$ be an array that contains $0$ or $1$ based on
-whether the corresponding photometric point is below or passes threshold. 
-Let the larger array $b$ be a combination of the $b_\nu$ from all transients.
-There are $2^{\sum_\nu M_\nu}$ possible permutations of $b$, and the underlying
-likelihood can be broken up into the sum of all possible combinations
+Recall that the sample likelihood has terms
+$\epsilon(Photometry_o, b_k)p(data| model)$, which turn out to be truncated Gaussians.
+
+\item Spectroscopic measurements are assumed
+to provide prefect determinations of transient type
+\begin{equation}
+Type_o | Type  \sim \delta(Type-Type_o).
+\end{equation}
+\item There are measurements of the host galaxy properties.
+The first complication is
+the correct identification of the host.  For transients that have spectroscopic
+confirmation, an unambiguous host determination is assumed such that
 \begin{align}
-p(A|C) &= \sum_k p(A, b_k| C)\\
-& = \sum_k \epsilon(n, b_k)p(A| C),
+Redshift_o  | Host & \sim \delta(Redshift_o- z)\\
+Host~properties_o  | Host & \sim \mathcal{N}(p, C),
 \end{align}
-where
-\begin{equation}
-\epsilon(n; b_{k})= \prod_{\nu i}\mathcal{H}\left((-1)^{b_{k\nu i}+1}(n_{k\nu i}-n_{0,\nu i})\right),
-\end{equation}
-where $\mathcal{H}$ is the Heaviside step function; when $b_{k\nu i}=1/0$ the step in the efficiency
-is up/down.  The indices correspond to configuration $k$,
-transient $\nu$, and photometric point $i$.
-
-For the analysis sample, are a smaller number of combinations of $b$ that satisfy
-the selection criteria;
-instead of $2^{M_\nu}$ there are $\sum_{k=N}^{M_{\nu}} \binom{M_{\nu}}{k}$ 
-distinct $b_{\nu}$'s that allow acceptance of transient $\nu$.  The selection efficiency
-for the complement set of possible $b$'s is zero.
-The sample likelihood is then as
-\begin{equation}
-p(A|\mathcal{S}, C) = \frac{\sum_k \epsilon(n, b_k)p(A| C)}{\int dA\, \sum_k \epsilon(n, b_k)p(A| C)},
-\end{equation}
-where the sum is
-over only the configurations that meet the selection criteria.
-
-The measurement uncertainties in the light curves $n$ are independent of the other
-measurements, and the measurement uncertainties are drawn from a Normal distribution:
-the likelihood is assembled from truncated Gaussians with the integrals over $n$ in the numerator
-proportional to error functions.
+where $p$ are the Host properties being measured,
+$C$ is the covariance of the measurement of the galaxy identified as the host.
+DES plans to get spectroscopic redshifts with negligible measurement uncertainties on all
+possible hosts.
+
+For the photometric sample, there is uncertainty in the identity of the host galaxy.
+From a set of potential host galaxies $\hat{G}$ each with probability $\pi$ of being the correct host,
+\begin{equation}
+G \sim \prod_i \delta(G-\hat{G}_i) \pi_i.
+\end{equation}
+Ravi can provide for each transient a list of candidate hosts and their probabilities.
+Thus for the photometric sample
+\begin{align}
+Redshift_o  | Host &  \sim \sum_i \pi_i \delta(Redshift_o- z_i)\\
+Host~properties_o  | Host & \sim  \sum_i \pi_i \mathcal{N}(p_i, C),
+\end{align}
+\end{itemize}
+
+This accounts for all the terms needed to assemble to pdf of the underlying distribution,
+from which the likelihood of the analysis sample is assembled.
 
@@
 \subsubsection{Likelihood for the {\it obs} Set}
-The likelihood for the {\it obs} set is
-\begin{multline}
-p(A|\mathcal{S},C) \propto
-\sum_k \epsilon(n, b_k) 
-\sum_T \int d\theta_{Ia}\, d\theta_{!Ia}\, dL\, p(n, {{T}}_S,{{z}}_S, \theta_{S}, G | T,  L, \Omega_M, w, r, \Theta_{Ia}, \Theta_{\mathit{!Ia}}, Z, g) \\
-p(L| T, \theta_{Ia},
-\theta_{!Ia},  \Omega_M, w, r, \Theta_{Ia},\Theta_{\mathit{!Ia}}, Z, g)
-p(T, \theta_{Ia}
-\theta_{!Ia}|  \Omega_M, w, r, \Theta_{Ia},\Theta_{\mathit{!Ia}}, Z, g).
-\end{multline}
-
-For our model and measurements
-\begin{multline}
-p(A|\mathcal{S},C) \propto 
-\sum_k \epsilon(n, b_k) \int dL\,
-p(n |  T= T_S, \theta_{T}=\theta_S, g=G, L, C)
-p(L| T, \theta_{T_S}, r, \Theta_{T_S}, g)\\
-\pi(r, z_S, T_S)p( \theta_{T_S}|  \Theta_{T_S},g=G) .
-\end{multline}
-
-\subsubsection{Likelihood for the {\it mis} Set}
-The likelihood for the {\it mis} set follows the same pattern as that of the
-{\it obs} set except for not having to account for spectroscopic data
-\begin{multline}
-p(n, \theta_{G} |  \mathcal{S}, C) 
- \propto \sum_k \epsilon(n; b_{k}) 
-\sum_T \int d\theta_{Ia}\, d\theta_{!Ia}\, dL\, 
-\sum_l
-\pi_l
-p(n |  g=\hat{G}_l, B, C)
-p(L| T, \theta_{Ia}, \theta_{!Ia}, r, \Theta_{Ia}, \Theta_{!Ia}, g)\\
-\pi(r, \hat{G}_l, T)p( \theta_{Ia},
-\theta_{!Ia}|  \Theta_{Ia},\Theta_{\mathit{!Ia}}, g=\hat{G}_l).
-\end{multline}
-
 %\begin{multline}

### 2015-10-22 src/pgm.py

@@ -1,0 +1,112 @@
+#!/usr/bin/env python
+
+from matplotlib import rc
+import matplotlib
+from daft import PGM, Node, Plate
+rc("font", family="serif", size=8)
+rc("text", usetex=True)
+
+
+pgm = PGM([8.5, 8.5], origin=[0., 0.2], observed_style='inner')
+
+#pgm.add_node(Node('dispersion',r"\center{$\sigma_{Ia}$ \newline $\sigma_{!Ia}$}", 1,6,scale=1.2,aspect=1.8))
+pgm.add_node(Node('rate',r"{\center Relative \newline Rates}", 2,8,scale=1.6,aspect=1.2))
+#pgm.add_node(Node('theta_T',r"\center{$\alpha_{Ia}$, $\alpha_{!Ia}$ \newline $\beta_{Ia}$, $\beta_{!Ia}$}", 4,6,scale=1.4,aspect=1.8))
+pgm.add_node(Node('theta_T',r"\center{SNe~Ia, Non-Ia \newline Populations}", 5,8,scale=1.8,aspect=1.2))
+#pgm.add_node(Node('theta_T2',r"{Non-Ia}", 4,8,scale=1.6,aspect=1.2))
+pgm.add_node(Node('mu',r"{\center Cosmology}", 7,8, scale=1.6,aspect=1.2))
+
+#pgm.add_node(Node('G_Ni',r"$g_{Ni}$", 8,5))
+
+
+#pgm.add_node(Node('Flux_g',r"$f_{gi}(\lambda)$", 8, 3))
+
+#pgm.add_node(Node('z',r"$z_i$", 3, 3, fixed=True,offset=(-10,-5)))
+
+
+#pgm.add_node(Node('Counts',r"$\overline{n}_i$", 7, 2,scale=1.2,fixed=True,offset=(-15,0)))
+#pgm.add_node(Node('Counts_g',r"$\overline{\mathit{ADU}}_{gi}$", 8, 2,scale=1.2,fixed=True,offset=(20,0)))
+#pgm.add_node(Node("Summary",r"$S({\mathit{ADU}_i})$", 9, 1, fixed=True, offset=(0,-25)))
+
+pgm.add_node(Node('G_i',r"{\centering Host Galaxy \newline (Redshift)}", 3,7, scale=1.6,aspect=1.2))
+
+
+pgm.add_node(Node('Type',r"\centering{Type \newline Subtype}", 2, 6, scale=1.6,aspect=1.2))
+
+
[…]

### 2015-10-23 doc/article.tex
new "done" version

@@
 \subsection{Model}
+\label{model:sec}
 This Section presents a candidate model
@@
 supernova analysis of the Dark Energy Survey and the Large Synoptic Survey Telescope.
-This model captures the current treatment in current analysis but expanded to include
+This model captures the current treatment in current analyses but expanded to include
 photometry-only transients.  This may not be the ultimate model used, indeed many models
@@
 that may enter
-the analysis.  The SALT2 model is a candidate for SNe~Ia, with parameters $\alpha$, $\beta$,
-and pdf's for $x_1$ and $c$.  The PSNID treatment of non-Ia's is a candidate for the other
+the analysis.  The SALT2 model is a candidate for SNe~Ia, with parameters $\alpha$, $\beta$.  The PSNID treatment of non-Ia's can be made into a model for the other
 transients.
-\item [Relative Rates] Relative rates of all the transients populations under consideration.  The
-model could be extended to measure absolute rates, but that is unnecessary if
+\item [Relative Rates] Relative rates of all the transients populations and
+subpopulations (e.g. SALT2 $x_1$, $c$) under consideration.  The
+model could of been extended to measure absolute rates, but that is unnecessary if
 the cosmological parameters are the goal.
@@
 the environment from which the transient arises.  The host is described by its redshift
-and parameters that may be correlated with Hubble diagram residuals, such as mass,
+and other parameters that may be of interest such as mass,
 specific star formation rate, metallicity.
-\item[Type Subtype] Specification of the the transient: which population to which it belongs
+\item[Type Subtype] Specification of the the transient: the population to which it belongs
 and its internal parameters.  For example, an object could be SN~Ia with specific
-values for its SALT2 parameters $c$, $x_1$, $t_0$ and its realization
-from the error snake.  This dependent on the relative rates and
+values for its SALT2 parameters $c$, $x_1$, $t_0$ and its random dispersion
+realization (both absolute magnitude and from the error snake). 
+This is dependent on the relative rates and
 its host galaxy including redshift.
@@
 which in our model corresponds to the cosmological redshift of the transient.  The value
-is fixed based on the cosmological model and redshift.
+is fixed based on the cosmology and redshift.
 \end{description}
@@
 \begin{description}
-\item[Throughput] The transmission function for the band at that date appropriate
-for the transient.  A simple parameterization could be calibration zeropoints; more
-sophisticated descriptions can vary the shape, not only the normalization, of the
-transmission.
+\item[Throughput] The transmission function experienced by the transient during
+the observation.  It depends on band, position on the focal plane, and date of observation.
 \end{description}
-The data subscripted by ``o'' are
+The data (subscripted by ``o'' for observation)  are:
 \begin{description}
-\item[$\text{Photometry}_o$] Photometric flux measurement.  The expected measurement
-is the incident flux integrated over the throughput.  Typically the measurement
-uncertainties are from a Poisson distribution.  In practice, photometric data extraction
-is performed in an independent analysis that isolates the transient flux
-from contaminating background light. 
-\item[$\text{Type Subtype}_o$] Measurement of the intrinsic transient type.  This is done
-through spectroscopy.
+\item[$\text{Photometry}_o$] Photometric flux measurement of the transient.
+The expected measurement
+is the incident flux integrated over the throughput.
+\item[$\text{Type Subtype}_o$] Spectroscopic
+measurements of the intrinsic transient type.  It is dependent on the underlying
+type.
 \item[$\text{Redshift}_o$] Measurement of the host redshift.  The redshift can be
-spectroscopic or photometric.  Uncertain host galaxy identification contribute
-to measurement errors.
+spectroscopic or photometric.  It is dependent on the host redshift, and
+redshifts of any other galaxies that may be confused as the host (not shown explicitly
+in the PGM).
 \item[$\text{Host Properties}_o$] Measurement of the host properties such
-as mass, sSFR, metallicity. Uncertain host galaxy identification contribute
-to measurement errors.
+as mass, sSFR, metallicity. It is dependent on the host galaxy, and
+any other galaxies that may be confused as the host.
 \end{description}
@@
    \caption{Probabilistic Graphical Model for the SN~Ia analysis.  
-   The forward modeling
-   flow goes from top to bottom, starting with the description of the universe, observatory,
-   and data.    A transient occurs in host galaxy $g_i$.  The type $T$ depends on the
-   host and relative rates $r$.  The transient parameters $\theta$ depend on the
-   transient model $\Theta$ and the host.  The luminosity $L$ depends on the preceding
-   parameters.  
-   A model with parameters $\Omega_M$ and $w$ fix the distance modulus $\mu_i$.
-   The 
-   incoming photon flux $f$  are then fixed
-   with host redshift and distance modulus.
-   The measured light curve depends on the instrumental throughput $Z$.  There are
-   spectroscopic
-   measurements $\theta_S$, $T_S$, $z_S$ of the transient parameters, type, and
-   redshift.  $G$ is the determination of the host galaxy from photometric data.
+   The description of the elements and dependencies of the model are given in
+   \S\ref{model:sec}.
    \label{pgm:fig}}
@@
 latent Type.  The system throughput is treated as a probabilistic variable
-allowing for self-calibration; this could be omitted from the model with calibration applied
+allowing for self-calibration; this could be omitted from the model with calibration
+and its uncertainties applied
 to the Photometry measurements.  Host-galaxy misclassification enters as measurement
@@
 requirements are applied.  Additionally, the probability for a transient to have successful
-spectroscopy may depend on parameters.
-These criteria have not yet been determined/selected
+spectroscopy may be dependent on model parameters.
+
+Sample selection criteria for DES have not yet been finalized
 (Argonne for photometry, OzDES/Ryan for spectroscopy are candidates to do this);
 presented here is a sketch of the likelihood calculation for a reasonable
-photometric selection criterion.
-
-For each transient $\nu$, the criterion is to have $\ge N$ photometric points
-above a signal-to-noise threshold given $M_\nu$ available measurements:
-every photometric point is associated with a flux threshold that it either passes
+photometric selection criterion:
+for each transient $\nu$, the criterion is to have $\ge N$ photometric points
+above a signal-to-noise threshold given $M_\nu$ available measurements.
+Each photometric point is associated with a flux threshold that it either passes
 or fails.  Given a total $M=\sum_\nu M_\nu$ data points, there are
-$2^M$ possible combinations
+$2^M$ possible configurations
 of passing or failing theshold, of which only
-$\prod_\nu \sum_{k=N}^{M_{\nu}} \binom{M_{\nu}}{k}$  combinations would lead to
+$\prod_\nu \sum_{k=N}^{M_{\nu}} \binom{M_{\nu}}{k}$  configurations lead to
 the inclusion of the transients in the sample.
 
-The probability distribution function for all possible data realizations can be written
-as the sum of the pdf's of all possible permutations
-\begin{equation}
-p(data|model) = \sum_{k=1}^{2^M} p(data, b_k| model),
+The likelihood for the analysis
+sample is the conditional distribution obtained by applying the selection criteria
+on the domain of the likelihood given no selection criteria.  This latter likelihood
+can be written
+as the sum of the contributions from all possible threshold-passing configurations
+\begin{equation}
+p(data|model) = \sum_{k=1}^{2^M} p(data, \hat{b}_k| model),
 \label{likelihood_u:eqn}
 \end{equation}
-where $b$ contains all possible combinations.
-The probability distribution function for all possible data realizations that pass
-our selection criteria is a conditional pdf. It is proportional to the underlying
-pdf after removal of conditions that are not achieved, i.e.\ removal from the sum
-in Eqn.~\ref{likelihood_u:eqn} of all combinations that do not meet the sample
-selection criteria. This leaves a reduced set $b$ of
-possible permutations
-\begin{equation}
-\mathcal{L}(data|\mathcal{S}, model) \propto \sum_{k=1}^{\prod_\nu \sum_{k=N}^{M_{\nu}} \binom{M_{\nu}}{k}} p(data, b_k| model),
-\end{equation}
-where $\mathcal{S}$ is the sample-selection condition.
+where $\hat{b}$ is the set containing all possible configurations.
+Let $b$ be the subset of $\hat{b}$ 
+that satisfies sample selection. Then the selection criteria is $\mathcal{S} = \hat{b}_k
+\in b$.
+The likelihood of the analysis sample is thus proportional to Eqn.~\ref{likelihood_u:eqn}
+with failing configurations removed
+\begin{equation}
+\mathcal{L}(data|\mathcal{S}, model) \propto
+\sum_{k=1}^{2^M} p(data, \hat{b}_k| \hat{b}_k
+\in b, model) = \sum_{k=1}^{\prod_\nu \sum_{k=N}^{M_{\nu}} \binom{M_{\nu}}{k}} p(data, b_k| model).
+\end{equation}
 
@@
 \end{equation}
-where the normalizing factor is included explicitly as a reminder that it has 
+where the normalizing factor is included explicitly as it has 
 parameter dependence and must not be neglected in calculations.
@@
 the sample distribution, there is $\binom{1}{1}=1$ possible configuration: the flux
-is above threshold.   The likelihood for the measured flux is the truncated version
-of the underlying distribution.
-
-For the case of a single object with two measurements and a single threshold requirement,
+is above threshold.   The likelihood for the measured flux is proportional to the original
+distribution truncated so that fluxes below threshold are assigned zero probability.
+
+For the case of a single object with two measurements of which only one is needed to
+pass threshold,
 there are $2^2=4$ possible configurations of which $\sum_{k=1}^{2} \binom{2}{k}=3$
-would allow sample selection, the exception being when both measurements fall below threshold.
+allow sample selection, the exception being when both measurements fall below threshold.
 The likelihood for each flux is composed from
 the sum of three truncated distributions of which one accepts faint fluxes,
-resulting in resultant likelihoods that do not fall to zero below detection threshold.
+resulting in likelihoods that are not zero below detection threshold.
 
@@
 & \times \int dType\, p(Type_0|Type) p(Type|Rates, Host) \nonumber \\
-& \times p(Redshift_o, Host_o| Host)
+& \times p(Redshift_o, Host_o| Host),
 \label{like:eqn}
@@
 where $data=\{Photometry_o, Type_o, Redshift_o, Host_o\}$,
-$model=\{Cosmology, Populations, Rates\}$, and we anticipate the independence
-of photometric and spectroscopic typing measurements.
-
-Now for specificity candidate models for the pdf's that enter Eqn.~\ref{like:eqn}
-are presented.
+$model=\{Cosmology, Populations, Rates\}$, and the independence
+of photometric and spectroscopic typing measurements is anticipated.
+
+For specificity candidate models for the pdf's that appear in Eqn.~\ref{like:eqn}
+are now presented.
 \begin{itemize}
@@
 \end{equation}
-where $\pi$ is a model for the relative rate of SNe~Ia as a
+where $\pi$ is a model for the relative rate of SNe~Ia parameterized by $r$ as a
 function of galaxy redshift $z$.  {\bf A reasonable choice for $\pi$ needs to be
@@
 place to start.
-\item The underlying SED of transients.  For SNe~Ia the SALT2 model
-is an option, although new models that separate dust and intrinsic color or
-identify new SN~Ia parameters are expected in the near future.  Absolute magnitudes
-that depend on host-galaxy properties need to be considered. 
-\begin{equation}
-Luminosity| Type
-, Host, Population \sim L_{SALT2}\left(\frac{t-t_0}{1+z}; \alpha, \beta, x_1, c\right) \exp{\left(\delta_G\mathcal{H}(g)\right)},
+
+Note that the rates may not have been important in spectroscopic analyses, but are important here to help infer the types/subtypes of transients without
+a spectrum.
+\item For the underlying SED of transients for SNe~Ia the SALT2 model
+is an option, although new models are expected to appear shortly.  Absolute magnitudes
+that depend on host-galaxy properties also need to be considered. 
+In the SALT2 context,
+\begin{equation}
+Luminosity(Type
+, Host, Population)= L_{SALT2}\left(\frac{t-t_0}{1+z}; \alpha, \beta, x_1, c\right) \exp{\left(\delta_G\mathcal{H}(g)\right)},
 \end{equation}
@@
 and $\delta_G$ is the size of the offset.  The host redshift is $z$.
+Note that for this model the parameter is fixed, though
+generally this may not be the case.
 
@@
 The expected photometric signal in counts depends on the flux and throughput of the
-optical chain.  A first model encapsulates flux calibration through a zeropoint
-\begin{equation}
-counts(Throughput, f) = 10^{Z/2.5} \int  f(\lambda) T_0(\lambda)d\lambda,
-\end{equation}
-where $T_0$ is a fiducial transmission function for the appropriate filter.  A more sophisticated
-analysis can have a transmission function specific to each observation.
+optical chain.  A simple model encapsulates flux calibration through a zeropoint $Z$
+and $T_0$  a fiducial transmission function for the appropriate filter.
+More
+sophisticated descriptions of calibration can vary the shape, not only the normalization, of the
+transmission.  For the simple model,
+\begin{equation}
+counts(Throughput, f) = 10^{Z/2.5} \int  f(\lambda) T_0(\lambda)d\lambda.
+\end{equation}
 
 Practically the photometric extraction is handled by independent software, which calculates
-the $n$ with uncertainties $C_P$
+the integrated counts with uncertainties $C_P$
 by modeling and separating out polluting background light from the transient
@@
 \end{equation}
-Dillon is providing this.
-Note that the model has explicit calibration parameters that are to be fit.  An alternative
-approach is to include calibration uncertainties in $C_P$.
-
-Recall that the sample likelihood has terms
-$\epsilon(Photometry_o, b_k)p(data| model)$, which turn out to be truncated Gaussians.
-
+Dillon is providing this $Photometry_o$ and $C_P$.
+
+An alternative model would be to remove Throughput
+and include calibration uncertainties in $C_P$.  This would be a huge covariance
+matrix!
 \item Spectroscopic measurements are assumed
@@
 \begin{equation}
-Type_o | Type  \sim \delta(Type-Type_o).
+Type_o(Type)  = Type.
 \end{equation}
 \item There are measurements of the host galaxy properties.
-The first complication is
-the correct identification of the host.  For transients that have spectroscopic
+For transients that have spectroscopic
 confirmation, an unambiguous host determination is assumed such that
 \begin{align}
-Redshift_o  | Host & \sim \delta(Redshift_o- z)\\
+Redshift_o(Host) & = z\\
 Host~properties_o  | Host & \sim \mathcal{N}(p, C),
 \end{align}
-where $p$ are the Host properties being measured,
-$C$ is the covariance of the measurement of the galaxy identified as the host.
-DES plans to get spectroscopic redshifts with negligible measurement uncertainties on all
+where $p$ are the Host properties being measured
+and
+$C$ their measurement uncertainty.
+
+For the photometric sample, there is uncertainty in the identity of the host galaxy.
+Suppose host-galaxy identification gives
+a set of potential hosts $\hat{G}$ each with probability $\pi$ of being the correct host,
+what Ravi is doing.
+Then for the photometric sample
+\begin{equation}
+p(Redshift_o, Host~properties_o   | Host) = \sum_i \pi_i \delta(Redshift_o- z_i)\mathcal{N}(Host~properties_o-p_i, C)).
+\end{equation}
+Recall that DES plans to get spectroscopic redshifts with negligible measurement uncertainties on all
 possible hosts.
-
-For the photometric sample, there is uncertainty in the identity of the host galaxy.
-From a set of potential host galaxies $\hat{G}$ each with probability $\pi$ of being the correct host,
-\begin{equation}
-G \sim \prod_i \delta(G-\hat{G}_i) \pi_i.
-\end{equation}
-Ravi can provide for each transient a list of candidate hosts and their probabilities.
-Thus for the photometric sample
-\begin{align}
-Redshift_o  | Host &  \sim \sum_i \pi_i \delta(Redshift_o- z_i)\\
-Host~properties_o  | Host & \sim  \sum_i \pi_i \mathcal{N}(p_i, C),
-\end{align}
 \end{itemize}
@@
 
-\subsection{Likelihoods}
-The transients are divided into
-the following subsets:
-{\it obs} are transients observed spectroscopically while active, from which $T_S=1$ are those typed
-as SN~Ia and $T_S=0$ as non-Ia.  {\it mis} transients are not observed
-spectroscopically when active.  The data from each subset have different forms for their likelihood.
-The  {\it obs} sample constrains and specifies the parameter distributions of the 
-parameters missing from the {\it mis} sample.
-
-\subsubsection{Likelihood for the {\it obs} Set}
-%\begin{multline}
-%p(n_{SN}, G |  \Omega_M, w, \theta_r, \alpha_{Ia}, \beta_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\beta_{\mathit{non-Ia}}, \sigma_{\mathit{non-Ia}},  Z, g, g_N, f_g)\\
-%= \sum_i \int_L dL\, p(n_{SN}, G | b_i, L, \ldots)
-%P(b_{i} |L, \ldots) P(L|\ldots) ,
-%\end{multline} 
-%\begin{equation}
-%p(n_{SN}, G | b_i, L, \ldots)
-%  =  \frac{ \prod_j
-% \epsilon(n_{SN,j}; b_{ij})
-%  p(n_{SN}, G | L, \ldots)}
-%  {\prod_j P(b_{ij}{ |L,\dots)}}.
-%\label{misconf:eqn}
-%\end{equation}
-
 \section{Tasks}
-\begin{table}[htdp]
-\caption{default}
-\begin{center}
-\begin{tabular}{|c|c|}
-\hline
-Task/Deliverable & Responsible \\ \hline
-Model Design & \\
-Sampler &\\
-Photometric Selection &\\
-Spectroscopy Selection &\\
-Host Galaxy Association &\\
-Host Galaxy Parameters &\\
-SN~Ia Models Selection &\\
-Non-Ia Models Selection &\\
-SN light curves ($n$) &\\
-Photometric Zeropoints &\\
-\hline
-\end{tabular}
-\end{center}
-\label{Tasks and Responsible Parties}
-\end{table}%
-
-\section{Misc}
-The simulation of data from the model presented in
-and their analysis is implemented in Python and are available
-on GitHub\footnote{{git@github.com:AlexGKim/abc.git}}.
-
+Here are a list of initial tasks and ingredients needed to proceed.
+\begin{itemize}
+\item Determination of flux thresholds for each photometric point given
+a $S/N$ threshold
+\begin{equation}
+threshold(point, S/N).
+\end{equation}
+If we work in the sky-noise dominated regime, I believe this information is already
+calculated by DM.
+\item Identification of selection criteria for spectroscopic success, as a function
+of data.
+\item A rates model for transient types and subtypes
+\begin{equation}
+\pi(z;r).
+\end{equation}
+\item Decision on how to model the distribution of $x_1$ and $c$.  For a first try a
+single normal distribution seems sufficient but do we want to be more ambitious?
+\item A non-Ia transient model.  Much of its usage is in classification, so the PSNID
+description is a place to start.
+\item Calibration model and uncertainties. Assuming we work with zeropoints
+$p(Z)$ is needed.
+\item Data! Spectroscopic Type and uncertainties, Spectroscopic redshifts and
+uncertainties, galaxy properties and uncertainties, host-galaxy associations
+and uncertainties, photometry and uncertainties.
+\item Determine the mechanics of doing the analysis.  A Bayesian MCMC could produce posteriors, which sampler that best suits our needs? Is a frequentist
+analysis technically unfeasible? If redshifts were free to wander I would think so, but maybe
+it is possible in this model.
+\end{itemize}
+
+%\section{Misc}
+%The simulation of data from the model presented in
+%and their analysis is implemented in Python and are available
+%on GitHub\footnote{{git@github.com:AlexGKim/abc.git}}.
+%
 %

### 2015-10-23 src/pgm.py

@@ -98,7 +98,7 @@ pgm.add_plate(Plate([1.4, 0.5, 6.2, 7.],
 
 pgm.add_plate(Plate([4.5, 0.6, 3, 4.],
                     label=r"{\centering LC Point $j = 1, \cdots, N_{band}$, $k = 1, \cdots, N_{date}$}",
-                    shift=-0.2,label_offset=[2,5]))
+                    shift=-0.2,label_offset=[2,2]))
 
 
 # Render and save.

### 2015-11-03 doc/article.tex
new version of document

@@
 supernova analysis of the Dark Energy Survey and the Large Synoptic Survey Telescope.
-This model captures the current treatment in current analyses but expanded to include
+This model captures the current treatment in current analyses and is expanded to include
 photometry-only transients.  This may not be the ultimate model used, indeed many models
@@
 the analysis.  The SALT2 model is a candidate for SNe~Ia, with parameters $\alpha$, $\beta$.  The PSNID treatment of non-Ia's can be made into a model for the other
-transients.
+transients or Natahsa Karpenka is working on a model of non-Type~II core collapse SNe.
 \item [Relative Rates] Relative rates of all the transients populations and
@@
 This is dependent on the relative rates and
-its host galaxy including redshift.
+its host galaxy including its redshift.
 \item[Distance] Distance modulus or equivalently the luminosity distance of the host galaxy,
@@
 corresponding to the date of observation.   This depends on the population, type,
-and subtype.  Given evidence for correlations between host properties and Hubble
-residuals, a direction connection between host galaxy and luminosity is made.
+and subtype.  Given that searching for correlations between  host properties and Hubble
+residuals is a good probe of systematics,
+a direction connection between host galaxy and luminosity is made.
 \item[Flux] Flux of the transient incident to earth at the date of observation.  It is 
@@
 have to be discovered in the first place and often more stringent photometric signal-to-noise
-requirements are applied.  Additionally, the probability for a transient to have successful
-spectroscopy may be dependent on model parameters.
+requirements are applied.  Additionally, transients that have
+successful spectroscopy may be drawn from an underlying population that differs from the
+underlying or photometrically-selected samples.
 
 Sample selection criteria for DES have not yet been finalized
-(Argonne for photometry, OzDES/Ryan for spectroscopy are candidates to do this);
+(Argonne Eve for photometry, OzDES/Ryan for spectroscopy are candidates to do this);
 presented here is a sketch of the likelihood calculation for a reasonable
@@
 $2^M$ possible configurations
-of passing or failing theshold, of which only
+of the individual points passing or failing theshold, of which only
 $\prod_\nu \sum_{k=N}^{M_{\nu}} \binom{M_{\nu}}{k}$  configurations lead to
@@
 \in b$.
-The likelihood of the analysis sample is thus proportional to Eqn.~\ref{likelihood_u:eqn}
+The likelihood of the analysis sample is proportional to Eqn.~\ref{likelihood_u:eqn}
 with failing configurations removed
 \begin{equation}
-\mathcal{L}(data|\mathcal{S}, model) \propto
+\mathcal{L}(data|\mathcal{S}, model) =
 \sum_{k=1}^{2^M} p(data, \hat{b}_k| \hat{b}_k
-\in b, model) = \sum_{k=1}^{\prod_\nu \sum_{k=N}^{M_{\nu}} \binom{M_{\nu}}{k}} p(data, b_k| model).
+\in b, model) \propto \sum_{k=1}^{\prod_\nu \sum_{k=N}^{M_{\nu}} \binom{M_{\nu}}{k}} p(data, b_k| model),
 \end{equation}
@@
 
-Models for non-Ia supernovae need to be selected.  The model used in PSNID is a good
-place to start.
+Models for non-Ia supernovae need to be selected.
 
@@
 
-{\bf The non-Ia model needs to be identified.  Perhaps PSNID.}
+{\bf The non-Ia model needs to be identified.}
 \item The theoretical distance modulus is
@@
 Here are a list of initial tasks and ingredients needed to proceed.
+\subsection{Photometric Selection}
+Here are desired properties of the set (or sets) of objects obtained from photometric selection.
+\begin{itemize}
+\item Sufficient data-quality to have a chance at photometric classification.
+SNe~Ia do look different from other transients: the principal source of type  ambiguity
+comes from poor signal-to-noise and poor temporal/wavelength sampling.
+\item A large set of likely SNe~Ia.
+\item All objects with photometry-only must have spectroscopically-typed analogs, preferably though not necessarily at the same redshift.  SNe~Ia subpopulations whose characteristics
+are unconstrained are not useful for cosmology.
+\item Obvious non-Ia's from populations that could be misconstrued as SN~Ia.  For example,
+a non-Ia at low redshift could be
+mistaken to be SN~Ia at high redshift due to degraded signal.
+\item Exclusion of objects that are not part of populations that could be misconstrued as SN~Ia.
+They would pollute inference of the non-Ia population.
+\end{itemize}
+
+A clean deliverable would be:
 \begin{itemize}
@@
 calculated by DM.
+\end{itemize}
+\subsection{Others}
+
+\begin{itemize}
 \item Identification of selection criteria for spectroscopic success, as a function
@@
 single normal distribution seems sufficient but do we want to be more ambitious?
-\item A non-Ia transient model.  Much of its usage is in classification, so the PSNID
-description is a place to start.
+\item A non-Ia transient model.  Much of its usage is in classification, PSNID or
+Karpenka could be places to start.
 \item Calibration model and uncertainties. Assuming we work with zeropoints
@@
 %
-%
 

### 2015-11-03 doc/article.tex
adding more stuff to section 3

@@
 comes from poor signal-to-noise and poor temporal/wavelength sampling.
+Having enough points with sufficient signal-to-noise over three adjacent bands over a 
+sufficiently large time window.
 \item A large set of likely SNe~Ia.
@@
 \end{itemize}
+
+\subsection{Spectroscopic Selection}
+Identification of selection criteria for spectroscopic success, as a function
+of data.
+
+\subsection{Relative Rates}
+\label{rates:sec}
+A rates model for transient types and subtypes
+\begin{equation}
+\pi(z;r).
+\end{equation}
+\subsection{SALT2}
+Decision on how to model the distribution of $x_1$ and $c$.  For a first try a
+single normal distribution seems sufficient but do we want to be more ambitious?
+\subsection{Non-Ia Transient Model}
+Needed is a model(s) for non-transients that could be mistaken as SN~Ia:
+both a description of the time-evolving SED and the relative rates
+with respect to Type~Ia's (see \S\ref{rates:sec}).
+
+The SED model is of the time evolving luminosity (or more precisely $\mathcal{M}$)
+for the range of possible non-Ia's.  It describes not only colors and light curve shapes,
+but also absolute magnitude.  Its parameters can be constrained part of the
+global analysis, indeed the pdf of the absolute magnitude is candidate.
+
+As much of its usage is in classification, PSNID is a place to start.
+Natasha Karpenka has been compiling a descriptions of non-Ia-Type~I's.  Can these
+be packaged into the following deliverable?
+
+The deliverable is a parameterized SED model that can be accessed through
+an interface such as $L(t,\lambda; \text{Non-Ia parameters})$.
+
+\subsection{Host-Galaxy Parameter Determination}
+Although a different group within DES is charged with deriving properties
+of galaxies (including our hosts), results do not seem to be forthcoming.
+Mat has said that there is a group within the SNWG interested in
+taking over this task.  Chris has discussed getting deep
+co-adds of galaxies uncontaminated by supernova light.
+Can we confirm who is part of this effort, if there is forward momentum,
+and get a single name that used as the point of contact?
+
+The deliverable are galaxy properties and a covariance matrix of their uncertainties,
+which are treated in the analysis as data.
+
+\subsection{NIR Data}
+VISTA NIR data have important probative value that can enhance about all aspects
+of our analysis even if available for a subset of objects.
+We should decide our intents on the timing of the use of this data.
+For example, on whether we plan on a DES-only paper and DES+NIR, and if
+we want to focus efforts on the former in the short term.
+
 \subsection{Others}
@@
 \begin{itemize}
-\item Identification of selection criteria for spectroscopic success, as a function
-of data.
-\item A rates model for transient types and subtypes
-\begin{equation}
-\pi(z;r).
-\end{equation}
-\item Decision on how to model the distribution of $x_1$ and $c$.  For a first try a
-single normal distribution seems sufficient but do we want to be more ambitious?
-\item A non-Ia transient model.  Much of its usage is in classification, PSNID or
-Karpenka could be places to start.
 \item Calibration model and uncertainties. Assuming we work with zeropoints

### 2015-11-05 src/pgm.py
fix throughput

@@ -7,14 +7,14 @@ rc("font", family="serif", size=8)
 rc("text", usetex=True)
 
 
-pgm = PGM([8.5, 8.5], origin=[0., 0.2], observed_style='inner')
+pgm = PGM([9.5, 8.5], origin=[0., 0.2], observed_style='inner')
 
 #pgm.add_node(Node('dispersion',r"\center{$\sigma_{Ia}$ \newline $\sigma_{!Ia}$}", 1,6,scale=1.2,aspect=1.8))
 pgm.add_node(Node('rate',r"{\center Relative \newline Rates}", 2,8,scale=1.6,aspect=1.2))
 #pgm.add_node(Node('theta_T',r"\center{$\alpha_{Ia}$, $\alpha_{!Ia}$ \newline $\beta_{Ia}$, $\beta_{!Ia}$}", 4,6,scale=1.4,aspect=1.8))
-pgm.add_node(Node('theta_T',r"\center{SNe~Ia, Non-Ia \newline Populations}", 5,8,scale=1.8,aspect=1.2))
+pgm.add_node(Node('theta_T',r"\center{SNe~Ia, Non-Ia \newline Populations}", 6,8,scale=1.8,aspect=1.2))
 #pgm.add_node(Node('theta_T2',r"{Non-Ia}", 4,8,scale=1.6,aspect=1.2))
-pgm.add_node(Node('mu',r"{\center Cosmology}", 7,8, scale=1.6,aspect=1.2))
+pgm.add_node(Node('mu',r"{\center Cosmology}", 8,8, scale=1.6,aspect=1.2))
 
 #pgm.add_node(Node('G_Ni',r"$g_{Ni}$", 8,5))
 
@@ -35,13 +35,13 @@ pgm.add_node(Node('Type',r"\centering{Type \newline Subtype}", 2, 6, scale=1.6,a
 
 
 #pgm.add_node(Node('theta_Ti',r"\centering{Transient \newline Parameters}", 1,5,scale=1.5,aspect=1.2))
-pgm.add_node(Node('HD',r"Distance", 7,6,fixed=True,offset=(-25,-15)))
+pgm.add_node(Node('HD',r"Distance", 8,6,fixed=True,offset=(-25,-15)))
 
 
-pgm.add_node(Node('Luminosity',r"Luminosity", 5, 4,scale=1.6,aspect=1.2))
+pgm.add_node(Node('Luminosity',r"Luminosity", 6, 4,scale=1.6,aspect=1.2))
 
 
[…]

### 2015-11-05 src/pgm.py
fix diagram throughput

@@ -12,9 +12,10 @@ pgm = PGM([9.5, 8.5], origin=[0., 0.2], observed_style='inner')
 #pgm.add_node(Node('dispersion',r"\center{$\sigma_{Ia}$ \newline $\sigma_{!Ia}$}", 1,6,scale=1.2,aspect=1.8))
 pgm.add_node(Node('rate',r"{\center Relative \newline Rates}", 2,8,scale=1.6,aspect=1.2))
 #pgm.add_node(Node('theta_T',r"\center{$\alpha_{Ia}$, $\alpha_{!Ia}$ \newline $\beta_{Ia}$, $\beta_{!Ia}$}", 4,6,scale=1.4,aspect=1.8))
-pgm.add_node(Node('theta_T',r"\center{SNe~Ia, Non-Ia \newline Populations}", 6,8,scale=1.8,aspect=1.2))
+pgm.add_node(Node('theta_T',r"\center{SNe~Ia, Non-Ia \newline Populations}", 5,8,scale=1.8,aspect=1.2))
+pgm.add_node(Node('Transmission',r"Throughput", 8, 8,scale=1.6,aspect=1.2))
 #pgm.add_node(Node('theta_T2',r"{Non-Ia}", 4,8,scale=1.6,aspect=1.2))
-pgm.add_node(Node('mu',r"{\center Cosmology}", 8,8, scale=1.6,aspect=1.2))
+pgm.add_node(Node('mu',r"{\center Cosmology}", 7,8, scale=1.6,aspect=1.2))
 
 #pgm.add_node(Node('G_Ni',r"$g_{Ni}$", 8,5))
 
@@ -35,16 +36,15 @@ pgm.add_node(Node('Type',r"\centering{Type \newline Subtype}", 2, 6, scale=1.6,a
 
 
 #pgm.add_node(Node('theta_Ti',r"\centering{Transient \newline Parameters}", 1,5,scale=1.5,aspect=1.2))
-pgm.add_node(Node('HD',r"Distance", 8,6,fixed=True,offset=(-25,-15)))
+pgm.add_node(Node('HD',r"Distance", 7,6,fixed=True,offset=(-25,-15)))
 
 
-pgm.add_node(Node('Luminosity',r"Luminosity", 6, 4,scale=1.6,aspect=1.2))
+pgm.add_node(Node('Luminosity',r"Luminosity", 5, 4,scale=1.6,aspect=1.2))
 
 
[…]

### 2015-11-05 doc/article.tex
more train of thought

@@
 \epsilon(Photometry_o; b_{k})= \prod_{\nu i}\mathcal{H}\left((-1)^{b_{k\nu i}+1}(Photometry_{o,k\nu i}-Threshold_{\nu i})\right),
+\label{eff:eqn}
 \end{equation}
@@
 
-A clean deliverable would be:
+\subsection{Detection Criteria (Malmquist Bias)}
+The photometric selection criteria are expected to be significantly more rigorous that
+the detection criteria.  Nevertheless, the detection efficiencies need to be characterized.
+Fakes already provide a good measure of this.  To first order, the efficiency depends
+on $S/N$, but a secondary dependence on the structure of background galaxies.
+The detection efficiency is more complicated than the step function
+shown in Eqn.~\ref{eff:eqn}.
+
+Deliverable is the detection efficiency to take the place of Eqn.~\ref{eff:eqn}.
+
+\subsection{Per-Exposure Thresholds}
+To understand the effect of sample-selection criteria and detection efficiency
+on a specific object, the
+properties of each photometric point is needed.  Although the photometric criteria
+have not been formalized, a $S/N$ threshold is a possible statistic to be used.
+As such, a clean deliverable would be:
 \begin{itemize}
-\item Determination of flux thresholds for each photometric point given
-a $S/N$ threshold
+\item Determination of flux thresholds for each photometric point of each candidate
+given
+a $S/N$
 \begin{equation}
@@
 
+\subsection{Photometric Data}
+
+Deliverable:
+transient counts and associated covariance matrix.  For flexibility, the counts and the
+flux calibration are delivered separately.
+
+\subsection{Calibration model and uncertainties}
+For the first analysis, it is presumably sufficient to describe calibration uncertainties
+as global zeropoints.  In the long term, it would be great to have a transmission
+function for every photometric point.
+
+It has to be decided whether calibration should be included
+as part of the photometric uncertainties, or as model parameters.
+The former requires the inversion of a full covariance matrix for all photometric
+points.  The latter may have a per-SN solution through importance sampling.
+
+Deliverable of $p(Z)$.
+
 \subsection{Others}
@@
 \begin{itemize}
-\item Calibration model and uncertainties. Assuming we work with zeropoints
-$p(Z)$ is needed.
 \item Data! Spectroscopic Type and uncertainties, Spectroscopic redshifts and

### 2015-11-08 src/toy.py
make distinct toy and real code.

@@ -1,0 +1,324 @@
+#!/usr/bin/env python
+
+#import matplotlib
+#matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+from matplotlib.backends.backend_pdf import PdfPages
+import pystan
+import numpy.random
+from astropy.cosmology import FlatLambdaCDM
+import scipy
+
+import pickle
+
+class Data(object):
+	"""docstring for Data"""
+	def __init__(self, N_sn, seed, pop2=False, asifIa = False):
+		super(Data, self).__init__()
+		self.N_sn = N_sn
+		self.seed = seed
+
+		self.omega_M=0.28
+		self.cosmo=FlatLambdaCDM(70,self.omega_M)
+
+		self.zmin=0.1
+		self.zmax=1.4
+
+		self.sigma_snIa=0.1
+		self.sigma_nonIa=1.
+		self.sigma_nonIa_2=0.25
+
+		self.alpha_snIa=2.
+		self.alpha_nonIa=self.alpha_snIa*10**(-2./2.5)
+		self.alpha_nonIa_2=self.alpha_snIa*10**(-0.5/2.5)
+
+		self.frac_Ia_0=.95
+		self.frac_Ia_1=.2
+
+		self.asifIa = asifIa
+
+
+		if pop2:
+			self.frac_nonIa_0=1.
+			self.frac_nonIa_1=0.2
+		else:
+			self.frac_nonIa_0=1.
+			self.frac_nonIa_1=1.
+
+
+		numpy.random.seed(seed)
+		self.initialize_()
+
+	def initialize_(self):
+		self.redshifts_()
+		self.types_()
+		self.adus_()
+		self.hosts_()
+
+	def redshifts_(self):
+		# zs : the true redshifts
+		# volume_zero = self.cosmo.comoving_volume(self.zmin).value
+		# volume_norm = self.cosmo.comoving_volume(self.zmax).value- volume_zero
+
+		# self.zs = numpy.sort(numpy.random.uniform(size=self.N_sn))
+
+		#self.zs=numpy.sort(numpy.random.uniform((1+self.zmin)**3,(1+self.zmax)**3,size=self.N_sn)**(1./3)-1)
+		#self.zs=numpy.sort(numpy.random.uniform((1+self.zmin)**3,(1+self.zmax)**3,size=self.N_sn)**(1./3)-1)
+		# for i in xrange(len(self.zs)):
[…]

### 2015-11-09 src/data.py
starting new code to simulate data based on pgm

@@ -1,0 +1,387 @@
+#!/usr/bin/env python
+
+#import matplotlib
+#matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+from matplotlib.backends.backend_pdf import PdfPages
+import pystan
+import numpy.random
+from astropy.cosmology import FlatLambdaCDM
+import scipy
+import sncosmo
+import pickle
+
+cosmology=FlatLambdaCDM(73.,0.28)
+
+class HostGalaxies(object):
+	"""docstring for HostGalaxy"""
+
+	zmin = 0.1
+	zmax = 1.4
+	def __init__(self, N_sn):
+		super(HostGalaxies, self).__init__()
+		self.N_sn = N_sn
+		self.zs = numpy.sort(numpy.random.uniform(HostGalaxies.zmin**3, HostGalaxies.zmax**3,size=self.N_sn)**(1./3))
+		self.parameters=None
+	
+	def redshift(self, index):
+		return self.zs[index]
+
+	def redshifts(self):
+		return self.zs
+
+class Throughput(object):
+	"""docstring for Throughput"""
+
+	def __init__(self):
+		super(Throughput, self).__init__()
+		self.zp_0 = numpy.array([22.,22,22,22])
+		self.stdev = numpy.array([0.01,0.01,0.01,0.02])
+		self.zp = numpy.random.normal(loc=self.zp_0, scale=self.stdev)
+
+	def zeropoints(self):
+		return numpy.array(self.zp)
+
+
+wefew
+
+class SNIa(object):
+	"""docstring for SNIa"""
+	__par_names__ = ['x0', 'x1', 'c','ebv', 'r_v']
+	def __init__(self):
+		super(SNIa, self).__init__()
+		self.source = sncosmo.SALT2Source(modeldir="../data/salt2-4")
+		self.dust = sncosmo.CCM89Dust()
+		self.model = sncosmo.Model(source=self.source, effects=[self.dust],effect_names=['host'], effect_frames=['rest'])
+		self.model.set(z=0.0001)
+
+
+	def luminosity(self, phase, **kwargs):
+		self.model.set(**kwargs)
+		self.model.set_source_peakabsmag(-19.0, 'bessellb', 'ab')
[…]

### 2015-11-10 src/data.py
making progress with simulated data generator but not done

@@ -6,382 +6,307 @@ import matplotlib.pyplot as plt
 from matplotlib.backends.backend_pdf import PdfPages
 import pystan
 import numpy.random
-from astropy.cosmology import FlatLambdaCDM
+from astropy.cosmology import FlatwCDM
 import scipy
 import sncosmo
 import pickle
+import astropy.units as u
+import abc
 
-cosmology=FlatLambdaCDM(73.,0.28)
+class Source(object):
 
-class HostGalaxies(object):
-	"""docstring for HostGalaxy"""
-
-	zmin = 0.1
-	zmax = 1.4
-	def __init__(self, N_sn):
-		super(HostGalaxies, self).__init__()
-		self.N_sn = N_sn
-		self.zs = numpy.sort(numpy.random.uniform(HostGalaxies.zmin**3, HostGalaxies.zmax**3,size=self.N_sn)**(1./3))
-		self.parameters=None
+	__metaclass__ = abc.ABCMeta
+	__input__ = None
 	
-	def redshift(self, index):
-		return self.zs[index]
+	#must have rates rule and luminosity 
+	# @abc.abstractmethod
+	# def luminosity(self):
+	# 	return
 
-	def redshifts(self):
-		return self.zs
+	# @abc.abstractmethod
+	# def relativeRates(self):
+	# 	return
+
+class Cosmology(object):
+	"""docstring for Cosmology"""
+
+	__input__ = None
+	__par_names__ = ['H0', 'Omega_M' 'w']
+
+	H0 = 72.
+	Omega_M = 0.28
+	w =-1
+
+	cosmology = FlatwCDM(H0,Omega_M,w)
+
 
 class Throughput(object):
 	"""docstring for Throughput"""
+	__input__ = None
+	__par_names__ = ['zp']
+
+	filters = [sncosmo.get_bandpass('desg'),sncosmo.get_bandpass('desr'),sncosmo.get_bandpass('desi'),
+		sncosmo.get_bandpass('desz')]
+
+	zp = numpy.array([22.,22,22,22])
+
+
+class HostGalaxy(object):
+	"""docstring for HostGalaxy"""
+
+	__input__ = None
+	__par_names__ = ['host_z']
+
+	zmin = 0.1
+	zmax = 1.4
 
 	def __init__(self):
-		super(Throughput, self).__init__()
-		self.zp_0 = numpy.array([22.,22,22,22])
[…]

### 2015-11-12 src/data.py
new calibration.  refinement of data simulation>

@@ -12,20 +12,28 @@ import sncosmo
 import pickle
 import astropy.units as u
 import abc
+import copy
 
-class Source(object):
+"""
+Each bubble of the PGM is described by a class.  The has internal variables __input__ and __par_names__
+to specify the anteceding bubbles and the PGM parameters that are realized in the bubble.  The values
+of the parameters are stored in class/object variables.  The parameters are either a class variable or
+created by the constructor.
 
-	__metaclass__ = abc.ABCMeta
-	__input__ = None
-	
-	#must have rates rule and luminosity 
-	# @abc.abstractmethod
-	# def luminosity(self):
-	# 	return
 
-	# @abc.abstractmethod
-	# def relativeRates(self):
-	# 	return
+There is one object per bubble.  For example, there is only one Cosmology, therefore the Cosmology
+class is a singleton.  There are many HostGalaxy's, and a distinct object is used
+to represent each one.
+
+The top-level Universal bubbles (Cosmolgy, Rates, Source, Throughput) have parameters that are fixed.
+For simulating data, they are fixed so we can precisely control the top-level configuration.
+We may want to change this.  In the analysis these parameters are probabilisitic.
+
+The Luminosity and Flux information are stored as an sncosmo.Model.
+
+All the observed parameters are distinguished with _o.
+
+"""
 
 class Cosmology(object):
 	"""docstring for Cosmology"""
@@ -40,16 +48,117 @@ class Cosmology(object):
 	cosmology = FlatwCDM(H0,Omega_M,w)
 
 
-class Throughput(object):
-	"""docstring for Throughput"""
+class GlobalThroughput(object):
+	"""docstring for GlobalThroughput"""
 	__input__ = None
-	__par_names__ = ['zp']
+	__par_names__ = ['zeropoints'] 
 
-	filters = [sncosmo.get_bandpass('desg'),sncosmo.get_bandpass('desr'),sncosmo.get_bandpass('desi'),
-		sncosmo.get_bandpass('desz')]
[…]

### 2015-11-12 src/pgm.py

@@ -13,7 +13,8 @@ pgm = PGM([9.5, 8.5], origin=[0., 0.2], observed_style='inner')
 pgm.add_node(Node('rate',r"{\center Relative \newline Rates}", 2,8,scale=1.6,aspect=1.2))
 #pgm.add_node(Node('theta_T',r"\center{$\alpha_{Ia}$, $\alpha_{!Ia}$ \newline $\beta_{Ia}$, $\beta_{!Ia}$}", 4,6,scale=1.4,aspect=1.8))
 pgm.add_node(Node('theta_T',r"\center{SNe~Ia, Non-Ia \newline Populations}", 5,8,scale=1.8,aspect=1.2))
-pgm.add_node(Node('Transmission',r"Throughput", 8, 8,scale=1.6,aspect=1.2))
+pgm.add_node(Node('Global Transmission',r"\centering{Global \newline Throughput}", 8, 8,scale=1.6,aspect=1.2))
+pgm.add_node(Node('Transmission',r"Throughput", 8, 4,scale=1.6,aspect=1.2))
 #pgm.add_node(Node('theta_T2',r"{Non-Ia}", 4,8,scale=1.6,aspect=1.2))
 pgm.add_node(Node('mu',r"{\center Cosmology}", 7,8, scale=1.6,aspect=1.2))
 
@@ -84,6 +85,7 @@ pgm.add_edge("Flux","^Counts")
 #pgm.add_edge("Flux_g","Counts_g")
 #pgm.add_edge("Counts","^Counts")
 #pgm.add_edge("Counts_g","^Counts")
+pgm.add_edge("Global Transmission","Transmission")
 pgm.add_edge("Transmission","^Counts")
 #pgm.add_edge("Transmission","Counts_g")
 pgm.add_edge("Type","ST")

### 2015-11-12 doc/article.tex
test of slack
test des-sn slack
get rid of absolute paths in document.
Fix flux calculation as sncosmo source normalization is based
of f, not f_lambda

@@
    \centering
-   \includegraphics[width=6.5in]{/Users/akim/project/abc/results/hdpgm.pdf} 
+   \includegraphics[width=6.5in]{../results/hdpgm.pdf} 
    \caption{Probabilistic Graphical Model for the SN~Ia analysis.  
@@
 from which the likelihood of the analysis sample is assembled.
+
+\section{Design}
+\subsection{Data}
+There is photometry, redshift, host properties, type/subtype.  The pdf's of redshift and
+host-properties may be more complicated than a normal distribution due to uncertain host
+determination and photometric redshifts.  The photometry is expected to be a Gaussian
+with a full covariance matrix due to the host-galaxy subtraction.
 
@@
 
+Danny writes everything!
 %\section{Misc}
@@
 \bibliographystyle{elsarticle-num} 
-\bibliography{/Users/akim/Documents/alex}
+\bibliography{alex}
 

### 2015-11-12 src/data.py

@@ -256,10 +256,10 @@ class Flux(object):
 
 		if self.luminosity.type.type ==0:
 			x0=self.model.get('x0')
-			self.model.set(z=host.host_z,x0=x0/distance.luminosity_distance**2/1e10*(1+self.host.host_z)**2)
+			self.model.set(z=host.host_z,x0=x0/distance.luminosity_distance**2/1e10)
 		else:
 			x0=self.model.get('amplitude')
-			self.model.set(z=host.host_z,amplitude=x0/distance.luminosity_distance**2/1e10*(1+self.host.host_z)**2)
+			self.model.set(z=host.host_z,amplitude=x0/distance.luminosity_distance**2/1e10)
 
 		self.model.set(t0=self.luminosity.type.t0)
 		

### 2015-11-12 src/data.py
fix throughput so there is one for each observation.

@@ -317,10 +317,10 @@ class Photometry(object):
 
 	sky_sigma = 1.
 	correlated_noise = .01
-	def __init__(self, flux, throughput):
+	def __init__(self, flux, throughputs):
 		super(Photometry, self).__init__()
 		self.flux = flux
-		self.throughput = throughput
+		self.throughputs = throughputs
 
 	def photometry(self,mjds,bands):
 		ans=dict()
@@ -329,7 +329,7 @@ class Photometry(object):
 			corr = numpy.random.normal(0,Photometry.correlated_noise)
 			for mjd in mjds:
 				try:
-					mn=self.flux.model.bandflux(b, mjd, zp = self.throughput.zeropoints[b], zpsys='ab')
+					mn=self.flux.model.bandflux(b, mjd, zp = self.throughputs[b][mjd].zeropoints[b], zpsys='ab')
 				except:
 					mn=0.
 
@@ -337,13 +337,24 @@ class Photometry(object):
 				ans[b][mjd]=mn+corr
 		return ans
 
+class ExtractedPhotometry(object):
+	"""docstring for MeasuredPhotometry"""
+
+	__input__ = [Photometry]
+	__par_names__ = ["ExtractedPhotometry_o"]
+	def __init__(self, arg):
+		super(ExtractedPhotometry, self).__init__()
+		self.arg = arg
+		
+
 
 def data(N_sn):
 
+	mjds=numpy.arange(53010, 53210,6)
 	out=dict()
 
 
-	gThroughput = GlobalThroughput()
+	#	gThroughput = GlobalThroughput()
 	for i in xrange(N_sn):
 		host  = HostGalaxy()
 	#	print host.host_z
@@ -363,7 +374,6 @@ def data(N_sn):
 
 		flux = Flux(luminosity,host,distance)
 
-		photometry = Photometry(flux, gThroughput)
 
 		#Data
 		specType = SpecType(modeltype)
@@ -375,8 +385,18 @@ def data(N_sn):
 		specRedshift = SpecRedshift(host)
 		print specRedshift.redshift_spec_o
 
+		throughput  = Throughput(GlobalThroughput)
 
-		phot = photometry.photometry(numpy.arange(53010, 53210,6), gThroughput.filters())
+
+		throughputs = dict()
+		for b in GlobalThroughput.filters():
+			throughputs[b] = dict()
+			for mjd in mjds:
+				throughputs[b][mjd] = throughput
+
[…]

### 2015-11-12 doc/article.tex

@@
 Large Synoptic Survey Telescope\footnote{\url{http://www.lsst.org}} (LSST)
-and the Wide-Field InfrarRed Survey Telescope
+and the Wide-Field InfraRed Survey Telescope
 \citep{2015arXiv150303757S}.
@@
 residuals is a good probe of systematics,
-a direction connection between host galaxy and luminosity is made.
+a direct connection between host galaxy and luminosity is made.
 \item[Flux] Flux of the transient incident to earth at the date of observation.  It is 
@@
 \end{description}
-The observatory is described by the following element:
+The observatory is described by the following elements:
 \begin{description}
@@
 \subsection{Detection Criteria (Malmquist Bias)}
-The photometric selection criteria are expected to be significantly more rigorous that
+The photometric selection criteria are expected to be significantly more rigorous than
 the detection criteria.  Nevertheless, the detection efficiencies need to be characterized.
@@
 on a specific object, the
-properties of each photometric point is needed.  Although the photometric criteria
+properties of each photometric point are needed.  Although the photometric criteria
 have not been formalized, a $S/N$ threshold is a possible statistic to be used.

### 2015-11-26 src/Sim.py
refactoring of simulation classes, and a driver for a specific implementation.

@@ -1,0 +1,397 @@
+import numpy.random
+from astropy.cosmology import FlatwCDM
+import scipy
+import sncosmo
+import abc
+import copy
+
+"""
+Each bubble of the PGM is described by a class.  The has internal variables __input__ and __par_names__
+to specify the anteceding bubbles and the PGM parameters that are realized in the bubble.  The values
+of the parameters are stored in class/object variables.  The parameters are either a class variable or
+created by the constructor.
+
+
+There is one object per bubble.  For example, there is only one Cosmology, therefore the Cosmology
+class is a singleton.  There are many HostGalaxy's, and a distinct object is used
+to represent each one.
+
+The top-level Universal bubbles (Cosmolgy, Rates, Source, Throughput) have parameters that are fixed.
+For simulating data, they are fixed so we can precisely control the top-level configuration.
+We may want to change this.  In the analysis these parameters are probabilisitic.
+
+The Luminosity and Flux information are stored as an sncosmo.Model.
+
+All the observed parameters are distinguished with _o.
+
+"""
+
+class Cosmology(object):
+	"""docstring for Cosmology"""
+
+	__input__ = None
+	__par_names__ = ['H0', 'Omega_M' 'w']
+
+	H0 = 72.
+	Omega_M = 0.28
+	w =-1
+
+	cosmology = FlatwCDM(H0,Omega_M,w)
+
+
+class GlobalThroughput(object):
+	"""docstring for GlobalThroughput"""
+	__input__ = None
+	__par_names__ = ['zeropoints'] 
+
+	zeropoints = dict(zip([sncosmo.get_bandpass('desg'),sncosmo.get_bandpass('desr'),sncosmo.get_bandpass('desi'),
+		sncosmo.get_bandpass('desz')],numpy.array([20.,20,20,20])))
+
+	@staticmethod
+	def filters():
+		return GlobalThroughput.zeropoints.keys()
+
+
+class Source(object):
+	"""docstring for Source"""
+	__metaclass__ = abc.ABCMeta
+	__input__ = None
+
+	model_pars =None
+	
+	@abc.abstractmethod
+	def luminosity(**kwargs):
+		return
+
[…]

### 2015-11-26 src/data.py

@@ -13,342 +13,21 @@ import pickle
 import astropy.units as u
 import abc
 import copy
-
-"""
-Each bubble of the PGM is described by a class.  The has internal variables __input__ and __par_names__
-to specify the anteceding bubbles and the PGM parameters that are realized in the bubble.  The values
-of the parameters are stored in class/object variables.  The parameters are either a class variable or
-created by the constructor.
-
-
-There is one object per bubble.  For example, there is only one Cosmology, therefore the Cosmology
-class is a singleton.  There are many HostGalaxy's, and a distinct object is used
-to represent each one.
-
-The top-level Universal bubbles (Cosmolgy, Rates, Source, Throughput) have parameters that are fixed.
-For simulating data, they are fixed so we can precisely control the top-level configuration.
-We may want to change this.  In the analysis these parameters are probabilisitic.
-
-The Luminosity and Flux information are stored as an sncosmo.Model.
-
-All the observed parameters are distinguished with _o.
-
-"""
-
-class Cosmology(object):
-	"""docstring for Cosmology"""
-
-	__input__ = None
-	__par_names__ = ['H0', 'Omega_M' 'w']
-
-	H0 = 72.
-	Omega_M = 0.28
-	w =-1
-
-	cosmology = FlatwCDM(H0,Omega_M,w)
-
-
-class GlobalThroughput(object):
-	"""docstring for GlobalThroughput"""
-	__input__ = None
-	__par_names__ = ['zeropoints'] 
-
-	zeropoints = dict(zip([sncosmo.get_bandpass('desg'),sncosmo.get_bandpass('desr'),sncosmo.get_bandpass('desi'),
-		sncosmo.get_bandpass('desz')],numpy.array([20.,20,20,20])))
-
-	@staticmethod
-	def filters():
-		return GlobalThroughput.zeropoints.keys()
-
-
-class Source(object):
-	"""docstring for Source"""
-	__metaclass__ = abc.ABCMeta
-	__input__ = None
-
-	model_pars =None
-	
-	@abc.abstractmethod
-	def luminosity(**kwargs):
-		return
-
[…]

### 2015-11-26 src/Sim.py
change output of realizer to dictioary

@@ -353,7 +353,11 @@ class SurveyModel(object):
 		self.global_throughput=global_throughput
 
 	def realize(self, survey):
+
+		ans = dict()
+
 		for i in xrange(survey.n_sn):
+			ans[i] = dict()
 			host  = self.host()
 
 			modeltype = ModelType(self.rates, host)
@@ -369,13 +373,13 @@ class SurveyModel(object):
 
 			#Data
 			specType = SpecType(modeltype)
-			print RelativeRates.sources[specType.type_o].__name__
+			ans[i]['Spec Type']= RelativeRates.sources[specType.type_o].__name__
 
 			photRedshift = PhotRedshift(host)
-			print photRedshift.redshift_phot_o
+			ans[i]['Phot Type']= photRedshift.redshift_phot_o
 
 			specRedshift = SpecRedshift(host)
-			print specRedshift.redshift_spec_o
+			ans[i]['Spec z']= specRedshift.redshift_spec_o
 
 			throughput  = Throughput(self.global_throughput)
 
@@ -386,12 +390,12 @@ class SurveyModel(object):
 				for mjd in survey.mjds:
 					throughputs[b][mjd] = throughput
 
+			ans[i]['Throughputs'] = throughputs
+
 			photometry = Photometry(flux, throughputs)
 
 			phot = photometry.photometry(survey.mjds, GlobalThroughput.filters())
 
-			for pkey in phot.keys():
-				print pkey.name
-				for mkey in phot[pkey]:
-					print mkey, phot[pkey][mkey]
+			ans[i]['Photometry'] = phot
+		return ans
 		

### 2015-11-26 src/data.py

@@ -25,7 +25,17 @@ def data():
 	global_throughput=  Sim.GlobalThroughput
 
 	sim   = Sim.SurveyModel(cosmology, rates, host, global_throughput)
-	sim.realize(survey)
+	ans = sim.realize(survey)
+
+	for k in iter(ans):
+		print 'SN ',k
+		print ans[k]['Spec Type']
+		print ans[k]['Phot Type']
+		print ans[k]['Spec z']
+		for pkey in ans[k]['Photometry'].keys():
+			print pkey.name
+			for mkey in ans[k]['Photometry'][pkey]:
+				print mkey, ans[k]['Photometry'][pkey][mkey]
 
 def data2(N_sn):
 

### 2015-11-26 src/data.py
erase old code

@@ -37,61 +37,6 @@ def data():
 			for mkey in ans[k]['Photometry'][pkey]:
 				print mkey, ans[k]['Photometry'][pkey][mkey]
 
-def data2(N_sn):
-
-	mjds=numpy.arange(53010, 53210,6)
-	out=dict()
-
-
-	#	gThroughput = GlobalThroughput()
-	for i in xrange(N_sn):
-		host  = Sim.HostGalaxy()
-	#	print host.host_z
-
-	#	model_pars = {'x0':1, 'x1':0, 'c':0 } #,'ebv':0, 'r_v':3.1}
-	#	print snIa.luminosity(0.,4400.,**model_pars)
-
-
-
-		modeltype = Sim.ModelType(Sim.RelativeRates, host)
-		# print ttype.ttype, ttype.subtype
-
-		distance = Sim.Distance(Sim.Cosmology, host)
-	#	print distance.luminosity_distance()
-
-		luminosity = Sim.Luminosity(modeltype,host)
-
-		flux = Sim.Flux(luminosity,host,distance)
-
-
-		#Data
-		specType = Sim.SpecType(modeltype)
-		print Sim.RelativeRates.sources[specType.type_o].__name__
-
-		photRedshift = Sim.PhotRedshift(host)
-		print photRedshift.redshift_phot_o
-
-		specRedshift = Sim.SpecRedshift(host)
-		print specRedshift.redshift_spec_o
-
-		throughput  = Sim.Throughput(Sim.GlobalThroughput)
-
-
-		throughputs = dict()
-		for b in Sim.GlobalThroughput.filters():
-			throughputs[b] = dict()
-			for mjd in mjds:
-				throughputs[b][mjd] = throughput
-
-		photometry = Sim.Photometry(flux, throughputs)
-
-		phot = photometry.photometry(mjds, Sim.GlobalThroughput.filters())
-
-		for pkey in phot.keys():
-			print pkey.name
-			for mkey in phot[pkey]:
-				print mkey, phot[pkey][mkey]
-
 def main():
 	ans = data()
 

### 2015-11-26 src/Sim.py
fix but in the passing of the transmission zeropoints

@@ -173,7 +173,7 @@ class Throughput(object):
 	def __init__(self, gthroughput):
 		super(Throughput, self).__init__()
 		self.global_throughput = gthroughput
-		self.zeropoints = gthroughput.filters
+		self.zeropoints = gthroughput.zeropoints
 
 	def filters(self):
 		return self.global_throughput.filters()
@@ -321,7 +321,6 @@ class Photometry(object):
 					mn=self.flux.model.bandflux(b, mjd, zp = self.throughputs[b][mjd].zeropoints[b], zpsys='ab')
 				except:
 					mn=0.
-
 				mn = numpy.random.normal(mn,Photometry.sky_sigma)
 				ans[b][mjd]=mn+corr
 		return ans
@@ -340,7 +339,7 @@ class Survey(object):
 	def __init__(self):
 		super(Survey, self).__init__()
 		self.mjds = mjds=numpy.arange(53010, 53210,6)
-		self.n_sn = 5
+		self.n_sn = 1
 		
 
 class SurveyModel(object):

### 2015-11-27 doc/article.tex
Updating master equation

@@
 , Host, Population) p(Type | Rates, Host)  \nonumber\\
-& \times \int dType\, p(Type_0|Type) p(Type|Rates, Host) \nonumber \\
+& \times \int dType\, p(Type_o|Type) p(Type|Rates, Host) \nonumber \\
 & \times p(Redshift_o, Host_o| Host),
@@
 where $data=\{Photometry_o, Type_o, Redshift_o, Host_o\}$,
-$model=\{Cosmology, Populations, Rates\}$, and the independence
+$model=\{Cosmology, Populations, Rates, Throughput, Host\}$, and the independence
 of photometric and spectroscopic typing measurements is anticipated.

### 2015-12-15 doc/article.tex
simplify the conditional likelihood equation

@@
 Assembling this together, the likelihood is
-\begin{equation}
-\mathcal{L}(data|\mathcal{S}, model) = \frac{\sum_{k=1}^{\prod_\nu \sum_{k=N}^{M_{\nu}} \binom{M_{\nu}}{k}} \epsilon(Photometry_o, b_k)p(data| model)}{\int ddata\,
-\sum_{k=1}^{\prod_\nu \sum_{k=N}^{M_{\nu}} \binom{M_{\nu}}{k}} \epsilon(Photometry_o, b_k)p(data| model)
+\begin{align}
+\mathcal{L}(data|\mathcal{S}, model) & = \frac{\sum_{k=1}^{\prod_\nu \sum_{k=N}^{M_{\nu}} \binom{M_{\nu}}{k}} \epsilon(Photometry_o, b_k)p(data| model)}{\int ddata'\,
+\sum_{k=1}^{\prod_\nu \sum_{k=N}^{M_{\nu}} \binom{M_{\nu}}{k}} \epsilon(Photometry_o', b_k)p(data'| model)
+}\\
+& = \frac{p(data| model)}{\int ddata'\,
+\sum_{k=1}^{\prod_\nu \sum_{k=N}^{M_{\nu}} \binom{M_{\nu}}{k}} \epsilon(Photometry_o', b_k)p(data'| model)
 }
-\end{equation}
+\end{align}
 where the normalizing factor is included explicitly as it has 

### 2016-02-02 doc/toy.tex
implemented normalization factor.  In principle everything in the toy pgm is accounted for. Have been having problems with theano nesting depth.  Now running to see how it does.

\documentclass[preprint,3p]{elsarticle}
%\documentclass[preprint]{aastex}
\usepackage{aas_macros}
\usepackage{amsmath,amssymb}
\usepackage{mathrsfs}
\usepackage{graphicx}
\usepackage{bm}
\usepackage{hyperref}
\DeclareMathOperator\erf{erf}
\newcommand{\mli}[1]{\mathit{#1}}
%\usepackage{epstopdf}

\begin{document}

%\begin{frontmatter}
%
%\title{Toy Model}
%\author{A.~G. Kim\corref{cor1}}
%\ead{agkim@lbl.gov}
%\address{Physics Division, Lawrence Berkeley National Laboratory, 1 Cyclotron Road, Berkeley CA, USA 94720}
%
%\begin{abstract}
%\end{abstract}
%\begin{keyword}
%\end{keyword}
%\end{frontmatter}

\section{Likelihood}
\label{likelihood:sec}

The ambition is to construct a model to determine the likelihood of DES-like
supernova data.
The conceptual structure of the model is shown in Figure~\ref{pgm:fig}. 
\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=6.5in]{../results//nodes_pgm.pdf} 
   \caption{Probabilistic Graphical Model for the SN~Ia analysis.  
   \label{pgm:fig}}
\end{figure}

In the toy model there are three types of data that
may be observed for each supernova:
\begin{itemize}
\item $c_o$: Counts at peak brightness.
\item $z_o$: Redshift.
\item $T_o$: Transient type.
\end{itemize}

There are selection criteria $S_c$ and $S_T$ for the inclusion of an object in the
sample and for a successul typing.
In what follows we assume that the typed objects are drawn from the same underlying
distribution as the sample $S_c=S_T$, and that the selection criterion is a brightness
threshold $S_c = c_o \ge c_T$.  (The spectroscopic sample $S_T$ 
eventually should depend on the
photometry and the quality of the spectroscopic data.)

For this preliminary discussion the top-level parameters are denoted by $X$,
latent parameters $L$ and $T$.

It is useful to split the data into two cases depending on whether or not
the transient has a type measurement $T_o$.

\subsection{Case Typed}
For Case Typed the likelihood is
\begin{align}
\mathcal{L}(T_o,z_o,c_o | S_c, S_T, z, X) & =  \int dL \sum_i p(T_o,z_o,c_o | T_i, L, S_c, S_T, z, X) p(L |  T_i,  S_c, S_T, z, X) P(T_i|S_c, S_T, z, X).
\end{align}
We assume that the observations give a perfect measurement of type and redshift,
so that
\begin{align}
p(T_o|T) & =\delta(T_o-T)\\
p(z_o|z) & =\delta(z_o-z);
\end{align}
practically $T$ and $z$ are no longer probabilistic but are fixed.
Then
\begin{align}
\mathcal{L}(T_o,z_o,c_o | S_c, S_T, z, X) & =  \int dL p(c_o | T=T_o, L, S_c, S_T, z=z_o, X) p(L| T=T_o, S_c, S_T, z=z_o, X)  P(T_o|S_c, S_T, z=z_o, X) \\
&= \int dL \frac{ p(c_o, S_c, S_T | T=T_o, L, z=z_o, X) }{P(S_c, S_T, | T=T_o, L,  z=z_o, X) }
\frac{p(L, S_c, S_T | T=T_o, z=z_o, X)}{P(S_c, S_T| T=T_o,  z=z_o, X)}
\frac{p(T_o, S_c, S_T | z=z_o, X)}{P(S_c, S_T| z=z_o, X)} \\
&= \frac{\int dL p(L|T_o, z=z_o, X) P(T_o|z=z_o, X) p(c_o, S_c, S_T | T=T_o, L, z=z_o, X)}{P(S_c, S_T| z=z_o, X)}
\end{align}

The normalization term is determined by
\begin{align}
P(S_c, S_T| z=z_o, X) & =\sum_i \int_{-\infty}^{\infty} dc_o \mathcal{L}(T_i,z_o,c_o | S_c, S_T, z, X) \\
& = \sum_i \int_{c_T}^{\infty} dc_o \mathcal{L}(T_i,z_o,c_o | S_c, S_T, z, X)\\
& = \sum_i  P(T_i|z=z_o, X)\int dL p(L|T_i, z=z_o, X)  \left[\int_{c_T}^{\infty} dc_o  p(c_o | T=T_i, L, z=z_o, X)\right]
\end{align}
as $p(c_o | T=T_o, L, z)=0$ when $c_o < c_T$.

\subsection{Case Not Typed}

For Case Not Typed the likelihood is
\begin{align}
\mathcal{L}(z_o,c_o | S_c, S_T, z, X) & =  \int dL \sum_i p(z_o,c_o | T_i, L, S_c, S_T, z, X) p(L |  T_i,  S_c, S_T, z, X) P(T_i|S_c, S_T, z, X).
\end{align}

For the redshift measurement, we take a set of potential host galaxies, where galaxy $j$
are redshift $z_j$ has probability $p_j$ of being the host
\begin{equation}
p(z_o|S_c, S_T, z, X) = \sum_j p_j\delta(z_j-z).
\end{equation}
Then
\begin{align}
\mathcal{L}(z_o,c_o | S_c, z, X) & =  \sum_j p_j \int dL \sum_{i} p(c_o | T_i, L, S_c, z=z_j, X) p(L |  T_i,  S_c,  z=z_j, X) P(T_i|S_c, z=z_j, X) \\
&=  \frac{\sum_j p_j \int dL \sum_{i}  p(L|T_i, z=z_j, X) P(T_i|z=z_j, X)  p(c_o, S_c | T=T_i, L, z=z_j, X) }{P(S_c| z=z_j, X)}
\end{align}

The normalization term is
\begin{align}
P(S_c| z=z_o, X) & = \int_{c_T}^{\infty} dc_o \mathcal{L}(T_i,z_o,c_o | S_c, S_T, z, X)\\
& =  \sum_j p_j  \sum_{i} P(T_i|z=z_j, X)  \int dL  p(L|T_i, z=z_j, X) 
\left[ \int_{c_T}^\infty dc_o p(c_o| T=T_i, L, z=z_j, X) \right].
\end{align}

\section{Model}
\label{model:sec}

We now go into more detail into the model and the form of the pdf's that enter
into the likelihoods described in \S\ref{likelihood:sec}.

A description of the nodes follow.  Numbers are illustrative.

\subsection{Cosmology}
The Flat $w$CDM cosmology.

\begin{align}
\Omega_M & \sim \ln{\mathcal{N}}(\ln{0.28},0.1)\\
w_0 & \sim \mathcal{N}(-1,0.05)
\end{align}

\subsection{Calibration}
Photometric zeropoints for each band.
\begin{equation}
Z \sim \mathcal{N}(0,0.02)
\end{equation}

\subsection{SNIa Rate}
Type~Ia SN rate. In the analysis only relative rates between different transients are important.
We take the rates relative to the SN~Ia rate
\begin{equation}
r_{SNIa} = 1.
\end{equation}

\subsection{SNII Rate}
Type~II SN rate, relative to the SN~Ia rate
\begin{equation}
r_{SNII} \sim \mathcal{U}(0.25, 4).
\end{equation}

\subsection{SNIa Luminosity}
The mean luminosity and intrinsic dispersion for SNe~Ia. In fact work with log-luminosity, intrinsic
dispersion in mag units.
\begin{align}
\ln{L}_{SNIa} & \sim \mathcal{N}(\ln{1}, 0.02) \\
\sigma_{SNIa} & \sim \ln{\mathcal{N}}(\ln{0.1},0.1).
\end{align}

\subsection{SNII Luminosity}
The mean luminosity and intrinsic dispersion for SNe~II. In fact work with log-luminosity, intrinsic
dispersion in mag units.
\begin{align}
\ln{L}_{SNII} & \sim \mathcal{N}(\ln{0.5}, 0.02) \\
\sigma_{SNII} & \sim \ln{\mathcal{N}}(\ln{0.4},0.1).
\end{align}

\subsection{SNIa~Probability}
Probability an object is SN~Ia
\begin{align}
p_{SNIa} &= \frac{r_{SNIa}}{r_{SNIa}+r_{SNII}} \nonumber \\
p_{SNII}&=1-p_{SNIa}.
\label{prob:eqn}
\end{align}
\subsection{Type}
The type of the object $T$ is drawn from the Bernoulli distribution 
\begin{equation}
T | p_{SNIa} \sim \mathcal{B}(1-p_{SNIa}),
\end{equation}
with the convention that $T=0$ corresponds to SN~Ia.

The type probability appears explicitly in the calculation of the likelihoods.
\begin{align}
P(T_{SNIa} | z=z_j, X) &= p_{SNIa}\\
P(T_{SNII} | z=z_j, X) &= p_{SNII}
\end{align}
\subsection{Observed Type}
The observed type is assumed to be perfect.
\begin{equation}
T_o = T.
\end{equation}

\subsection{Luminosity}
For our model
\begin{equation}
\ln{L} | T, \ln{L}_{T},\sigma_{T} \sim \mathcal{N}\left( \ln{L}_{T},\frac{\ln{10}}{2.5}\sigma_{T}\right).
\end{equation}

The corresponding pdf appears in the likelihood.

\subsection{Redshift}
The redshift is drawn from a flat distribution
\begin{equation}
z\sim \mathcal{U}(0,\infty).
\end{equation}
%
%\subsection{Neighbor Galaxy Redshifts}
%Each neighbor redshift is drawn from a flat distribution.  The redshift for neighbor
%$i$ is  
%\begin{equation}
%z_{N,i} \sim \mathcal{U}(0,\infty).
%\end{equation}

\subsection{Observed Redshift}
In our model the measured redshift is a sum of delta functions
\begin{equation}
p(z_o|z) = \sum_i p_i \delta(z-z_i),
\end{equation}
where galaxy $i$ at
redshift $z_i$ has probability $p_i$ of being
the host.

\subsection{Counts}
The luminosity distance comes from the physics-theory function
\begin{equation}
d_L = d_L(z; \Omega_M, w0),
\end{equation}
the flux is
\begin{equation}
f = \frac{L}{4\pi d_L^2},
\end{equation}
and expected counts is
\begin{equation}
c_\star = 10^{Z/2.5}f.
\end{equation}
The distribution of counts for all transients is 
\begin{equation}
c_o | c_\star, \sigma_c \sim \mathcal{N}(c_\star, \sigma_c),
\end{equation}
where $\sigma_c$ is the measurement noise.

\subsection{Sample Selection Normalization}
Anticipating the use of available statistical packages, the likelihoods have been constructed
from standard distribution functions.  The truncated distributions from sample selection
are accounted by the normalization 
terms $P(S_c, S_T| z=z_o, X)$, $P(S_c| z=z_o, X)$.  Although they do not appear
in the PGM, they are treated as nodes who contribute 
$-\ln{P(S_c, S_T| z=z_o, X)}$ to the log-likelihood, where the negative sign reflects that this is a normalization
factor.

\end{document}

### 2016-02-02 src/Nodes.py

@@ -1,18 +1,132 @@
 #!/usr/bin/env python
-
 import numpy
 from pymc3 import NUTS, Model, Normal, Lognormal, Flat, Bernoulli, Uniform
 from astropy.cosmology import FlatwCDM
 from pymc3.distributions import Continuous
 from pymc3.distributions.dist_math import bound, std_cdf
+from pymc3.backends import SQLite
 
 from astropy import constants as const
 from astropy import units as u
 
 import matplotlib.pyplot as plt
 
+import theano
 import theano.tensor as T
 from theano import pp
+from theano.compile.ops import as_op
+
+cosmo = FlatwCDM(H0=72, Om0=0.28, w0=-1)
+h0 = (const.c/cosmo.H0).to(u.Mpc).value
+
+def hinv(z, Om0, w0):
+    return T.pow((1+z)**3 * (Om0 + (1-Om0)*(1+z)**(3*w0)),-0.5)
+
+def luminosity_distance(z, Om0, w0):
+    return 0.5/h0*(z+z**2)*(1+ hinv(z, Om0, w0))
+
+def normalization_integrand(lnLoversigma, lnL, sigma, Z, threshold, ld):
+    luminosity = T.exp(lnLoversigma*sigma-lnL)
+    flux = (1./4/numpy.pi)*luminosity/ld**2
+    counts = flux*numpy.exp(Counts.ln10/2.5)*T.exp(Z)
+    ccdf  = 1-std_cdf((threshold-counts)/1e-9)
+    return numpy.exp(-lnLoversigma**2/2.)*ccdf
+
+def normalization_integral(lnL, sigma, Z, threshold, ld):
+    # integral with coordinates in lnL/sigma units
+    # coarse trapezoidal integral over L
+    # This ugliness is due to nesting problems in theano
+    #for index in xrange(-3,4):
+    return 0.5*normalization_integrand(-3, lnL, sigma, Z, threshold, ld) +\
+        normalization_integrand(-2, lnL, sigma, Z, threshold, ld) + \
+        normalization_integrand(-1, lnL, sigma, Z, threshold, ld) + \
+        normalization_integrand(0, lnL, sigma, Z, threshold, ld) + \
+        normalization_integrand(1, lnL, sigma, Z, threshold, ld) + \
+        normalization_integrand(2, lnL, sigma, Z, threshold, ld) + \
+        0.5 * normalization_integrand(3, lnL, sigma, Z, threshold, ld)
+
[…]
